### 2015-06-05 AffGR-PRD.tex
Sent to PRD

\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint]{revtex4-1}

\usepackage{amsmath,amsthm,latexsym,amssymb,amsfonts}
\usepackage{xcolor}
\usepackage[%
  colorlinks=true,
  urlcolor=blue,
  linkcolor=blue,
  citecolor=blue
]{hyperref}
\usepackage{etoolbox}
\usepackage{breqn}

\makeatletter
\let\cat@comma@active\@empty
\makeatother

%------------------
%--------- Definitions
%------------------
%% \input{Def-article.tex}
\usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
\usepackage{graphicx}
\usepackage{centernot}
%% \usepackage{hyperref}
\usepackage{xcolor}
\usepackage{comment}
%% \hypersetup{linktocpage,colorlinks=true,urlcolor=blue!80!red,linkcolor=blue,citecolor=red}
%\usepackage{feynmf}
\usepackage{siunitx}
\usepackage{array}
%% \usepackage{ulem}
%\usepackage{tikz}
\usepackage{braket}
\usepackage{xparse}

%-------------------------------Theorems
\newtheorem{Def}{Definition}[section]
\newtheorem{Thm}[Def]{Theorem}
\newtheorem{Lem}[Def]{Lemma}
\newtheorem{Pos}[Def]{Postulate}
\newtheorem{Exa}[Def]{Example}
\newtheorem{Cor}[Def]{Corrolary}
\newtheorem{Pro}[Def]{Proposition}

%---------------------------------New commands
\newcommand{\A}{\mathcal{A}} %% This is equivalent to \Ag (no args)
\newcommand{\abs}[1]{\left|{#1}\right|}
\DeclareMathOperator{\ad}{ad}
\DeclareMathOperator{\Ad}{Ad}
\DeclareDocumentCommand{\Ag}{ s o }{ \IfBooleanTF{#1}
    { \IfValueTF{#2}{ \boldsymbol{\mathcal{A}}_{(#2)} }{ \boldsymbol{\mathcal{A}} } }
    { \IfValueTF{#2}{            {\mathcal{A}}_{(#2)} }{            {\mathcal{A}} } } }
%% \newcommand{\Ag}{\mathcal{A}_{(1)}}
%% \newcommand{\Agf}{\boldsymbol{\mathcal{A}}}
\DeclareDocumentCommand{\Af}{ s o }{ \IfBooleanTF{#1}
    { \IfValueTF{#2}{ \boldsymbol{A}_{(#2)} }{ \boldsymbol{A} } }
    { \IfValueTF{#2}{            {A}_{(#2)} }{            {A} } } }
%% \newcommand{\Af}{ {\mathbf{A}} }
%% \newcommand{\AF}[1]{ {\mathbf{A}}_{({#1})} }
\newcommand{\hAf}{ \hat{\mathbf{A}}_{(1)} }
\newcommand{\hAF}[1]{ \hat{\mathbf{A}}_{(#1)} }
\newcommand{\bboxed}[1]{{\color{red}{\boxed{\boxed{\textcolor{black}{#1}}}}}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Cl}{\mathcal{C}\!\ell}
\newcommand{\cdf}[1][]{{\boldsymbol{\mathcal{D}}}{#1}\!}
\newcommand{\covd}{\mathcal{D}}
\newcommand{\D}{\mathscr{D}}
\newcommand{\df}[1][]{\mathbf{d}{#1}}
\newcommand{\dfd}{{\mathbf{d}}^\dag\!}
\newcommand\ded{\mathrm{d}^\dag}
\DeclareMathOperator{\End}{End}
\newcommand{\ele}[2][]{\frac{d}{dt}\left(\frac{\partial\mathcal{L}}{\partial \dot{#2}^{#1}}\right) - \frac{\partial\mathcal{L}}{\partial {#2}^{#1}}}
\newcommand{\fele}[2][]{\partial_\mu \left(\frac{\delta\mathcal{L}}{\delta\left(\partial_\mu{#2}^{#1}\right)}\right) - \frac{\delta\mathcal{L}}{\delta {#2}^{#1}}}
\newcommand{\vb}[1]{\vec{e}_{#1}}
%% \newcommand{\fb}[1]{\widetilde{e}{}^{ #1}}
\newcommand{\fb}[1]{\widetilde{e}{}^{ #1}}
\newcommand\fder[3][]{\frac{\delta^{#1}{#2}}{\delta {#3}^{#1}}}
\newcommand\fdern[4][]{\frac{\delta^{#1}{#2}}{\delta {#3} \cdots \delta {#4}}}
%% \newcommand{\Fc}{\mathcal{F}}
%% \newcommand{\F}{\boldsymbol{\mathcal{F}}}
%% \newcommand{\Fg}{\boldsymbol{\mathcal{F}}_{(2)}}
\DeclareDocumentCommand{\Fg}{ s o }{ \IfBooleanTF{#1}
    { \IfValueTF{#2}{ \boldsymbol{\mathcal{F}}_{(#2)} }{ \boldsymbol{\mathcal{F}} } }
    { \IfValueTF{#2}{            {\mathcal{F}}_{(#2)} }{            {\mathcal{F}} } } }
%% \newcommand{\Ff}{{\mathbf{F}}}
\DeclareDocumentCommand{\Ff}{ o }{ \IfValueTF{#1}{ F_{(#1)} }{ F } }
\newcommand{\FF}[1]{{\mathbf{F}}_{(#1)}}
\newcommand{\hFF}[1]{{\mathbf{\hat{F}}}_{(#1)}}
\newcommand{\fy}{\centernot}
\newcommand{\G}{\mathscr{G}}
\newcommand{\ga}{\gamma}
\newcommand{\gf}{\boldsymbol{\gamma}}
\newcommand{\Ga}{\Gamma}
\newcommand{\conn}[3]{\left(\Gamma_{#1}\right)^{#2}{}_{#3}}
\newcommand{\connn}[3]{\Gamma_{#1}{}^{#2}{}_{#3}}
\newcommand{\hcon}[3]{\hat{\Gamma}_{#1}{}^{#2}{}_{#3}}
\newcommand{\Ha}{\mathscr{H}}
\newcommand{\He}{\mathbb{H}}
\newcommand{\Hi}{\mathcal{H}}
\newcommand{\Hint}{\underline{\sc Hint:} }
\DeclareMathOperator{\hs}{\star\!\!}
\DeclareMathOperator{\st}{\star}
\newcommand{\J}{\mathscr{J}}
\newcommand{\K}{\mathbb{K}}
\newcommand{\KK}{Kaluza-Klein\ }
\newcommand{\Lag}{\mathscr{L}}
\newcommand{\Li}{\mathcal{L}}
\newcommand{\La}[1][]{\triangle_{#1}}
\newcommand{\Lap}{\nabla^2}
\newcommand{\lr}[1]{\stackrel{\leftrightarrow}{#1}}
\newcommand{\M}{\ensuremath{\mathscr{M}}}
\DeclareMathOperator{\Mat}{Mat}
\newcommand{\Mi}{\mathcal{M}}
\newcommand{\MN}{Maldacena-N\'u\~nez\ }
\newcommand{\N}{\ensuremath{\mathscr{N}}}
\newcommand{\Na}{\mathbb{N}}
\newcommand{\No}{\mathcal{N}}
\newcommand{\norm}[1]{\left\|#1\right\|}
\newcommand{\Op}{\mathcal{O}}
\newcommand{\Or}{\mathscr{O}}
\newcommand\pder[3][]{\frac{\partial^{#1}{#2}}{\partial {#3}^{#1}}}
\newcommand\pdern[4][]{\frac{\partial^{#1}#2}{\partial #3\cdots\partial #4}}
\DeclareMathOperator{\Pfaff}{Pfaff}
\newcommand{\Qh}[1][]{\ensuremath{\hat{Q}_{#1}}}
\newcommand{\R}{\mathbb{R}}
\newcommand{\Ri}{\mathcal{R}}
%% \newcommand{\S}{\mathscr{S}}
\newcommand{\SM}{Standard Model {}}%\mathscr{S}}
\DeclareDocumentCommand\Te{o o m }{\mathcal{T}{}^{#1}_{#2}(#3)}
\newcommand{\T}{\mathscr{T}}
\newcommand{\tor}{\mathcal{T}}
\newcommand{\tors}[3]{\mathcal{T}{}_{#1}{}^{#2}{}_{#3}}
\newcommand{\torss}[3]{T_{#1}{}^{#2}{}_{#3}}
\newcommand\vdj[1]{\left< \Delta J \right>_{#1}}
\newcommand{\w}{{\scriptstyle\wedge}\!}
\newcommand{\we}{{\scriptstyle\wedge}}
\newcommand{\Z}{\mathbb{Z}}

\newcommand{\dbar}[1]{\ensuremath{\mathchar'26\mkern-12mu \mathrm{d}^{#1}}\!}

%--------------------------- New Greek
\newcommand{\tht}{\ensuremath{\theta}}
\newcommand{\bet}{\ensuremath{\bar{\eta}}}
\newcommand{\bps}{\ensuremath{\bar{\psi}}}
\newcommand{\bc}{\ensuremath{\bar{\chi}}}
\newcommand{\Bps}{\ensuremath{\bar{\Psi}}}
\newcommand{\Bx}{\ensuremath{\bar{\Xi}}}
\newcommand{\bph}{\ensuremath{\bar{\phi}}}
\newcommand{\vph}{\ensuremath{\varphi}}
\newcommand{\bvph}{\ensuremath{\bar{\varphi}}}
\newcommand{\bth}{\ensuremath{\bar{\theta}}}
\newcommand{\hph}{\ensuremath{\hat{\phi}}}

\newcommand{\bs}[1]{\boldsymbol{#1}}

\renewcommand{\div}{{\mathbf{div}}}
\newcommand{\grad}{{\mathbf{grad}}}
\newcommand{\curl}{{\mathbf{curl}}}

\newcommand\VI[2]{\hat{e}^{\hat{#1}}_{\hat{#2}}}
\newcommand\VIF[1]{\hat{\boldsymbol{e}}^{\hat{#1}}}
\newcommand\VIN[2]{\hat{E}^{\hat{#1}}_{\hat{#2}}}
\newcommand\VINF[1]{\hat{\boldsymbol{E}}_{\hat{#1}}}
\newcommand\hvi[2]{\hat{e}^{{#1}}_{{#2}}}
\newcommand\hvin[2]{\hat{E}^{{#1}}_{{#2}}}
\newcommand\hvif[1]{\hat{\boldsymbol{e}}^{{#1}}}
\newcommand\hvinf[1]{\hat{\boldsymbol{E}}_{{#1}}}
\newcommand\vi[2]{e^{{#1}}_{{#2}}}
\newcommand\vin[2]{E^{{#1}}_{{#2}}}
\newcommand\vif[1]{\boldsymbol{e}^{{#1}}}
\newcommand\vinf[1]{\boldsymbol{E}_{{#1}}}
%% \newcommand\Vi[2]{e^{\hat{#1}}_{\hat{#2}}}
%% \newcommand\Vin[2]{E^{\hat{#1}}_{\hat{#2}}}
\newcommand\GAM[1]{{\gamma}^{\hat{#1}}}
%% \newcommand\Gam[1]{\gamma^{\hat{#1}}} 
\newcommand\gam[1]{\gamma^{{#1}}}
\newcommand\hgam[1]{\hat{\gamma}^{{#1}}}
\newcommand\NAB[1]{\hat{\nabla}_{\hat{#1}}}
\newcommand\Nab[1]{\nabla_{\hat{#1}}}
\newcommand\nab[1]{\nabla_{{#1}}}
\newcommand\PA[1]{\partial_{\hat{#1}}}
\newcommand\pa[1]{\partial_{{#1}}}
\newcommand\PAU[1]{\partial^{\hat{#1}}}
\newcommand\pau[1]{\partial^{{#1}}}
\newcommand\lf[1]{{\omega}^{{#1}}}
\newcommand\lft[1]{\hat{\omega}^{{#1}}}
\newcommand\SPI[1]{\hat{\omega}_{\hat{#1}}}
\newcommand\SPIF[2]{\hat{\boldsymbol{\omega}}^{\hat{#1}}{}_{\hat{#2}}}
%% \newcommand\Spi[1]{\omega_{\hat{#1}}}
\newcommand\spi[1]{\omega_{{#1}}}
\newcommand\tspi[1]{\tilde{\omega}_{{#1}}}
\newcommand\spif[2]{{\boldsymbol{\omega}}^{{#1}}{}_{{#2}}}
\newcommand\tspif[2]{{\tilde{\boldsymbol{\omega}}}^{{#1}}{}_{{#2}}}
\newcommand\hspi[1]{\hat{\omega}_{{#1}}}
\newcommand\hspif[2]{\hat{\boldsymbol{\omega}}^{{#1}}{}_{{#2}}}
%%%%%%%%% Beware of the inconsistency between
%%%%%%%%% \Rif and \RIF
\newcommand{\RIF}[2]{\hat{\boldsymbol{\mathcal{R}}}^{\hat{#1}}{}_{\hat{#2}}}
\newcommand{\hRif}[2]{\hat{\boldsymbol{\mathcal{R}}}^{{#1}}{}_{{#2}}}
\newcommand{\Rif}[2]{\boldsymbol{\mathcal{R}}^{{#1}}{}_{{#2}}}
\newcommand{\tRif}[2]{\tilde{\boldsymbol{\mathcal{R}}}^{{#1}}{}_{{#2}}}
\newcommand{\Tf}[1]{\boldsymbol{\mathcal{T}}^{#1}}
\newcommand{\hTf}[1]{\hat{\boldsymbol{\mathcal{T}}}^{#1}}
\newcommand{\TF}[1]{\hat{\boldsymbol{\mathcal{T}}}^{\hat{#1}}}
\newcommand{\Tor}[2]{\mathcal{T}^{#1}{}_{#2}}
\newcommand{\cont}[3]{\mathcal{K}_{#1}{}^{#2}{}_{#3}}
\newcommand{\contf}[2]{\boldsymbol{\mathcal{K}}^{#1}{}_{#2}}
\newcommand{\hcont}[3]{\hat{\mathcal{K}}_{#1}{}^{#2}{}_{#3}}
\newcommand{\hcontf}[2]{\hat{\boldsymbol{\mathcal{K}}}^{#1}{}_{#2}}
\newcommand{\CONT}[3]{\hat{\mathcal{K}}_{\hat{#1}}{}^{\hat{#2}}{}_{\hat{#3}}}
\newcommand{\CONTF}[2]{\hat{\boldsymbol{\mathcal{K}}}^{\hat{#1}}{}_{\hat{#2}}}

%% \newcommand{\ket}[1]{\left.\left|#1\right.\right>}
%% \newcommand{\bra}[1]{\left.\left<#1\right.\right|}
\renewcommand\bra[1]{\Bra{#1}}
\renewcommand\ket[1]{\Ket{#1}}
\newcommand{\bkt}[3]{\Braket{ {#1} | {#2} | {#3} } }
\newcommand{\bk}[2]{\Braket{ {#1} | {#2} } }
\newcommand{\comm}[2]{\left[#1,#2\right]}
\newcommand{\acomm}[2]{\left\{#1,#2\right\}}
\newcommand{\vev}[1]{\ensuremath{\left<#1\right>}}
\renewcommand{\set}[1]{\ensuremath{\Set{ #1 }}}

\newcommand{\relphantom}[1]{\mathrel{\phantom{#1}}}

\newcommand{\Ric}{\operatorname{Ric}}
\newcommand*{\diag}{\operatorname{diag}}
\newcommand{\id}{\operatorname{id}}
\newcommand{\tr}{\operatorname{tr}}
\newcommand{\Tr}{\operatorname{Tr}}
\newcommand{\Ker}{\operatorname{Ker}}
\renewcommand{\Im}{\operatorname{Im}}
\newcommand{\sgn}{\operatorname{sgn}}
\newcommand{\Ln}{\operatorname{Ln}}
\newcommand{\Ei}{\operatorname{Ei}}
\newcommand{\csch}{\operatorname{csch}}
\newcommand{\arcsinh}{\operatorname{arcsinh}}
\DeclareMathOperator\Br{Br}

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\ber}{\begin{eqnarray}}
\newcommand{\eer}{\end{eqnarray}}

\renewcommand{\(}{\left(}
\renewcommand{\)}{\right)}
\renewcommand{\[}{\left[}
\renewcommand{\]}{\right]}

\newcommand{\uf}[2][]{\ensuremath{u_{#1}\(\vec{#2}\)}}
\newcommand{\ufb}[2][]{\ensuremath{\bar{u}_{#1}\(\vec{#2}\)}}
\newcommand{\vf}[2][]{\ensuremath{v_{#1}\(\vec{#2}\)}}
\newcommand{\vfb}[2][]{\ensuremath{\bar{v}_{#1}\(\vec{#2}\)}}
\newcommand\pol[2][]{\ensuremath{\varepsilon_{#1}(\vec{#2})}}
\newcommand\polc[2][]{\ensuremath{\varepsilon^*_{#1}(\vec{#2})}}
\newcommand{\ann}[3]{\ensuremath{#1\(\vec{#2},#3\)}}
\newcommand{\cre}[3]{\ensuremath{#1^\dag\(\vec{#2},#3\)}}
%% \newcommand{\uf}[2]{\ensuremath{u\(\vec{#1},#2\)}}
%% \newcommand{\ufb}[2]{\ensuremath{\bar{u}\(\vec{#1},#2\)}}
%% \newcommand{\vf}[2]{\ensuremath{v\(\vec{#1},#2\)}}
%% \newcommand{\vfb}[2]{\ensuremath{\bar{v}\(\vec{#1},#2\)}}
%% \newcommand{\ann}[3]{\ensuremath{#1\(\vec{#2},#3\)}}
%% \newcommand{\cre}[3]{\ensuremath{#1^\dag\(\vec{#2},#3\)}}

\newcommand{\dif}{{\mathrm{d}}}
\newcommand{\difn}[1]{{\mathrm{d}}^{#1}}
\newcommand{\dn}[2]{{\mathrm{d}}^{#1}\!{#2}\;}
\newcommand{\dbarn}[2]{\dbar{#1}{#2}\;}
\newcommand*{\de}[1]{\mathop{\mathrm{d}#1}\nolimits}% differential, facultative argoment between square parentheses
\newcommand*{\desec}[1][]{\mathop{\mathrm{d^2}#1}\nolimits}% second differential, facultative argoment between square parentheses
\newcommand{\der}[2]{\frac{\de{#1}}{\de{#2}}}% first derivative 
%\newcommand{\pder}[2]{\frac{\pa{}#1}{\pa{}{#2}}}% first derivative 
\newcommand{\inlineder}[2]{\mathrm{d}{#1}/\mathrm{d}{#2}}% in-line first derivative
\newcommand{\dersec}[2]{\frac{{\desec[#1]}}{\de[{#2}^2]}}% second derivative
%% \newcommand{\dx}{\de[x]}% frequently used differentials
%% \newcommand{\dy}{\de[y]}
%\newcommand{\df}{\de[f]}

%------------------
%--------- Format
%------------------
\newcommand{\out}[1]{{\color{red} {#1}}}
\newcommand{\pro}[1]{{\color{blue!70!black} {#1}}}
\newcommand{\hl}[1]{{\color{red} \bfseries{#1}}}

\newcommand\UTFSM{Departamento de F\'\i sica, Universidad T\'{e}cnica Federico Santa Mar\'\i a, \\ Casilla 110-V, Valpara\'\i so, Chile}
\newcommand\CCTVal{Centro Cient\'\i fico Tecnol\'ogico de Valpara\'\i so, \\ Casilla 110-V, Valpara\'\i so, Chile}
\newcommand\CFF{Centro de F\'\i sica Fundamental,  Universidad de los Andes,\\ 5101 M\'erida, Venezuela}

\hypersetup{%
  pdftitle={Einstein's Gravity from an Affine Model},
  pdfauthor={Oscar Castillo-Felisola,}{Aureliano Skirzewski},
  pdfkeywords={Affine Gravity,} {Torsion,} {Generalised Gravity.},
  pdflang={English}
}

%------------------
%--------- Document
%------------------
\begin{document}

\title{Einstein's gravity from an affine model}

\author{Oscar \surname{Castillo-Felisola}}
\email{o.castillo.felisola@gmail.com}
\affiliation{\CCTVal.}
\affiliation{\UTFSM.}

\author{Aureliano \surname{Skirzewski}}
\email{askirz@gmail.com}
\affiliation{\CFF.}

%% --------- Abstract
\begin{abstract}
  We show that the effective field equations for a recently formulated affine model of gravity, in the sector of a metric-compatible (torsion-free) connection, accept general Einstein manifolds ---with or without cosmological constant--- as solutions. Moreover, these effective field equations coincide with those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory. Additionally, we find an equivalence between a minimally coupled massless scalar field in General Relativity with a ``minimally'' coupled scalar field in this affine model.
\end{abstract}

\pacs{02.40.Ma,04.50.Kd,04.90.+e}
\keywords{Affine Gravity, Torsion, Generalised Gravity.}

\maketitle

%%%%%%%%% THE MODEL %%%%%%%%%
In a previous paper~\cite{Skirzewski:2014eta}, we presented a purely affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms. We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravity. We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}. Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}. However, in the considered framework all graviton self-interaction is mediated by the torsion, which might allow to bypass the general postulates supporting the theorem.

The four-dimensional action is written in terms of the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
\begin{equation}
  \hat{\Gamma}^\mu{}_{\rho\sigma} = {\Gamma}^\mu{}_{\rho\sigma} + T^\mu{}_{\rho\sigma} = {\Gamma}^\mu{}_{\rho\sigma} + \epsilon_{\rho\sigma\lambda\kappa}T^{\mu,\lambda\kappa}+A_{[\rho}\delta^\mu_{\nu]},
\end{equation}
where ${\Gamma}^\mu{}_{\rho\sigma}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying $T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$ and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$. Since no metric is present  the epsilon symbols are not related but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}
\begin{widetext}
Using the above decomposition, the most general (power-counting renormalizable) action preserving diffeomorphisms is~\footnote{We have dropped all terms which can be related to those in Eq.~\eqref{4dfull} through a boundary term.}
  \begin{dmath}
    \label{4dfull}
    S[{\Gamma},T,A] =
    \int\dn{4}{x}\Bigg[
      B_1\, R_{\mu\nu}{}^{\mu}{}_{\rho} T^{\nu,\alpha\beta}T^{\rho,\gamma\delta}\epsilon_{\alpha\beta\gamma\delta}
      +B_2\, R_{\mu\nu}{}^{\sigma}{}_\rho T^{\beta,\mu\nu}T^{\rho,\gamma\delta}\epsilon_{\sigma\beta\gamma\delta}
      +B_3\, R_{\mu\nu}{}^{\mu}{}_{\rho} T^{\nu,\rho\sigma}A_\sigma
      +B_4\, R_{\mu\nu}{}^{\sigma}{}_\rho T^{\rho,\mu\nu}A_\sigma
      +B_5\, R_{\mu\nu}{}^{\rho}{}_\rho T^{\sigma,\mu\nu}A_\sigma
      +C_1\, R_{\mu\rho}{}^{\mu}{}_\nu \nabla_\sigma T^{\nu,\rho\sigma}
      +C_2\, R_{\mu\nu}{}^{\rho}{}_\rho \nabla_\sigma T^{\sigma,\mu\nu} 
      +D_1\, T^{\alpha,\mu\nu}T^{\beta,\rho\sigma}\nabla_\gamma T^{(\lambda, \kappa) \gamma}\epsilon_{\beta\mu\nu\lambda}\epsilon_{\alpha\rho\sigma\kappa}
      +D_2\,T^{\alpha,\mu\nu}T^{\lambda,\beta\gamma}\nabla_\lambda T^{\delta,\rho\sigma}\epsilon_{\alpha\beta\gamma\delta}\epsilon_{\mu\nu\rho\sigma}
      +D_3\,T^{\mu,\alpha\beta}T^{\lambda,\nu\gamma}\nabla_\lambda T^{\delta,\rho\sigma}\epsilon_{\alpha\beta\gamma\delta}\epsilon_{\mu\nu\rho\sigma}
      +D_4\,T^{\lambda,\mu\nu}T^{\kappa,\rho\sigma}\nabla_{(\lambda} A_{\kappa)} \epsilon_{\mu\nu\rho\sigma}
      +D_5\,T^{\lambda,\mu\nu}\nabla_{[\lambda}T^{\kappa,\rho\sigma} A_{\kappa]} \epsilon_{\mu\nu\rho\sigma}
      +D_6\,T^{\lambda,\mu\nu}A_\nu\nabla_{(\lambda} A_{\mu)}
      +D_7\,T^{\lambda,\mu\nu}A_\lambda\nabla_{[\mu} A_{\nu]} 
      +E_1\,\nabla_{(\rho} T^{\rho,\mu\nu}\nabla_{\sigma)} T^{\sigma,\lambda\kappa}\epsilon_{\mu\nu\lambda\kappa}
      +E_2\,\nabla_{(\lambda} T^{\lambda,\mu\nu}\nabla_{\mu)} A_\nu
      +T^{\alpha,\beta\gamma}T^{\delta,\eta\kappa}T^{\lambda,\mu\nu}T^{\rho,\sigma\tau}
      \Big(F_1\,\epsilon_{\beta\gamma\eta\kappa}\epsilon_{\alpha\rho\mu\nu}\epsilon_{\delta\lambda\sigma\tau}
      +F_2\,\epsilon_{\beta\lambda\eta\kappa}\epsilon_{\gamma\rho\mu\nu}\epsilon_{\alpha\delta\sigma\tau}\Big) 
      +F_3\, T^{\rho,\alpha\beta}T^{\gamma,\mu\nu}T^{\lambda,\sigma\tau}A_\tau \epsilon_{\alpha\beta\gamma\lambda}\epsilon_{\mu\nu\rho\sigma}
      +F_4\,T^{\eta,\alpha\beta}T^{\kappa,\gamma\delta}A_\eta A_\kappa\epsilon_{\alpha\beta\gamma\delta}\Bigg].
  \end{dmath}
\end{widetext}
Although there is no obvious equivalence between the action in Eq.~\eqref{4dfull} and General Relativity, particularly due to the lack of a source metric field, we analyzed in Ref.~\cite{Skirzewski:2014eta} the scalar perturbations around a static homogeneous and isotropic background. In the non-relativistic (low-momentum) limit, the geodesic deviation of inertial observers is also discussed.

Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action. Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we used ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions. However, for the simple case of the Einstein--Hilbert action, it is in fact the inverse metric density.}, defined as the variation of the action with respect to the symmetric part of the Ricci tensor~(see Refs.~\cite{Eddington1923math,schrodinger1950space,Poplawski:2012bw}), i.e.,%% \hl{JZ: def. $R_{(\mu\nu)}$}
\begin{equation}
  \label{metric}
  \frac{\delta\ }{\delta R_{(\mu\nu)}} S[\Gamma] \equiv \sqrt{\mathsf{g}} \, \mathsf{g}^{\mu\nu} = \bar{g}^{\mu\nu} ,
\end{equation}
by assuming a matter action that depends on $\bar{g}^{\mu\nu}$.

From the geodesic equations and the linearized action on scalar perturbation, we found that the effective geodesic deviation
\begin{equation}
  \label{NewtonPot}
  \Gamma^i{}_{00} = - \frac{1}{8\pi} \frac{ \partial\mathcal{L}_{\text{Matter}} }{ \partial \bar{g}^{00} } \, \nabla^i \left(\frac{1}{|\vec{x}|}\right),
\end{equation}
is the usual Newtonian force induced by a massive source.

%%%%%%%%% COMPARISON GR %%%%%%%%%
Although we obtained the Newtonian gravitational potential~\eqref{NewtonPot}, the post-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source. Therefore, we should go beyond the Newtonian limit in order to compare our model with GR.

%%\hl{A comparison between our affine model and GR requires the imposition of vanishing torsion (JZ: Why?).}
Even though a comparison between our affine model and GR does not require the imposition of vanishing torsion, at this stage we shall focus on a sector of the theory in which the connection is metric and torsion-free. Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements, and the only nontrivial field equation is the one for the Curtright, $T^{\nu,\mu\rho}$,
\begin{equation*}
  \nab{[\rho} R_{\mu]\lambda}{}^{\lambda}{}_{\nu} + \kappa \nab{\nu} R_{\mu\rho}{}^\lambda{}_\lambda = 0,
\end{equation*}
with $\kappa$ a constant related with the couplings of the model. In the considered sector the connection is compatible with a metric, therefore, the second term vanishes and the gravitational equations are
\begin{equation}
  \nab{[\rho} R_{\mu]\nu} = 0.
  \label{SimpleEOM}
\end{equation}

The above equation is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature ---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.} The parallel Ricci curvature is a generalization of the Einstein condition which assures that although the manifold is not generally Einstein, the metric has to be locally a product of Einstein metrics~\cite{Besse}.

A corollary is that all Einstein manifolds, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model. Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from GR are present in the chosen scenario of our model.

Additionally, for a Riemannian manifold $(\Mi,g)$ the condition in Eq.~\eqref{SimpleEOM} is equivalent to the following statements (see Ref.~\cite{Derdzinski:1985,Besse}): (i) the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}, (ii) the manifold has harmonic curvature~\cite{bourguignon1981varietes}, i.e. \mbox{$\nabla^\mu R_{\mu\nu}{}^\lambda{}_\rho = 0$,} and (iii) in the four-dimensional case the manifold has harmonic Weyl tensor~\cite{Berger:1969} and constant scalar curvature.

Interestingly, the Eq.~\eqref{SimpleEOM} can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974},
\begin{equation}
  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \we \st \Rif{}{} \right),
\end{equation}
where $\Rif{}{} \in \Omega^2(\Mi, T^*\Mi \otimes T\Mi)$ is the curvature two-form, the operator $\st$ denotes the Hodge star, and the trace is taken on the bundle indices (see Ref.~\cite{bourguignon1982yang}). Albeit this effective theory has been widely studied, it has been considered as a model for a metric field instead of a theory for the connection. Therefore, within the formalism of Palatini, besides Eq.~\eqref{SimpleEOM} an extra field equation appears (for the vielbein field), which strongly constraints the solutions of the gravitational Yang--Mills~\footnote{We thank J.~Zanelli for sharing his personal communications with C.~N.~Yang, and clarify this aspect of the effective model.}. Intriguingly, this effective theory is not renormalizable ---according to the arguments in Refs.~\cite{McGady:2013sga,Camanho:2014apa}---, although it has been discussed in Ref.~\cite{Chen:2010at} that at least the ghost problem can be avoided through the arguments exposed in Refs.~\cite{Kleinert:1987eb,Bender:2007wu,Bender:2008vh,Mannheim:2009zj}.

%%%%%%%%% MATTER %%%%%%%%%
Until now, the most general diffeomorphism-invariant and power-counting renormalizable (gravitational) theory for an affine connection has been built, and we have showed that in a certain sector it is equivalent to General Relativity. In what follows, we show an attempt of including scalar matter into the model. The theory does not require a spacetime metric, but instead we should consider the most general $\binom{2}{0}$-tensor density, $\mathfrak{g}^{\mu\nu}$,  built with the available fields, and use it to build Lagrangian densities for the matter content. Following our precept, the matter content ---scalar matter--- should couple to $\mathfrak{g}^{\mu\nu}$, given by %% which for Eq.~\eqref{4dfull} is
\begin{dmath}
  \mathfrak{g}^{\mu\nu} = \alpha \, \nabla_\lambda T^{\mu,\nu\lambda} + \beta \, A_\lambda T^{\mu,\nu\lambda} + \gamma \, \epsilon_{\lambda\kappa\rho\sigma} T^{\mu, \lambda\kappa} T^{\nu, \rho\sigma},
\end{dmath}
with $\alpha$, $\beta$ and $\gamma$ arbitrary coefficients.

We consider the action provided by the ``kinetic term''
\begin{dmath}
  \label{ScalarAction}
  S_\phi = -  \int \dn{4}{x} \Big( \alpha \, \nabla_\lambda T^{\mu,\nu\lambda}  + \beta \, A_\lambda T^{\mu,\nu\lambda} + \gamma \, \epsilon_{\lambda\kappa\rho\sigma} T^{\mu, \lambda\kappa} T^{\nu, \rho\sigma} \Big) \partial_\mu\phi\partial_\nu\phi,
\end{dmath}
which makes a nontrivial contribution to the field equations once we restrict to the sector of interest, where the torsion is set to zero and the connection is compatible with a metric.

The equation for the Curtright field when the scalar field is turned on is (without lost of generality we fixed the coefficient $C_1 = 1$)
\begin{equation*}
  \nabla_{[\sigma} R_{\rho]\mu}{}^{\mu}{}_\nu - {C_2} \nabla_\nu  R_{\rho\sigma}{}^{\mu}{}_\mu - \alpha \nabla_{[\sigma} \Big( \partial_{\rho]}\phi \partial_\nu\phi \Big) = 0,
\end{equation*}
which under our considerations simplifies to 
\begin{equation}
  \nabla_{[\sigma} R_{\rho]\nu} - \alpha \nabla_{[\sigma} \Big( \partial_{\rho]}\phi \partial_\nu\phi \Big) = 0.
  \label{SimpleEOMwS}
\end{equation}
%% when the connection is the Levi-Civita one.
In that case, we find a particular solution of Eq.~\eqref{SimpleEOMwS},%% \hl{JZ: What if non-LC connection?}
\begin{equation*}
  R_{\mu\nu} - \alpha \pa{\mu} \phi \pa{\nu} \phi = \Lambda g_{\mu\nu},
\end{equation*}
that can be written in the more conventional form~\footnote{Notice that $\alpha$ is the gravitational coupling constant, which in Einstein--Hilbert gravity is $G_N$.}
\begin{equation}
  R_{\mu\nu} - \frac{1}{2} g_{\mu\nu} R + \Lambda g_{\mu\nu} = \alpha \Big( \pa{\mu} \phi \pa{\nu} \phi - \frac{1}{2} g_{\mu\nu} \big( \partial\phi \big)^2 \Big).
\end{equation}
Additionally, the second Bianchi identity imposes
\begin{equation}
  \nabla^\mu \pa{\mu} \phi = 0.
\end{equation}
%% \hl{JZ: Esto muestra que la teoria contiene a R.G. com ocaso particular, pero tiene probablemente mucho mas. Que es lo extra?}
This condition is, in the sense argued in Ref.~\cite{Bekenstein:2014uwa}, the equation of motion for the scalar field. Notice that, the Euler--Lagrange equation of motion for the scalar field yields no information after taking the vanishing torsion \emph{truncation}.

It is well-known that this system of equations can be obtained effectively from the Einstein--Hilbert action coupled minimally to a massless scalar field
\begin{equation}
  S_{\text{eff}} = \frac{1}{\alpha} \int \dn{4}{x} \sqrt{g} \left( R + 2 \Lambda - \frac{\alpha}{2} g^{\mu\nu} \pa{\mu}\phi \pa{\nu} \phi \right).
\end{equation}

Summarizing, we have shown that the  \emph{purely affine gravity} constructed in Ref.~\cite{Skirzewski:2014eta} possesses a well-defined torsionless limit, which generalizes the equations of motion  from General Relativity, and its field equations are equivalent to those obtained from a Yang--Mills theory for the spacetime connection, or Stephenson--Kilmister--Yang theory. Consequently, all gravitational effects described by standard General Relativity are contained in our model, even though the torsion field is kept to zero. Regarding this aspect, we would like to emphazise that there is enough liberty to start considering new cosmological effects coming from both nonvanishing torsion and non-metric connections with vanishing torsion, beside the results reported in Ref.~\cite{Chen:2013kia,Chen:2013ota}.
Moreover, our gravitational model coupled to a scalar field through the \emph{tensor density} $\mathfrak{g}^{\mu\nu}$ ---in the vanishing torsion consideration---, generalizes GR minimally coupled to a massless scalar field. In a forthcoming paper, we will consider more general matter content (unrelated to the work in Ref.~\cite{Cook:2008mx}), and some properties of the field equations which differ from those of General Relativity.

%%%%%%%%% ACKNOWLEGMENTS %%%%%%%%%
\begin{acknowledgments}
  We thank to N.~Pantoja, A.~Melfo and R.~L.~Bryant for their helpful discussions and inspiring comments, to J. Zanelli for his suggestions on the physical insight into the problem and careful but critical review of the manuscript.
  This work was partially supported by CONICYT (Chile) under project No. 79140040.
\end{acknowledgments}

%%%%%%%%% BIBLIOGRAPHY %%%%%%%%%
\bibliographystyle{apsrev4-1}
\bibliography{References.bib}

\end{document}

### 2015-07-02 AffGR-PRD.tex
First try of an introduction

@@
 
+\section{\label{intro}Introduction}
+
+Classically, General Relativity is the most successful theory of gravitational interactions.
+However, it is believed to be the effective theory of a, yet to be discover, more fundamental one.
+Among the problems of General Relativity we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}.
+Second, the Wheeler--DeWitt equations are not well-defined in general due to their non-polynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables.
+One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
+On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added ---in particular fermionic matter---.
+
+Therefore, under the premises of non-completeness and non-polynomial structure of the theory, 
 %%%%%%%%% THE MODEL %%%%%%%%%
-In a previous paper~\cite{Skirzewski:2014eta}, we presented a purely affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms.
+in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms.
 We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravity.
@@
 However, in the considered framework all graviton self-interaction is mediated by the torsion, which might allow to bypass the general postulates supporting the theorem.
+
+\section{\label{model}Polynomial affine gravity}
 

### 2015-07-02 AffGR-PRD.tex
Still working on the intro

@@
 Among the problems of General Relativity we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}.
-Second, the Wheeler--DeWitt equations are not well-defined in general due to their non-polynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables.
+Second, the Wheeler--DeWitt equations are not well-defined in general due to their non-polynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
 One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
-On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added ---in particular fermionic matter---.
+On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter.
+
+Standing of the argument of the necessity of a quantum theory of gravity, several generalizations of Einstein's General Relativity have been proposed.
+One important class of these generalizations consider the connection field to be independent of the metric, known as Palatini type theories.
+Within this class of theories one finds the generalization due to Cartan, which consider a connection with nonvanishing torsion~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
+Interestingly, gravitational theories with generic connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
+Albeit these gravitational theories with an arbitrary connection posses ghosts, it has been argued that ...
 
@@
 
+\section{\label{conclusions}Conclusions}
+
 Summarizing, we have shown that the  \emph{purely affine gravity} constructed in Ref.~\cite{Skirzewski:2014eta} possesses a well-defined torsionless limit, which generalizes the equations of motion  from General Relativity, and its field equations are equivalent to those obtained from a Yang--Mills theory for the spacetime connection, or Stephenson--Kilmister--Yang theory.

### 2015-07-20 AffGR-PRD.tex
References added

@@
 Interestingly, gravitational theories with generic connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
-Albeit these gravitational theories with an arbitrary connection posses ghosts, it has been argued that ...
+Albeit these gravitational theories with an arbitrary connection posses ghosts, it has been argued in Refs.~\cite{Ilhan:2013xe,} ---through the simple example of a Pais-Uhlenbenbeck oscillator--- that ...
 
-Therefore, under the premises of non-completeness and non-polynomial structure of the theory, 
+Therefore, under the premises of non-completeness and non-polynomial structure of the theory, 4
 %%%%%%%%% THE MODEL %%%%%%%%%

### 2015-07-21 AffGR-PRD.tex
Extended intro

--- 2015-07-02 AffGR-PRD.tex
@@
 Interestingly, gravitational theories with generic connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
-Albeit these gravitational theories with an arbitrary connection posses ghosts, it has been argued that ...
+Albeit these gravitational theories with an arbitrary connection posses ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe} or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
 
@@
 %%%%%%%%% THE MODEL %%%%%%%%%
-in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms.
-We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravity.
+in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms (which by no means guaranty the renormalizability of the system).
+We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravitational potential, despite the existence of torsion.
 We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}.
-Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}.
+
+Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton self-interaction is mediated by the torsion.
+This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it is proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
+%%Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}.
 However, in the considered framework all graviton self-interaction is mediated by the torsion, which might allow to bypass the general postulates supporting the theorem.
+
+The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations in vacuum.
+In addition, we show that ---in the same sector--- under the assumption of the existence of a unique non-degenerated, covariantly constant $\binom{0}{2}$-tensor, $g$ (which could be thought as a metric), the system of a scalar field coupled with the polynomial affine gravity accepts the minimally coupled Einstein--Klein--Gordon as a solution.
+
+The paper is organized as follows.
+In Sec.~\ref{model}, we present briefly the polynomial affine gravity model, and summarize the results obtained in Ref.~\cite{Skirzewski:2014eta} concerning the Newtonian limit of the model.
+In Sec.~\ref{rlimit}, we restrict ourselves to the sector of the theory with vanishing torsion, and find the field equations; which surprisingly are a known generalization of the Einstein's field equation.
+Then, in Sec.~\ref{matter} we show that under certain considerations the coupling of the gravitational model with a scalar field represents a generalization of the minimally coupled system Einstein--Klein--Gordon.
+Finally, in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results.
 
@@
 
+\section{\label{rlimit}Relativistic limit}
 %%%%%%%%% COMPARISON GR %%%%%%%%%
@@
 %%%%%%%%% MATTER %%%%%%%%%
+\section{\label{matter}Polynomial affine gravity coupled with a scalar field}
+
 Until now, the most general diffeomorphism-invariant and power-counting renormalizable (gravitational) theory for an affine connection has been built, and we have showed that in a certain sector it is equivalent to General Relativity.

### 2015-07-22 AffGR-PRD.tex
Extending the non-relativ limit

@@
 \newcommand{\difn}[1]{{\mathrm{d}}^{#1}}
-\newcommand{\dn}[2]{{\mathrm{d}}^{#1}\!{#2}\;}
+\newcommand{\dn}[2]{{\mathrm{d}}^{#1}{#2}\;}
 \newcommand{\dbarn}[2]{\dbar{#1}{#2}\;}
@@
 
-The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations in vacuum.
+The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations.% in vacuum.
 In addition, we show that ---in the same sector--- under the assumption of the existence of a unique non-degenerated, covariantly constant $\binom{0}{2}$-tensor, $g$ (which could be thought as a metric), the system of a scalar field coupled with the polynomial affine gravity accepts the minimally coupled Einstein--Klein--Gordon as a solution.
@@
 
-The four-dimensional action is written in terms of the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
+First of all, we highlight that the model constructed below has as fundamental field an affine connection, and no metric fields is needed for neither contract nor lowering or raising indices.
+Moreover, in order to guarantee the correct transformation of the Lagrangian density, the geometrical objects used to write down the action will be the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
 \begin{equation}
@@
 where ${\Gamma}^\mu{}_{\rho\sigma}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying $T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$ and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$.
-Since no metric is present  the epsilon symbols are not related but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}
+Since no metric is present  the epsilon symbols are not related by raising (lowering) their indices, but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}
 \begin{widetext}
@@
 \end{widetext}
-Although there is no obvious equivalence between the action in Eq.~\eqref{4dfull} and General Relativity, particularly due to the lack of a source metric field, we analyzed in Ref.~\cite{Skirzewski:2014eta} the scalar perturbations around a static homogeneous and isotropic background.
-In the non-relativistic (low-momentum) limit, the geodesic deviation of inertial observers is also discussed.
+Although there is no obvious equivalence between the action in Eq.~\eqref{4dfull} and General Relativity, particularly due to the lack of a source metric field, we analyzed in Ref.~\cite{Skirzewski:2014eta} the scalar perturbations and studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
+In the rest of this section we summarize the procedure which leads to the Newtonian limit of the model.
 
-Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
+First, we considered a static, homogeneous, and isotropic expansion of fields,
+\begin{align}
+  A_\mu &= \delta_\mu^0 A + a_\mu,\\
+  T^{\mu,\nu\rho} &= \delta^{\mu}_m\delta^{\nu\rho}_{m0}T + t^{\mu,\nu\rho},\\
+  %\shortintertext{and}
+  \Gamma^\lambda{}_{\mu\nu} &= E \delta^\lambda_0 \delta^m_\mu \delta^m_\nu + F \delta^\lambda_m \delta^m_{(\mu}\delta^0_{\nu)} + G\delta^\lambda_0 \delta^0_{\mu}\delta^0_{\nu} + \gamma^\lambda{}_{\mu\nu},
+  \label{GammaExp}
+\end{align}
+with $\delta^{\mu\nu}_{\lambda\kappa}=\delta^{\mu}_{\lambda}\delta^{\nu}_{\kappa}-\delta^{\mu}_{\kappa}\delta^{\nu}_{\lambda}$.
+Next, by analysing the first order perturbations of the actions, we found a choice of the coupling constants which allow nontrivial solutions of these field equations, together with the non-relativistic limit of the geodesic equation.
+Then, we substitute the field components by their their scalar perturbation decomposition,
+\begin{equation}
+  a_\mu \to \delta_\mu^0 a+\delta_\mu^m \partial_{m}a_L,
+\end{equation}
+\begin{equation}
+  \begin{split}
+    t^{\mu,\nu\rho} &\to \delta^{\mu}_m\delta^{\nu\rho}_{n0} \Big(t \delta^{m n} + \partial^m \partial^n t_L \Big)
+    +\delta^{\mu}_0 \delta^{\nu\rho}_{m0} \partial^m c_L
+    \\
+    & \quad + \Big(\delta^{\mu}_0\delta^{\nu\rho}_{mn}-\delta^{\mu}_m\delta^{\nu\rho}_{n0}\Big)\epsilon^{m n p} \partial_{p} b
+    \\
+    & \quad +\delta^{\mu}_m \delta^{\nu}_{n} \delta^{\rho}_{p} \Big(\epsilon^{n p q}\partial_q \partial^m d_1 +  (\delta^{m n} \partial^p - \delta^{m p} \partial^n)d_2\Big)
+  \end{split}
+\end{equation}
+and
+\begin{equation}
+  \begin{split}
+    \gamma^\lambda_{\mu\nu}
+    &\to
+    \delta^\lambda_0\delta^0_\mu\delta^0_\nu u 
+    + \delta^\lambda_m \delta^0_\mu\delta^0_\nu \partial^m v_L
+    + 2\delta^\lambda_0 \delta^0_{(\mu}\delta^m_{\nu)} \partial_m w_L
+    \\
+    & \quad + \delta^\lambda_0 \delta^m_\mu\delta^n_\nu \Big(x \delta_{mn} + \partial_m \partial_n x_L\Big)
+    \\
+    & \quad + 2\delta^\lambda_m \delta^0_{(\mu}\delta^n_{\nu)} \Big(y_1 \delta^m{}_n + \epsilon^{m p}{}_{n} \partial_p y_2 + \partial^m \partial_n y_L\Big)
+    \\
+    & \quad + \delta^\lambda_m \delta^n_{\mu}\delta^p_{\nu} \Big(\delta_{n p} \partial^m z_1 + (\delta^m{}_n \partial_p+\delta^m{}_p \partial_n) z_2
+    \\
+    & \qquad +  (\epsilon^{m q}{}_n \partial_p+\epsilon^{m q}{}_p \partial_n) \partial_q z_3 + \partial^m \partial_n \partial_p z_L\Big),
+  \end{split}
+\end{equation}
+where the ``L'' sub-index identifies the longitudinal degrees of freedom.
+
+%% In the non-relativistic (low-momentum) limit, the geodesic deviation of inertial observers is also discussed.
+
+%% Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
 Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we used ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.

### 2015-07-23 AffGR-PRD.tex
Extended Sec. NR-limit

@@
 %% Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
-Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we used ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.
+Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general $\binom{2}{0}$-type symmetric tensor density, $\mathfrak{g}^{\mu \nu}$, constructed with at most quadratic terms in the available fields.
+This tensor density coincides with what we call the ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.
 However, for the simple case of the Einstein--Hilbert action, it is in fact the inverse metric density.}, defined as the variation of the action with respect to the symmetric part of the Ricci tensor~(see Refs.~\cite{Eddington1923math,schrodinger1950space,Poplawski:2012bw}), i.e.,%% \hl{JZ: def.
@@
   \label{metric}
-  \frac{\delta\ }{\delta R_{(\mu\nu)}} S[\Gamma] \equiv \sqrt{\mathsf{g}} \, \mathsf{g}^{\mu\nu} = \bar{g}^{\mu\nu} ,
+  \frac{\delta\ }{\delta R_{(\mu\nu)}} S[\Gamma] \equiv \sqrt{\mathsf{g}} \, \mathsf{g}^{\mu\nu} = \mathfrak{g}^{\mu\nu}.
 \end{equation}
-by assuming a matter action that depends on $\bar{g}^{\mu\nu}$.
+%% by assuming a matter action that depends on $\bar{g}^{\mu\nu}$.
 
-From the geodesic equations and the linearized action on scalar perturbation, we found that the effective geodesic deviation
+From the geodesic equations and the linearized action on scalar perturbation, we found that only a few terms in the scalar perturbation affect the geodesic equation.
+The effective geodesic deviation is given by
 \begin{equation}

### 2015-07-23 AffGR-PRD.tex
Updating Relativistic Limit

@@
   \label{NewtonPot}
-  \Gamma^i{}_{00} = - \frac{1}{8\pi} \frac{ \partial\mathcal{L}_{\text{Matter}} }{ \partial \bar{g}^{00} } \, \nabla^i \left(\frac{1}{|\vec{x}|}\right),
+  \Gamma^i{}_{00} = - \frac{1}{8\pi} \frac{ \partial\mathcal{L}_{\text{Matter}} }{ \partial \mathfrak{g}^{00} } \, \nabla^i \left(\frac{1}{|\vec{x}|}\right),
 \end{equation}
@@
 %%%%%%%%% COMPARISON GR %%%%%%%%%
-Although we obtained the Newtonian gravitational potential~\eqref{NewtonPot}, the post-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
+Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, the post-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
 Therefore, we should go beyond the Newtonian limit in order to compare our model with GR.
@@
 %%\hl{A comparison between our affine model and GR requires the imposition of vanishing torsion (JZ: Why?).}
-Even though a comparison between our affine model and GR does not require the imposition of vanishing torsion, at this stage we shall focus on a sector of the theory in which the connection is metric and torsion-free.
-Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements, and the only nontrivial field equation is the one for the Curtright, $T^{\nu,\mu\rho}$,
+Even though a comparison between our affine model and GR does not require the imposition of vanishing torsion, for the sake of simplicity, at this stage we shall focus on a sector of the theory in which the connection is compatible with a metric, and torsion-free.
+Notice that the vanishing torsion limit ---equivalent to taking $T^{\lambda,\mu\nu} \to 0$ and $A_\mu \to 0$--- cannot be taken at the action level, and should be taken in the field equations.
+Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements, because only the terms of the action linear in these fields will be relevant, i.e.,
+\begin{equation*}
+  %\label{eff-action}
+  S_{\text{eff}} = \int\dn{4}{x} \Big( C_1\, R_{\mu\rho}{}^{\mu}{}_\nu \nabla_\sigma T^{\nu,\rho\sigma} + C_2 \, R_{\mu\nu}{}^{\rho}{}_\rho \nabla_\sigma T^{\sigma,\mu\nu} \Big),
+\end{equation*}
+and the only nontrivial field equation is the one for the Curtright, $T^{\nu,\mu\rho}$,
 \begin{equation*}
@@
 
-The above equation is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature ---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.} The parallel Ricci curvature is a generalization of the Einstein condition which assures that although the manifold is not generally Einstein, the metric has to be locally a product of Einstein metrics~\cite{Besse}.
+Equation~\eqref{SimpleEOM} is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature ---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.} For all Einstein manifolds, whose Ricci tensor is proportional to the metric, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
+Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from GR are present in the chosen scenario of our model.
+As an additional comment, the parallel Ricci curvature assures that although the manifold is not in general a Einstein manifold, the metric has to be locally a product of Einstein metrics~\cite{Besse}.
 
-A corollary is that all Einstein manifolds, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
+%% A corollary is that all Einstein manifolds, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
 Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from GR are present in the chosen scenario of our model.

### 2015-07-24 AffGR-PRD.tex
About to compare with Maxell

@@
 Even though a comparison between our affine model and GR does not require the imposition of vanishing torsion, for the sake of simplicity, at this stage we shall focus on a sector of the theory in which the connection is compatible with a metric, and torsion-free.
-Notice that the vanishing torsion limit ---equivalent to taking $T^{\lambda,\mu\nu} \to 0$ and $A_\mu \to 0$--- cannot be taken at the action level, and should be taken in the field equations.
+Notice that the vanishing torsion limit ---equivalent to take $T^{\lambda,\mu\nu} \to 0$ and $A_\mu \to 0$--- cannot be taken at the action level, and should be taken in the field equations.
 Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements, because only the terms of the action linear in these fields will be relevant, i.e.,
@@
 
-Additionally, for a Riemannian manifold $(\Mi,g)$ the condition in Eq.~\eqref{SimpleEOM} is equivalent to the following statements (see Ref.~\cite{Derdzinski:1985,Besse}): (i) the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}, (ii) the manifold has harmonic curvature~\cite{bourguignon1981varietes}, i.e.
+%%Additionally, for a Riemannian manifold $(\Mi,g)$ the condition in Eq.~\eqref{SimpleEOM} is equivalent to the following statements (see Ref.~\cite{Derdzinski:1985,Besse}): (i) the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}, (ii) the manifold has harmonic curvature~\cite{bourguignon1981varietes}, i.e.
 \mbox{$\nabla^\mu R_{\mu\nu}{}^\lambda{}_\rho = 0$,} and (iii) in the four-dimensional case the manifold has harmonic Weyl tensor~\cite{Berger:1969} and constant scalar curvature.
 
+For a Riemannian manifold $(\Mi,g)$ the Eq.~\eqref{SimpleEOM} is related through the first Bianchi identity to the harmonic curvature condition~\cite{bourguignon1981varietes},
+\begin{equation}
+  \label{harm-curv}
+  \nabla_\lambda R_{\mu\nu}{}^\lambda{}_\rho = 0,
+\end{equation}
+and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor~\cite{Berger:1969} and constant scalar curvature, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}.
+For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.
+
+Equations.~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
 Interestingly, the Eq.~\eqref{SimpleEOM} can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974},

### 2015-07-29 AffGR-PRD.tex
Askirz corrections, about compare with Maxwell

@@
 \hypersetup{%
-  pdftitle={Einstein's Gravity from an Affine Model},
+  pdftitle={Einstein's gravity from a polynomial affine model},
   pdfauthor={Oscar Castillo-Felisola,}{Aureliano Skirzewski},
@@
 
-\title{Einstein's gravity from an affine model}
+\title{Einstein's gravity from a polynomial affine model}
 
@@
 \begin{abstract}
-  We show that the effective field equations for a recently formulated affine model of gravity, in the sector of a metric-compatible (torsion-free) connection, accept general Einstein manifolds ---with or without cosmological constant--- as solutions.
+  We show that the effective field equations for a recently formulated polynomial affine model of gravity, in the sector of a torsion-free connection, accept general Einstein manifolds ---with or without cosmological constant--- as solutions.
 Moreover, these effective field equations coincide with those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
-Additionally, we find an equivalence between a minimally coupled massless scalar field in General Relativity with a ``minimally'' coupled scalar field in this affine model.
+Additionally, we find a generalization of a minimally coupled massless scalar field in General Relativity with a ``minimally'' coupled scalar field in this affine model.
 \end{abstract}
@@
 \pacs{02.40.Ma,04.50.Kd,04.90.+e}
-\keywords{Affine Gravity, Torsion, Generalised Gravity.}
+\keywords{Affine Gravity, Torsion, Generalized Gravity.}
 
@@
 Classically, General Relativity is the most successful theory of gravitational interactions.
-However, it is believed to be the effective theory of a, yet to be discover, more fundamental one.
+However, it is believed to be the effective theory of a, yet to be discovered, more fundamental one.
 Among the problems of General Relativity we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}.
@@
 
-Standing of the argument of the necessity of a quantum theory of gravity, several generalizations of Einstein's General Relativity have been proposed.
-One important class of these generalizations consider the connection field to be independent of the metric, known as Palatini type theories.
-Within this class of theories one finds the generalization due to Cartan, which consider a connection with nonvanishing torsion~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
-Interestingly, gravitational theories with generic connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
-Albeit these gravitational theories with an arbitrary connection posses ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe} or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
+Standing on the argument of the necessity of a quantum theory of gravity, several generalizations of Einstein's General Relativity have been proposed.
+One important class of these generalizations considers the connection field to be independent of the metric, known as Palatini type theories.
+Within this class of theories one finds the generalization due to Cartan, which considers a connection with nonvanishing torsion~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
+Interestingly, gravitational theories with generic linear connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
+Albeit these gravitational theories with an arbitrary connection possess ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe} or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
 
@@
 %%%%%%%%% THE MODEL %%%%%%%%%
-in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms (which by no means guaranty the renormalizability of the system).
+in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms (which by no means guarantees the renormalizability of the system).
 We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravitational potential, despite the existence of torsion.
-We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}.
+We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}, due to the absence of a fundamental metric.
 
@@
 
-First of all, we highlight that the model constructed below has as fundamental field an affine connection, and no metric fields is needed for neither contract nor lowering or raising indices.
+First of all, we highlight that the model constructed below has as fundamental field an affine connection, and no metric fields is needed for neither contracting nor lowering or raising indices.
 Moreover, in order to guarantee the correct transformation of the Lagrangian density, the geometrical objects used to write down the action will be the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
@@
 \end{equation}
-where ${\Gamma}^\mu{}_{\rho\sigma}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying $T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$ and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$.
+where ${\Gamma}^\mu{}_{\rho\sigma}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying \mbox{$T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$} and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$.
 Since no metric is present  the epsilon symbols are not related by raising (lowering) their indices, but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}

### 2015-08-03 AffGR-PRD.tex
Added bibliography and small corrections

@@
 Among the problems of General Relativity we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}.
-Second, the Wheeler--DeWitt equations are not well-defined in general due to their non-polynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
+Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
 One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
-On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter.
+On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba}.
 
@@
 
-Therefore, under the premises of non-completeness and non-polynomial structure of the theory, 
+Therefore, under the premises of incompleteness and non-polynomial structure of the theory, 
 %%%%%%%%% THE MODEL %%%%%%%%%
@@
 We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravitational potential, despite the existence of torsion.
-We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}, due to the absence of a fundamental metric.
+We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}, due to the absence of a fundamental metric, or in other words, the absence of flux operators.
 
@@
 
-The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations.% in vacuum.
+The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations.
+% in vacuum.
 In addition, we show that ---in the same sector--- under the assumption of the existence of a unique non-degenerated, covariantly constant $\binom{0}{2}$-tensor, $g$ (which could be thought as a metric), the system of a scalar field coupled with the polynomial affine gravity accepts the minimally coupled Einstein--Klein--Gordon as a solution.
-
 The paper is organized as follows.
@@
 %% Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
-Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general $\binom{2}{0}$-type symmetric tensor density, $\mathfrak{g}^{\mu \nu}$, constructed with at most quadratic terms in the available fields.
-This tensor density coincides with what we call the ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.
+Albeit the inclusion of matter in a nonmetric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general $\binom{2}{0}$-type symmetric tensor density, $\mathfrak{g}^{\mu \nu}$, constructed with at most quadratic terms in the available fields.
+A simple \emph{dimensional analysis} shows that this tensor density contains the same terms as what we call the ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.
 However, for the simple case of the Einstein--Hilbert action, it is in fact the inverse metric density.}, defined as the variation of the action with respect to the symmetric part of the Ricci tensor~(see Refs.~\cite{Eddington1923math,schrodinger1950space,Poplawski:2012bw}), i.e.,%% \hl{JZ: def.
@@
   \label{metric}
-  \frac{\delta\ }{\delta R_{(\mu\nu)}} S[\Gamma] \equiv \sqrt{\mathsf{g}} \, \mathsf{g}^{\mu\nu} = \mathfrak{g}^{\mu\nu}.
+  \frac{\delta\ }{\delta R_{(\mu\nu)}} S[\Gamma] \equiv \sqrt{\mathsf{g}} \, \mathsf{g}^{\mu\nu} = \bar{g}^{\mu\nu}.
 \end{equation}
@@
 
-From the geodesic equations and the linearized action on scalar perturbation, we found that only a few terms in the scalar perturbation affect the geodesic equation.
+From the geodesic equations and the linearized action on scalar perturbation, we found that only a few terms in the scalar perturbation affect the geodesic equation~\footnote{We cross-check our result using the software Cadabra~\cite{Peeters2007550,peeters2007symbolic,Peeters:2007wn}.}.
 The effective geodesic deviation is given by
@@
 Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, the post-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
-Therefore, we should go beyond the Newtonian limit in order to compare our model with GR.
+Therefore, we should go beyond the Newtonian limit in order to compare our model with General Relativity.
 
 %%\hl{A comparison between our affine model and GR requires the imposition of vanishing torsion (JZ: Why?).}
-Even though a comparison between our affine model and GR does not require the imposition of vanishing torsion, for the sake of simplicity, at this stage we shall focus on a sector of the theory in which the connection is compatible with a metric, and torsion-free.
+Even though a comparison between the models does not require the imposition of vanishing torsion, for the sake of simplicity, at this stage we shall focus on a sector of the theory in which the connection is torsion-free.
 Notice that the vanishing torsion limit ---equivalent to take $T^{\lambda,\mu\nu} \to 0$ and $A_\mu \to 0$--- cannot be taken at the action level, and should be taken in the field equations.
-Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements, because only the terms of the action linear in these fields will be relevant, i.e.,
-\begin{equation*}
+Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements.
+Since only the terms of the action linear in these fields will be relevant, one can consider the effective action linear in the torsion's fields, i.e.,
+\begin{equation}
   %\label{eff-action}
-  S_{\text{eff}} = \int\dn{4}{x} \Big( C_1\, R_{\mu\rho}{}^{\mu}{}_\nu \nabla_\sigma T^{\nu,\rho\sigma} + C_2 \, R_{\mu\nu}{}^{\rho}{}_\rho \nabla_\sigma T^{\sigma,\mu\nu} \Big),
-\end{equation*}
-and the only nontrivial field equation is the one for the Curtright, $T^{\nu,\mu\rho}$,
-\begin{equation*}
-  \nab{[\rho} R_{\mu]\lambda}{}^{\lambda}{}_{\nu} + \kappa \nab{\nu} R_{\mu\rho}{}^\lambda{}_\lambda = 0,
-\end{equation*}
-with $\kappa$ a constant related with the couplings of the model.
-In the considered sector the connection is compatible with a metric, therefore, the second term vanishes and the gravitational equations are
+  S_{\text{eff}} = \int\dn{4}{x} \Big( C_1\, R_{\lambda\mu}{}^{\lambda}{}_\nu \nabla_\rho %T^{\nu,\rho\sigma}
+  + C_2 \, R_{\mu\rho}{}^{\lambda}{}_\lambda \nabla_\nu \Big) T^{\nu,\mu\rho} ,
+\end{equation}
+and the only nontrivial field equation after the limit will be the one for the Curtright, $T^{\nu,\mu\rho}$,
+\begin{equation}
+  \nab{[\rho} R_{\mu]\nu} + \kappa \nab{\nu} R_{\mu\rho}{}^\lambda{}_\lambda = 0,
+\end{equation}
+with $\kappa$ a constant related with the original couplings of the model.
+We assume that the connection is compatible with volume form, i.e., it is equi-affine~\cite{nomizu1994affine,MO-Bryant02}.
+The equi-affine condition assures that the Ricci tensor of the connection is symmetric, and the contraction of the last indices vanishes, thus the second term in the field equation is absent and the gravitational equations are
 \begin{equation}
@@
 
-Equation~\eqref{SimpleEOM} is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature ---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.} For all Einstein manifolds, whose Ricci tensor is proportional to the metric, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
-Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from GR are present in the chosen scenario of our model.
+Equation~\eqref{SimpleEOM} is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature ---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.}  All Einstein manifolds, whose Ricci tensor is proportional to the metric, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition due to the metricity condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
+Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from General Relativity are present in the chosen scenario of our model.
 As an additional comment, the parallel Ricci curvature assures that although the manifold is not in general a Einstein manifold, the metric has to be locally a product of Einstein metrics~\cite{Besse}.
@@
 
-For a Riemannian manifold $(\Mi,g)$ the Eq.~\eqref{SimpleEOM} is related through the first Bianchi identity to the harmonic curvature condition~\cite{bourguignon1981varietes},
+The Eq.~\eqref{SimpleEOM} is related through the second Bianchi identity to the harmonic curvature condition~\cite{bourguignon1981varietes},
 \begin{equation}
@@
 Consequently, all gravitational effects described by standard General Relativity are contained in our model, even though the torsion field is kept to zero.
-Regarding this aspect, we would like to emphazise that there is enough liberty to start considering new cosmological effects coming from both nonvanishing torsion and non-metric connections with vanishing torsion, beside the results reported in Ref.~\cite{Chen:2013kia,Chen:2013ota}.
+Regarding this aspect, we would like to emphazise that there is enough liberty to start considering new cosmological effects coming from both nonvanishing torsion and nonmetric connections with vanishing torsion, beside the results reported in Ref.~\cite{Chen:2013kia,Chen:2013ota}.
 Moreover, our gravitational model coupled to a scalar field through the \emph{tensor density} $\mathfrak{g}^{\mu\nu}$ ---in the vanishing torsion consideration---, generalizes GR minimally coupled to a massless scalar field.
@@
 %%%%%%%%% BIBLIOGRAPHY %%%%%%%%%
-\bibliographystyle{apsrev4-1}
+%%\bibliographystyle{apsrev4-1}
 \bibliography{References.bib}

### 2015-10-20 AffGR-PRD.tex
Starting new update counting

@@
 %% \newcommand{\Ff}{{\mathbf{F}}}
-\DeclareDocumentCommand{\Ff}{ o }{ \IfValueTF{#1}{ F_{(#1)} }{ F } }
+%% \DeclareDocumentCommand{\Ff}{ o }{ \IfValueTF{#1}{ F_{(#1)} }{ F } }
+\DeclareDocumentCommand{\Ff}{ s o }{ \IfBooleanTF{#1}
+    { \IfValueTF{#2}{ \boldsymbol{F}_{(#2)} }{ \boldsymbol{F} } }
+    { \IfValueTF{#2}{            {F}_{(#2)} }{            {F} } } }
 \newcommand{\FF}[1]{{\mathbf{F}}_{(#1)}}
@@
 \end{equation}
-and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor~\cite{Berger:1969} and constant scalar curvature, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}.
+and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor and constant scalar curvature~\cite{Berger:1969}, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}.
 For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.
 
-Equations.~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
-Interestingly, the Eq.~\eqref{SimpleEOM} can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974},
+%% Equations~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
+Notice that Eqs.~\eqref{SimpleEOM} and~\eqref{harm-curv} accept a geometrical interpretation equivalent to that of the field equations of a pure Yang--Mills theory, which in the language of differential forms are
+\begin{align}
+  \df \Ff*[2] &= 0, & \df \st \Ff*[2] &= 0,
+\end{align}
+where $\Ff*[2]$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle), and the operator $\st$ denotes the Hodge star.
+Now, these Yang--Mills field equations are obtained from the well-known action functional
 \begin{equation}
-  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \we \st \Rif{}{} \right),
+  S_{\textsc{ym}} = \int \Tr \Big( \Ff*[2] \st \Ff*[2] \Big).
+\end{equation}
+
+Interestingly, the Eq.~\eqref{SimpleEOM} ---equivalently Eq.~\eqref{harm-curv}--- can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, %constructed as the trace of the
+\begin{equation}
+  \label{SKY}
+  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \st \Rif{}{} \right) = \int \left( \Rif{a}{b} \st \Rif{b}{a} \right),
 \end{equation}
 where $\Rif{}{} \in \Omega^2(\Mi, T^*\Mi \otimes T\Mi)$ is the curvature two-form, the operator $\st$ denotes the Hodge star, and the trace is taken on the bundle indices (see Ref.~\cite{bourguignon1982yang}).
+
+The gravitational model described by the action in Eq.~\eqref{SKY} is called Stephenson--Kilmister--Yang (or SKY for short).
+However, the standard interpretation of this model requires a metric tensor.
+Therefore, a quick analysis of the field equations \`a la Palatini shows that the field equation
+
+%% \documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint]{revtex4-1}
+
+%% \usepackage{amsmath,amsthm,latexsym,amssymb,amsfonts}
+%% \usepackage{xcolor}
+%% \usepackage[%
+%%   colorlinks=true,
+%%   urlcolor=blue,
+%%   linkcolor=blue,
+%%   citecolor=blue
+%% ]{hyperref}
+%% \usepackage{etoolbox}
+%% \usepackage{breqn}
+
+%% \makeatletter
+%% \let\cat@comma@active\@empty
+%% \makeatother
+
+%% %------------------
+%% %--------- Definitions
+%% %------------------
+%% %% \input{Def-article.tex}
+%% \usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
+%% \usepackage{graphicx}
+%% \usepackage{centernot}
+%% %% \usepackage{hyperref}
+%% \usepackage{xcolor}
+%% \usepackage{comment}
+%% %% \hypersetup{linktocpage,colorlinks=true,urlcolor=blue!80!red,linkcolor=blue,citecolor=red}
+%% %\usepackage{feynmf}
+%% \usepackage{siunitx}
+%% \usepackage{array}
+%% %% \usepackage{ulem}
+%% %\usepackage{tikz}
+%% \usepackage{braket}
+%% \usepackage{xparse}
+
+%% %-------------------------------Theorems
+%% \newtheorem{Def}{Definition}[section]
+%% \newtheorem{Thm}[Def]{Theorem}
+%% \newtheorem{Lem}[Def]{Lemma}
+%% \newtheorem{Pos}[Def]{Postulate}
+%% \newtheorem{Exa}[Def]{Example}
+%% \newtheorem{Cor}[Def]{Corrolary}
+%% \newtheorem{Pro}[Def]{Proposition}
+
+%% %---------------------------------New commands
+%% \newcommand{\A}{\mathcal{A}} %% This is equivalent to \Ag (no args)
+%% \newcommand{\abs}[1]{\left|{#1}\right|}
+%% \DeclareMathOperator{\ad}{ad}
+%% \DeclareMathOperator{\Ad}{Ad}
+%% \DeclareDocumentCommand{\Ag}{ s o }{ \IfBooleanTF{#1}
+%%     { \IfValueTF{#2}{ \boldsymbol{\mathcal{A}}_{(#2)} }{ \boldsymbol{\mathcal{A}} } }
+%%     { \IfValueTF{#2}{            {\mathcal{A}}_{(#2)} }{            {\mathcal{A}} } } }
+%% %% \newcommand{\Ag}{\mathcal{A}_{(1)}}
+%% %% \newcommand{\Agf}{\boldsymbol{\mathcal{A}}}
+%% \DeclareDocumentCommand{\Af}{ s o }{ \IfBooleanTF{#1}
+%%     { \IfValueTF{#2}{ \boldsymbol{A}_{(#2)} }{ \boldsymbol{A} } }
+%%     { \IfValueTF{#2}{            {A}_{(#2)} }{            {A} } } }
+%% %% \newcommand{\Af}{ {\mathbf{A}} }
+%% %% \newcommand{\AF}[1]{ {\mathbf{A}}_{({#1})} }
+%% \newcommand{\hAf}{ \hat{\mathbf{A}}_{(1)} }
+%% \newcommand{\hAF}[1]{ \hat{\mathbf{A}}_{(#1)} }
+%% \newcommand{\bboxed}[1]{{\color{red}{\boxed{\boxed{\textcolor{black}{#1}}}}}}
+%% \newcommand{\C}{\mathbb{C}}
+%% \newcommand{\Cl}{\mathcal{C}\!\ell}
+%% \newcommand{\cdf}[1][]{{\boldsymbol{\mathcal{D}}}{#1}\!}
+%% \newcommand{\covd}{\mathcal{D}}
+%% \newcommand{\D}{\mathscr{D}}
+%% \newcommand{\df}[1][]{\mathbf{d}{#1}}
+%% \newcommand{\dfd}{{\mathbf{d}}^\dag\!}
+%% \newcommand\ded{\mathrm{d}^\dag}
+%% \DeclareMathOperator{\End}{End}
+%% \newcommand{\ele}[2][]{\frac{d}{dt}\left(\frac{\partial\mathcal{L}}{\partial \dot{#2}^{#1}}\right) - \frac{\partial\mathcal{L}}{\partial {#2}^{#1}}}
+%% \newcommand{\fele}[2][]{\partial_\mu \left(\frac{\delta\mathcal{L}}{\delta\left(\partial_\mu{#2}^{#1}\right)}\right) - \frac{\delta\mathcal{L}}{\delta {#2}^{#1}}}
+%% \newcommand{\vb}[1]{\vec{e}_{#1}}
+%% %% \newcommand{\fb}[1]{\widetilde{e}{}^{ #1}}
+%% \newcommand{\fb}[1]{\widetilde{e}{}^{ #1}}
+%% \newcommand\fder[3][]{\frac{\delta^{#1}{#2}}{\delta {#3}^{#1}}}
+%% \newcommand\fdern[4][]{\frac{\delta^{#1}{#2}}{\delta {#3} \cdots \delta {#4}}}
+%% %% \newcommand{\Fc}{\mathcal{F}}
+%% %% \newcommand{\F}{\boldsymbol{\mathcal{F}}}
+%% %% \newcommand{\Fg}{\boldsymbol{\mathcal{F}}_{(2)}}
+%% \DeclareDocumentCommand{\Fg}{ s o }{ \IfBooleanTF{#1}
+%%     { \IfValueTF{#2}{ \boldsymbol{\mathcal{F}}_{(#2)} }{ \boldsymbol{\mathcal{F}} } }
+%%     { \IfValueTF{#2}{            {\mathcal{F}}_{(#2)} }{            {\mathcal{F}} } } }
+%% %% \newcommand{\Ff}{{\mathbf{F}}}
+%% %% \DeclareDocumentCommand{\Ff}{ o }{ \IfValueTF{#1}{ F_{(#1)} }{ F } }
+%% \DeclareDocumentCommand{\Ff}{ s o }{ \IfBooleanTF{#1}
+%%     { \IfValueTF{#2}{ \boldsymbol{F}_{(#2)} }{ \boldsymbol{F} } }
+%%     { \IfValueTF{#2}{            {F}_{(#2)} }{            {F} } } }
+%% \newcommand{\FF}[1]{{\mathbf{F}}_{(#1)}}
+%% \newcommand{\hFF}[1]{{\mathbf{\hat{F}}}_{(#1)}}
+%% \newcommand{\fy}{\centernot}
+%% \newcommand{\G}{\mathscr{G}}
+%% \newcommand{\ga}{\gamma}
+%% \newcommand{\gf}{\boldsymbol{\gamma}}
+%% \newcommand{\Ga}{\Gamma}
+%% \newcommand{\conn}[3]{\left(\Gamma_{#1}\right)^{#2}{}_{#3}}
+%% \newcommand{\connn}[3]{\Gamma_{#1}{}^{#2}{}_{#3}}
+%% \newcommand{\hcon}[3]{\hat{\Gamma}_{#1}{}^{#2}{}_{#3}}
+%% \newcommand{\Ha}{\mathscr{H}}
+%% \newcommand{\He}{\mathbb{H}}
+%% \newcommand{\Hi}{\mathcal{H}}
+%% \newcommand{\Hint}{\underline{\sc Hint:} }
+%% \DeclareMathOperator{\hs}{\star\!\!}
+%% \DeclareMathOperator{\st}{\star}
+%% \newcommand{\J}{\mathscr{J}}
+%% \newcommand{\K}{\mathbb{K}}
+%% \newcommand{\KK}{Kaluza-Klein\ }
+%% \newcommand{\Lag}{\mathscr{L}}
+%% \newcommand{\Li}{\mathcal{L}}
+%% \newcommand{\La}[1][]{\triangle_{#1}}
+%% \newcommand{\Lap}{\nabla^2}
+%% \newcommand{\lr}[1]{\stackrel{\leftrightarrow}{#1}}
+%% \newcommand{\M}{\ensuremath{\mathscr{M}}}
+%% \DeclareMathOperator{\Mat}{Mat}
+%% \newcommand{\Mi}{\mathcal{M}}
+%% \newcommand{\MN}{Maldacena-N\'u\~nez\ }
+%% \newcommand{\N}{\ensuremath{\mathscr{N}}}
+%% \newcommand{\Na}{\mathbb{N}}
+%% \newcommand{\No}{\mathcal{N}}
+%% \newcommand{\norm}[1]{\left\|#1\right\|}
+%% \newcommand{\Op}{\mathcal{O}}
+%% \newcommand{\Or}{\mathscr{O}}
+%% \newcommand\pder[3][]{\frac{\partial^{#1}{#2}}{\partial {#3}^{#1}}}
+%% \newcommand\pdern[4][]{\frac{\partial^{#1}#2}{\partial #3\cdots\partial #4}}
+%% \DeclareMathOperator{\Pfaff}{Pfaff}
+%% \newcommand{\Qh}[1][]{\ensuremath{\hat{Q}_{#1}}}
+%% \newcommand{\R}{\mathbb{R}}
+%% \newcommand{\Ri}{\mathcal{R}}
+%% %% \newcommand{\S}{\mathscr{S}}
+%% \newcommand{\SM}{Standard Model {}}%\mathscr{S}}
+%% \DeclareDocumentCommand\Te{o o m }{\mathcal{T}{}^{#1}_{#2}(#3)}
+%% \newcommand{\T}{\mathscr{T}}
+%% \newcommand{\tor}{\mathcal{T}}
+%% \newcommand{\tors}[3]{\mathcal{T}{}_{#1}{}^{#2}{}_{#3}}
+%% \newcommand{\torss}[3]{T_{#1}{}^{#2}{}_{#3}}
+%% \newcommand\vdj[1]{\left< \Delta J \right>_{#1}}
+%% \newcommand{\w}{{\scriptstyle\wedge}\!}
+%% \newcommand{\we}{{\scriptstyle\wedge}}
+%% \newcommand{\Z}{\mathbb{Z}}
+
+%% \newcommand{\dbar}[1]{\ensuremath{\mathchar'26\mkern-12mu \mathrm{d}^{#1}}\!}
+
+%% %--------------------------- New Greek
+%% \newcommand{\tht}{\ensuremath{\theta}}
+%% \newcommand{\bet}{\ensuremath{\bar{\eta}}}
+%% \newcommand{\bps}{\ensuremath{\bar{\psi}}}
+%% \newcommand{\bc}{\ensuremath{\bar{\chi}}}
+%% \newcommand{\Bps}{\ensuremath{\bar{\Psi}}}
+%% \newcommand{\Bx}{\ensuremath{\bar{\Xi}}}
+%% \newcommand{\bph}{\ensuremath{\bar{\phi}}}
+%% \newcommand{\vph}{\ensuremath{\varphi}}
+%% \newcommand{\bvph}{\ensuremath{\bar{\varphi}}}
+%% \newcommand{\bth}{\ensuremath{\bar{\theta}}}
+%% \newcommand{\hph}{\ensuremath{\hat{\phi}}}
+
+%% \newcommand{\bs}[1]{\boldsymbol{#1}}
+
+%% \renewcommand{\div}{{\mathbf{div}}}
+%% \newcommand{\grad}{{\mathbf{grad}}}
+%% \newcommand{\curl}{{\mathbf{curl}}}
+
+%% \newcommand\VI[2]{\hat{e}^{\hat{#1}}_{\hat{#2}}}
+%% \newcommand\VIF[1]{\hat{\boldsymbol{e}}^{\hat{#1}}}
+%% \newcommand\VIN[2]{\hat{E}^{\hat{#1}}_{\hat{#2}}}
+%% \newcommand\VINF[1]{\hat{\boldsymbol{E}}_{\hat{#1}}}
+%% \newcommand\hvi[2]{\hat{e}^{{#1}}_{{#2}}}
+%% \newcommand\hvin[2]{\hat{E}^{{#1}}_{{#2}}}
+%% \newcommand\hvif[1]{\hat{\boldsymbol{e}}^{{#1}}}
+%% \newcommand\hvinf[1]{\hat{\boldsymbol{E}}_{{#1}}}
+%% \newcommand\vi[2]{e^{{#1}}_{{#2}}}
+%% \newcommand\vin[2]{E^{{#1}}_{{#2}}}
+%% \newcommand\vif[1]{\boldsymbol{e}^{{#1}}}
+%% \newcommand\vinf[1]{\boldsymbol{E}_{{#1}}}
+%% %% \newcommand\Vi[2]{e^{\hat{#1}}_{\hat{#2}}}
+%% %% \newcommand\Vin[2]{E^{\hat{#1}}_{\hat{#2}}}
+%% \newcommand\GAM[1]{{\gamma}^{\hat{#1}}}
+%% %% \newcommand\Gam[1]{\gamma^{\hat{#1}}} 
+%% \newcommand\gam[1]{\gamma^{{#1}}}
+%% \newcommand\hgam[1]{\hat{\gamma}^{{#1}}}
+%% \newcommand\NAB[1]{\hat{\nabla}_{\hat{#1}}}
+%% \newcommand\Nab[1]{\nabla_{\hat{#1}}}
+%% \newcommand\nab[1]{\nabla_{{#1}}}
+%% \newcommand\PA[1]{\partial_{\hat{#1}}}
+%% \newcommand\pa[1]{\partial_{{#1}}}
+%% \newcommand\PAU[1]{\partial^{\hat{#1}}}
+%% \newcommand\pau[1]{\partial^{{#1}}}
+%% \newcommand\lf[1]{{\omega}^{{#1}}}
+%% \newcommand\lft[1]{\hat{\omega}^{{#1}}}
+%% \newcommand\SPI[1]{\hat{\omega}_{\hat{#1}}}
+%% \newcommand\SPIF[2]{\hat{\boldsymbol{\omega}}^{\hat{#1}}{}_{\hat{#2}}}
+%% %% \newcommand\Spi[1]{\omega_{\hat{#1}}}
+%% \newcommand\spi[1]{\omega_{{#1}}}
+%% \newcommand\tspi[1]{\tilde{\omega}_{{#1}}}
+%% \newcommand\spif[2]{{\boldsymbol{\omega}}^{{#1}}{}_{{#2}}}
+%% \newcommand\tspif[2]{{\tilde{\boldsymbol{\omega}}}^{{#1}}{}_{{#2}}}
+%% \newcommand\hspi[1]{\hat{\omega}_{{#1}}}
+%% \newcommand\hspif[2]{\hat{\boldsymbol{\omega}}^{{#1}}{}_{{#2}}}
+%% %%%%%%%%% Beware of the inconsistency between
+%% %%%%%%%%% \Rif and \RIF
+%% \newcommand{\RIF}[2]{\hat{\boldsymbol{\mathcal{R}}}^{\hat{#1}}{}_{\hat{#2}}}
+%% \newcommand{\hRif}[2]{\hat{\boldsymbol{\mathcal{R}}}^{{#1}}{}_{{#2}}}
+%% \newcommand{\Rif}[2]{\boldsymbol{\mathcal{R}}^{{#1}}{}_{{#2}}}
+%% \newcommand{\tRif}[2]{\tilde{\boldsymbol{\mathcal{R}}}^{{#1}}{}_{{#2}}}
+%% \newcommand{\Tf}[1]{\boldsymbol{\mathcal{T}}^{#1}}
+%% \newcommand{\hTf}[1]{\hat{\boldsymbol{\mathcal{T}}}^{#1}}
+%% \newcommand{\TF}[1]{\hat{\boldsymbol{\mathcal{T}}}^{\hat{#1}}}
+%% \newcommand{\Tor}[2]{\mathcal{T}^{#1}{}_{#2}}
+%% \newcommand{\cont}[3]{\mathcal{K}_{#1}{}^{#2}{}_{#3}}
+%% \newcommand{\contf}[2]{\boldsymbol{\mathcal{K}}^{#1}{}_{#2}}
+%% \newcommand{\hcont}[3]{\hat{\mathcal{K}}_{#1}{}^{#2}{}_{#3}}
+%% \newcommand{\hcontf}[2]{\hat{\boldsymbol{\mathcal{K}}}^{#1}{}_{#2}}
+%% \newcommand{\CONT}[3]{\hat{\mathcal{K}}_{\hat{#1}}{}^{\hat{#2}}{}_{\hat{#3}}}
+%% \newcommand{\CONTF}[2]{\hat{\boldsymbol{\mathcal{K}}}^{\hat{#1}}{}_{\hat{#2}}}
+
+%% %% \newcommand{\ket}[1]{\left.\left|#1\right.\right>}
+%% %% \newcommand{\bra}[1]{\left.\left<#1\right.\right|}
+%% \renewcommand\bra[1]{\Bra{#1}}
+%% \renewcommand\ket[1]{\Ket{#1}}
+%% \newcommand{\bkt}[3]{\Braket{ {#1} | {#2} | {#3} } }
+%% \newcommand{\bk}[2]{\Braket{ {#1} | {#2} } }
+%% \newcommand{\comm}[2]{\left[#1,#2\right]}
+%% \newcommand{\acomm}[2]{\left\{#1,#2\right\}}
+%% \newcommand{\vev}[1]{\ensuremath{\left<#1\right>}}
+%% \renewcommand{\set}[1]{\ensuremath{\Set{ #1 }}}
+
+%% \newcommand{\relphantom}[1]{\mathrel{\phantom{#1}}}
+
+%% \newcommand{\Ric}{\operatorname{Ric}}
+%% \newcommand*{\diag}{\operatorname{diag}}
+%% \newcommand{\id}{\operatorname{id}}
+%% \newcommand{\tr}{\operatorname{tr}}
+%% \newcommand{\Tr}{\operatorname{Tr}}
+%% \newcommand{\Ker}{\operatorname{Ker}}
+%% \renewcommand{\Im}{\operatorname{Im}}
+%% \newcommand{\sgn}{\operatorname{sgn}}
+%% \newcommand{\Ln}{\operatorname{Ln}}
+%% \newcommand{\Ei}{\operatorname{Ei}}
+%% \newcommand{\csch}{\operatorname{csch}}
+%% \newcommand{\arcsinh}{\operatorname{arcsinh}}
+%% \DeclareMathOperator\Br{Br}
+
+%% \newcommand{\beq}{\begin{equation}}
+%% \newcommand{\eeq}{\end{equation}}
+%% \newcommand{\ber}{\begin{eqnarray}}
+%% \newcommand{\eer}{\end{eqnarray}}
+
+%% \renewcommand{\(}{\left(}
+%% \renewcommand{\)}{\right)}
+%% \renewcommand{\[}{\left[}
+%% \renewcommand{\]}{\right]}
+
+%% \newcommand{\uf}[2][]{\ensuremath{u_{#1}\(\vec{#2}\)}}
+%% \newcommand{\ufb}[2][]{\ensuremath{\bar{u}_{#1}\(\vec{#2}\)}}
+%% \newcommand{\vf}[2][]{\ensuremath{v_{#1}\(\vec{#2}\)}}
+%% \newcommand{\vfb}[2][]{\ensuremath{\bar{v}_{#1}\(\vec{#2}\)}}
+%% \newcommand\pol[2][]{\ensuremath{\varepsilon_{#1}(\vec{#2})}}
+%% \newcommand\polc[2][]{\ensuremath{\varepsilon^*_{#1}(\vec{#2})}}
+%% \newcommand{\ann}[3]{\ensuremath{#1\(\vec{#2},#3\)}}
+%% \newcommand{\cre}[3]{\ensuremath{#1^\dag\(\vec{#2},#3\)}}
+%% %% \newcommand{\uf}[2]{\ensuremath{u\(\vec{#1},#2\)}}
+%% %% \newcommand{\ufb}[2]{\ensuremath{\bar{u}\(\vec{#1},#2\)}}
+%% %% \newcommand{\vf}[2]{\ensuremath{v\(\vec{#1},#2\)}}
+%% %% \newcommand{\vfb}[2]{\ensuremath{\bar{v}\(\vec{#1},#2\)}}
+%% %% \newcommand{\ann}[3]{\ensuremath{#1\(\vec{#2},#3\)}}
+%% %% \newcommand{\cre}[3]{\ensuremath{#1^\dag\(\vec{#2},#3\)}}
+
+%% \newcommand{\dif}{{\mathrm{d}}}
+%% \newcommand{\difn}[1]{{\mathrm{d}}^{#1}}
+%% \newcommand{\dn}[2]{{\mathrm{d}}^{#1}{#2}\;}
+%% \newcommand{\dbarn}[2]{\dbar{#1}{#2}\;}
+%% \newcommand*{\de}[1]{\mathop{\mathrm{d}#1}\nolimits}% differential, facultative argoment between square parentheses
+%% \newcommand*{\desec}[1][]{\mathop{\mathrm{d^2}#1}\nolimits}% second differential, facultative argoment between square parentheses
+%% \newcommand{\der}[2]{\frac{\de{#1}}{\de{#2}}}% first derivative 
+%% %\newcommand{\pder}[2]{\frac{\pa{}#1}{\pa{}{#2}}}% first derivative 
+%% \newcommand{\inlineder}[2]{\mathrm{d}{#1}/\mathrm{d}{#2}}% in-line first derivative
+%% \newcommand{\dersec}[2]{\frac{{\desec[#1]}}{\de[{#2}^2]}}% second derivative
+%% %% \newcommand{\dx}{\de[x]}% frequently used differentials
+%% %% \newcommand{\dy}{\de[y]}
+%% %\newcommand{\df}{\de[f]}
+
+%% %------------------
+%% %--------- Format
+%% %------------------
+%% \newcommand{\out}[1]{{\color{red} {#1}}}
+%% \newcommand{\pro}[1]{{\color{blue!70!black} {#1}}}
+%% \newcommand{\hl}[1]{{\color{red} \bfseries{#1}}}
+
+%% \newcommand\UTFSM{Departamento de F\'\i sica, Universidad T\'{e}cnica Federico Santa Mar\'\i a, \\ Casilla 110-V, Valpara\'\i so, Chile}
+%% \newcommand\CCTVal{Centro Cient\'\i fico Tecnol\'ogico de Valpara\'\i so, \\ Casilla 110-V, Valpara\'\i so, Chile}
+%% \newcommand\CFF{Centro de F\'\i sica Fundamental,  Universidad de los Andes,\\ 5101 M\'erida, Venezuela}
+
+%% \hypersetup{%
+%%   pdftitle={Einstein's gravity from a polynomial affine model},
+%%   pdfauthor={Oscar Castillo-Felisola,}{Aureliano Skirzewski},
+%%   pdfkeywords={Affine Gravity,} {Torsion,} {Generalised Gravity.},
+%%   pdflang={English}
+%% }
+
+%% %------------------
+%% %--------- Document
+%% %------------------
+%% \begin{document}
+
+%% \title{Einstein's gravity from a polynomial affine model}
+
+%% \author{Oscar \surname{Castillo-Felisola}}
+%% \email{o.castillo.felisola@gmail.com}
+%% \affiliation{\CCTVal.}
+%% \affiliation{\UTFSM.}
+
+%% \author{Aureliano \surname{Skirzewski}}
+%% \email{askirz@gmail.com}
+%% \affiliation{\CFF.}
+
+%% %% --------- Abstract
+%% \begin{abstract}
+%%   We show that the effective field equations for a recently formulated polynomial affine model of gravity, in the sector of a torsion-free connection, accept general Einstein manifolds ---with or without cosmological constant--- as solutions.
+Moreover, these effective field equations coincide with those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
+Additionally, we find a generalization of a minimally coupled massless scalar field in General Relativity with a ``minimally'' coupled scalar field in this affine model.
+%% \end{abstract}
+
+%% \pacs{02.40.Ma,04.50.Kd,04.90.+e}
+%% \keywords{Affine Gravity, Torsion, Generalized Gravity.}
+
+%% \maketitle
+
+%% \section{\label{intro}Introduction}
+
+%% Classically, General Relativity is the most successful theory of gravitational interactions.
+However, it is believed to be the effective theory of a, yet to be discovered, more fundamental one.
+Among the problems of General Relativity we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}.
+Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
+One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
+On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba}.
+
+%% Standing on the argument of the necessity of a quantum theory of gravity, several generalizations of Einstein's General Relativity have been proposed.
+One important class of these generalizations considers the connection field to be independent of the metric, known as Palatini type theories.
+Within this class of theories one finds the generalization due to Cartan, which considers a connection with nonvanishing torsion~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
+Interestingly, gravitational theories with generic linear connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
+Albeit these gravitational theories with an arbitrary connection possess ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe} or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
+
+%% Therefore, under the premises of incompleteness and non-polynomial structure of the theory, 
+%% %%%%%%%%% THE MODEL %%%%%%%%%
+%% in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms (which by no means guarantees the renormalizability of the system).
+We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravitational potential, despite the existence of torsion.
+We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}, due to the absence of a fundamental metric, or in other words, the absence of flux operators.
+
+%% Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton self-interaction is mediated by the torsion.
+This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it is proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
+%% %%Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}.
+However, in the considered framework all graviton self-interaction is mediated by the torsion, which might allow to bypass the general postulates supporting the theorem.
+
+%% The aim of this work is to show that in the vanishing torsion sector, the field equations of the polynomial affine gravity are a generalization of the Einstein's equations.
+% in vacuum.
+In addition, we show that ---in the same sector--- under the assumption of the existence of a unique non-degenerated, covariantly constant $\binom{0}{2}$-tensor, $g$ (which could be thought as a metric), the system of a scalar field coupled with the polynomial affine gravity accepts the minimally coupled Einstein--Klein--Gordon as a solution.
+%% The paper is organized as follows.
+In Sec.~\ref{model}, we present briefly the polynomial affine gravity model, and summarize the results obtained in Ref.~\cite{Skirzewski:2014eta} concerning the Newtonian limit of the model.
+In Sec.~\ref{rlimit}, we restrict ourselves to the sector of the theory with vanishing torsion, and find the field equations; which surprisingly are a known generalization of the Einstein's field equation.
+Then, in Sec.~\ref{matter} we show that under certain considerations the coupling of the gravitational model with a scalar field represents a generalization of the minimally coupled system Einstein--Klein--Gordon.
+Finally, in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results.
+
+%% \section{\label{model}Polynomial affine gravity}
+
+%% First of all, we highlight that the model constructed below has as fundamental field an affine connection, and no metric fields is needed for neither contracting nor lowering or raising indices.
+Moreover, in order to guarantee the correct transformation of the Lagrangian density, the geometrical objects used to write down the action will be the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
+%% \begin{equation}
+%%   \hat{\Gamma}^\mu{}_{\rho\sigma} = {\Gamma}^\mu{}_{\rho\sigma} + T^\mu{}_{\rho\sigma} = {\Gamma}^\mu{}_{\rho\sigma} + \epsilon_{\rho\sigma\lambda\kappa}T^{\mu,\lambda\kappa}+A_{[\rho}\delta^\mu_{\nu]},
+%% \end{equation}
+%% where ${\Gamma}^\mu{}_{\rho\sigma}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying \mbox{$T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$} and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$.
+Since no metric is present  the epsilon symbols are not related by raising (lowering) their indices, but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}
+%% \begin{widetext}
+%% Using the above decomposition, the most general (power-counting renormalizable) action preserving diffeomorphisms is~\footnote{We have dropped all terms which can be related to those in Eq.~\eqref{4dfull} through a boundary term.}
+%%   \begin{dmath}
+%%     \label{4dfull}
+%%     S[{\Gamma},T,A] =
+%%     \int\dn{4}{x}\Bigg[
+%%       B_1\, R_{\mu\nu}{}^{\mu}{}_{\rho} T^{\nu,\alpha\beta}T^{\rho,\gamma\delta}\epsilon_{\alpha\beta\gamma\delta}
+%%       +B_2\, R_{\mu\nu}{}^{\sigma}{}_\rho T^{\beta,\mu\nu}T^{\rho,\gamma\delta}\epsilon_{\sigma\beta\gamma\delta}
+%%       +B_3\, R_{\mu\nu}{}^{\mu}{}_{\rho} T^{\nu,\rho\sigma}A_\sigma
+%%       +B_4\, R_{\mu\nu}{}^{\sigma}{}_\rho T^{\rho,\mu\nu}A_\sigma
+%%       +B_5\, R_{\mu\nu}{}^{\rho}{}_\rho T^{\sigma,\mu\nu}A_\sigma
+%%       +C_1\, R_{\mu\rho}{}^{\mu}{}_\nu \nabla_\sigma T^{\nu,\rho\sigma}
+%%       +C_2\, R_{\mu\nu}{}^{\rho}{}_\rho \nabla_\sigma T^{\sigma,\mu\nu} 
+%%       +D_1\, T^{\alpha,\mu\nu}T^{\beta,\rho\sigma}\nabla_\gamma T^{(\lambda, \kappa) \gamma}\epsilon_{\beta\mu\nu\lambda}\epsilon_{\alpha\rho\sigma\kappa}
+%%       +D_2\,T^{\alpha,\mu\nu}T^{\lambda,\beta\gamma}\nabla_\lambda T^{\delta,\rho\sigma}\epsilon_{\alpha\beta\gamma\delta}\epsilon_{\mu\nu\rho\sigma}
+%%       +D_3\,T^{\mu,\alpha\beta}T^{\lambda,\nu\gamma}\nabla_\lambda T^{\delta,\rho\sigma}\epsilon_{\alpha\beta\gamma\delta}\epsilon_{\mu\nu\rho\sigma}
+%%       +D_4\,T^{\lambda,\mu\nu}T^{\kappa,\rho\sigma}\nabla_{(\lambda} A_{\kappa)} \epsilon_{\mu\nu\rho\sigma}
+%%       +D_5\,T^{\lambda,\mu\nu}\nabla_{[\lambda}T^{\kappa,\rho\sigma} A_{\kappa]} \epsilon_{\mu\nu\rho\sigma}
+%%       +D_6\,T^{\lambda,\mu\nu}A_\nu\nabla_{(\lambda} A_{\mu)}
+%%       +D_7\,T^{\lambda,\mu\nu}A_\lambda\nabla_{[\mu} A_{\nu]} 
+%%       +E_1\,\nabla_{(\rho} T^{\rho,\mu\nu}\nabla_{\sigma)} T^{\sigma,\lambda\kappa}\epsilon_{\mu\nu\lambda\kappa}
+%%       +E_2\,\nabla_{(\lambda} T^{\lambda,\mu\nu}\nabla_{\mu)} A_\nu
+%%       +T^{\alpha,\beta\gamma}T^{\delta,\eta\kappa}T^{\lambda,\mu\nu}T^{\rho,\sigma\tau}
+%%       \Big(F_1\,\epsilon_{\beta\gamma\eta\kappa}\epsilon_{\alpha\rho\mu\nu}\epsilon_{\delta\lambda\sigma\tau}
+%%       +F_2\,\epsilon_{\beta\lambda\eta\kappa}\epsilon_{\gamma\rho\mu\nu}\epsilon_{\alpha\delta\sigma\tau}\Big) 
+%%       +F_3\, T^{\rho,\alpha\beta}T^{\gamma,\mu\nu}T^{\lambda,\sigma\tau}A_\tau \epsilon_{\alpha\beta\gamma\lambda}\epsilon_{\mu\nu\rho\sigma}
+%%       +F_4\,T^{\eta,\alpha\beta}T^{\kappa,\gamma\delta}A_\eta A_\kappa\epsilon_{\alpha\beta\gamma\delta}\Bigg].
+%%   \end{dmath}
+%% \end{widetext}
+%% Although there is no obvious equivalence between the action in Eq.~\eqref{4dfull} and General Relativity, particularly due to the lack of a source metric field, we analyzed in Ref.~\cite{Skirzewski:2014eta} the scalar perturbations and studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
+In the rest of this section we summarize the procedure which leads to the Newtonian limit of the model.
+
+%% First, we considered a static, homogeneous, and isotropic expansion of fields,
+%% \begin{align}
+%%   A_\mu &= \delta_\mu^0 A + a_\mu,\\
+%%   T^{\mu,\nu\rho} &= \delta^{\mu}_m\delta^{\nu\rho}_{m0}T + t^{\mu,\nu\rho},\\
+%%   %\shortintertext{and}
+%%   \Gamma^\lambda{}_{\mu\nu} &= E \delta^\lambda_0 \delta^m_\mu \delta^m_\nu + F \delta^\lambda_m \delta^m_{(\mu}\delta^0_{\nu)} + G\delta^\lambda_0 \delta^0_{\mu}\delta^0_{\nu} + \gamma^\lambda{}_{\mu\nu},
+%%   \label{GammaExp}
+%% \end{align}
+%% with $\delta^{\mu\nu}_{\lambda\kappa}=\delta^{\mu}_{\lambda}\delta^{\nu}_{\kappa}-\delta^{\mu}_{\kappa}\delta^{\nu}_{\lambda}$.
+Next, by analysing the first order perturbations of the actions, we found a choice of the coupling constants which allow nontrivial solutions of these field equations, together with the non-relativistic limit of the geodesic equation.
+Then, we substitute the field components by their their scalar perturbation decomposition,
+%% \begin{equation}
+%%   a_\mu \to \delta_\mu^0 a+\delta_\mu^m \partial_{m}a_L,
+%% \end{equation}
+%% \begin{equation}
+%%   \begin{split}
+%%     t^{\mu,\nu\rho} &\to \delta^{\mu}_m\delta^{\nu\rho}_{n0} \Big(t \delta^{m n} + \partial^m \partial^n t_L \Big)
+%%     +\delta^{\mu}_0 \delta^{\nu\rho}_{m0} \partial^m c_L
+%%     \\
+%%     & \quad + \Big(\delta^{\mu}_0\delta^{\nu\rho}_{mn}-\delta^{\mu}_m\delta^{\nu\rho}_{n0}\Big)\epsilon^{m n p} \partial_{p} b
+%%     \\
+%%     & \quad +\delta^{\mu}_m \delta^{\nu}_{n} \delta^{\rho}_{p} \Big(\epsilon^{n p q}\partial_q \partial^m d_1 +  (\delta^{m n} \partial^p - \delta^{m p} \partial^n)d_2\Big)
+%%   \end{split}
+%% \end{equation}
+%% and
+%% \begin{equation}
+%%   \begin{split}
+%%     \gamma^\lambda_{\mu\nu}
+%%     &\to
+%%     \delta^\lambda_0\delta^0_\mu\delta^0_\nu u 
+%%     + \delta^\lambda_m \delta^0_\mu\delta^0_\nu \partial^m v_L
+%%     + 2\delta^\lambda_0 \delta^0_{(\mu}\delta^m_{\nu)} \partial_m w_L
+%%     \\
+%%     & \quad + \delta^\lambda_0 \delta^m_\mu\delta^n_\nu \Big(x \delta_{mn} + \partial_m \partial_n x_L\Big)
+%%     \\
+%%     & \quad + 2\delta^\lambda_m \delta^0_{(\mu}\delta^n_{\nu)} \Big(y_1 \delta^m{}_n + \epsilon^{m p}{}_{n} \partial_p y_2 + \partial^m \partial_n y_L\Big)
+%%     \\
+%%     & \quad + \delta^\lambda_m \delta^n_{\mu}\delta^p_{\nu} \Big(\delta_{n p} \partial^m z_1 + (\delta^m{}_n \partial_p+\delta^m{}_p \partial_n) z_2
+%%     \\
+%%     & \qquad +  (\epsilon^{m q}{}_n \partial_p+\epsilon^{m q}{}_p \partial_n) \partial_q z_3 + \partial^m \partial_n \partial_p z_L\Big),
+%%   \end{split}
+%% \end{equation}
+%% where the ``L'' sub-index identifies the longitudinal degrees of freedom.
+
+%% %% In the non-relativistic (low-momentum) limit, the geodesic deviation of inertial observers is also discussed.
+
+%% %% Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
+%% Albeit the inclusion of matter in a nonmetric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general $\binom{2}{0}$-type symmetric tensor density, $\mathfrak{g}^{\mu \nu}$, constructed with at most quadratic terms in the available fields.
+A simple \emph{dimensional analysis} shows that this tensor density contains the same terms as what we call the ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.
+However, for the simple case of the Einstein--Hilbert action, it is in fact the inverse metric density.}, defined as the variation of the action with respect to the symmetric part of the Ricci tensor~(see Refs.~\cite{Eddington1923math,schrodinger1950space,Poplawski:2012bw}), i.e.,%% \hl{JZ: def.
+$R_{(\mu\nu)}$}
+%% \begin{equation}
+%%   \label{metric}
+%%   \frac{\delta\ }{\delta R_{(\mu\nu)}} S[\Gamma] \equiv \sqrt{\mathsf{g}} \, \mathsf{g}^{\mu\nu} = \bar{g}^{\mu\nu}.
+%% \end{equation}
+%% %% by assuming a matter action that depends on $\bar{g}^{\mu\nu}$.
+
+%% From the geodesic equations and the linearized action on scalar perturbation, we found that only a few terms in the scalar perturbation affect the geodesic equation~\footnote{We cross-check our result using the software Cadabra~\cite{Peeters2007550,peeters2007symbolic,Peeters:2007wn}.}.
+The effective geodesic deviation is given by
+%% \begin{equation}
+%%   \label{NewtonPot}
+%%   \Gamma^i{}_{00} = - \frac{1}{8\pi} \frac{ \partial\mathcal{L}_{\text{Matter}} }{ \partial \mathfrak{g}^{00} } \, \nabla^i \left(\frac{1}{|\vec{x}|}\right),
+%% \end{equation}
+%% is the usual Newtonian force induced by a massive source.
+
+%% \section{\label{rlimit}Relativistic limit}
+%% %%%%%%%%% COMPARISON GR %%%%%%%%%
+%% Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, the post-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
+Therefore, we should go beyond the Newtonian limit in order to compare our model with General Relativity.
+
+%% %%\hl{A comparison between our affine model and GR requires the imposition of vanishing torsion (JZ: Why?).}
+%% Even though a comparison between the models does not require the imposition of vanishing torsion, for the sake of simplicity, at this stage we shall focus on a sector of the theory in which the connection is torsion-free.
+Notice that the vanishing torsion limit ---equivalent to take $T^{\lambda,\mu\nu} \to 0$ and $A_\mu \to 0$--- cannot be taken at the action level, and should be taken in the field equations.
+Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements.
+Since only the terms of the action linear in these fields will be relevant, one can consider the effective action linear in the torsion's fields, i.e.,
+%% \begin{equation}
+%%   %\label{eff-action}
+%%   S_{\text{eff}} = \int\dn{4}{x} \Big( C_1\, R_{\lambda\mu}{}^{\lambda}{}_\nu \nabla_\rho %T^{\nu,\rho\sigma}
+%%   + C_2 \, R_{\mu\rho}{}^{\lambda}{}_\lambda \nabla_\nu \Big) T^{\nu,\mu\rho} ,
+%% \end{equation}
+%% and the only nontrivial field equation after the limit will be the one for the Curtright, $T^{\nu,\mu\rho}$,
+%% \begin{equation}
+%%   \nab{[\rho} R_{\mu]\nu} + \kappa \nab{\nu} R_{\mu\rho}{}^\lambda{}_\lambda = 0,
+%% \end{equation}
+%% with $\kappa$ a constant related with the original couplings of the model.
+We assume that the connection is compatible with volume form, i.e., it is equi-affine~\cite{nomizu1994affine,MO-Bryant02}.
+The equi-affine condition assures that the Ricci tensor of the connection is symmetric, and the contraction of the last indices vanishes, thus the second term in the field equation is absent and the gravitational equations are
+%% \begin{equation}
+%%   \nab{[\rho} R_{\mu]\nu} = 0.
+%%   \label{SimpleEOM}
+%% \end{equation}
+
+%% Equation~\eqref{SimpleEOM} is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature ---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.}  All Einstein manifolds, whose Ricci tensor is proportional to the metric, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition due to the metricity condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
+Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from General Relativity are present in the chosen scenario of our model.
+As an additional comment, the parallel Ricci curvature assures that although the manifold is not in general a Einstein manifold, the metric has to be locally a product of Einstein metrics~\cite{Besse}.
+
+%% %% A corollary is that all Einstein manifolds, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
+Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from GR are present in the chosen scenario of our model.
+
+%% %%Additionally, for a Riemannian manifold $(\Mi,g)$ the condition in Eq.~\eqref{SimpleEOM} is equivalent to the following statements (see Ref.~\cite{Derdzinski:1985,Besse}): (i) the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}, (ii) the manifold has harmonic curvature~\cite{bourguignon1981varietes}, i.e.
+\mbox{$\nabla^\mu R_{\mu\nu}{}^\lambda{}_\rho = 0$,} and (iii) in the four-dimensional case the manifold has harmonic Weyl tensor~\cite{Berger:1969} and constant scalar curvature.
+
+%% The Eq.~\eqref{SimpleEOM} is related through the second Bianchi identity to the harmonic curvature condition~\cite{bourguignon1981varietes},
+%% \begin{equation}
+%%   \label{harm-curv}
+%%   \nabla_\lambda R_{\mu\nu}{}^\lambda{}_\rho = 0,
+%% \end{equation}
+%% and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor and constant scalar curvature~\cite{Berger:1969}, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}.
+For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.
+
+%% %% Equations~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
+%% Notice that Eqs.~\eqref{SimpleEOM} and~\eqref{harm-curv} accept a geometrical interpretation equivalent to that of the field equations of a pure Yang--Mills theory, which in the language of differential forms are
+%% \begin{align}
+%%   \df \Ff*[2] &= 0, & \df \st \Ff*[2] &= 0,
+%% \end{align}
+%% where $\Ff*[2]$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle), and the operator $\st$ denotes the Hodge star.
+Now, these Yang--Mills field equations are obtained from the well-known action functional
+%% \begin{equation}
+%%   S_{\textsc{ym}} = \int \Tr \Big( \Ff*[2] \st \Ff*[2] \Big).
+%% \end{equation}
+
+%% Interestingly, the Eq.~\eqref{SimpleEOM} ---equivalently Eq.~\eqref{harm-curv}--- can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, %constructed as the trace of the
+%% \begin{equation}
+%%   \label{SKY}
+%%   S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \st \Rif{}{} \right) = \int \left( \Rif{a}{b} \st \Rif{b}{a} \right),
+%% \end{equation}
+%% where $\Rif{}{} \in \Omega^2(\Mi, T^*\Mi \otimes T\Mi)$ is the curvature two-form, the operator $\st$ denotes the Hodge star, and the trace is taken on the bundle indices (see Ref.~\cite{bourguignon1982yang}).
+
+The gravitational model described by the action in Eq.~\eqref{SKY} is called Stephenson--Kilmister--Yang (or SKY for short).
+However, the standard interpretation of this model requires a metric tensor.
+Therefore, a quick analysis of the field equations \`a la Palatini shows that the field equation
+
 Albeit this effective theory has been widely studied, it has been considered as a model for a metric field instead of a theory for the connection.

### 2015-10-20 AffGR-PRD.tex
Cleaning up

--- 2015-08-03 AffGR-PRD.tex
@@
 \end{equation}
-and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor~\cite{Berger:1969} and constant scalar curvature, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}.
+and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor and constant scalar curvature~\cite{Berger:1969}, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}.
 For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.
 
-Equations.~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
-Interestingly, the Eq.~\eqref{SimpleEOM} can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974},
+%% Equations~\eqref{SimpleEOM} and~\eqref{harm-curv} are geometrically equivalent to the 
+Notice that Eqs.~\eqref{SimpleEOM} and~\eqref{harm-curv} accept a geometrical interpretation equivalent to that of the field equations of a pure Yang--Mills theory, which in the language of differential forms are
+\begin{align}
+  \df \Ff*[2] &= 0, & \df \st \Ff*[2] &= 0,
+\end{align}
+where $\Ff*[2]$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle), and the operator $\st$ denotes the Hodge star.
+Now, these Yang--Mills field equations are obtained from the well-known action functional
 \begin{equation}
-  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \we \st \Rif{}{} \right),
+  S_{\textsc{ym}} = \int \Tr \Big( \Ff*[2] \st \Ff*[2] \Big).
+\end{equation}
+
+Interestingly, the Eq.~\eqref{SimpleEOM} ---equivalently Eq.~\eqref{harm-curv}--- can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, %constructed as the trace of the
+\begin{equation}
+  \label{SKY}
+  S_{\textsc{ym}} = \int \Tr \left( \Rif{}{} \st \Rif{}{} \right) = \int \left( \Rif{a}{b} \st \Rif{b}{a} \right),
 \end{equation}
 where $\Rif{}{} \in \Omega^2(\Mi, T^*\Mi \otimes T\Mi)$ is the curvature two-form, the operator $\st$ denotes the Hodge star, and the trace is taken on the bundle indices (see Ref.~\cite{bourguignon1982yang}).
+
+The gravitational model described by the action in Eq.~\eqref{SKY} is called Stephenson--Kilmister--Yang (or SKY for short).
+However, the standard interpretation of this model requires a metric tensor.
+Therefore, a quick analysis of the field equations \`a la Palatini shows that the field equation
+
 Albeit this effective theory has been widely studied, it has been considered as a model for a metric field instead of a theory for the connection.

### 2015-10-21 AffGR-PRD.tex
Reviewed until Eq. (14)

@@
-\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint]{revtex4-1}
+\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint,longbibliography]{revtex4-1}
 
@@
   We show that the effective field equations for a recently formulated polynomial affine model of gravity, in the sector of a torsion-free connection, accept general Einstein manifolds ---with or without cosmological constant--- as solutions.
-Moreover, these effective field equations coincide with those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
+Moreover, these effective field equations coincide with some of those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
 Additionally, we find a generalization of a minimally coupled massless scalar field in General Relativity with a ``minimally'' coupled scalar field in this affine model.
+Finally, we present a naive analysis of the propagators of the gravitational theory, an their relation with the presence of ghost in the model.
 \end{abstract}
@@
 One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
-On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba}.
+On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
 
@@
 
-Therefore, under the premises of incompleteness and non-polynomial structure of the theory, 
 %%%%%%%%% THE MODEL %%%%%%%%%
-in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance, and restricting ourselves to consider only naive power-counting renormalizable terms (which by no means guarantees the renormalizability of the system).
+In order to undertake the premises of incompleteness and non-polynomial structure of the theory, in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance.
+Worth to mention that the most general action built this way contains only power-counting renormalizable terms (which by no means guarantees the renormalizability of the system).
 We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravitational potential, despite the existence of torsion.
@@
 \begin{widetext}
-Using the above decomposition, the most general (power-counting renormalizable) action preserving diffeomorphisms is~\footnote{We have dropped all terms which can be related to those in Eq.~\eqref{4dfull} through a boundary term.}
+Using the above decomposition, the most general action preserving diffeomorphisms is
   \begin{dmath}
@@
 \end{widetext}
+In Eq.~\eqref{4dfull}, we have dropped all terms which can be related through partial integration, and those which are topological invariant.
+A straightforward dimensional counting shows the impossibility of other contributions in to the action, \hl{see Appendix ...}.
+Interestingly, the above action turns to be power-counting renormalizable, which does not guarantees renormalizability but is a good signal.
+The structure of the model yields no three-point graviton vertices, which might allow to overcome  the no-go theorems found in Refs.~\cite{McGady:2013sga,Camanho:2014apa}.
+It is worth mentioning that all coupling constants are dimensionless, which might be a hint of conformal invariance of the model~\cite{Buchholz:1976hz}.
+
 Although there is no obvious equivalence between the action in Eq.~\eqref{4dfull} and General Relativity, particularly due to the lack of a source metric field, we analyzed in Ref.~\cite{Skirzewski:2014eta} the scalar perturbations and studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
@@
 \end{equation}
-is the usual Newtonian force induced by a massive source.
+is the usual Newtonian force induced by a massive source. Notice that we restricted ourselves to consider $\mathfrak{g}^{\mu \nu} = \bar{g}^{\mu\nu}$ to obtain the above result.
 
@@
 %%%%%%%%% COMPARISON GR %%%%%%%%%
-Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, the post-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
+Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, a beyond-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
 Therefore, we should go beyond the Newtonian limit in order to compare our model with General Relativity.
@@
 Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements.
-Since only the terms of the action linear in these fields will be relevant, one can consider the effective action linear in the torsion's fields, i.e.,
+It can be realized as follows, since only the terms of the action linear in these fields will be relevant, one can consider the effective action linear in the torsion's fields, i.e.,
 \begin{equation}
@@
 Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from General Relativity are present in the chosen scenario of our model.
-As an additional comment, the parallel Ricci curvature assures that although the manifold is not in general a Einstein manifold, the metric has to be locally a product of Einstein metrics~\cite{Besse}.
+An additional comment, the parallel Ricci curvature assures that although the manifold is not Einstein in general, the metric has to be locally a product of Einstein metrics~\cite{Besse}.
 

### 2015-10-22 AffGR-PRD.tex
Sec III updated

@@
 \begin{align}
-  \df \Ff*[2] &= 0, & \df \st \Ff*[2] &= 0,
+  \cdf \Ff*[2] &= 0, & \cdf \st \Ff*[2] &= 0,
 \end{align}
-where $\Ff*[2]$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle), and the operator $\st$ denotes the Hodge star.
-Now, these Yang--Mills field equations are obtained from the well-known action functional
+where $\Ff*[2] = \cdf \Af*[1]$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle, see for example Ref.~\cite{bourguignon1982yang,Nakahara}), and the operator $\st$ denotes the Hodge star.
+Now, these Yang--Mills field equations are obtained from the variation of the action functional
 \begin{equation}
-  S_{\textsc{ym}} = \int \Tr \Big( \Ff*[2] \st \Ff*[2] \Big).
+  S_{\textsc{ym}} = \int \Tr \Big( \Ff*[2] \st \Ff*[2] \Big),
 \end{equation}
+and the Jacobi identity for the covariant derivative.
 
@@
 However, the standard interpretation of this model requires a metric tensor.
-Therefore, a quick analysis of the field equations \`a la Palatini shows that the field equation
+A quick analysis of the field equations \`a la Palatini shows that Eqs.~\eqref{SimpleEOM} and~\eqref{harm-curv} are obtained only from the variation with respect to the connection.
+Albeit this effective theory has been widely studied, the extra field equation (for the metric field) strongly constraints the solutions of the gravitational Yang--Mills~\footnote{We thank J.~Zanelli for sharing his personal communications with C.~N.~Yang, and clarify this aspect of the effective model.}.
+However, that complication does not affect our affine interpretation of the theory, where the metric is absent.
 
-Albeit this effective theory has been widely studied, it has been considered as a model for a metric field instead of a theory for the connection.
-Therefore, within the formalism of Palatini, besides Eq.~\eqref{SimpleEOM} an extra field equation appears (for the vielbein field), which strongly constraints the solutions of the gravitational Yang--Mills~\footnote{We thank J.~Zanelli for sharing his personal communications with C.~N.~Yang, and clarify this aspect of the effective model.}.
-Intriguingly, this effective theory is not renormalizable ---according to the arguments in Refs.~\cite{McGady:2013sga,Camanho:2014apa}---, although it has been discussed in Ref.~\cite{Chen:2010at} that at least the ghost problem can be avoided through the arguments exposed in Refs.~\cite{Kleinert:1987eb,Bender:2007wu,Bender:2008vh,Mannheim:2009zj}.
+Intriguingly, the effective theory is not renormalizable ---according to the arguments in Refs.~\cite{McGady:2013sga,Camanho:2014apa}---, although it has been discussed in Ref.~\cite{Chen:2010at} that at least the ghost problem can be avoided through the arguments exposed in Refs.~\cite{Kleinert:1987eb,Bender:2007wu,Bender:2008vh,Mannheim:2009zj}.
 

### 2015-10-27 AffGR-PRD.tex
Appendix: dimensional analysis (mid)
Starting the propagator analysis

@@
 \begin{align}
-  A_\mu &= \delta_\mu^0 A + a_\mu,\\
-  T^{\mu,\nu\rho} &= \delta^{\mu}_m\delta^{\nu\rho}_{m0}T + t^{\mu,\nu\rho},\\
-  %\shortintertext{and}
-  \Gamma^\lambda{}_{\mu\nu} &= E \delta^\lambda_0 \delta^m_\mu \delta^m_\nu + F \delta^\lambda_m \delta^m_{(\mu}\delta^0_{\nu)} + G\delta^\lambda_0 \delta^0_{\mu}\delta^0_{\nu} + \gamma^\lambda{}_{\mu\nu},
-  \label{GammaExp}
+  A_\mu &= \delta_\mu^0 A + a_\mu, \notag \\
+  T^{\mu,\nu\rho} &= \delta^{\mu}_m\delta^{\nu\rho}_{m0}T + t^{\mu,\nu\rho},
+  \label{GammaExp} \\
+  \Gamma^\lambda{}_{\mu\nu} &= E \delta^\lambda_0 \delta^m_\mu \delta^m_\nu + F \delta^\lambda_m \delta^m_{(\mu}\delta^0_{\nu)} + G\delta^\lambda_0 \delta^0_{\mu}\delta^0_{\nu} + \gamma^\lambda{}_{\mu\nu}, \notag
 \end{align}
@@
 
+%%%%%%%%% Propagators %%%%%%%%%
+\section{Analysis of propagators}
+
+A first step toward the analysis of renormalizability of the model should be the computation of the free propagators of the model around a given background.
+The choice of background will necessarily be taken in order to simplify the computations.
+Our first task is to expand up to second order in the fields around a flat background.
+Under these assumptions, and using the notation of Eqs.~\eqref{GammaExp}, the relevant part of the action~\eqref{4dfull} is
+\begin{widetext}
+  \begin{dmath}[compact, spread=2pt]
+    \label{4dflatx}
+    S[\gamma,t,a] =
+    \int\dn{4}{x} \bigg[
+      C_1 \partial_{\mu}\gamma^{\mu}{}_{\rho\nu} \partial_\sigma t^{\nu\rho\sigma}
+      +2 C_2 \partial_{\mu}\gamma^{\rho}{}_{\nu\rho} \partial_\sigma t^{\sigma\mu\nu}
+      + E_1 \partial_{(\rho}t^{\rho\mu\nu}\partial_{\sigma)}t^{\sigma\lambda\kappa}\epsilon_{\mu\nu\lambda\kappa}
+      + E_2 \partial_{(\lambda} t^{\lambda\mu\nu}\partial_{\mu)} a_\nu
+      \bigg].
+  \end{dmath}
+\end{widetext}
+In momentum space, the second order perturbation is
+\begin{dmath}[compact, spread=2pt]
+  \label{4dflat}
+  S =
+  \int\dn{4}{p}\bigg[
+    C_1 p_{\mu} p_\sigma\tilde\gamma^{\mu}{}_{\rho\nu}^* \tilde t^{\nu\rho\sigma}
+    + 2 C_2 p_{\mu} p_\sigma\tilde\gamma^{\rho}{}_{\nu\rho}^* \tilde t^{\sigma\mu\nu}
+    + E_1 p_{\rho} p_{\sigma} \tilde t^{\rho\mu\nu}{}^*\tilde t^{\sigma\lambda\kappa} \epsilon_{\mu\nu\lambda\kappa}
+    + E_2 p_{\lambda} p_{\mu} \tilde t^{\lambda\mu\nu}{}^* \tilde a_\nu
+    \bigg].
+\end{dmath}
+Longitudinal and transverse projectors can be introduced in order to decompose the action and specify in a more standard fashion the dynamics of Eq.~\eqref{4dflat}.
+This can be done since we have the metric $\eta_{\mu\nu}$ compatible with the connection and $p^\mu = \eta^{\mu\nu}p_\nu$.
+We define the projector into logitudinal vectors $P_{\texttt{L}}{}^\mu_\nu = \tfrac{1}{p^2}p^\mu p_\nu $, such that $$A_{\texttt{L}\mu} = P_{\texttt{L}}{}^\nu_\mu \, A_\nu = A_{\texttt{L}}{}p_{\mu},$$ where $A_{\texttt{L}}=\tfrac{1}{p^2} p^\mu A_\mu$.
+Similarly, $P_\perp{}^\mu_\nu=\delta^\mu_\nu -P_{\texttt{L}}{}^\mu_\nu$ defines the projector into transverse vectors, i.e., $A_{\perp \mu}=P_{\perp}{}_\mu^\nu A_\nu$.
+Thus,
+\begin{dmath}
+  \label{transversea}
+  \tilde a_\nu=a_\perp{}_{\nu}+a_{\texttt{L}} p_\nu,
+\end{dmath}
+\begin{dmath}
+  \label{transverset}
+  \tilde t^{\lambda\mu\nu}=\frac{1}{p}\epsilon^{\mu\nu\kappa\rho}p_\rho t_\perp^{\lambda}{}_\kappa+\frac{1}{p^2}p^\lambda\epsilon^{\mu\nu\kappa\rho}p_\rho t_{\texttt{a}\kappa}-\frac{2}{p^2}p^{[\mu}\epsilon^{\nu]\lambda\kappa\rho}p_\rho t_{\texttt{a}\kappa}+\frac{2}{p}p^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+\frac{2}{p^2}p^\lambda p^{[\mu} t_{\texttt{v}}^{\nu]},
+\end{dmath}
+\begin{dmath}
+  \label{transversegamma}
+  \tilde \gamma^{\lambda}{}_{\mu\nu}=\gamma_\perp^{\lambda}{}_{\mu\nu}+\frac{1}{p}p^\lambda \gamma_{\texttt{s}}{}_{\mu\nu}+\frac{2}{p}p_{(\mu} \gamma^\lambda{}_{\nu)}+\frac{2}{p^2}p^\lambda p_{(\mu} \gamma_{\texttt{v}}{}_{\nu)}+ \frac{1}{p^2}p_{\mu} p_{\nu} \gamma'_{\texttt{v}}{}^\lambda+\frac{1}{p^3}p^\lambda p_{\mu} p_{\nu} \gamma_{\texttt{L}},
+\end{dmath}
+where all the indices are transverse except those of the momentum $p_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the subindices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation.
+In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless.
+Additionally, we could separate the fields into irreducible representations by projecting them into their traceless part and other lower dimensional tensor representations.
+In the meanwhile we shall not do this expansion.
+\begin{widetext}
+  Using Eqs.~\eqref{transversea}, \eqref{transverset} and~\eqref{transversegamma}, the action~\eqref{4dflat} is then rewritten
+  \begin{dmath}
+    \label{4dtransverse}
+    S =
+    \int\dn{4}{p}p^2
+    \bigg[
+      2C_1 \hat{p}_\mu \hat{p}_\sigma\Big(\gamma_\perp^{\mu}{}_{\rho\nu}+\hat{p}^\mu \gamma_{\texttt{s}}{}_{\rho\nu}+2\hat{p}_{(\rho} \gamma^\mu{}_{\nu)}+2\hat{p}^\mu \hat{p}_{(\rho} \gamma_{\texttt{v}}{}_{\nu)}+ \hat{p}_{\rho} \hat{p}_{\nu} \gamma'_{\texttt{v}}{}^\mu+\hat{p}^\mu \hat{p}_{\rho} \hat{p}_{\nu} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\rho\sigma\delta\eta}\hat{p}_\eta t_\perp^{\nu}{}_\delta+\hat{p}^\nu t_{\texttt{a}}^{\rho\sigma}-2\hat{p}^{[\rho} t_{\texttt{a}}^{\sigma]\nu}+2\hat{p}^{[\rho} t_{\texttt{s}}^{\sigma]\nu}+2\hat{p}^\nu \hat{p}^{[\rho} t_{\texttt{v}}^{\sigma]}\Big)
+      +2C_2 \hat{p}_{\mu} \hat{p}_\sigma\Big(\gamma_\perp^{\rho}{}_{\nu\rho}+\hat{p}^\rho \gamma_{\texttt{s}}{}_{\nu\rho}+2\hat{p}_{(\nu} \gamma^\rho{}_{\rho)}+2\hat{p}^\rho \hat{p}_{(\nu} \gamma_{\texttt{v}}{}_{\rho)}+\hat{p}_{\nu} \hat{p}_{\rho} \gamma'_{\texttt{v}}{}^\rho +\hat{p}^\rho \hat{p}_{\nu} \hat{p}_{\rho} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\kappa+\hat{p}^\sigma t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\sigma}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\sigma}+2\hat{p}^\sigma \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)
+      +E_1 \hat{p}_{\rho} \hat{p}_{\sigma}\Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\rho}{}_\kappa+\hat{p}^\rho t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{\mu} t_{\texttt{a}}^{\nu\rho}+2\hat{p}^{\mu} t_{\texttt{s}}^{\nu\rho}+2\hat{p}^\rho \hat{p}^{\mu} t_{\texttt{v}}^{\nu}\Big)^*\Big(\epsilon^{\lambda\kappa\delta\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\delta+\hat{p}^\sigma t_{\texttt{a}}^{\lambda\kappa}-2\hat{p}^{\lambda} t_{\texttt{a}}^{\kappa\sigma}+2\hat{p}^{\lambda} t_{\texttt{s}}^{\kappa\sigma}+2\hat{p}^\sigma \hat{p}^{\lambda} t_{\texttt{v}}^{\kappa}\Big)\epsilon_{\mu\nu\lambda\kappa}
+      +E_2 \hat{p}_{\lambda} \hat{p}_{\mu} \Big(\epsilon^{\mu\nu\kappa\rho}\hat{p}_\rho t_\perp^{\lambda}{}_\kappa+\hat{p}^\lambda t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\lambda}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+2\hat{p}^\lambda \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)^*\Big(a_\perp{}_\nu+\hat{p}_\nu a_{\texttt{L}}\Big)
+      \bigg],
+  \end{dmath}
+\end{widetext}
+simplifiying
+\begin{dmath}
+  \label{WithGhosts}
+  S=\int d^4p\Bigg[-2C_1 p^2\gamma_{\texttt{s}\mu\nu}^*t_{\texttt{s}}^{\mu\nu}
+    +p^2\Big((-2C_1+2C_2)\gamma_{\texttt{v}\mu}+2C_2\gamma_{\perp\mu\nu}^\nu
+    +8E_1t_{\texttt{a}\mu}+E_2a_{\perp\mu}\Big)^*t_{\texttt{v}}^\mu
+    \Bigg]
+\end{dmath}
+
+%%%%%%%%% Conclusions %%%%%%%%%
 \section{\label{conclusions}Conclusions}
@@
 
+\appendix
+
+\input{DA.tex}
+
 %%%%%%%%% BIBLIOGRAPHY %%%%%%%%%

### 2015-10-27 AffGR-PRD.tex
More Appendix: Dim. Anal.

@@
 In Eq.~\eqref{4dfull}, we have dropped all terms which can be related through partial integration, and those which are topological invariant.
-A straightforward dimensional counting shows the impossibility of other contributions in to the action, \hl{see Appendix ...}.
+A straightforward dimensional counting shows the impossibility of other contributions in to the action, see Appendix~\ref{DA}.
 Interestingly, the above action turns to be power-counting renormalizable, which does not guarantees renormalizability but is a good signal.
@@
 The theory does not require a spacetime metric, but instead we should consider the most general $\binom{2}{0}$-tensor density, $\mathfrak{g}^{\mu\nu}$,  built with the available fields, and use it to build Lagrangian densities for the matter content.
-Following our precept, the matter content ---scalar matter--- should couple to $\mathfrak{g}^{\mu\nu}$, given by %% which for Eq.~\eqref{4dfull} is
+Following our precept, the matter content ---scalar matter--- should couple to $\mathfrak{g}^{\mu\nu}$, given by
 \begin{dmath}
   \mathfrak{g}^{\mu\nu} = \alpha \, \nabla_\lambda T^{\mu,\nu\lambda} + \beta \, A_\lambda T^{\mu,\nu\lambda} + \gamma \, \epsilon_{\lambda\kappa\rho\sigma} T^{\mu, \lambda\kappa} T^{\nu, \rho\sigma},
+  \label{geng}
 \end{dmath}

### 2015-11-03 DA.tex
Commiting the appendices

\section{\label{DA}Dimensional analysis for building the polynomial affine gravity}

We built the model using six ingredients, a Curtright ($T^{\mu,\nu\lambda}$), a vector ($A_\mu$), the covariant derivative ($\nab{\mu}$), both Levi-Civita tensors ($\epsilon_{\mu\nu\lambda\rho}$ and $\epsilon^{\mu\nu\lambda\rho}$), and the Riemannian curvature ($R_{\mu\nu}{}^\lambda{}_\rho$).

Our interest is in general to build tensor densities. Therefore, we need to account for the number of \emph{free} indices, and weight density of these quantities. Denote by $N(\Phi)$  the operator which count the number (and position) of indices of the field $\Phi$, being positive (negative) for upper (lower) indices. Thus, we have that
\begin{equation*}
  \begin{aligned}
    N( T^{\mu,\nu\lambda} ) &= 3 & N( A_\mu ) &= -1 & N(  \nab{\mu} ) &= -1 \\
    N( \epsilon_{\mu\nu\lambda\rho} ) &= -4 & N( \epsilon^{\mu\nu\lambda\rho} ) &= 4 & N( R_{\mu\nu}{}^\lambda{}_\rho ) &= -2.
  \end{aligned}
\end{equation*}
Then, for a general expression of the form
\begin{equation*}
  T^a A^b \nabla^c {\epsilon_{\dots}}^d {\epsilon^{\dots}}^e R^f,
\end{equation*}
the indices counting yield
\begin{equation}
  N( T^a A^b \nabla^c {\epsilon_{\dots}}^d {\epsilon^{\dots}}^e R^f ) = n,
\end{equation}
with
\begin{equation}
  n = 3a -b -c -4d + 4e -2f.
  \label{ni}
\end{equation}

In the same spirit, we define an operator which counts the weight density,
\begin{equation*}
  \begin{aligned}
    W( T^{\mu,\nu\lambda} ) &= 1 & W( A_\mu ) &= 0 & W(  \nab{\mu} ) &= 0 \\
    W( \epsilon_{\mu\nu\lambda\rho} ) &= -1 & W( \epsilon^{\mu\nu\lambda\rho} ) &= 1 & W( R_{\mu\nu}{}^\lambda{}_\rho ) &= 0.
  \end{aligned}
\end{equation*}
Thus, the weight ($w$) of the general expression above is given by
\begin{equation}
  w = a - d + e.
  \label{wd}
\end{equation}

\subsection{Inverse metric density}

Now, we illustrate the usefulness of the \emph{dimensional analysis} by building the most general symmetric $\binom{2}{0}$-tensor density, which we call the \emph{inverse metric density}. This particular case fixes $n = 2$ and $w = 1$.

One solution of Eq.~\eqref{wd} is $a=1$ with $d=e$, which implies that Eq.~\eqref{ni} is restricted to
\begin{equation*}
  3 - b - c - 2f = 2.
\end{equation*}
It follows that $f=0$, while still there is room to choose either $b=1$ or $c=1$. Notice that, albeit there is an ambiguity in the value of $d$ and $e$, the fact that all other factors are fixed, and the properties of epsilon contractions implies that all terms are equivalent to choose $d=e=0$. Therefore, the only possible terms built with this choice are
\begin{equation}
  T^{\mu,\nu\lambda} A_\lambda \text{ and } \nabla_\lambda T^{\mu,\nu\lambda}.
\end{equation}
No other contraction of indices is allowed due to the symmetry.

Similarly, if one solves Eq.~\eqref{wd} by choosing $e=1$, and $d=a=0$, Eq.~\eqref{ni} yields
\begin{equation*}
  4 - b - c - 2f = 2,
\end{equation*}
which can be solved by $f=1$, $b=2$, $c=2$, or $b=c=1$. However, by construction the last three choices do not yield symmetric tensors, and the first one vanishes due to the first Bianchi identity.

A third option is to solve Eq.~\eqref{wd} with $a=2$, $d=1$ and $e=0$. In this case, Eq.~\eqref{ni} is an identity. Thus, the only term originated this way is 
\begin{equation}
  \epsilon_{\lambda\kappa\rho\sigma} T^{\mu, \lambda\kappa} T^{\nu, \rho\sigma}.
\end{equation}

Finally, one can check that any other choice to solve Eq.~\eqref{wd} make impossible to solve Eq.~\eqref{ni}. Ergo, there is no other term in a symmetric $\binom{2}{0}$-tensor density built up with these fields. Explicitly, this general tensor density is written in Eq.~\eqref{geng}.

\subsection{Lagrangian density}

\begin{table}[t]
  \caption{Possible selection of terms in the Lagrangian density}
  \label{tab:a1}
  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
    \hline
    \multicolumn{3}{|c|}{$a=1$} \\
    \hline
    $b$ & $c$ & $f$ \\
    \hline
    3 & 0 & 0 \\
    2 & 1 & 0 \\
    1 & 2 & 0 \\
    0 & 3 & 0 \\
    1 & 0 & 1 \\
    0 & 1 & 1 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[t]
  \caption{Possible selection of terms in the Lagrangian density}
  \label{tab:e1} 
  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
    \hline
    \multicolumn{3}{|c|}{$e=1$} \\
    \hline
    $b$ & $c$ & $f$ \\
    \hline
    0 & 0 & 2 \\
    2 & 0 & 1 \\
    1 & 1 & 1 \\
    0 & 2 & 1 \\
    0 & 4 & 0 \\
    1 & 3 & 0 \\
    2 & 2 & 0 \\
    3 & 1 & 0 \\
    4 & 0 & 0 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[t]
  \caption{Possible selection of terms in the Lagrangian density}
  \label{tab:a2}  
  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
    \hline
    \multicolumn{3}{|c|}{$a=2$, $d=1$} \\
    \hline
    $b$ & $c$ & $f$ \\
    \hline
    0 & 0 & 1 \\
    2 & 0 & 0 \\
    1 & 1 & 0 \\
    0 & 2 & 0 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[t]
  \caption{Possible selection of terms in the Lagrangian density}
  \label{tab:a3}
  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
    \hline
    \multicolumn{3}{|c|}{$a=3$, $d=2$} \\
    \hline
    $b$ & $c$ & $f$ \\
    \hline
    1 & 0 & 0 \\
    0 & 1 & 0 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[t]
  \caption{Possible selection of terms in the Lagrangian density}
  \label{tab:a4}
  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
    \hline
    \multicolumn{3}{|c|}{$a=4$, $d=3$} \\
    \hline
    $b$ & $c$ & $f$ \\
    \hline
    0 & 0 & 0 \\
    \hline
  \end{tabular}
\end{table}

The work of building up the most general scalar density with our ingredients is as simple as before, but the analysis is much longer. Thus, we will show the procedure with lesser details than before.

First, we are interested in a scalar density, which sets $n = 0$ and $w = 1$ in Eqs.~\eqref{ni} and~\eqref{wd}, i.e.,
\begin{align}
  3a -b -c - 4d +4e - 2f &= 0, \\
  a - d + e &= 1.
\end{align}

A possible solution of Eq~\eqref{wd} is $a=1$ and $d=e$, and such choice allows to consider the possibilities, see Table~\ref{tab:a1}, but only three of them are independent (and nonvanishing). These generate the terms of Eq.~\eqref{4dfull} whose coefficients were called $B_3$, $B_4$, $B_5$, $C_1$, $C_2$, $D_6$ and $D_7$.

If one choose $e=1$ for solving Eq.~\eqref{wd}, see Table~\ref{tab:e1}, all possible solutions for Eq.~\eqref{ni} are either vanishing or yield topological terms.
%%The action in Eq.~\eqref{4dfull} was written up to topological and boundary terms, thus

The case with $a=2$ and $d=1$ gives four possibilities to solve Eq.~\eqref{ni}, see  Table~\ref{tab:a2}, and these choices give the terms the Lagrangian density whose coefficients are $B_1$, $B_2$, $D_4$, $D_5$, $E_1$, $E_2$ and $F_4$.

For $a=3$ and $d=2$ there are only two possible solutions of Eq.~\eqref{ni}, see  Table~\ref{tab:a3}, and these yield the terms of the action with coefficients $D_1$, $D_2$, $D_3$ and $F_3$. And also, the choice $a=4$ and $d=3$ solves the equations, see  Table~\ref{tab:a4}, and yield the terms in the action with coefficients $F_1$ and $F_2$.

Notice that for values $a \ge 5$, it is not possible to solve both Eqs.~\eqref{ni} and~\eqref{wd} simultaneously. Therefore, we conclude that Eq.~\eqref{4dfull} is the most general action built up with these fields.

### 2015-11-03 MS.tex
Commiting the appendices

\section{Known metric solutions to the parallel Ricci equations}

In this Appendix, we will present a brief compendium of known (Riemannian) metric solutions of Eq.~\eqref{SimpleEOM} in four dimensions. None of these workis original ---except the analysis presented as example in Sec.~\ref{Ex:sch}, and can be found in Refs.~\cite{gray1978einstein,derdzinski1980classification,derdzinski1982compact,Derdzinski:1985,Besse}. Additionally, in Ref.~\cite{cahen2000symplectic} \hl{What is this...}

\paragraph{Einstein spaces.---} The simplest example of a manifold with parallel Ricci is a Riemannian Einstein manifols. This example was explained on the main text.

\paragraph{Riemannian products.---} The Riemamian product of manifolds with harmonic curvature.

\paragraph{Conformally flat manifolds.---} These are solutions in four dimensions if their scalar curvature is constant.

\paragraph{Warped products.---} Compact warped products of the form \mbox{$(S^1 \times \bar{M}, \de{t}^2 + f(t) \de{s}^2(\bar{g}) )$,} where $(\bar{M}, \bar{g})$ is an Einstein manifold with positive scalar curvature, $\bar{R} > 0$, and $f$ is a positive function on $S^1$ satisfying the differential equation
\begin{equation}
  \ddot{f} - \frac{1}{3} \bar{R} = c f,
\end{equation}
for a negative constant $c$.

{Twisted} warped products of the form $(\R \times \bar{M} ) / \Z$ have parallel Ricci, if the $\Z$-action on the product metric involves an isometry of $\bar{g}$.

Compact warped products of the form \mbox{$(M_1 \times M_2, f^{2} \cdot (g_1 \times g_2) )$,} where $M_1$ are two dimensional, $M_1$ has constant Gau\ss{}ian curvature, $K_1 < 0$, and $M_2$ is an Einstein manifold with scalar curvature $R_2 = - 2 K_1$ 
\hl{Working here}
%%\paragraph{}

\subsection{Explicit example: Schwarzschild metric, and Birkhoff theorem\label{Ex:sch}}

As a disclaimer, we clarify that the example below is a pseudo-Riemannian manifold.

%%\subsubsection{Schwarzschild metric}

As pointed out, all vacuum solutions of Einstein's equations ---with and without cosmological constant--- satisfy the parallel Ricci condition trivially~\cite{bourguignon1981varietes}. Nonetheless, an important result in General Relativity is the stability of the Schwarzschild metric, known as the Birkhoff theorem~\cite{Jebsen1921,Birkhoff1923,Alexandrow1923,Eisland1925}, which implies that the gravitational collapse of a spherically symmetric astrophysical object cannot emit gravitational radiation.

In this section it will be shown that a static and spherically symmetric metric, which solves the field equations~\eqref{SimpleEOM} is necessarily the $\Lambda$--Schwarzschild metric.

Consider first the simplest metric ansatz, whose line element is
\begin{equation}
  \de{s}^2 = - f(t,r) \de{t}^2 + \frac{ \de{r}^2 }{ f(t,r) } + r^2 \de{\Omega}^2.
  \label{simpleSchw}
\end{equation}
\begin{widetext}
  The nontrivial field equation for the ansatz~\eqref{simpleSchw} are
  \begin{dmath}
    \nabla_{[1} R_{0]0} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) ,
    \label{e100}
  \end{dmath}
  \begin{dmath}
    \nabla_{[1} R_{0]1} = \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) .
    \label{e101}
  \end{dmath}
  \begin{dmath}
    \nabla_{[2} R_{0]2} = r \frac{\partial^2}{\partial t^{}\partial r^{}}f,
    \label{e202}
  \end{dmath}
  \begin{dmath}
    \nabla_{[2} R_{1]2} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg),
    \label{e212}
  \end{dmath}
  \begin{dmath}
    \nabla_{[3} R_{0]3} = r \sin\left({\theta}\right)^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}f,
    \label{e303}
  \end{dmath}
  and
  \begin{dmath}
    \nabla_{[3} R_{1]3} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3}\Bigg) \sin\left({\theta}\right)^{2}.
    \label{e313}
  \end{dmath}
\end{widetext}
Even though four out of the six nontrivial field equations are independent, the system can be solve uniquely. First, Eq.~\eqref{e202} yields $f = T(t) + R(r)$. Then, one notices that Eq.~\eqref{e101} contains a term depending solely on $t$, which implies that $\dot{T}$ vanishes, i.e., $T$ is a constant. From here, Eq.~\eqref{e212} gets simpler enough to be solved and yields, \mbox{$R(r) = 1 - T + \frac{\alpha}{r} + \beta r^2$} or equivalently
\begin{equation}
  f(r) = 1 + \frac{\alpha}{r} + \beta r^2,
  \label{simplef}
\end{equation}
with $\alpha$ and $\beta$ integration constants. Finally, it can be checked that albeit Eq.~\eqref{e100} was not used, it is satisfied by Eq.~\eqref{simplef}.

The above shows that the simplest time-dependent generalization of Schwarzschild metric is not a solution for the field equations of the considered affine model. Unless, the spacetime metric is static and exactly that for a Schwarzschild exterior solution, with or without cosmological constant.

However, if one tries a metric ansatz with two different factors, say
\begin{equation}
  \de{s}^2 = - A(t,r) \de{t}^2 + \frac{ \de{r}^2 }{ B(t,r) } + r^2 \de{\Omega}^2,
  \label{ABmetric}
\end{equation}
the field equations are so complicated, that although hints on the solubility were found ---and yield to Eq.~\eqref{simplef} for both $A$ and $B$---, the uniqueness of the solution is far for been proved. The field equations for the metric~\eqref{ABmetric} are %%shown in Appendix~\ref{app:eqAB}.
\begin{widetext}
  %%  \section{\label{app:eqAB}Field equations for Schwarzschild metric with two factors}
  \begin{dmath}
    \nabla_{[1} R_{0]0} = \frac{1}{4 \, r^{2} B^{3} A^{2}} \Bigg( 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{3} + 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial r^{3}}A + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}B - 6 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}B - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}A + 6 \, {\left(r^{2} A^{2} \frac{\partial}{\partial r^{}}B - r B A^{2}\right)} \frac{\partial}{\partial t^{}}B^{2} - 2 \, {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B + r B^{4} A\right)} \frac{\partial}{\partial r^{}}A^{2} - 2 \, {\left(r^{2} B A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A^{2}\right)} \frac{\partial^2}{\partial t^{2}}B - {\left(r^{2} B^{2} A \frac{\partial^2}{\partial t^{}\partial r^{}}B - 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - {\left(r^{2} B A \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A\right)} \frac{\partial}{\partial t^{}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial^2}{\partial r^{2}}B + 2 \, r B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, B^{4} A^{2} + 3 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial r^{}}A + {\left(3 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A + 4 \, r B^{4} A^{2}\right)} \frac{\partial^2}{\partial r^{2}}A \Bigg),
    \label{eq100}
  \end{dmath}

  \begin{dmath}
    \nabla_{[1} R_{0]1} = \frac{1}{4 \, r^{2} B^{4} A^{3}} \Bigg( 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial t^{}\partial r^{2}}A + r^{2} B^{3} A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial r^{2}}A + 4 \, B^{3} A^{3} \frac{\partial}{\partial t^{}}B + 6 \, r^{2} A^{2} \frac{\partial}{\partial t^{}}B^{3} - 8 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}B + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{3}}B + 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A^{2} - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}A - {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{4} A \frac{\partial^2}{\partial r^{2}}A - 4 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} + 3 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A\right)} \frac{\partial^2}{\partial t^{}\partial r^{}}A \Bigg),
    \label{eq101}
  \end{dmath}

  \begin{dmath}
    \nabla_{[2} R_{0]2} = \frac{1}{2 \, A^{2}} \Bigg( r A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B + r B A \frac{\partial^2}{\partial t^{}\partial r^{}}A + r A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - r B \frac{\partial}{\partial t^{}}A \frac{\partial}{\partial r^{}}A \Bigg),
    \label{eq202}
  \end{dmath}

  \begin{dmath}
    \nabla_{[2} R_{1]2} = \frac{1}{4 \, r B^{2} A^{2}} \Bigg( 2 \, r^{2} B^{2} A^{2} \frac{\partial^2}{\partial r^{2}}B + r^{2} B^{2} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} \frac{\partial}{\partial r^{}}A^{2} + 3 \, r^{2} A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B A \frac{\partial^2}{\partial t^{2}}B + r^{2} B \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A - 4 \, {\left(B^{3} - B^{2}\right)} A^{2} \Bigg),
    \label{eq212}
  \end{dmath}

  \begin{align*}
    \nabla_{[3} R_{0]3} &= \nabla_{[2} R_{0]2} \sin\left({\theta}\right)^{2}, &
    \nabla_{[3} R_{1]3} &= \nabla_{[2} R_{1]2} \sin\left({\theta}\right)^{2},
  \end{align*}
which are very complex, and ---to our knowledge--- are not possible to solve in general.
\end{widetext}

Hence, further analysis requires a new strategy. Instead of considering a metric, a connection ansatz is proposed based in the structure of a spherically symmetric metric of the form,
\begin{equation}
  \de{s}^2 = g_{ab}(x) \, \de{x}^a\de{x}^b + e^{2\rho(x)} \, g_{AB}(\vph)  \de{\vph}^A\de{\vph}^B,
  \label{sphere-gen}
\end{equation}
where $x^m$ represent the temporal an radial directions, while $\vph^M$ represent angular coordinates. Notice that the four-dimensional indices have been partitioned as \mbox{$\mu = (a,A)$,} then the general form of the connection is~\footnote{For the metric of Eq.~\eqref{sphere-gen}, the factors are \mbox{$M^a(x) = - e^{2\rho(x)} g^{am}\partial_m \rho$} and \mbox{$N_c = \partial_c \rho$.}}
\begin{dmath}
  \Ga^\lambda{}_{\mu\nu} = \delta^\lambda_a \delta^b_\mu \delta^c_\nu \ga^a{}_{bc} + \delta^\lambda_A \delta^B_\mu \delta^C_\nu \ga^A{}_{BC} + \delta^\lambda_a \delta^B_\mu \delta^C_\nu g_{BC} M^a(x) + 2 \delta^\lambda_A \delta^A_{(\mu} \delta^c_{\nu)} N_{c}(x),
  \label{connSchw}
\end{dmath}
where $\ga^a{}_{bc}$ and $\ga^A{}_{BC}$ are the Levi-Civita connection for the metrics $g_{ab}$ and $g_{AB}$ respectively.

From the connection ansatz~\eqref{connSchw} the Ricci tensor is calculated,
\begin{dmath}
  R_{\mu\nu}
  = \delta_\mu^m \delta_\nu^n \( R_{mn} - 2 \nab{m} N_n - 2 N_m N_n \)
  + \delta_\mu^M \delta_\nu^N \( R_{MN} + g_{MN} \nab{a} M^a \)
  + ( \delta_\mu^M \delta_\nu^n + \delta_\mu^n \delta_\nu^M ) \gamma^A{}_{AM} N_n
\end{dmath}

### 2015-11-04 AffGR-PRD.tex
Commiting the appendices
New version of Dimensional Analysis

@@
 \usepackage{array}
+\newcolumntype{L}[1]{>{\raggedright\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{C}[1]{>{\centering\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
+\newcolumntype{R}[1]{>{\raggedleft\let\newline\\\arraybackslash\hspace{0pt}}m{#1}}
 %% \usepackage{ulem}
@@
 \end{equation}
+We have show, so far, that our model of polynomial purely affine gravity is compatible with General Relativity in the sector of vanishing torsion, and in addition the compatibility can be extended to include the interaction with a free scalar field.
+The analysis of this coupled system could be enhanced to include a potential for the scalar field,
 
@@
 \input{DA.tex}
+\input{MS.tex}
 

### 2015-11-04 MS.tex
New version of Dimensional Analysis

@@
 
-Compact warped products of the form \mbox{$(M_1 \times M_2, f^{2} \cdot (g_1 \times g_2) )$,} where $M_1$ are two dimensional, $M_1$ has constant Gau\ss{}ian curvature, $K_1 < 0$, and $M_2$ is an Einstein manifold with scalar curvature $R_2 = - 2 K_1$
-\hl{Working here}
+Compact warped products of the form \mbox{$(M_1 \times M_2, f^{2} \cdot (g_1 \times g_2) )$,} where $M_i$ are two two-dimensional manifolds, $M_1$ has constant Gau\ss{}ian curvature, $K_1 < 0$, and $M_2$ is an Einstein manifold with scalar curvature $R_2 = - 2 K_1$.
+The function $f: M_1 \to \R^+$ is a $C^\infty$ solution of
+\begin{equation*}
+  \Lap f = c \, f^3 \text{ for } c > 0.
+\end{equation*}
+
+Many examples and explicit conditions of Riemannian metrics with harmonic curvature, and conditions for them to have parallel Ricci, can be found in Ref.~\cite{derdzinski1988riemannian}.
+
 %%\paragraph{}

### 2016-01-27 MS.tex
Equations of Birkhoff written covariantly

@@
 None of these workis original ---except the analysis presented as example in Sec.~\ref{Ex:sch}, and can be found in Refs.~\cite{gray1978einstein,derdzinski1980classification,derdzinski1982compact,Derdzinski:1985,Besse}.
-Additionally, in Ref.~\cite{cahen2000symplectic} \hl{What is this...}
 
@@
 
-%%\paragraph{}
+Although the above are examples of manifolds with parallel Ricci within the context of ``Riemannian'' geometries, examples of connnections with parallel Ricci can be found in symplectic geometries, see Ref.~\cite{cahen2000symplectic}.
 
-\subsection{Explicit example: Schwarzschild metric, and Birkhoff theorem\label{Ex:sch}}
+\section{Explicit example: Schwarzschild ansatz, and (incomplete) Birkhoff theorem\label{Ex:sch}}
 
-As a disclaimer, we clarify that the example below is a pseudo-Riemannian manifold.
+%% As a disclaimer\hl{What is this... Should this be dropped?}, we clarify that the example below is a pseudo-Riemannian manifold.
 
-%%\subsubsection{Schwarzschild metric}
+%% \subsubsection{Schwarzschild metric}
 
@@
 
-In this section it will be shown that a static and spherically symmetric metric, which solves the field equations~\eqref{SimpleEOM} is necessarily the $\Lambda$--Schwarzschild metric.
+In this section we show that the simplest ansatz of a static and spherically symmetric metric, which solves the Eq.~\eqref{SimpleEOM} is necessarily the $\Lambda$--Schwarzschild metric.
+This should be taken as a first step toward a Birkhoff theorem, despite the fact that a complete proof is far from been achieved.
 
@@
   \begin{dmath}
-    \nabla_{[1} R_{0]0} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) ,
-    \label{e100}
+    \nabla_{[\mu} R_{\nu]\lambda} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) \,
+    \delta_{\mu\nu}^{10} \delta_\lambda^0
+    +
+    \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) \,
+    \delta_{\mu\nu}^{10} \delta_\lambda^1
+    +
+    r \frac{\partial^2}{\partial t^{}\partial r^{}}f \,
+    \Big( \delta_{\mu\nu}^{20} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{30} \delta_\lambda^3 \Big)
+    +
+    \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg) \,
+    \Big( \delta_{\mu\nu}^{21} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{31} \delta_\lambda^3 \Big)
+    = 0
   \end{dmath}
-  \begin{dmath}
-    \nabla_{[1} R_{0]1} = \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) .
-    \label{e101}
-  \end{dmath}
-  \begin{dmath}
-    \nabla_{[2} R_{0]2} = r \frac{\partial^2}{\partial t^{}\partial r^{}}f,
-    \label{e202}
-  \end{dmath}
-  \begin{dmath}
-    \nabla_{[2} R_{1]2} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg),
-    \label{e212}
-  \end{dmath}
-  \begin{dmath}
-    \nabla_{[3} R_{0]3} = r \sin\left({\theta}\right)^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}f,
-    \label{e303}
-  \end{dmath}
-  and
-  \begin{dmath}
-    \nabla_{[3} R_{1]3} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3}\Bigg) \sin\left({\theta}\right)^{2}.
-    \label{e313}
-  \end{dmath}
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%   \begin{dmath}
+  %%   \nabla_{[1} R_{0]0} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) ,
+  %%   \label{e100}
+  %% \end{dmath}
+  %% \begin{dmath}
+  %%   \nabla_{[1} R_{0]1} = \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) .
+  %%   \label{e101}
+  %% \end{dmath}
+  %% \begin{dmath}
+  %%   \nabla_{[2} R_{0]2} = r \frac{\partial^2}{\partial t^{}\partial r^{}}f,
+  %%   \label{e202}
+  %% \end{dmath}
+  %% \begin{dmath}
+  %%   \nabla_{[2} R_{1]2} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg),
+  %%   \label{e212}
+  %% \end{dmath}
+  %% %% \begin{dmath}
+  %% %%   \nabla_{[3} R_{0]3} = r \sin\left({\theta}\right)^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}f,
+  %% %%   \label{e303}
+  %% %% \end{dmath}
+  %% %% and
+  %% %% \begin{dmath}
+  %% %%   \nabla_{[3} R_{1]3} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3}\Bigg) \sin\left({\theta}\right)^{2}.
+  %% %%   \label{e313}
+  %% %% \end{dmath}
+  %% \begin{align}
+  %%   \nabla_{[3} R_{0]3} &= \sin\left({\theta}\right)^{2} \nabla_{[2} R_{0]2}, &
+  %%   \nabla_{[3} R_{1]3} &= \sin\left({\theta}\right)^{2} \nabla_{[2} R_{1]2}.
+  %% \end{align}
 \end{widetext}
 Even though four out of the six nontrivial field equations are independent, the system can be solve uniquely.
-First, Eq.~\eqref{e202} yields $f = T(t) + R(r)$.
-Then, one notices that Eq.~\eqref{e101} contains a term depending solely on $t$, which implies that $\dot{T}$ vanishes, i.e., $T$ is a constant.
-From here, Eq.~\eqref{e212} gets simpler enough to be solved and yields, \mbox{$R(r) = 1 - T + \frac{\alpha}{r} + \beta r^2$} or equivalently
+First, the component along the $(\mu\nu\lambda) = (2,0,2)$ yields $f = T(t) + R(r)$.
+Then, one notices that the equation along $(\mu\nu\lambda) = (1,0,1)$ contains a term depending solely on $t$, which implies that $\dot{T}$ vanishes, i.e., $T$ is a constant.
+From here, the equation for $(\mu\nu\lambda) = (2,1,2)$ gets simple enough to be solved and yields, \mbox{$R(r) = 1 - T + \frac{\alpha}{r} + \beta r^2$} or equivalently
 \begin{equation}
@@
 \end{equation}
-with $\alpha$ and $\beta$ integration constants. Finally, it can be checked that albeit Eq.~\eqref{e100} was not used, it is satisfied by Eq.~\eqref{simplef}.
+with $\alpha$ and $\beta$ integration constants.
+Finally, it can be checked that albeit the equation along the components $(\mu,\nu,\lambda) = (1,0,0)$ was not used, it is satisfied by Eq.~\eqref{simplef}.
 
@@
 \begin{widetext}
-  %%  \section{\label{app:eqAB}Field equations for Schwarzschild metric with two factors}
   \begin{dmath}
-    \nabla_{[1} R_{0]0} = \frac{1}{4 \, r^{2} B^{3} A^{2}} \Bigg( 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{3} + 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial r^{3}}A + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}B - 6 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}B - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}A + 6 \, {\left(r^{2} A^{2} \frac{\partial}{\partial r^{}}B - r B A^{2}\right)} \frac{\partial}{\partial t^{}}B^{2} - 2 \, {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B + r B^{4} A\right)} \frac{\partial}{\partial r^{}}A^{2} - 2 \, {\left(r^{2} B A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A^{2}\right)} \frac{\partial^2}{\partial t^{2}}B - {\left(r^{2} B^{2} A \frac{\partial^2}{\partial t^{}\partial r^{}}B - 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - {\left(r^{2} B A \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A\right)} \frac{\partial}{\partial t^{}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial^2}{\partial r^{2}}B + 2 \, r B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, B^{4} A^{2} + 3 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial r^{}}A + {\left(3 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A + 4 \, r B^{4} A^{2}\right)} \frac{\partial^2}{\partial r^{2}}A \Bigg),
-    \label{eq100}
+    \nabla_{[\mu} R_{\nu]\lambda} = \frac{1}{4 \, r^{2} B^{3} A^{2}} \Bigg( 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{3} + 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial r^{3}}A + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}B - 6 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}B - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}A + 6 \, {\left(r^{2} A^{2} \frac{\partial}{\partial r^{}}B - r B A^{2}\right)} \frac{\partial}{\partial t^{}}B^{2} - 2 \, {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B + r B^{4} A\right)} \frac{\partial}{\partial r^{}}A^{2} - 2 \, {\left(r^{2} B A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A^{2}\right)} \frac{\partial^2}{\partial t^{2}}B - {\left(r^{2} B^{2} A \frac{\partial^2}{\partial t^{}\partial r^{}}B - 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - {\left(r^{2} B A \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A\right)} \frac{\partial}{\partial t^{}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial^2}{\partial r^{2}}B + 2 \, r B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, B^{4} A^{2} + 3 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial r^{}}A + {\left(3 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A + 4 \, r B^{4} A^{2}\right)} \frac{\partial^2}{\partial r^{2}}A \Bigg) \,
+    \delta_{\mu\nu}^{10} \delta_\lambda^0
+    +
+    \frac{1}{4 \, r^{2} B^{4} A^{3}} \Bigg( 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial t^{}\partial r^{2}}A + r^{2} B^{3} A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial r^{2}}A + 4 \, B^{3} A^{3} \frac{\partial}{\partial t^{}}B + 6 \, r^{2} A^{2} \frac{\partial}{\partial t^{}}B^{3} - 8 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}B + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{3}}B + 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A^{2} - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}A - {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{4} A \frac{\partial^2}{\partial r^{2}}A - 4 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} + 3 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A\right)} \frac{\partial^2}{\partial t^{}\partial r^{}}A \Bigg) \,
+    \delta_{\mu\nu}^{10} \delta_\lambda^1
+    +
+    \frac{1}{2 \, A^{2}} \Bigg( r A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B + r B A \frac{\partial^2}{\partial t^{}\partial r^{}}A + r A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - r B \frac{\partial}{\partial t^{}}A \frac{\partial}{\partial r^{}}A \Bigg) \,
+    \Big( \delta_{\mu\nu}^{20} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{30} \delta_\lambda^3 \Big)
+    +
+    \frac{1}{4 \, r B^{2} A^{2}} \Bigg( 2 \, r^{2} B^{2} A^{2} \frac{\partial^2}{\partial r^{2}}B + r^{2} B^{2} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} \frac{\partial}{\partial r^{}}A^{2} + 3 \, r^{2} A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B A \frac{\partial^2}{\partial t^{2}}B + r^{2} B \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A - 4 \, {\left(B^{3} - B^{2}\right)} A^{2} \Bigg) \,
+    \Big( \delta_{\mu\nu}^{21} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{31} \delta_\lambda^3 \Big)
+    = 0,
   \end{dmath}
-
-  \begin{dmath}
-    \nabla_{[1} R_{0]1} = \frac{1}{4 \, r^{2} B^{4} A^{3}} \Bigg( 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial t^{}\partial r^{2}}A + r^{2} B^{3} A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial r^{2}}A + 4 \, B^{3} A^{3} \frac{\partial}{\partial t^{}}B + 6 \, r^{2} A^{2} \frac{\partial}{\partial t^{}}B^{3} - 8 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}B + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{3}}B + 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A^{2} - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}A - {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{4} A \frac{\partial^2}{\partial r^{2}}A - 4 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} + 3 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A\right)} \frac{\partial^2}{\partial t^{}\partial r^{}}A \Bigg),
-    \label{eq101}
-  \end{dmath}
-
-  \begin{dmath}
-    \nabla_{[2} R_{0]2} = \frac{1}{2 \, A^{2}} \Bigg( r A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B + r B A \frac{\partial^2}{\partial t^{}\partial r^{}}A + r A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - r B \frac{\partial}{\partial t^{}}A \frac{\partial}{\partial r^{}}A \Bigg),
-    \label{eq202}
-  \end{dmath}
-
-  \begin{dmath}
-    \nabla_{[2} R_{1]2} = \frac{1}{4 \, r B^{2} A^{2}} \Bigg( 2 \, r^{2} B^{2} A^{2} \frac{\partial^2}{\partial r^{2}}B + r^{2} B^{2} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} \frac{\partial}{\partial r^{}}A^{2} + 3 \, r^{2} A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B A \frac{\partial^2}{\partial t^{2}}B + r^{2} B \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A - 4 \, {\left(B^{3} - B^{2}\right)} A^{2} \Bigg),
-    \label{eq212}
-  \end{dmath}
-
-  \begin{align*}
-    \nabla_{[3} R_{0]3} &= \nabla_{[2} R_{0]2} \sin\left({\theta}\right)^{2}, &
-    \nabla_{[3} R_{1]3} &= \nabla_{[2} R_{1]2} \sin\left({\theta}\right)^{2},
-  \end{align*}
-which are very complex, and ---to our knowledge--- are not possible to solve in general.
 \end{widetext}
+which are very complex, and ---to our knowledge--- these are not possible to solve in general.
+Nonetheless, the symmetries in some of the components of these equations seems to favour the relation $A = B$ as solution.
+In addition, we found a very interesting reference in which a proof of the Birkhoff theorem is given for an Einstein--Cartan theory coupled with the gravitational Yang--Mills~\cite{Ramaswamy:1979zz}, which support the hand-waving symmetry argument above.
 

### 2016-03-24 MS.tex
With the EOM in MS appendix

@@
 
-From the connection ansatz~\eqref{connSchw} the Ricci tensor is calculated,
+From the connection ansatz~\eqref{connSchw} the Ricci tensor is
 \begin{dmath}
@@
   = \delta_\mu^m \delta_\nu^n \( R_{mn} - 2 \nab{m} N_n - 2 N_m N_n \)
-  + \delta_\mu^M \delta_\nu^N \( R_{MN} + g_{MN} \nab{a} M^a \)
-  + ( \delta_\mu^M \delta_\nu^n + \delta_\mu^n \delta_\nu^M ) \gamma^A{}_{AM} N_n
+  + \delta_\mu^M \delta_\nu^N \( R_{MN} + g_{MN} \nab{a} M^a \),
+  %% + ( \delta_\mu^M \delta_\nu^n + \delta_\mu^n \delta_\nu^M ) \gamma^A{}_{AM} N_n
 \end{dmath}
+and the equations of motion are
+\begin{widetext}
+  \begin{dmath}
+    \nabla_{[\lambda} R_{\mu]\nu}
+    = \delta_\lambda^l \delta_\mu^m \delta_\nu^n  \bigg( \frac{1}{2} g_{n[m} \partial_{l]} R_x + 2 R_x  g_{n[m} N_{l]}(x) - 2 \nabla_{[l} \Big( N_{m]} N_n \Big) \bigg)
+    + \delta_\lambda^{[l} \delta_\mu^{M]} \delta_\nu^N \, g_{MN} \bigg( \nab{l} \nab{a} M^a + \frac{R_x}{2} g_{la} M^a - 2 N_l - 2 \nab{a} \Big( M^a N_l \Big) - 2 M^a N_a N_l \bigg).
+  \end{dmath}
+\end{widetext}
+We have used that $g_{AB}(\varphi)$ is the metric of a two-sphere, and its curvature tensors are well known.
+In addition, since the metric $g_{ab}(x)$ is two-dimensional too, its curvature tensors are related with the metric by the relation
+\begin{dmath}
+  R_{ab}{}^c{}_d = \frac{R_x}{2} \Big( \delta^c_a g_{bd} - \delta^c_b g_{ad} \Big).
+\end{dmath}

### 2016-03-24 AffGR-PRD.tex

@@
 
-Classically, General Relativity is the most successful theory of gravitational interactions.
+A hundred years ago, A.~Einstein presented by the first time the correct field equations of its relativistic theory of gravitation, known as General Relativity~\cite{einstein1915feldgleichungen}.
+It was not only consistent with the available observations, but it also predicted several effects that have been consistently observed and measured---see Ref.~\cite{Will:2014kxa} for a recent review---, being the last one the confirmation of gravitational waves~\cite{Abbott:2016blz}.
+Thus, General Relativity has become the most successful theory of gravitational interactions nowadays.
+
+However, General Relativity seems to be an effective theory of a, yet to be discover, more fundamental one.
+A first hint was pointed out by E.~Cartan, after noticing that that a part of the connection was left behind if one chooses to work with the Levi-Civita connection~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
+One could also see this by considering Palatini's framework for General Relativity, in which both fields are independent, and noticing that the theory is not complete because there are terms which are zero in pure General Relativity that do not vanish in Palatini's generalization.
+In addition, we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}, suggests the theory can be thought as an effective theory.
+Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
+One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
+On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
+
+%% Classically, General Relativity is the most successful theory of gravitational interactions.
 However, it is believed to be the effective theory of a, yet to be discovered, more fundamental one.
@@
 
-First of all, we highlight that the model constructed below has as fundamental field an affine connection, and no metric fields is needed for neither contracting nor lowering or raising indices.
+First of all, we highlight that the model constructed below has as fundamental field an affine connection, and no metric field is needed for neither contracting nor lowering or raising indices.
 Moreover, in order to guarantee the correct transformation of the Lagrangian density, the geometrical objects used to write down the action will be the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
@@
 A straightforward dimensional counting shows the impossibility of other contributions in to the action, see Appendix~\ref{DA}.
-Interestingly, the above action turns to be power-counting renormalizable, which does not guarantees renormalizability but is a good signal.
+Interestingly, the above action turns to be power-counting renormalizable, which does not guarantee renormalizability but is a good signal.
 The structure of the model yields no three-point graviton vertices, which might allow to overcome  the no-go theorems found in Refs.~\cite{McGady:2013sga,Camanho:2014apa}.
@@
 and it can be shown that a manifold with harmonic curvature is equivalent (in four dimensions) to a manifold with harmonic Weyl tensor and constant scalar curvature~\cite{Berger:1969}, or in other words the Ricci tensor is a Codazzi tensor~\footnote{A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$, satisfying the condition \mbox{$D_X T(Y,Z) = D_Y T(X,Z)$~\cite{Derdzinski01071983}.}}.
-For prove of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.
+For proofs of these equivalences, see Refs.~\cite{Derdzinski:1985,Besse}.
 

### 2016-03-24 DA.tex

@@
 
-We built the model using six ingredients, a Curtright ($T^{\mu,\nu\lambda}$), a vector ($A_\mu$), the covariant derivative ($\nab{\mu}$), both Levi-Civita tensors ($\epsilon_{\mu\nu\lambda\rho}$ and $\epsilon^{\mu\nu\lambda\rho}$), and the Riemannian curvature ($R_{\mu\nu}{}^\lambda{}_\rho$).
+We built the model using six ingredients, a Curtright ($T^{\mu,\nu\lambda}$), a vector ($A_\mu$), the covariant derivative defined with the Levi-Civita connection ($\nab{\mu}$), both Levi-Civita tensors ($\epsilon_{\mu\nu\lambda\rho}$ and $\epsilon^{\mu\nu\lambda\rho}$), and the Riemannian curvature ($R_{\mu\nu}{}^\lambda{}_\rho$).
+Since the Riemannian curvature is defined as the commutator of the covariant derivative, it is not an independent field, so it will be left out of the analysis, and only five ingredients remain.
 
@@
     N( T^{\mu,\nu\lambda} ) &= 3 & N( A_\mu ) &= -1 & N(  \nab{\mu} ) &= -1 \\
-    N( \epsilon_{\mu\nu\lambda\rho} ) &= -4 & N( \epsilon^{\mu\nu\lambda\rho} ) &= 4 & N( R_{\mu\nu}{}^\lambda{}_\rho ) &= -2.
+    N( \epsilon_{\mu\nu\lambda\rho} ) &= -4 & & & N( \epsilon^{\mu\nu\lambda\rho} ) &= 4 
   \end{aligned}
@@
 \begin{equation*}
-  T^a A^b \nabla^c {\epsilon_{\dots}}^d {\epsilon^{\dots}}^e R^f,
+  T^a A^b \nabla^c {\epsilon_{\dots}}^d {\epsilon^{\dots}}^e,
 \end{equation*}
@@
 \begin{equation}
-  N( T^a A^b \nabla^c {\epsilon_{\dots}}^d {\epsilon^{\dots}}^e R^f ) = n,
+  N( T^a A^b \nabla^c {\epsilon_{\dots}}^d {\epsilon^{\dots}}^e ) = n,
 \end{equation}
@@
 \begin{equation}
-  n = 3a -b -c -4d + 4e -2f.
+  n = 3a -b -c -4d + 4e = 3 a -b - c + 4 \ell,
   \label{ni}
 \end{equation}
+where we defined $\ell = e - d$, for the sake of simplicity.
 
@@
     W( T^{\mu,\nu\lambda} ) &= 1 & W( A_\mu ) &= 0 & W(  \nab{\mu} ) &= 0 \\
-    W( \epsilon_{\mu\nu\lambda\rho} ) &= -1 & W( \epsilon^{\mu\nu\lambda\rho} ) &= 1 & W( R_{\mu\nu}{}^\lambda{}_\rho ) &= 0.
+    W( \epsilon_{\mu\nu\lambda\rho} ) &= -1 & & & W( \epsilon^{\mu\nu\lambda\rho} ) &= 1 .
   \end{aligned}
@@
 \begin{equation}
-  w = a - d + e.
+  w = a + \ell.
   \label{wd}
@@
 
-One solution of Eq.~\eqref{wd} is $a=1$ with $d=e$, which implies that Eq.~\eqref{ni} is restricted to
+Equation~\eqref{wd} can solved by choosing either $a=1$ or $\ell = 1$, which imply that Eq.~\eqref{ni} is restricted to
 \begin{equation*}
-  3 - b - c - 2f = 2.
+  3 - b - c = 2,
 \end{equation*}
-It follows that $f=0$, while still there is room to choose either $b=1$ or $c=1$.
-Notice that, albeit there is an ambiguity in the value of $d$ and $e$, the fact that all other factors are fixed, and the properties of epsilon contractions implies that all terms are equivalent to choose $d=e=0$.
-Therefore, the only possible terms built with this choice are
+or
+\begin{equation*}
+  4 - b - c = 2,
+\end{equation*}
+respectively. The former, yields the terms
 \begin{equation}
-  T^{\mu,\nu\lambda} A_\lambda \text{ and } \nabla_\lambda T^{\mu,\nu\lambda}.
+  T^{\mu,\nu\lambda} A_\lambda \text{ and } \nabla_\lambda T^{\mu,\nu\lambda},
 \end{equation}
-No other contraction of indices is allowed due to the symmetry.
-
-Similarly, if one solves Eq.~\eqref{wd} by choosing $e=1$, and $d=a=0$, Eq.~\eqref{ni} yields
-\begin{equation*}
-  4 - b - c - 2f = 2,
-\end{equation*}
-which can be solved by $f=1$, $b=2$, $c=2$, or $b=c=1$. However, by construction the last three choices do not yield symmetric tensors, and the first one vanishes due to the first Bianchi identity.
-
-A third option is to solve Eq.~\eqref{wd} with $a=2$, $d=1$ and $e=0$. In this case, Eq.~\eqref{ni} is an identity. Thus, the only term originated this way is 
+no other contraction of indices is allowed due to the symmetry. The latter, yields another possibility,
 \begin{equation}
@@
 
-Finally, one can check that any other choice to solve Eq.~\eqref{wd} make impossible to solve Eq.~\eqref{ni}.
+Finally, one can check that any other choice to solve Eq.~\eqref{wd} ---by allowing negative values of $\ell$--- make impossible to solve Eq.~\eqref{ni}.
 Ergo, there is no other term in a symmetric $\binom{2}{0}$-tensor density built up with these fields.
 Explicitly, this general tensor density is written in Eq.~\eqref{geng}.
-
-\subsection{Lagrangian density}
-
-\begin{table}[t]
-  \caption{Possible selection of terms in the Lagrangian density}
-  \label{tab:a1}
-  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
+The summary of this analysis is presented in Table~\ref{tab:imd}.
+\begin{table}
+  \caption{Possible terms contributing to the inverse density metric. }
+  \label{tab:imd}
+  \begin{tabular}{|C{.23\linewidth}C{.23\linewidth}C{.23\linewidth}C{.23\linewidth}|}
     \hline
-    \multicolumn{3}{|c|}{$a=1$} \\
+    $a$ & $b$ & $c$ & $\ell$ \\
     \hline
-    $b$ & $c$ & $f$ \\
-    \hline
-    3 & 0 & 0 \\
-    2 & 1 & 0 \\
-    1 & 2 & 0 \\
-    0 & 3 & 0 \\
-    1 & 0 & 1 \\
-    0 & 1 & 1 \\
+    1 & 1 & 0 & 0 \\
+    1 & 0 & 1 & 0 \\
+    2 & 0 & 0 &-1 \\
+    0 & 2 & 0 & 1 \\
+    0 & 1 & 1 & 1 \\
+    0 & 0 & 2 & 1 \\
     \hline
@@
 
-\begin{table}[t]
-  \caption{Possible selection of terms in the Lagrangian density}
-  \label{tab:e1} 
-  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
+\subsection{Lagrangian density}
+
+\begin{table}
+  \caption{Possible terms contributing to the Lagrangian density.}
+  \label{tab:ld}
+  \begin{tabular}{|C{.23\linewidth}C{.23\linewidth}C{.23\linewidth}C{.23\linewidth}|}
     \hline
-    \multicolumn{3}{|c|}{$e=1$} \\
+    $a$ & $b$ & $c$ & $\ell$ \\
     \hline
-    $b$ & $c$ & $f$ \\
-    \hline
-    0 & 0 & 2 \\
-    2 & 0 & 1 \\
-    1 & 1 & 1 \\
-    0 & 2 & 1 \\
-    0 & 4 & 0 \\
-    1 & 3 & 0 \\
-    2 & 2 & 0 \\
-    3 & 1 & 0 \\
-    4 & 0 & 0 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[t]
-  \caption{Possible selection of terms in the Lagrangian density}
-  \label{tab:a2}  
-  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
-    \hline
-    \multicolumn{3}{|c|}{$a=2$, $d=1$} \\
-    \hline
-    $b$ & $c$ & $f$ \\
-    \hline
-    0 & 0 & 1 \\
-    2 & 0 & 0 \\
-    1 & 1 & 0 \\
-    0 & 2 & 0 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[t]
-  \caption{Possible selection of terms in the Lagrangian density}
-  \label{tab:a3}
-  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
-    \hline
-    \multicolumn{3}{|c|}{$a=3$, $d=2$} \\
-    \hline
-    $b$ & $c$ & $f$ \\
-    \hline
-    1 & 0 & 0 \\
-    0 & 1 & 0 \\
-    \hline
-  \end{tabular}
-\end{table}
-
-\begin{table}[t]
-  \caption{Possible selection of terms in the Lagrangian density}
-  \label{tab:a4}
-  \begin{tabular}{|p{\linewidth/3}p{\linewidth/3}p{\linewidth/3}|}
-    \hline
-    \multicolumn{3}{|c|}{$a=4$, $d=3$} \\
-    \hline
-    $b$ & $c$ & $f$ \\
-    \hline
-    0 & 0 & 0 \\
+    1 & 3 & 0 & 0\\
+    1 & 2 & 1 & 0\\
+    1 & 1 & 2 & 0\\
+    1 & 0 & 3 & 0\\
+    2 & 2 & 0 & -1\\
+    2 & 1 & 1 & -1\\
+    2 & 0 & 2 & -1\\
+    3 & 1 & 0 & -2\\
+    3 & 0 & 1 & -2\\
+    4 & 0 & 0 & -3\\
+    0 & 4 & 0 & 1\\
+    0 & 3 & 1 & 1\\
+    0 & 2 & 2 & 1\\
+    0 & 1 & 3 & 1\\
+    0 & 0 & 4 & 1\\
     \hline
@@
 \begin{align}
-  3a -b -c - 4d +4e - 2f &= 0, \\
-  a - d + e &= 1.
+  3a -b -c  + 4\ell &= 0, \label{nib}\\
+  a + \ell &= 1. \label{wdb}
 \end{align}
 
-A possible solution of Eq~\eqref{wd} is $a=1$ and $d=e$, and such choice allows to consider the possibilities, see Table~\ref{tab:a1}, but only three of them are independent (and nonvanishing).
-These generate the terms of Eq.~\eqref{4dfull} whose coefficients were called $B_3$, $B_4$, $B_5$, $C_1$, $C_2$, $D_6$ and $D_7$.
+A possible solution of Eq~\eqref{wdb} is $a=1$ and $\ell = 0$.
+Such choice allows four possible solutions of Eq.~\eqref{nib}, but only three of them are nonvanishing.
+These generate the terms of Eq.~\eqref{4dfull} whose coefficients were called $B_3$, $B_4$, $B_5$, $C_1$, $C_2$, $D_6$, $D_7$ and $E_2$.
 
-If one choose $e=1$ for solving Eq.~\eqref{wd}, see Table~\ref{tab:e1}, all possible solutions for Eq.~\eqref{ni} are either vanishing or yield topological terms.
+If one choose $\ell = 1$ for solving Eq.~\eqref{wdb}, all possible solutions for Eq.~\eqref{nib} are either vanishing or yield topological terms.
 %%The action in Eq.~\eqref{4dfull} was written up to topological and boundary terms, thus
 
-The case with $a=2$ and $d=1$ gives four possibilities to solve Eq.~\eqref{ni}, see  Table~\ref{tab:a2}, and these choices give the terms the Lagrangian density whose coefficients are $B_1$, $B_2$, $D_4$, $D_5$, $E_1$, $E_2$ and $F_4$.
+The case with $a=2$ and $\ell = -1$ gives three possibilities to solve Eq.~\eqref{nib}.
+These choices give the terms the Lagrangian density whose coefficients are $B_1$, $B_2$, $D_4$, $D_5$, $E_1$, and $F_4$.
 
-For $a=3$ and $d=2$ there are only two possible solutions of Eq.~\eqref{ni}, see  Table~\ref{tab:a3}, and these yield the terms of the action with coefficients $D_1$, $D_2$, $D_3$ and $F_3$.
-And also, the choice $a=4$ and $d=3$ solves the equations, see  Table~\ref{tab:a4}, and yield the terms in the action with coefficients $F_1$ and $F_2$.
+For $a = 3$ and $\ell = -2$ there are only two possible solutions of Eq.~\eqref{nib}, and these yield the terms of the action with coefficients $D_1$, $D_2$, $D_3$ and $F_3$.
+And also, the choice $a = 4$ and $\ell = -3$ solves the equations, and yield the terms in the action with coefficients $F_1$ and $F_2$.
 
-Notice that for values $a \ge 5$, it is not possible to solve both Eqs.~\eqref{ni} and~\eqref{wd} simultaneously.
+Notice that for values $a \ge 5$, it is not possible to solve both Eqs.~\eqref{nib} and~\eqref{wdb} simultaneously.
 Therefore, we conclude that Eq.~\eqref{4dfull} is the most general action built up with these fields.
+A summary of the choices for building the Lagrangian density is presented in Table~\ref{tab:ld}.

### 2016-04-06 MS.tex
Developing the new method for Birkhoff

@@
 where $x^m$ represent the temporal an radial directions, while $\vph^M$ represent angular coordinates.
-Notice that the four-dimensional indices have been partitioned as \mbox{$\mu = (a,A)$,} then the general form of the connection is~\footnote{For the metric of Eq.~\eqref{sphere-gen}, the factors are \mbox{$M^a(x) = - e^{2\rho(x)} g^{am}\partial_m \rho$} and \mbox{$N_c = \partial_c \rho$.}}
+Notice that the four-dimensional indices have been partitioned as \mbox{$\mu = (a,A)$,} then the general form of the connection is
+%~\footnote{For the metric of Eq.~\eqref{sphere-gen}, the factors are \mbox{$M^a(x) = - e^{2\rho(x)} g^{am}\partial_m \rho$} and \mbox{$N_c = \partial_c \rho$.}}
 \begin{dmath}
-  \Ga^\lambda{}_{\mu\nu} = \delta^\lambda_a \delta^b_\mu \delta^c_\nu \ga^a{}_{bc} + \delta^\lambda_A \delta^B_\mu \delta^C_\nu \ga^A{}_{BC} + \delta^\lambda_a \delta^B_\mu \delta^C_\nu g_{BC} M^a(x) + 2 \delta^\lambda_A \delta^A_{(\mu} \delta^c_{\nu)} N_{c}(x),
+  \Ga^\lambda{}_{\mu\nu} = \delta^\lambda_a \delta^b_\mu \delta^c_\nu \ga^a{}_{bc} + \delta^\lambda_A \delta^B_\mu \delta^C_\nu \ga^A{}_{BC} + \delta^\lambda_a \delta^B_\mu \delta^C_\nu g_{BC} M^a(x) +  \delta^\lambda_A \delta^A_{(\mu} \delta^c_{\nu)} N_{c}(x),
   \label{connSchw}
 \end{dmath}
-where $\ga^a{}_{bc}$ and $\ga^A{}_{BC}$ are the Levi-Civita connection for the metrics $g_{ab}$ and $g_{AB}$ respectively.
+where $\ga^a{}_{bc}$ and $\ga^A{}_{BC}$ are the Levi-Civita connection for the metrics $g_{ab}$ and $g_{AB}$ respectively, and the factors are \mbox{$M^a(x) = - \tfrac{1}{2}  g^{am}\partial_m e^{2\rho(x)}$} and \mbox{$N_c = 2 \partial_c \rho$}.
 
@@
     \nabla_{[\lambda} R_{\mu]\nu}
-    = \delta_\lambda^l \delta_\mu^m \delta_\nu^n  \bigg( \frac{1}{2} g_{n[m} \partial_{l]} R_x + 2 R_x  g_{n[m} N_{l]}(x) - 2 \nabla_{[l} \Big( N_{m]} N_n \Big) \bigg)
-    + \delta_\lambda^{[l} \delta_\mu^{M]} \delta_\nu^N \, g_{MN} \bigg( \nab{l} \nab{a} M^a + \frac{R_x}{2} g_{la} M^a - 2 N_l - 2 \nab{a} \Big( M^a N_l \Big) - 2 M^a N_a N_l \bigg).
+    = \delta_\lambda^l \delta_\mu^m \delta_\nu^n  \bigg( \frac{1}{2} g_{n[m} \partial_{l]} \mathcal{R} + 2 \mathcal{R}  g_{n[m} N_{l]}(x) - 2 \nabla_{[l} \Big( N_{m]} N_n \Big) \bigg)
+    + \delta_\lambda^{[l} \delta_\mu^{M]} \delta_\nu^N \, g_{MN} \bigg( \nab{l} \nab{a} M^a + \frac{\mathcal{R}}{2} g_{la} M^a - 2 N_l - 2 \nab{a} \Big( M^a N_l \Big) - 2 M^a N_a N_l \bigg).
+    \label{OurEq}
   \end{dmath}
@@
 \begin{dmath}
-  R_{ab}{}^c{}_d = \frac{R_x}{2} \Big( \delta^c_a g_{bd} - \delta^c_b g_{ad} \Big).
+  R_{ab}{}^c{}_d = \frac{\mathcal{R}}{2} \Big( \delta^c_a g_{bd} - \delta^c_b g_{ad} \Big).
 \end{dmath}
+
+As argue  in Refs.~\cite{bergmann1965spherically,hawking1973large},  the solution depends on the nature of the surfaces described by $\rho = \text{const.}$, which in our parametrization translate to the nature of $N_a$.
+We first consider the condition $g^{ab} N_a N_b > 0 $, which allows to set $\rho$ as a good radial coordinate.
+Therefore, the general metric ansatz $g_{ab}$ is diagonal, and the radial direction would be $\rho$, i.e.,
+\begin{equation}
+  g_{ab} = - \alpha^2(t,\rho) \de{t}_a \otimes \de{t}_b + \beta^2(t,\rho) \de{\rho}_a \otimes \de{\rho}_b.
+\end{equation}
+With this ansatz, the nontrivial components of Eq.~\eqref{OurEq} are
+\begin{align}
+  \beta^2 \pa{t} \mathcal{R} + 8 \gamma^\rho{}_{t \rho} &= 0,
+  \label{eq1}
+  \\
+  \pa{\rho} \mathcal{R} - 4 \mathcal{R} + 16 \alpha^{-2} \gamma^\rho{}_{tt} &= 0,
+  \label{eq2}
+  \\
+  \pa{t} \big( \Delta_x e^{2\rho} \big) + 4 \beta^{-2} e^{2\rho} \gamma^\rho{}_{t \rho} &= 0,
+  \label{eq3}
+\end{align}
+and
+\begin{dmath}
+  \pa{\rho} \big( \Delta_x e^{2\rho} \big) + 8 - 4 \Delta_x e^{2\rho} - 16 \beta^{-2} e^{2\rho} - 4 \beta^{-2} e^{2\rho} \gamma^{\rho}{}_{\rho\rho}  + \mathcal{R} e^{2\rho} = 0.
+  \label{eq4}
+\end{dmath}
+Equation~\eqref{eq1} can be rewritten as
+\begin{equation}
+  \pa{t} \big( \mathcal{R} - 8 \beta^{-2} \big) = 0,
+\end{equation}
+or 
+\begin{equation}
+  \mathcal{R} - 8 \beta^{-2} = G_1(\rho).
+\end{equation}
+Since
+\begin{equation}
+  \Delta_x e^{2\rho} = e^{2\rho} \bigg[ 4 \beta^{-2} + \frac{2}{\alpha \beta} \pa{\rho} \bigg( \frac{\alpha}{\beta} \bigg) \bigg] \equiv  e^{2\rho} \Big[ 4 \beta^{-2} + F \Big],
+\end{equation}
+it follows from Eq.~\eqref{eq3} that,
+\begin{equation}
+  mmmmmmmmm
+\end{equation}

### 2016-04-08 AffGR-PRD.tex
Introduction reviewed

@@
   We show that the effective field equations for a recently formulated polynomial affine model of gravity, in the sector of a torsion-free connection, accept general Einstein manifolds ---with or without cosmological constant--- as solutions.
-Moreover, these effective field equations coincide with some of those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
+Moreover, the effective field equations coincide with some of those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
 Additionally, we find a generalization of a minimally coupled massless scalar field in General Relativity with a ``minimally'' coupled scalar field in this affine model.
@@
 However, General Relativity seems to be an effective theory of a, yet to be discover, more fundamental one.
-A first hint was pointed out by E.~Cartan, after noticing that that a part of the connection was left behind if one chooses to work with the Levi-Civita connection~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
-One could also see this by considering Palatini's framework for General Relativity, in which both fields are independent, and noticing that the theory is not complete because there are terms which are zero in pure General Relativity that do not vanish in Palatini's generalization.
+A first hint was pointed out by E.~Cartan, after remarking that the curvature is not built up from a metric field but from a connection, and that a part of it was left behind if one chooses to work with the Levi-Civita connection~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
+One could also see this by considering Palatini's approach in General Relativity, in which both metric and connection fields are independent, and noticing that generically the theory possesses terms which do not appear in General Relativity.
 In addition, we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}, suggests the theory can be thought as an effective theory.
 Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
-One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
+One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, by Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
 On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
@@
 One important class of these generalizations considers the connection field to be independent of the metric, known as Palatini type theories.
-Within this class of theories one finds the generalization due to Cartan, which considers a connection with nonvanishing torsion~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
+Within this class of theories one finds the generalization due to Cartan---which considers a connection with nonvanishing torsion~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}---, but also a broader kind of generalization which do not require the metricity condition, see for example Refs.~\cite{Hehl:1976kj,Hehl:1994ue,Pagani:2015ema}.
+
 Interestingly, gravitational theories with generic linear connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
 Albeit these gravitational theories with an arbitrary connection possess ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe} or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
+The last sentence, allows to argue that a model cannot be discarded  for the presence of ghosts model, without a rigorous analysis of its stability.
 
@@
 Worth to mention that the most general action built this way contains only power-counting renormalizable terms (which by no means guarantees the renormalizability of the system).
-We showed that its non-relativistic limit around a homogeneous and isotropic spacetime yields a Newtonian gravitational potential, despite the existence of torsion.
+We showed that its non-relativistic limit, around a homogeneous and isotropic spacetime, yields a geodesic deviation corresponding to the generated by a Newtonian gravitational potential, despite the existence of torsion.
 We also highlighted the possibility of using standard methods to quantize the model, due to its polynomial structure (unlike the earliest proposals~\cite{Eddington1923math,schrodinger1950space}), and also the likelihood of avoiding the uniqueness of diffeomorphism-invariant states from Loop Quantum Gravity programme~\cite{Lewandowski:2005jk}, due to the absence of a fundamental metric, or in other words, the absence of flux operators.
@@
 Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton self-interaction is mediated by the torsion.
-This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it is proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
+This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it was proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
 %%Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}.
@@
 Then, in Sec.~\ref{matter} we show that under certain considerations the coupling of the gravitational model with a scalar field represents a generalization of the minimally coupled system Einstein--Klein--Gordon.
-Finally, in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results.
+In Sec.~\ref{propag}, we present a brief analysis of the propagators of the model, which represent a first step toward a thorough study of the degrees of freedom of these theory.
+And in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results.
+In order to make the paper self-contained, we have included three appendices: In Appendix~\ref{DA}, we describe a dimensional analysis strategy that allowed us to build up the most general action consistent with diffeomorphisms.
+In Appendix~\ref{Known}, we show a collection of known solutions to the effective field equations of the model.
+Finally, in Appendix~\ref{Schw}, we demonstrate---restricting ourselves to the vanishing torsion sector---the equivalent of the Birkhoff's theorem of the theory.
 
@@
 %%%%%%%%% Propagators %%%%%%%%%
-\section{Analysis of propagators}
+\section{\label{propag}Analysis of propagators}
 

### 2016-04-08 MS.tex
Introduction reviewed

@@
-\section{Known metric solutions to the parallel Ricci equations}
+\section{\label{Known}Known metric solutions to the parallel Ricci equations}
 
@@
 
-\section{Explicit example: Schwarzschild ansatz, and (incomplete) Birkhoff theorem\label{Ex:sch}}
+\section{\label{Schw}Explicit example: Schwarzschild ansatz, and Birkhoff theorem\label{Ex:sch}}
 
@@
     = 0,
+    \label{hugeeq}
   \end{dmath}
@@
   g_{ab} = - \alpha^2(t,\rho) \de{t}_a \otimes \de{t}_b + \beta^2(t,\rho) \de{\rho}_a \otimes \de{\rho}_b.
+  \label{metr2d}
 \end{equation}
@@
 \end{dmath}
-Equation~\eqref{eq1} can be rewritten as
-\begin{equation}
-  \pa{t} \big( \mathcal{R} - 8 \beta^{-2} \big) = 0,
-\end{equation}
-or 
+From equation~\eqref{eq1} it follows that,
+%% can be rewritten as
+%% \begin{equation}
+%%   \pa{t} \big( \mathcal{R} - 8 \beta^{-2} \big) = 0,
+%%   \label{eq1a}
+%% \end{equation}
+%% or 
 \begin{equation}
   \mathcal{R} - 8 \beta^{-2} = G_1(\rho).
+  \label{eq1b}
 \end{equation}
-Since
+In addition, since
 \begin{equation}
-  \Delta_x e^{2\rho} = e^{2\rho} \bigg[ 4 \beta^{-2} + \frac{2}{\alpha \beta} \pa{\rho} \bigg( \frac{\alpha}{\beta} \bigg) \bigg] \equiv  e^{2\rho} \Big[ 4 \beta^{-2} + F \Big],
+  \Delta_x e^{2\rho}
+  = e^{2\rho} \bigg[ 4 \beta^{-2} + \frac{2}{\alpha \beta} \pa{\rho} \bigg( \frac{\alpha}{\beta} \bigg) \bigg]
+  \equiv  e^{2\rho} \Big[ 4 \beta^{-2} + \mathcal{F} \Big],
 \end{equation}
-it follows from Eq.~\eqref{eq3} that,
+it follows from Eqs.~\eqref{eq3} that,
+%% \begin{equation}
+%%   \pa{t} \big( F + 2 \beta^{-2} \big) = 0,
+%%   \label{eq3a}
+%% \end{equation}
+%% or 
 \begin{equation}
-  mmmmmmmmm
+  \mathcal{F} + 2 \beta^{-2} = G_2(\rho).
+  \label{eq3b}
 \end{equation}
+
+Equations~\eqref{eq1b} and~\eqref{eq3b} implies that all temporal dependence on time within $\mathcal{R}$, $\mathcal{F}$ and $\beta^{-2}$, enters through an additive common function, say $B(t,\rho)$.
+However, the consistency of these equations with the value of $\mathcal{R}$ calculated from the metric ansatz, in Eq.~\eqref{metr2d}, sets this additive function to zero, $B(t,\rho)$.
+Therefore, neither $\mathcal{R}$, $\mathcal{F}$ nor $\beta^{-2}$ depend on $t$.
+By extension---from the definition of $\mathcal{F}$---, $\alpha$ could depend on time through a multiplicative function.
+Nonetheless, this multiplicative function can be eliminated of the problem by a redefinition of the \emph{time} coordinate.
+
+At this stage, we have proved that \emph{any spherically symmetric (metric) solution of the Eqs.~\eqref{SimpleEOM} is necessarily static}, which is one of the main statements of Birkhoff's theorem.
+This result, simplifies the Eq.~\eqref{hugeeq} and makes clearer the necessity of setting $A(r) = B(r)$ to solve the equations of motion.
+Finally, according to Eq.~\eqref{simplef} the general (metric) solution is the (Anti-)de-Sitter--Schwarzschild metric.

### 2016-04-11 AffGR-PRD.tex
With Vijay comments, and others by me

@@
-\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint,longbibliography]{revtex4-1}
+\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint%,longbibliography
+]{revtex4-1}
 
@@
 
-However, General Relativity seems to be an effective theory of a, yet to be discover, more fundamental one.
+However, General Relativity seems to be an effective theory of a, yet to be discovered, more fundamental one.
 A first hint was pointed out by E.~Cartan, after remarking that the curvature is not built up from a metric field but from a connection, and that a part of it was left behind if one chooses to work with the Levi-Civita connection~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
 One could also see this by considering Palatini's approach in General Relativity, in which both metric and connection fields are independent, and noticing that generically the theory possesses terms which do not appear in General Relativity.
-In addition, we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}, suggests the theory can be thought as an effective theory.
+In addition, we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization, General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}, suggests the theory can be thought as an effective theory.
 Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
@@
 Interestingly, gravitational theories with generic linear connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
-Albeit these gravitational theories with an arbitrary connection possess ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe} or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
+Albeit these gravitational theories with an arbitrary connection possess ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe}, or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
 The last sentence, allows to argue that a model cannot be discarded  for the presence of ghosts model, without a rigorous analysis of its stability.
@@
 In order to undertake the premises of incompleteness and non-polynomial structure of the theory, in a previous paper~\cite{Skirzewski:2014eta}, we presented a polynomial (purely) affine gravitational model in four dimensions built up entirely on the basis of full diffeomorphism invariance.
-Worth to mention that the most general action built this way contains only power-counting renormalizable terms (which by no means guarantees the renormalizability of the system).
+Worth to mention is that the most general action built this way contains only power-counting renormalizable terms (which by no means guarantees the renormalizability of the system).
 We showed that its non-relativistic limit, around a homogeneous and isotropic spacetime, yields a geodesic deviation corresponding to the generated by a Newtonian gravitational potential, despite the existence of torsion.
@@
 
-First of all, we highlight that the model constructed below has as fundamental field an affine connection, and no metric field is needed for neither contracting nor lowering or raising indices.
+First of all, we highlight that the model constructed below has as only fundamental field an affine connection, and no metric field is needed either for contracting nor lowering or raising indices.
 Moreover, in order to guarantee the correct transformation of the Lagrangian density, the geometrical objects used to write down the action will be the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
@@
 where ${\Gamma}^\mu{}_{\rho\sigma}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying \mbox{$T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$} and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$.
-Since no metric is present  the epsilon symbols are not related by raising (lowering) their indices, but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}
+Since no metric is present, the epsilon symbols are not related by raising (lowering) their indices, but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}
 \begin{widetext}
@@
 In Eq.~\eqref{4dfull}, we have dropped all terms which can be related through partial integration, and those which are topological invariant.
-A straightforward dimensional counting shows the impossibility of other contributions in to the action, see Appendix~\ref{DA}.
-Interestingly, the above action turns to be power-counting renormalizable, which does not guarantee renormalizability but is a good signal.
-The structure of the model yields no three-point graviton vertices, which might allow to overcome  the no-go theorems found in Refs.~\cite{McGady:2013sga,Camanho:2014apa}.
+A straightforward dimensional counting shows the impossibility of other contributions into the action, see Appendix~\ref{DA}.
+Interestingly, the above action turns out to be power-counting renormalizable, which does not guarantee renormalizability but is a nice feature.
+The structure of the model yields no three-point graviton vertices, which might allow to overcome  the \emph{no-go} theorems found in Refs.~\cite{McGady:2013sga,Camanho:2014apa}.
 It is worth mentioning that all coupling constants are dimensionless, which might be a hint of conformal invariance of the model~\cite{Buchholz:1976hz}.
@@
 %% Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
-Albeit the inclusion of matter in a nonmetric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general $\binom{2}{0}$-type symmetric tensor density, $\mathfrak{g}^{\mu \nu}$, constructed with at most quadratic terms in the available fields.
-A simple \emph{dimensional analysis} shows that this tensor density contains the same terms as what we call the ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.
+Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general $\binom{2}{0}$-type symmetric tensor density, $\mathfrak{g}^{\mu \nu}$, constructed with at most quadratic terms in the available fields.
+The dimensional analysis in Sec.~\ref{sec:im} shows that this tensor density contains the same terms as what we call the ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.
 However, for the simple case of the Einstein--Hilbert action, it is in fact the inverse metric density.}, defined as the variation of the action with respect to the symmetric part of the Ricci tensor~(see Refs.~\cite{Eddington1923math,schrodinger1950space,Poplawski:2012bw}), i.e.,%% \hl{JZ: def.
@@
 %% by assuming a matter action that depends on $\bar{g}^{\mu\nu}$.
+Therefore, in the following we will restrict ourselves to consider $\mathfrak{g}^{\mu \nu} = \bar{g}^{\mu\nu}$.
 
@@
 \end{equation}
-is the usual Newtonian force induced by a massive source. Notice that we restricted ourselves to consider $\mathfrak{g}^{\mu \nu} = \bar{g}^{\mu\nu}$ to obtain the above result.
+is the usual Newtonian force induced by a massive source.
+%% Notice that we restricted ourselves to consider $\mathfrak{g}^{\mu \nu} = \bar{g}^{\mu\nu}$ to obtain the above result.
 
@@
 %%%%%%%%% COMPARISON GR %%%%%%%%%
-Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, a beyond-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
+Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, a \emph{post}-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
 Therefore, we should go beyond the Newtonian limit in order to compare our model with General Relativity.
@@
 Even though a comparison between the models does not require the imposition of vanishing torsion, for the sake of simplicity, at this stage we shall focus on a sector of the theory in which the connection is torsion-free.
-Notice that the vanishing torsion limit ---equivalent to take $T^{\lambda,\mu\nu} \to 0$ and $A_\mu \to 0$--- cannot be taken at the action level, and should be taken in the field equations.
+Notice that the vanishing torsion limit---equivalent to take $T^{\lambda,\mu\nu} \to 0$ and $A_\mu \to 0$---cannot be taken at the action level, but in the field equations.
 Interestingly, the field equations from Eq.~\eqref{4dfull} can be consistently \emph{truncated} under such requirements.
@@
 
-Intriguingly, the effective theory is not renormalizable ---according to the arguments in Refs.~\cite{McGady:2013sga,Camanho:2014apa}---, although it has been discussed in Ref.~\cite{Chen:2010at} that at least the ghost problem can be avoided through the arguments exposed in Refs.~\cite{Kleinert:1987eb,Bender:2007wu,Bender:2008vh,Mannheim:2009zj}.
+Intriguingly enough, the effective theory is not renormalizable---according to the arguments in Refs.~\cite{McGady:2013sga,Camanho:2014apa}---, although it has been discussed in Ref.~\cite{Chen:2010at} that at least the ghost problem can be avoided through the arguments exposed in Refs.~\cite{Kleinert:1987eb,Bender:2007wu,Bender:2008vh,Mannheim:2009zj}.
 

### 2016-04-11 MS.tex
With Vijay comments, and others by me

@@
 In this Appendix, we will present a brief compendium of known (Riemannian) metric solutions of Eq.~\eqref{SimpleEOM} in four dimensions.
-None of these workis original ---except the analysis presented as example in Sec.~\ref{Ex:sch}, and can be found in Refs.~\cite{gray1978einstein,derdzinski1980classification,derdzinski1982compact,Derdzinski:1985,Besse}.
+The results presented in this Appendix is not original, and can be found in Refs.~\cite{gray1978einstein,derdzinski1980classification,derdzinski1982compact,Derdzinski:1985,Besse}.
 
@@
 
-\section{\label{Schw}Explicit example: Schwarzschild ansatz, and Birkhoff theorem\label{Ex:sch}}
+\section{\label{Schw}Explicit example: Schwarzschild ansatz, and Birkhoff theorem}
 

### 2016-04-12 AffGR-PRD.tex
Improved conclusions, unfinished

@@
 \begin{equation}
-  %\label{eff-action}
+  \label{eff-action}
   S_{\text{eff}} = \int\dn{4}{x} \Big( C_1\, R_{\lambda\mu}{}^{\lambda}{}_\nu \nabla_\rho %T^{\nu,\rho\sigma}
@@
   \nab{[\rho} R_{\mu]\nu} + \kappa \nab{\nu} R_{\mu\rho}{}^\lambda{}_\lambda = 0,
+  \label{almostSimpleEOM}
 \end{equation}
@@
 A quick analysis of the field equations \`a la Palatini shows that Eqs.~\eqref{SimpleEOM} and~\eqref{harm-curv} are obtained only from the variation with respect to the connection.
-Albeit this effective theory has been widely studied, the extra field equation (for the metric field) strongly constraints the solutions of the gravitational Yang--Mills~\footnote{We thank J.~Zanelli for sharing his personal communications with C.~N.~Yang, and clarify this aspect of the effective model.}.
+Albeit this effective theory has been widely studied, the extra field equation (for the metric field) strongly constraints the solutions of the gravitational Yang--Mills~\cite{JZcomm}.
 However, that complication does not affect our affine interpretation of the theory, where the metric is absent.
@@
 
-Summarizing, we have shown that the  \emph{purely affine gravity} constructed in Ref.~\cite{Skirzewski:2014eta} possesses a well-defined torsionless limit, which generalizes the equations of motion  from General Relativity, and its field equations are equivalent to those obtained from a Yang--Mills theory for the spacetime connection, or Stephenson--Kilmister--Yang theory.
+In this paper we have shown that the \emph{purely affine gravity} presented in Ref.~\cite{Skirzewski:2014eta} is the most general (polynomial) model for an affine theory of gravity, see the Appendix~\ref{sec:ld}, consistent with invariance under diffeomorphisms.
+The action in Eq.~\eqref{4dfull}, is parametrized by a nineteen-dimensional moduli space---after the boundary and topological terms have been dropped---, which in some sense made us wonder about a possible \emph{duality} between this model and the one proposed in Ref.~\cite{Pagani:2015ema}, even though the last one possesses a metric field.
+%% (boundary condition, topological terms, ...)
+
+The field equations obtained from the action~\eqref{4dfull} are a set of very complex coupled partial differential equations.
+However, they are consistent with the limit of $T^{\lambda,\mu\nu}$ and $A_\mu$ going to zero.
+This consistency is what is usually called a \emph{consistent truncation} of the theory.
+In this paper we have restrict ourselves to such a truncation of our model, which constrained us to the torsion-less sector of the moduli space.
+Additionally, this truncation leaves only one nontrivial field equation, Eq.~\eqref{SimpleEOM}.
+%%, which can be obtained from a simple ``effective'' theory whose action is Eq.~\eqref{eff-action}.
+Moreover, by considering torsion-free equi-affine connections---those preserving a volume element---or a Levi-Civita connection---in the cases where the manifold is metric---, the remaining field equation simplifies even further to Eq.~\eqref{SimpleEOM}.
+
+The equation~\eqref{SimpleEOM} is a generalization of the field equations in General Relativity, in the sense that, any Einstein manifold (whose Ricci tensor is proportional to the metric) satisfy the parallel Ricci condition,
+\begin{equation}
+  \nab{\lambda} R_{\mu\nu} = 0.
+\end{equation}
+Although all Einstein manifolds satisfy the parallel Ricci condition, the contrary does not hold.
+Therefore, in Appendix~\ref{Known} we present a summary of known (metric) solutions to Eq.~\eqref{SimpleEOM}.
+In addition, in Appendix~\ref{Schw} we prove that an ansatz metric with spherical symmetry solves the field equation only if it is static.
+This is a Birkhoff-like theorem for our model, however, the non-linearity of the equations does not assure the uniqueness of the solution.
+Nonetheless, certain equations become linear if the functions $A$ and $B$ in Eq.~\eqref{ABmetric} are equal.
+Therefore, the unique solution is the $\Lambda$-Schwarzschild solution.
+
+We also pointed that our field equation~\eqref{SimpleEOM} can be obtained from an effective action, known as Stephenson--Kilmister--Yang (SKY) theory~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, which is built up in the spirit of a Yang--Mills theory for gravity.
+Despite the SKY theory has been criticized by many people, including C.~N.~Yang himself~\cite{JZcomm}, because its field equations are higher order differential equations for the metric field, and also because the field equation for the metric is so restrictive that the Schwarzschild metric is not a solution, in our model the fundamental gravitational field is the connection.
+The field equation~\eqref{SimpleEOM} is a second order partial differential equation for the connection.
+Although we have presented a series of metric solutions of the effective field equations (restricted to the torsion-free sector of the theory), the correct way to proceed is to propose a connection ansatz compatible with the symmetries of the problem.
+Using this procedure, we expect to find a non-metric solution to the field equation~\cite{OCF-future2}.
+
+We would like to highlight that, since all gravitational effects described by standard General Relativity are contained in our model, particularly in the sector of metric compatible, torsion-free connections, there is enough liberty to start considering new cosmological effects coming from both nonvanishing torsion and non-metric connections with vanishing torsion, beside the results reported in Ref.~\cite{Chen:2013kia,Chen:2013ota}.
+
+As a first step toward the coupling of matter with our polynomial affine gravity, we showed that there is a construct which might play the role of an inverse metric density.
+Notice that such a tensor density \emph{does not} necessarily satisfy a non-degeneracy condition as required for a metric, but even though it is an interesting question to ask under what considerations does this construct satisfy the properties of a metric.
+Using this tensor density, we proposed a \emph{kinetic} term for a scalar field (under diffeomorphisms), and show that in generically the effective field equations for gravity are equivalent to those of General Relativity, when we restrict ourselves to the torsion-free sector.
+Despite the fact that in this sector the field equation for the scalar field collapses, and cannot be obtained from the variation of the action, using the algorithm proposed in Ref.~\cite{Bekenstein:2014uwa}, the usual scalar field equation is recovered in virtue of the second Bianchi identity.
+
+Finally, we analyzed the second order perturbation of the action in Eq.~\eqref{4dfull}, around a maximally symmetric spacetime.
+
+{\huge{\textcolor{red}{Working Here!}}}
+
+%% Summarizing, we have shown that the \emph{purely affine gravity} presented in Ref.~\cite{Skirzewski:2014eta} possesses a well-defined torsionless limit, which generalizes the equations of motion  from General Relativity, and its field equations are equivalent to those obtained from a Yang--Mills theory for the spacetime connection, or Stephenson--Kilmister--Yang theory.
 Consequently, all gravitational effects described by standard General Relativity are contained in our model, even though the torsion field is kept to zero.
 Regarding this aspect, we would like to emphazise that there is enough liberty to start considering new cosmological effects coming from both nonvanishing torsion and nonmetric connections with vanishing torsion, beside the results reported in Ref.~\cite{Chen:2013kia,Chen:2013ota}.
-Moreover, our gravitational model coupled to a scalar field through the \emph{tensor density} $\mathfrak{g}^{\mu\nu}$ ---in the vanishing torsion consideration---, generalizes GR minimally coupled to a massless scalar field.
+%% Moreover, our gravitational model coupled to a scalar field through the \emph{tensor density} $\mathfrak{g}^{\mu\nu}$ ---in the vanishing torsion consideration---, generalizes GR minimally coupled to a massless scalar field.
 In a forthcoming paper, we will consider more general matter content (unrelated to the work in Ref.~\cite{Cook:2008mx}), and some properties of the field equations which differ from those of General Relativity.
@@
 \begin{acknowledgments}
-  We thank to N.~Pantoja, A.~Melfo and R.~L.~Bryant for their helpful discussions and inspiring comments, to J.
-Zanelli for his suggestions on the physical insight into the problem and careful but critical review of the manuscript.
+  We thank to N.~Pantoja, A.~Melfo, M.~Blagojevi\'c, B.~Cvetkovi\'c, V.~Sharma, O.~Orellana and R.~L.~Bryant for their helpful discussions and inspiring comments, to J.~Zanelli for his suggestions on the physical insight into the problem and careful but critical review of the manuscript.
   This work was partially supported by CONICYT (Chile) under project No. 79140040.

### 2016-05-03 AffGR-PRD.tex
Several modifications. Comments about future changes

@@
 \end{equation*}
-that can be written in the more conventional form~\footnote{Notice that $\alpha$ is the gravitational coupling constant, which in Einstein--Hilbert gravity is $G_N$.}
+that can be written in the more conventional form~\footnote{We have used a suggestive notation by denoting with $g_{\mu\nu}$ a covariantly constant, invertible, and symmetric two-tensor.
+Notice that $\alpha$ is the gravitational coupling constant, which in Einstein--Hilbert gravity is proportional to $G_N$.}
 \begin{equation}
@@
 
-A first step toward the analysis of renormalizability of the model should be the computation of the free propagators of the model around a given background.
-The choice of background will necessarily be taken in order to simplify the computations.
-Our first task is to expand up to second order in the fields around a flat background.
-Under these assumptions, and using the notation of Eqs.~\eqref{GammaExp}, the relevant part of the action~\eqref{4dfull} is
+A step toward the analysis of renormalizability of the model should be the computation of the free propagators of the model around a given background.
+The choice of background will necessarily in order to simplify the computations.
+Our first task is to expand up to second order in the fields around a maximally symmetric Riemannian background.
+Maximally symmetric spaces possess remarkably simple curvature tensors~\cite{weinberg1972gravitation},
+\begin{equation}
+  R_{\mu\nu}{}^\lambda{}_\rho = {K} \Big( g_{\nu\rho} \delta^\lambda_\mu - g_{\mu\rho} \delta^\lambda_\nu \Big),
+\end{equation}
+and the Einstein's field equations in vacuum
+\begin{equation}
+  R_{\mu\nu} = \Lambda \, g_{\mu\nu},
+\end{equation}
+require that $K = \frac{\Lambda}{3}$. 
+%% Additionally, 
+Therefore, in notation of Eqs.~\eqref{GammaExp} we have that $A = T = 0$, and the contribution due to the torsion (and non-metricity) enters as a perturbative effect.
+Thus, most terms in the action~\eqref{4dfull} do not contribute to the propagator analysis.
+Additionally, the first order perturbation of the curvature tensor is
+\begin{equation}
+  R_{\mu\nu}{}^\lambda{}_\rho = \frac{\Lambda}{3}\,   {\delta}^{\lambda}_{\mu} {g}_{\rho \nu} - \frac{\Lambda}{3}\,   {\delta}^{\lambda}_{\nu} {g}_{\rho \mu} + {\nabla}_{\mu}{{\gamma}^{\lambda}\,_{\rho \nu}}\,  - {\nabla}_{\nu}{{\gamma}^{\lambda}\,_{\rho \mu}}.
+\end{equation}
+Under these assumptions, the relevant terms of the action~\eqref{4dfull} are those accompanied by the couplings $B_i$, $C_i$ and $E_i$, and the second order perturbation of the action yields
 \begin{widetext}
@@
     \label{4dflatx}
-    S[\gamma,t,a] =
+    S^{(2)}[\gamma,t,a] =
     \int\dn{4}{x} \bigg[
-      C_1 \partial_{\mu}\gamma^{\mu}{}_{\rho\nu} \partial_\sigma t^{\nu\rho\sigma}
-      +2 C_2 \partial_{\mu}\gamma^{\rho}{}_{\nu\rho} \partial_\sigma t^{\sigma\mu\nu}
-      + E_1 \partial_{(\rho}t^{\rho\mu\nu}\partial_{\sigma)}t^{\sigma\lambda\kappa}\epsilon_{\mu\nu\lambda\kappa}
-      + E_2 \partial_{(\lambda} t^{\lambda\mu\nu}\partial_{\mu)} a_\nu
+      C_1 \big( - \Lambda {\nabla}_{\alpha}{{t}^{\beta \alpha \gamma}}\,  {g}_{\beta \gamma} - \Lambda {\gamma}^{\alpha}\,_{\beta \delta} {g}_{\alpha \gamma} {t}^{\beta \delta \gamma} + {\nabla}_{\alpha}{{\gamma}^{\alpha}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\beta \delta \gamma}}\,  - {\nabla}_{\alpha}{{\gamma}^{\beta}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\delta \alpha \gamma}}\, \big)
+      + 2\, C_2 {\nabla}_{\alpha}{{\gamma}^{\beta}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\gamma \alpha \delta}}\,
+      + E_1 {\epsilon}_{\alpha \beta \delta \eta} {\nabla}_{\gamma}{{t}^{\gamma \alpha \beta}}\,  {\nabla}_{\lambda}{{t}^{\lambda \delta \eta}}\,
+      + E_2 \big({\nabla}_{\alpha}{{a}_{\beta}}\,  {\nabla}_{\gamma}{{t}^{\gamma \alpha \beta}}\,  - {\nabla}_{\alpha}{{a}_{\beta}}\,  {\nabla}_{\gamma}{{t}^{\alpha \beta \gamma}}\, \big)
+      + \Big(B_1 + \frac{1}{3}\, B_2 \Big) \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {g}_{\eta \lambda} {t}^{\eta \alpha \beta} {t}^{\lambda \gamma \delta}
+      + \Big( - B_3 + \frac{2}{3}\, B_4 \Big) \Lambda {a}_{\alpha} {g}_{\beta \gamma} {t}^{\beta \alpha \gamma}
       \bigg].
+    \label{4dmax}
   \end{dmath}
 \end{widetext}
-In momentum space, the second order perturbation is
+%% In momentum space, the second order perturbation is
+%% \begin{dmath}[compact, spread=2pt]
+%%   \label{4dflat}
+%%   S =
+%%   \int\dn{4}{p}\bigg[
+%%     C_1 p_{\mu} p_\sigma\tilde\gamma^{\mu}{}_{\rho\nu}^* \tilde t^{\nu\rho\sigma}
+%%     + 2 C_2 p_{\mu} p_\sigma\tilde\gamma^{\rho}{}_{\nu\rho}^* \tilde t^{\sigma\mu\nu}
+%%     + E_1 p_{\rho} p_{\sigma} \tilde t^{\rho\mu\nu}{}^*\tilde t^{\sigma\lambda\kappa} \epsilon_{\mu\nu\lambda\kappa}
+%%     + E_2 p_{\lambda} p_{\mu} \tilde t^{\lambda\mu\nu}{}^* \tilde a_\nu
+%%     \bigg].
+%% \end{dmath}
+Longitudinal and transverse projectors can be introduced in order to decompose the action and specify in a more standard fashion the dynamics of Eq.~\eqref{4dmax}.
+This can be done since we have the metric $g_{\mu\nu}$ compatible with the connection, and $\nabla^\mu=g^{\mu\nu}\nabla_\nu$.
+Additionally we will denote by $\Delta = \nabla^\mu\nabla_\mu$ the covariant Laplacian.
+Let us define $P_{\texttt{L}}{}^\mu{}_\nu=\nabla^\mu\Delta^{-1} \nabla_\nu $, the projector into logitudinal vectors, and similarly $P_\perp{}^\mu{}_\nu=\delta^\mu_\nu -P_{\texttt{L}}{}^\mu{}_\nu$ is the projector into transverse vectors.
+Therefore, transverse indices are defined such that $\nabla_\mu A_\perp{}^{\mu}=0$.
+
+Thus, the perturbations can be split into their longitudinal and transverse components as
+\begin{dmath}
+  a_\mu = {a_\perp}_{\mu} + {\nabla}_{\mu}{aL},
+\end{dmath}
+\begin{dmath}
+  {t}^{\lambda \mu \nu} =
+  {t_\perp}^{\lambda \mu \nu}
+  + 2  {\nabla}^{\lambda} {t_{\texttt{a}}^{\mu \nu}}
+  - 2  {\nabla}^{[\mu}{{t_{\texttt{a}}}^{\nu] \lambda}} 
+  + 2  {\nabla}^{\mu}{{t_{\texttt{s}}}^{\nu \lambda}}
+  + 2  {\nabla}^{\lambda [\mu}{{t_{\texttt{v}}}^{\nu]}}
+\end{dmath}
+and
+\begin{dmath}
+  {\gamma}^{\lambda}\,_{\mu \nu}  =
+  {\gamma_\perp}^{\lambda}{}_{\mu \nu}
+  + {\nabla}^{\lambda}{{\gamma_{\texttt{s}}}_{\mu \nu}}
+  + 2  {\nabla}_{(\mu}{{\gamma}^{\lambda}\,_{\nu)}}
+  + 2  {\nabla}^{\lambda}\nabla_{(\mu}{{\gamma_{\texttt{v}}}_{\nu)}}
+  + 2  \nab{(\mu} \nab{\nu)} {{\gamma_{\texttt{v}'}}^{\lambda}} 
+  + 2  {\nabla}^{\lambda}\nab{(\mu} \nab{\nu)}{\gamma_{\texttt{L}}},
+\end{dmath}
+where all the indices are transverse except those of the derivative $\nabla_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the sub indices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation.
+In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless.
+\hl{check the last sentence.
+Is this ${t_s}^{\alpha}{}_{\alpha}$?...
+If true, this condition will kill the scalars contribution in the next equations}
+
+\begin{widetext}
+  \label{pert-Lambda}
   \begin{dmath}[compact, spread=2pt]
-  \label{4dflat}
-  S =
-  \int\dn{4}{p}\bigg[
-    C_1 p_{\mu} p_\sigma\tilde\gamma^{\mu}{}_{\rho\nu}^* \tilde t^{\nu\rho\sigma}
-    + 2 C_2 p_{\mu} p_\sigma\tilde\gamma^{\rho}{}_{\nu\rho}^* \tilde t^{\sigma\mu\nu}
-    + E_1 p_{\rho} p_{\sigma} \tilde t^{\rho\mu\nu}{}^*\tilde t^{\sigma\lambda\kappa} \epsilon_{\mu\nu\lambda\kappa}
-    + E_2 p_{\lambda} p_{\mu} \tilde t^{\lambda\mu\nu}{}^* \tilde a_\nu
-    \bigg].
+    S = \int \dn{4}{x} \Bigg(
+    C_1 \Big( {t_s}^{\alpha\beta }-\frac{1}{4}g^{\alpha\beta}{{t_s}^{\gamma}{}_{\gamma}} \Big) \bigg( -  (\frac{4\Lambda^2}{3}+\Lambda \Delta+\Delta^2) {\gamma_s}_{\alpha\beta}  
+    - \frac{8}{3}   \Lambda\Delta {{\gamma}_{\alpha\beta}} 
+    \bigg)
+    + {{t_v}^{\alpha}}\bigg(
+    \Big(( C_1 - 2\, C_2) \Delta^3 + \frac{1}{3}( C_1 + 2C_2 )\Lambda\Delta^2 + \frac{2}{3}( 2C_1 +  C_2 )\Lambda^2\Delta - \frac{1}{3}C_1  \Lambda^3\Big){{\gamma_v}_{\alpha}}
+    + \Big((C_1 - 2\, C_2) \Lambda\Delta - 2\, C_2 \Delta^2\Big){{\gamma_\perp}^{\beta}\,_{\beta \alpha}}
+    + 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} \Delta{\nabla}^{\beta }\Delta{{t_a}^{\gamma\delta}}  
+    +\Big(- 2\, E_2 \Delta^2 +  (- E_2 + B_3 - \frac{2}{3}\, B_4) \Lambda\Delta\Big){a_\perp}_{\alpha} 
+    \bigg)
+    + {{t_s}^{\alpha}{}_{\alpha}}\bigg( \frac{2}{3}C_1 \Lambda\Delta{{\gamma}^{\beta}\,_{\beta}} 
+    + \frac{2}{3}E_2 \Lambda \Delta{a_L}  
+    - \frac{4}{3}C_1 \Lambda^2 \Delta{g_L}
+    - \frac{1}{4}C_1 (\Lambda + \Delta)  \Delta{{\gamma_s}^{\beta}{}_{\beta}}
+    \bigg)   \Bigg),
   \end{dmath}
-Longitudinal and transverse projectors can be introduced in order to decompose the action and specify in a more standard fashion the dynamics of Eq.~\eqref{4dflat}.
-This can be done since we have the metric $\eta_{\mu\nu}$ compatible with the connection and $p^\mu = \eta^{\mu\nu}p_\nu$.
-We define the projector into logitudinal vectors $P_{\texttt{L}}{}^\mu_\nu = \tfrac{1}{p^2}p^\mu p_\nu $, such that $$A_{\texttt{L}\mu} = P_{\texttt{L}}{}^\nu_\mu \, A_\nu = A_{\texttt{L}}{}p_{\mu},$$ where $A_{\texttt{L}}=\tfrac{1}{p^2} p^\mu A_\mu$.
+  \hl{1.- Is it Ok? 2.- Are the $B_3$ and $B_4$ there?}
+  where $\Delta \equiv \nabla^{\alpha}\nabla_{\alpha}$ is the Laplacian operator.
+  This action sets the dynamics of two transverse-traceless tensors (or specific combination of tensors), as well as two transverse vectors and two scalars.
+\end{widetext}
+%% We define the projector into logitudinal vectors $P_{\texttt{L}}{}^\mu_\nu = \tfrac{1}{p^2}p^\mu p_\nu $, with $p^\mu = g^{\mu\nu} p_\nu$, such that $$A_{\texttt{L}\mu} = P_{\texttt{L}}{}^\nu_\mu \, A_\nu = A_{\texttt{L}} \, p_{\mu},$$ where $A_{\texttt{L}}=\tfrac{1}{p^2} p^\mu A_\mu$.
 Similarly, $P_\perp{}^\mu_\nu=\delta^\mu_\nu -P_{\texttt{L}}{}^\mu_\nu$ defines the projector into transverse vectors, i.e., $A_{\perp \mu}=P_{\perp}{}_\mu^\nu A_\nu$.
 Thus,
-\begin{dmath}
-  \label{transversea}
-  \tilde a_\nu=a_\perp{}_{\nu}+a_{\texttt{L}} p_\nu,
-\end{dmath}
-\begin{dmath}
-  \label{transverset}
-  \tilde t^{\lambda\mu\nu}=\frac{1}{p}\epsilon^{\mu\nu\kappa\rho}p_\rho t_\perp^{\lambda}{}_\kappa+\frac{1}{p^2}p^\lambda\epsilon^{\mu\nu\kappa\rho}p_\rho t_{\texttt{a}\kappa}-\frac{2}{p^2}p^{[\mu}\epsilon^{\nu]\lambda\kappa\rho}p_\rho t_{\texttt{a}\kappa}+\frac{2}{p}p^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+\frac{2}{p^2}p^\lambda p^{[\mu} t_{\texttt{v}}^{\nu]},
-\end{dmath}
-\begin{dmath}
-  \label{transversegamma}
-  \tilde \gamma^{\lambda}{}_{\mu\nu}=\gamma_\perp^{\lambda}{}_{\mu\nu}+\frac{1}{p}p^\lambda \gamma_{\texttt{s}}{}_{\mu\nu}+\frac{2}{p}p_{(\mu} \gamma^\lambda{}_{\nu)}+\frac{2}{p^2}p^\lambda p_{(\mu} \gamma_{\texttt{v}}{}_{\nu)}+ \frac{1}{p^2}p_{\mu} p_{\nu} \gamma'_{\texttt{v}}{}^\lambda+\frac{1}{p^3}p^\lambda p_{\mu} p_{\nu} \gamma_{\texttt{L}},
-\end{dmath}
-where all the indices are transverse except those of the momentum $p_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the subindices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation.
+%% \begin{dmath}
+%%   \label{transversea}
+%%   \tilde a_\nu=a_\perp{}_{\nu}+a_{\texttt{L}} p_\nu,
+%% \end{dmath}
+%% \begin{dmath}
+%%   \label{transverset}
+%%   \tilde t^{\lambda\mu\nu}=\frac{1}{p}\epsilon^{\mu\nu\kappa\rho}p_\rho t_\perp^{\lambda}{}_\kappa+\frac{1}{p^2}p^\lambda\epsilon^{\mu\nu\kappa\rho}p_\rho t_{\texttt{a}\kappa}-\frac{2}{p^2}p^{[\mu}\epsilon^{\nu]\lambda\kappa\rho}p_\rho t_{\texttt{a}\kappa}+\frac{2}{p}p^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+\frac{2}{p^2}p^\lambda p^{[\mu} t_{\texttt{v}}^{\nu]},
+%% \end{dmath}
+%% \begin{dmath}
+%%   \label{transversegamma}
+%%   \tilde \gamma^{\lambda}{}_{\mu\nu}=\gamma_\perp^{\lambda}{}_{\mu\nu}+\frac{1}{p}p^\lambda \gamma_{\texttt{s}}{}_{\mu\nu}+\frac{2}{p}p_{(\mu} \gamma^\lambda{}_{\nu)}+\frac{2}{p^2}p^\lambda p_{(\mu} \gamma_{\texttt{v}}{}_{\nu)}+ \frac{1}{p^2}p_{\mu} p_{\nu} \gamma'_{\texttt{v}}{}^\lambda+\frac{1}{p^3}p^\lambda p_{\mu} p_{\nu} \gamma_{\texttt{L}},
+%% \end{dmath}
+%% where all the indices are transverse except those of the momentum $p_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the subindices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation.
 In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless.
@@
 In the meanwhile we shall not do this expansion.
-\begin{widetext}
-  Using Eqs.~\eqref{transversea}, \eqref{transverset} and~\eqref{transversegamma}, the action~\eqref{4dflat} is then rewritten
+%% \begin{widetext}
+%%   Using Eqs.~\eqref{transversea}, \eqref{transverset} and~\eqref{transversegamma}, the action~\eqref{4dflat} is then rewritten
+%%   \begin{dmath}
+%%     \label{4dtransverse}
+%%     S =
+%%     \int\dn{4}{p}p^2
+%%     \bigg[
+%%       2C_1 \hat{p}_\mu \hat{p}_\sigma\Big(\gamma_\perp^{\mu}{}_{\rho\nu}+\hat{p}^\mu \gamma_{\texttt{s}}{}_{\rho\nu}+2\hat{p}_{(\rho} \gamma^\mu{}_{\nu)}+2\hat{p}^\mu \hat{p}_{(\rho} \gamma_{\texttt{v}}{}_{\nu)}+ \hat{p}_{\rho} \hat{p}_{\nu} \gamma'_{\texttt{v}}{}^\mu+\hat{p}^\mu \hat{p}_{\rho} \hat{p}_{\nu} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\rho\sigma\delta\eta}\hat{p}_\eta t_\perp^{\nu}{}_\delta+\hat{p}^\nu t_{\texttt{a}}^{\rho\sigma}-2\hat{p}^{[\rho} t_{\texttt{a}}^{\sigma]\nu}+2\hat{p}^{[\rho} t_{\texttt{s}}^{\sigma]\nu}+2\hat{p}^\nu \hat{p}^{[\rho} t_{\texttt{v}}^{\sigma]}\Big)
+%%       +2C_2 \hat{p}_{\mu} \hat{p}_\sigma\Big(\gamma_\perp^{\rho}{}_{\nu\rho}+\hat{p}^\rho \gamma_{\texttt{s}}{}_{\nu\rho}+2\hat{p}_{(\nu} \gamma^\rho{}_{\rho)}+2\hat{p}^\rho \hat{p}_{(\nu} \gamma_{\texttt{v}}{}_{\rho)}+\hat{p}_{\nu} \hat{p}_{\rho} \gamma'_{\texttt{v}}{}^\rho +\hat{p}^\rho \hat{p}_{\nu} \hat{p}_{\rho} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\kappa+\hat{p}^\sigma t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\sigma}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\sigma}+2\hat{p}^\sigma \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)
+%%       +E_1 \hat{p}_{\rho} \hat{p}_{\sigma}\Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\rho}{}_\kappa+\hat{p}^\rho t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{\mu} t_{\texttt{a}}^{\nu\rho}+2\hat{p}^{\mu} t_{\texttt{s}}^{\nu\rho}+2\hat{p}^\rho \hat{p}^{\mu} t_{\texttt{v}}^{\nu}\Big)^*\Big(\epsilon^{\lambda\kappa\delta\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\delta+\hat{p}^\sigma t_{\texttt{a}}^{\lambda\kappa}-2\hat{p}^{\lambda} t_{\texttt{a}}^{\kappa\sigma}+2\hat{p}^{\lambda} t_{\texttt{s}}^{\kappa\sigma}+2\hat{p}^\sigma \hat{p}^{\lambda} t_{\texttt{v}}^{\kappa}\Big)\epsilon_{\mu\nu\lambda\kappa}
+%%       +E_2 \hat{p}_{\lambda} \hat{p}_{\mu} \Big(\epsilon^{\mu\nu\kappa\rho}\hat{p}_\rho t_\perp^{\lambda}{}_\kappa+\hat{p}^\lambda t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\lambda}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+2\hat{p}^\lambda \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)^*\Big(a_\perp{}_\nu+\hat{p}_\nu a_{\texttt{L}}\Big)
+%%       \bigg],
+%%   \end{dmath}
+%% \end{widetext}
+%% simplifiying
+%% \begin{dmath}
+%%   \label{WithGhosts}
+%%   S=\int d^4p\Bigg[-2C_1 p^2\gamma_{\texttt{s}\mu\nu}^*t_{\texttt{s}}^{\mu\nu}
+%%     +p^2\Big((-2C_1+2C_2)\gamma_{\texttt{v}\mu}+2C_2\gamma_{\perp\mu\nu}^\nu
+%%     +8E_1t_{\texttt{a}\mu}+E_2a_{\perp\mu}\Big)^*t_{\texttt{v}}^\mu
+%%     \Bigg]
+%% \end{dmath}
+When we restrict ourselves to perturbations around a flat (Minkowski) spacetime, the above equation simplifies greatly,
 \begin{dmath}
-    \label{4dtransverse}
-    S =
-    \int\dn{4}{p}p^2
-    \bigg[
-      2C_1 \hat{p}_\mu \hat{p}_\sigma\Big(\gamma_\perp^{\mu}{}_{\rho\nu}+\hat{p}^\mu \gamma_{\texttt{s}}{}_{\rho\nu}+2\hat{p}_{(\rho} \gamma^\mu{}_{\nu)}+2\hat{p}^\mu \hat{p}_{(\rho} \gamma_{\texttt{v}}{}_{\nu)}+ \hat{p}_{\rho} \hat{p}_{\nu} \gamma'_{\texttt{v}}{}^\mu+\hat{p}^\mu \hat{p}_{\rho} \hat{p}_{\nu} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\rho\sigma\delta\eta}\hat{p}_\eta t_\perp^{\nu}{}_\delta+\hat{p}^\nu t_{\texttt{a}}^{\rho\sigma}-2\hat{p}^{[\rho} t_{\texttt{a}}^{\sigma]\nu}+2\hat{p}^{[\rho} t_{\texttt{s}}^{\sigma]\nu}+2\hat{p}^\nu \hat{p}^{[\rho} t_{\texttt{v}}^{\sigma]}\Big)
-      +2C_2 \hat{p}_{\mu} \hat{p}_\sigma\Big(\gamma_\perp^{\rho}{}_{\nu\rho}+\hat{p}^\rho \gamma_{\texttt{s}}{}_{\nu\rho}+2\hat{p}_{(\nu} \gamma^\rho{}_{\rho)}+2\hat{p}^\rho \hat{p}_{(\nu} \gamma_{\texttt{v}}{}_{\rho)}+\hat{p}_{\nu} \hat{p}_{\rho} \gamma'_{\texttt{v}}{}^\rho +\hat{p}^\rho \hat{p}_{\nu} \hat{p}_{\rho} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\kappa+\hat{p}^\sigma t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\sigma}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\sigma}+2\hat{p}^\sigma \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)
-      +E_1 \hat{p}_{\rho} \hat{p}_{\sigma}\Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\rho}{}_\kappa+\hat{p}^\rho t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{\mu} t_{\texttt{a}}^{\nu\rho}+2\hat{p}^{\mu} t_{\texttt{s}}^{\nu\rho}+2\hat{p}^\rho \hat{p}^{\mu} t_{\texttt{v}}^{\nu}\Big)^*\Big(\epsilon^{\lambda\kappa\delta\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\delta+\hat{p}^\sigma t_{\texttt{a}}^{\lambda\kappa}-2\hat{p}^{\lambda} t_{\texttt{a}}^{\kappa\sigma}+2\hat{p}^{\lambda} t_{\texttt{s}}^{\kappa\sigma}+2\hat{p}^\sigma \hat{p}^{\lambda} t_{\texttt{v}}^{\kappa}\Big)\epsilon_{\mu\nu\lambda\kappa}
-      +E_2 \hat{p}_{\lambda} \hat{p}_{\mu} \Big(\epsilon^{\mu\nu\kappa\rho}\hat{p}_\rho t_\perp^{\lambda}{}_\kappa+\hat{p}^\lambda t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\lambda}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+2\hat{p}^\lambda \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)^*\Big(a_\perp{}_\nu+\hat{p}_\nu a_{\texttt{L}}\Big)
+  S = \int \dn{4}{x} \, \bigg[
+    - C_1 ( \Delta\gamma_{\texttt{s}\mu\nu})^* \Delta t_{\texttt{s}}^{\mu\nu}
+    + \Big( ( C_1 - 2 C_2) \nabla^\nu \Delta \nabla_\nu \gamma_{\texttt{v}\mu}
+    - 2 C_2 \Delta \gamma^\nu_{\perp\nu\mu}
+    - 8 E_1 \epsilon_{\alpha\beta\nu\mu} \nabla^{\alpha} \Delta t_{\texttt{a}}^{\beta\nu}
+    - 2 E_2 \Delta a_{\perp\mu} \Big)^* \Delta t_{\texttt{v}}^\mu
     \bigg],
 \end{dmath}
-\end{widetext}
-simplifiying
-\begin{dmath}
-  \label{WithGhosts}
-  S=\int d^4p\Bigg[-2C_1 p^2\gamma_{\texttt{s}\mu\nu}^*t_{\texttt{s}}^{\mu\nu}
-    +p^2\Big((-2C_1+2C_2)\gamma_{\texttt{v}\mu}+2C_2\gamma_{\perp\mu\nu}^\nu
-    +8E_1t_{\texttt{a}\mu}+E_2a_{\perp\mu}\Big)^*t_{\texttt{v}}^\mu
-    \Bigg]
-\end{dmath}
+\hl{Where are the scalars?
+This has 18 dof, while the previous one has 20 dof.
+According to the counting, there are 18...
+I suppose that eighteen is the correct answer, but What is wrong in the first expression?} and it is clear that there are only eighteen degrees of freedom, corresponding to a couple of transverse-traceless rank-two-tensors, and a couple of transverse vectors.
+
+We have checked, using the method introduced in Ref.~\cite{Diaz:2014yua}, that the formal counting of degrees of freedom for the effective action in Eq.~\eqref{eff-action} yields eighteen degrees of freedom.
+We discover during the implementation of these program, that our model presents an extra symmetry associated to the metric independence property.
 
@@
 
-In this paper we have shown that the \emph{purely affine gravity} presented in Ref.~\cite{Skirzewski:2014eta} is the most general (polynomial) model for an affine theory of gravity, see the Appendix~\ref{sec:ld}, consistent with invariance under diffeomorphisms.
+In this paper we have shown that the \emph{polynomial affine gravity} presented in Ref.~\cite{Skirzewski:2014eta} is the most general (polynomial) model for an affine theory of gravity, see the Appendix~\ref{sec:ld}, consistent with invariance under diffeomorphisms.
 The action in Eq.~\eqref{4dfull}, is parametrized by a nineteen-dimensional moduli space---after the boundary and topological terms have been dropped---, which in some sense made us wonder about a possible \emph{duality} between this model and the one proposed in Ref.~\cite{Pagani:2015ema}, even though the last one possesses a metric field.

### 2016-05-03 MS.tex
Several modifications. Comments about future changes

@@
 At this stage, we have proved that \emph{any spherically symmetric (metric) solution of the Eqs.~\eqref{SimpleEOM} is necessarily static}, which is one of the main statements of Birkhoff's theorem.
-This result, simplifies the Eq.~\eqref{hugeeq} and makes clearer the necessity of setting $A(r) = B(r)$ to solve the equations of motion.
-Finally, according to Eq.~\eqref{simplef} the general (metric) solution is the (Anti-)de-Sitter--Schwarzschild metric.
+
+This result, simplifies the Eq.~\eqref{hugeeq} but the equations are still non-linear.
+However, one can get ride off the non-linearity by setting $A(r) = B(r)$.
+In this \emph{linearized} regime, according to Eq.~\eqref{simplef} the general (metric) solution is the (Anti-)de-Sitter--Schwarzschild metric.
+
+Although we restricted ourselves to the \emph{linearized} regime of the field equations, it is possible to go a bit further in the nonlinear regime.
+As a preliminary result~\cite{OCF-future2}, we have found that using the Frobenius methods with a Laurent series expansion, the leading order of the solutions is three-fold in the radial coordinate.
+These solutions correspond to the pairs given by $(\alpha,\beta)$---$\alpha$ (resp.
+$\beta)$ is the leading order of the series expansion for the function $A(r)$ (resp.
+$B(r)$)---equals to $(-1,-1)$, $(2,-2)$ and $(-2,2)$.
+%%Two of these branches coincide with the reciprocal and quadratic dependence on $r$ of $A$ and $B$, while the third one gives novel dependence,
+%% \begin{equation}
+%%   A(r) = 1 + \frac{\alpha}{r} + \beta r^2 + \frac{\gamma}{r^2},
+%% \end{equation}
+%% and
+%% \begin{equation}
+%%   B(r) = 1 + \frac{\alpha}{r} + (\beta + \gamma) r^2.
+%% \end{equation}

### 2016-05-04 AffGR-PRD.tex
Almost complete. Please finish conclusions

@@
 \begin{abstract}
-  We show that the effective field equations for a recently formulated polynomial affine model of gravity, in the sector of a torsion-free connection, accept general Einstein manifolds ---with or without cosmological constant--- as solutions.
+  We show that the effective field equations for a recently formulated polynomial affine model of gravity, in the sector of a torsion-free connection, accept general Einstein manifolds---with or without cosmological constant---as solutions.
 Moreover, the effective field equations coincide with some of those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
@@
 Finally, we present a naive analysis of the propagators of the gravitational theory, an their relation with the presence of ghost in the model.
+For completeness we include three appendices, including one in which it is shown that a Birkhoff-like theorem is valid for the analyzed sector.
 \end{abstract}
@@
 Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
-One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, by Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
+One of the most successful quantization methods of gravitational interactions---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, by Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
 On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
@@
 Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
-One of the most successful quantization methods of gravitational interactions ---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
+One of the most successful quantization methods of gravitational interactions---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, and Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
 On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
@@
 
-Equation~\eqref{SimpleEOM} is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature ---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.}  All Einstein manifolds, whose Ricci tensor is proportional to the metric, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition due to the metricity condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
+Equation~\eqref{SimpleEOM} is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.}  All Einstein manifolds, whose Ricci tensor is proportional to the metric, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition due to the metricity condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
 Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from General Relativity are present in the chosen scenario of our model.
@@
 
-Interestingly, the Eq.~\eqref{SimpleEOM} ---equivalently Eq.~\eqref{harm-curv}--- can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, %constructed as the trace of the
+Interestingly, the Eq.~\eqref{SimpleEOM}---equivalently Eq.~\eqref{harm-curv}---can be obtained from an effective gravitational Yang--Mills functional action~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, %constructed as the trace of the
 \begin{equation}
@@
 The theory does not require a spacetime metric, but instead we should consider the most general $\binom{2}{0}$-tensor density, $\mathfrak{g}^{\mu\nu}$,  built with the available fields, and use it to build Lagrangian densities for the matter content.
-Following our precept, the matter content ---scalar matter--- should couple to $\mathfrak{g}^{\mu\nu}$, given by
+Following our precept, the matter content---scalar matter---should couple to $\mathfrak{g}^{\mu\nu}$, given by
 \begin{dmath}
@@
 We have show, so far, that our model of polynomial purely affine gravity is compatible with General Relativity in the sector of vanishing torsion, and in addition the compatibility can be extended to include the interaction with a free scalar field.
-The analysis of this coupled system could be enhanced to include a potential for the scalar field,
+The analysis of this coupled system could be enhanced to include a potential for the scalar field, however, we are not considering this case at the moment.
 
@@
 Additionally we will denote by $\Delta = \nabla^\mu\nabla_\mu$ the covariant Laplacian.
-Let us define $P_{\texttt{L}}{}^\mu{}_\nu=\nabla^\mu\Delta^{-1} \nabla_\nu $, the projector into logitudinal vectors, and similarly $P_\perp{}^\mu{}_\nu=\delta^\mu_\nu -P_{\texttt{L}}{}^\mu{}_\nu$ is the projector into transverse vectors.
+Let us define $P_{\mathtt{L}}{}^\mu{}_\nu=\nabla^\mu\Delta^{-1} \nabla_\nu $, the projector into logitudinal vectors, and similarly $P_\perp{}^\mu{}_\nu=\delta^\mu_\nu -P_{\mathtt{L}}{}^\mu{}_\nu$ is the projector into transverse vectors.
 Therefore, transverse indices are defined such that $\nabla_\mu A_\perp{}^{\mu}=0$.
@@
 \begin{dmath}
-  a_\mu = {a_\perp}_{\mu} + {\nabla}_{\mu}{aL},
+  a_\mu = {a_\perp}_{\mu} + {\nabla}_{\mu}{a_{\mathtt{L}}},
 \end{dmath}
@@
   {t_\perp}^{\lambda \mu \nu}
-  + 2  {\nabla}^{\lambda} {t_{\texttt{a}}^{\mu \nu}}
-  - 2  {\nabla}^{[\mu}{{t_{\texttt{a}}}^{\nu] \lambda}} 
-  + 2  {\nabla}^{\mu}{{t_{\texttt{s}}}^{\nu \lambda}}
-  + 2  {\nabla}^{\lambda [\mu}{{t_{\texttt{v}}}^{\nu]}}
+  + 2  {\nabla}^{\lambda} {t_{\mathtt{a}}^{\mu \nu}}
+  - 2  {\nabla}^{[\mu}{{t_{\mathtt{a}}}^{\nu] \lambda}} 
+  + 2  {\nabla}^{\mu}{{t_{\mathtt{s}}}^{\nu \lambda}}
+  + 2  {\nabla}^{\lambda [\mu}{{t_{\mathtt{v}}}^{\nu]}}
 \end{dmath}
@@
   {\gamma_\perp}^{\lambda}{}_{\mu \nu}
-  + {\nabla}^{\lambda}{{\gamma_{\texttt{s}}}_{\mu \nu}}
+  + {\nabla}^{\lambda}{{\gamma_{\mathtt{s}}}_{\mu \nu}}
   + 2  {\nabla}_{(\mu}{{\gamma}^{\lambda}\,_{\nu)}}
-  + 2  {\nabla}^{\lambda}\nabla_{(\mu}{{\gamma_{\texttt{v}}}_{\nu)}}
-  + 2  \nab{(\mu} \nab{\nu)} {{\gamma_{\texttt{v}'}}^{\lambda}} 
-  + 2  {\nabla}^{\lambda}\nab{(\mu} \nab{\nu)}{\gamma_{\texttt{L}}},
+  + 2  {\nabla}^{\lambda}\nabla_{(\mu}{{\gamma_{\mathtt{v}}}_{\nu)}}
+  + 2  \nab{(\mu} \nab{\nu)} {{\gamma_{\mathtt{v}'}}^{\lambda}} 
+  + 2  {\nabla}^{\lambda}\nab{(\mu} \nab{\nu)}{\gamma_{\mathtt{L}}},
 \end{dmath}
-where all the indices are transverse except those of the derivative $\nabla_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the sub indices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation.
-In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless.
+where all the indices are transverse except those of the derivative $\nabla_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\mathtt{L}}$ indicates that this is the longitudinal projection of the tensor, while the sub indices $\mathtt{s}$, $\mathtt{a}$ and $\mathtt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation.
+%%In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless.
 \hl{check the last sentence.
@@
 \begin{widetext}
+  The perturbed action is then
+  \begin{dmath}[compact, spread=2pt]
   \label{pert-Lambda}
-  \begin{dmath}[compact, spread=2pt]
     S = \int \dn{4}{x} \Bigg(
-    C_1 \Big( {t_s}^{\alpha\beta }-\frac{1}{4}g^{\alpha\beta}{{t_s}^{\gamma}{}_{\gamma}} \Big) \bigg( -  (\frac{4\Lambda^2}{3}+\Lambda \Delta+\Delta^2) {\gamma_s}_{\alpha\beta}  
+    C_1 \Big( {t_{\mathtt{s}}}^{\alpha\beta }-\frac{1}{4}g^{\alpha\beta}{{t_{\mathtt{s}}}^{\gamma}{}_{\gamma}} \Big) \bigg( -  (\frac{4\Lambda^2}{3}+\Lambda \Delta+\Delta^2) {\gamma_{\mathtt{s}}}_{\alpha\beta}
     - \frac{8}{3}   \Lambda\Delta {{\gamma}_{\alpha\beta}} 
     \bigg)
-    + {{t_v}^{\alpha}}\bigg(
-    \Big(( C_1 - 2\, C_2) \Delta^3 + \frac{1}{3}( C_1 + 2C_2 )\Lambda\Delta^2 + \frac{2}{3}( 2C_1 +  C_2 )\Lambda^2\Delta - \frac{1}{3}C_1  \Lambda^3\Big){{\gamma_v}_{\alpha}}
+    + {{t_{\mathtt{v}}}^{\alpha}}\bigg(
+    \Big(( C_1 - 2\, C_2) \Delta^3 + \frac{1}{3}( C_1 + 2C_2 )\Lambda\Delta^2 + \frac{2}{3}( 2C_1 +  C_2 )\Lambda^2\Delta - \frac{1}{3}C_1  \Lambda^3\Big){{\gamma_{\mathtt{v}}}_{\alpha}}
     + \Big((C_1 - 2\, C_2) \Lambda\Delta - 2\, C_2 \Delta^2\Big){{\gamma_\perp}^{\beta}\,_{\beta \alpha}}
-    + 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} \Delta{\nabla}^{\beta }\Delta{{t_a}^{\gamma\delta}}  
+    + 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} \Delta{\nabla}^{\beta }\Delta{{t_{\mathtt{a}}}^{\gamma\delta}}  
     +\Big(- 2\, E_2 \Delta^2 +  (- E_2 + B_3 - \frac{2}{3}\, B_4) \Lambda\Delta\Big){a_\perp}_{\alpha} 
     \bigg)
-    + {{t_s}^{\alpha}{}_{\alpha}}\bigg( \frac{2}{3}C_1 \Lambda\Delta{{\gamma}^{\beta}\,_{\beta}} 
-    + \frac{2}{3}E_2 \Lambda \Delta{a_L}  
-    - \frac{4}{3}C_1 \Lambda^2 \Delta{g_L}
-    - \frac{1}{4}C_1 (\Lambda + \Delta)  \Delta{{\gamma_s}^{\beta}{}_{\beta}}
+    + {{t_{\mathtt{s}}}^{\alpha}{}_{\alpha}}\bigg( \frac{2}{3}C_1 \Lambda\Delta{{\gamma}^{\beta}\,_{\beta}} 
+    + \frac{2}{3}E_2 \Lambda \Delta{a_{\mathtt{L}}}  
+    - \frac{4}{3}C_1 \Lambda^2 \Delta{g_{\mathtt{L}}}
+    - \frac{1}{4}C_1 (\Lambda + \Delta)  \Delta{{\gamma_{\mathtt{s}}}^{\beta}{}_{\beta}}
     \bigg)   \Bigg),
   \end{dmath}
-  \hl{1.- Is it Ok? 2.- Are the $B_3$ and $B_4$ there?}
+  \hl{1.- Is it Ok?}
+\end{widetext}
 where $\Delta \equiv \nabla^{\alpha}\nabla_{\alpha}$ is the Laplacian operator.
-  This action sets the dynamics of two transverse-traceless tensors (or specific combination of tensors), as well as two transverse vectors and two scalars.
-\end{widetext}
-%% We define the projector into logitudinal vectors $P_{\texttt{L}}{}^\mu_\nu = \tfrac{1}{p^2}p^\mu p_\nu $, with $p^\mu = g^{\mu\nu} p_\nu$, such that $$A_{\texttt{L}\mu} = P_{\texttt{L}}{}^\nu_\mu \, A_\nu = A_{\texttt{L}} \, p_{\mu},$$ where $A_{\texttt{L}}=\tfrac{1}{p^2} p^\mu A_\mu$.
-Similarly, $P_\perp{}^\mu_\nu=\delta^\mu_\nu -P_{\texttt{L}}{}^\mu_\nu$ defines the projector into transverse vectors, i.e., $A_{\perp \mu}=P_{\perp}{}_\mu^\nu A_\nu$.
-Thus,
-%% \begin{dmath}
-%%   \label{transversea}
-%%   \tilde a_\nu=a_\perp{}_{\nu}+a_{\texttt{L}} p_\nu,
-%% \end{dmath}
-%% \begin{dmath}
-%%   \label{transverset}
-%%   \tilde t^{\lambda\mu\nu}=\frac{1}{p}\epsilon^{\mu\nu\kappa\rho}p_\rho t_\perp^{\lambda}{}_\kappa+\frac{1}{p^2}p^\lambda\epsilon^{\mu\nu\kappa\rho}p_\rho t_{\texttt{a}\kappa}-\frac{2}{p^2}p^{[\mu}\epsilon^{\nu]\lambda\kappa\rho}p_\rho t_{\texttt{a}\kappa}+\frac{2}{p}p^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+\frac{2}{p^2}p^\lambda p^{[\mu} t_{\texttt{v}}^{\nu]},
-%% \end{dmath}
-%% \begin{dmath}
-%%   \label{transversegamma}
-%%   \tilde \gamma^{\lambda}{}_{\mu\nu}=\gamma_\perp^{\lambda}{}_{\mu\nu}+\frac{1}{p}p^\lambda \gamma_{\texttt{s}}{}_{\mu\nu}+\frac{2}{p}p_{(\mu} \gamma^\lambda{}_{\nu)}+\frac{2}{p^2}p^\lambda p_{(\mu} \gamma_{\texttt{v}}{}_{\nu)}+ \frac{1}{p^2}p_{\mu} p_{\nu} \gamma'_{\texttt{v}}{}^\lambda+\frac{1}{p^3}p^\lambda p_{\mu} p_{\nu} \gamma_{\texttt{L}},
-%% \end{dmath}
-%% where all the indices are transverse except those of the momentum $p_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\texttt{L}}$ indicates that this is the longitudinal projection of the tensor, while the subindices $\texttt{s}$, $\texttt{a}$ and $\texttt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation.
-In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless.
-Additionally, we could separate the fields into irreducible representations by projecting them into their traceless part and other lower dimensional tensor representations.
-In the meanwhile we shall not do this expansion.
-%% \begin{widetext}
-%%   Using Eqs.~\eqref{transversea}, \eqref{transverset} and~\eqref{transversegamma}, the action~\eqref{4dflat} is then rewritten
-%%   \begin{dmath}
-%%     \label{4dtransverse}
-%%     S =
-%%     \int\dn{4}{p}p^2
-%%     \bigg[
-%%       2C_1 \hat{p}_\mu \hat{p}_\sigma\Big(\gamma_\perp^{\mu}{}_{\rho\nu}+\hat{p}^\mu \gamma_{\texttt{s}}{}_{\rho\nu}+2\hat{p}_{(\rho} \gamma^\mu{}_{\nu)}+2\hat{p}^\mu \hat{p}_{(\rho} \gamma_{\texttt{v}}{}_{\nu)}+ \hat{p}_{\rho} \hat{p}_{\nu} \gamma'_{\texttt{v}}{}^\mu+\hat{p}^\mu \hat{p}_{\rho} \hat{p}_{\nu} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\rho\sigma\delta\eta}\hat{p}_\eta t_\perp^{\nu}{}_\delta+\hat{p}^\nu t_{\texttt{a}}^{\rho\sigma}-2\hat{p}^{[\rho} t_{\texttt{a}}^{\sigma]\nu}+2\hat{p}^{[\rho} t_{\texttt{s}}^{\sigma]\nu}+2\hat{p}^\nu \hat{p}^{[\rho} t_{\texttt{v}}^{\sigma]}\Big)
-%%       +2C_2 \hat{p}_{\mu} \hat{p}_\sigma\Big(\gamma_\perp^{\rho}{}_{\nu\rho}+\hat{p}^\rho \gamma_{\texttt{s}}{}_{\nu\rho}+2\hat{p}_{(\nu} \gamma^\rho{}_{\rho)}+2\hat{p}^\rho \hat{p}_{(\nu} \gamma_{\texttt{v}}{}_{\rho)}+\hat{p}_{\nu} \hat{p}_{\rho} \gamma'_{\texttt{v}}{}^\rho +\hat{p}^\rho \hat{p}_{\nu} \hat{p}_{\rho} \gamma_{\texttt{L}}\Big)^* \Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\kappa+\hat{p}^\sigma t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\sigma}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\sigma}+2\hat{p}^\sigma \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)
-%%       +E_1 \hat{p}_{\rho} \hat{p}_{\sigma}\Big(\epsilon^{\mu\nu\kappa\eta}\hat{p}_\eta t_\perp^{\rho}{}_\kappa+\hat{p}^\rho t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{\mu} t_{\texttt{a}}^{\nu\rho}+2\hat{p}^{\mu} t_{\texttt{s}}^{\nu\rho}+2\hat{p}^\rho \hat{p}^{\mu} t_{\texttt{v}}^{\nu}\Big)^*\Big(\epsilon^{\lambda\kappa\delta\eta}\hat{p}_\eta t_\perp^{\sigma}{}_\delta+\hat{p}^\sigma t_{\texttt{a}}^{\lambda\kappa}-2\hat{p}^{\lambda} t_{\texttt{a}}^{\kappa\sigma}+2\hat{p}^{\lambda} t_{\texttt{s}}^{\kappa\sigma}+2\hat{p}^\sigma \hat{p}^{\lambda} t_{\texttt{v}}^{\kappa}\Big)\epsilon_{\mu\nu\lambda\kappa}
-%%       +E_2 \hat{p}_{\lambda} \hat{p}_{\mu} \Big(\epsilon^{\mu\nu\kappa\rho}\hat{p}_\rho t_\perp^{\lambda}{}_\kappa+\hat{p}^\lambda t_{\texttt{a}}^{\mu\nu}-2\hat{p}^{[\mu} t_{\texttt{a}}^{\nu]\lambda}+2\hat{p}^{[\mu} t_{\texttt{s}}^{\nu]\lambda}+2\hat{p}^\lambda \hat{p}^{[\mu} t_{\texttt{v}}^{\nu]}\Big)^*\Big(a_\perp{}_\nu+\hat{p}_\nu a_{\texttt{L}}\Big)
-%%       \bigg],
-%%   \end{dmath}
-%% \end{widetext}
-%% simplifiying
-%% \begin{dmath}
-%%   \label{WithGhosts}
-%%   S=\int d^4p\Bigg[-2C_1 p^2\gamma_{\texttt{s}\mu\nu}^*t_{\texttt{s}}^{\mu\nu}
-%%     +p^2\Big((-2C_1+2C_2)\gamma_{\texttt{v}\mu}+2C_2\gamma_{\perp\mu\nu}^\nu
-%%     +8E_1t_{\texttt{a}\mu}+E_2a_{\perp\mu}\Big)^*t_{\texttt{v}}^\mu
-%%     \Bigg]
-%% \end{dmath}
-When we restrict ourselves to perturbations around a flat (Minkowski) spacetime, the above equation simplifies greatly,
-\begin{dmath}
-  S = \int \dn{4}{x} \, \bigg[
-    - C_1 ( \Delta\gamma_{\texttt{s}\mu\nu})^* \Delta t_{\texttt{s}}^{\mu\nu}
-    + \Big( ( C_1 - 2 C_2) \nabla^\nu \Delta \nabla_\nu \gamma_{\texttt{v}\mu}
-    - 2 C_2 \Delta \gamma^\nu_{\perp\nu\mu}
-    - 8 E_1 \epsilon_{\alpha\beta\nu\mu} \nabla^{\alpha} \Delta t_{\texttt{a}}^{\beta\nu}
-    - 2 E_2 \Delta a_{\perp\mu} \Big)^* \Delta t_{\texttt{v}}^\mu
-    \bigg],
-\end{dmath}
-\hl{Where are the scalars?
-This has 18 dof, while the previous one has 20 dof.
-According to the counting, there are 18...
-I suppose that eighteen is the correct answer, but What is wrong in the first expression?} and it is clear that there are only eighteen degrees of freedom, corresponding to a couple of transverse-traceless rank-two-tensors, and a couple of transverse vectors.
+This action sets the dynamics of two transverse-traceless tensors (or specific combination of tensors), as well as two transverse vectors and two scalars, which are associated to eighteen degrees of freedom.
 
@@
 We discover during the implementation of these program, that our model presents an extra symmetry associated to the metric independence property.
+
+In addition, when we restrict ourselves to perturbations around a flat (Minkowski) spacetime, the above equation simplifies greatly,
+\begin{dmath}
+  S = \int \dn{4}{x} \, \bigg[
+    - C_1 ( \Delta\gamma_{\mathtt{s}\mu\nu})^* \Delta t_{\mathtt{s}}^{\mu\nu}
+    + \Big( ( C_1 - 2 C_2) \nabla^\nu \Delta \nabla_\nu \gamma_{\mathtt{v}\mu}
+    - 2 C_2 \Delta \gamma^\nu_{\perp\nu\mu}
+    - 8 E_1 \epsilon_{\alpha\beta\nu\mu} \nabla^{\alpha} \Delta t_{\mathtt{a}}^{\beta\nu}
+    - 2 E_2 \Delta a_{\perp\mu} \Big)^* \Delta t_{\mathtt{v}}^\mu
+    \bigg],
+\end{dmath}
+and it is clearer that there are only eighteen degrees of freedom.
 
@@
 In this paper we have restrict ourselves to such a truncation of our model, which constrained us to the torsion-less sector of the moduli space.
-Additionally, this truncation leaves only one nontrivial field equation, Eq.~\eqref{SimpleEOM}.
+Additionally, this truncation leaves only one nontrivial field equation, Eq.~\eqref{almostSimpleEOM}.
 %%, which can be obtained from a simple ``effective'' theory whose action is Eq.~\eqref{eff-action}.
@@
 Therefore, in Appendix~\ref{Known} we present a summary of known (metric) solutions to Eq.~\eqref{SimpleEOM}.
-In addition, in Appendix~\ref{Schw} we prove that an ansatz metric with spherical symmetry solves the field equation only if it is static.
-This is a Birkhoff-like theorem for our model, however, the non-linearity of the equations does not assure the uniqueness of the solution.
+In addition, in Appendix~\ref{Schw} we prove that a metric ansatz with spherical symmetry solves the field equation only if it is static, i.e., a Birkhoff-like theorem for our model.
+However, the non-linearity of the equations does not assure the uniqueness of the solution.
 Nonetheless, certain equations become linear if the functions $A$ and $B$ in Eq.~\eqref{ABmetric} are equal.
-Therefore, the unique solution is the $\Lambda$-Schwarzschild solution.
+Therefore, the unique solution is the (Anti-)de-Sitter--Schwarzschild solution.
 
 We also pointed that our field equation~\eqref{SimpleEOM} can be obtained from an effective action, known as Stephenson--Kilmister--Yang (SKY) theory~\cite{stephenson1958quadratic,kilmister1961use,Yang1974}, which is built up in the spirit of a Yang--Mills theory for gravity.
-Despite the SKY theory has been criticized by many people, including C.~N.~Yang himself~\cite{JZcomm}, because its field equations are higher order differential equations for the metric field, and also because the field equation for the metric is so restrictive that the Schwarzschild metric is not a solution, in our model the fundamental gravitational field is the connection.
-The field equation~\eqref{SimpleEOM} is a second order partial differential equation for the connection.
+Despite the SKY theory has been criticized by many people, including C.~N.~Yang himself~\cite{JZcomm}, because its field equations are higher order differential equations for the metric field,
+%% and also because the field equation for the metric is so restrictive that the Schwarzschild metric is not a solution,
+in our model the fundamental gravitational field is the connection.
+Equation~\eqref{SimpleEOM} is a second order partial differential equation for the connection.
 Although we have presented a series of metric solutions of the effective field equations (restricted to the torsion-free sector of the theory), the correct way to proceed is to propose a connection ansatz compatible with the symmetries of the problem.

### 2016-05-09 AffGR-PRD.tex
Just before the final read-proof

@@
 Finally, we analyzed the second order perturbation of the action in Eq.~\eqref{4dfull}, around a maximally symmetric spacetime.
-
-{\huge{\textcolor{red}{Working Here!}}}
+From this analysis it is possible to conclude that, at perturbative level, the number of degrees of freedom are eighteen.
+These degrees of freedom come from a pair of transverse, symmetric, rank-two-tensors, and a pair of transverse vectors.
+Moreover, we applied the Lagrangian equivalent of Dirac's formalism for constrained systems (see Ref.~\cite{Diaz:2014yua}), and obtain the same number of physical states---which in principle do not need to coincide, because the perturbative analysis is not exact~\footnote{We want to thank to M.~Blagojevi\'c and B.~Cvetkovi\'c for clarifications in this respect.}.
 

### 2016-05-09 AffGR-PRD.tex
Corrected abstract, part of the introduction

@@
   We show that the effective field equations for a recently formulated polynomial affine model of gravity, in the sector of a torsion-free connection, accept general Einstein manifolds---with or without cosmological constant---as solutions.
-Moreover, the effective field equations coincide with some of those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
-Additionally, we find a generalization of a minimally coupled massless scalar field in General Relativity with a ``minimally'' coupled scalar field in this affine model.
-Finally, we present a naive analysis of the propagators of the gravitational theory, an their relation with the presence of ghost in the model.
-For completeness we include three appendices, including one in which it is shown that a Birkhoff-like theorem is valid for the analyzed sector.
+Moreover, the effective field equations are partially those obtained from a gravitational Yang--Mills theory known as Stephenson--Kilmister--Yang theory.
+Additionally, we find a generalization of a minimally coupled massless scalar field in General Relativity within a ``minimally'' coupled scalar field in this affine model.
+Finally, we present a brief analysis of the propagators of the gravitational theory, and count the degrees of freedom.
+For completeness we include three appendices, including one in which we show that a Birkhoff-like theorem is valid for the analyzed sector.
 \end{abstract}
@@
 A hundred years ago, A.~Einstein presented by the first time the correct field equations of its relativistic theory of gravitation, known as General Relativity~\cite{einstein1915feldgleichungen}.
-It was not only consistent with the available observations, but it also predicted several effects that have been consistently observed and measured---see Ref.~\cite{Will:2014kxa} for a recent review---, being the last one the confirmation of gravitational waves~\cite{Abbott:2016blz}.
+It was not only consistent with the available observations, but it also predicted several effects that have been consistently observed and measured---see Ref.~\cite{Will:2014kxa} for a recent review---, being the last one the confirmation of the existence of the existence of gravitational waves~\cite{Abbott:2016blz}.
 Thus, General Relativity has become the most successful theory of gravitational interactions nowadays.
@@
 A first hint was pointed out by E.~Cartan, after remarking that the curvature is not built up from a metric field but from a connection, and that a part of it was left behind if one chooses to work with the Levi-Civita connection~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
-One could also see this by considering Palatini's approach in General Relativity, in which both metric and connection fields are independent, and noticing that generically the theory possesses terms which do not appear in General Relativity.
-In addition, we mention a few aspects related with the quantization: First, the fact that in the standard formalism of quantization, General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}, suggests the theory can be thought as an effective theory.
+One could also see this by considering Palatini's approach in General Relativity, in which both metric and connection fields are independent, and noticing that generically the theory possesses terms which do not appear in General Relativity (when it is coupled to matter).
+In addition, we mention a few aspects related with the quantization: First, the fact that within the standard formalism of quantization, General Relativity is non-renormalizable~\cite{'tHooft:1973us,'tHooft:1974bx,Deser:1974cz,Deser:1974cy}, suggests the theory can be thought as an effective theory.
 Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
 One of the most successful quantization methods of gravitational interactions---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, by Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
-On the other hand, it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
+Finally, it is well known that once matter couples to gravity (in particular fermionic matter), the assumption of vanishing torsion in standard General Relativity is no longer preserved as a field equation, and the best approach is to consider Cartan's generalization of General Relativity~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
+%%it is well known that in the standard formulation of General Relativity the skew-symmetric part of the connection (or torsion) is assumed to be zero, albeit it is known that such assumption can be relaxed once matter is added, in particular fermionic matter~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
 
@@
 
-Interestingly, gravitational theories with generic linear connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
+Interestingly, gravitational theories with a generic linear connections have degrees of freedom which do not correspond to the expected massless graviton~\cite{Sezgin:1979zf}.
 Albeit these gravitational theories with an arbitrary connection possess ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe}, or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
@@
   \end{dmath}
-  \hl{1.- Is it Ok?}
+  %% \hl{1.- Is it Ok?}
 \end{widetext}
@@
 \begin{acknowledgments}
-  We thank to N.~Pantoja, A.~Melfo, M.~Blagojevi\'c, B.~Cvetkovi\'c, V.~Sharma, O.~Orellana and R.~L.~Bryant for their helpful discussions and inspiring comments, to J.~Zanelli for his suggestions on the physical insight into the problem and careful but critical review of the manuscript.
+  We thank to N.~Pantoja, A.~Melfo, M.~Blagojevi\'c, B.~Cvetkovi\'c, C.~Corral, V.~Sharma, O.~Orellana and R.~L.~Bryant for their helpful discussions and inspiring comments, to J.~Zanelli for his suggestions on the physical insight into the problem and careful but critical review of the manuscript.
   This work was partially supported by CONICYT (Chile) under project No. 79140040.

### 2016-05-09 AffGR-PRD.tex
Introduction finished

@@
 
-Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton self-interaction is mediated by the torsion.
+Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton \emph{self-interaction} is mediated by non-Riemannian parts of the connection.
 This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it was proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
@@
 Then, in Sec.~\ref{matter} we show that under certain considerations the coupling of the gravitational model with a scalar field represents a generalization of the minimally coupled system Einstein--Klein--Gordon.
-In Sec.~\ref{propag}, we present a brief analysis of the propagators of the model, which represent a first step toward a thorough study of the degrees of freedom of these theory.
+In Sec.~\ref{propag}, we present a brief analysis of the propagators of the model, which allows us to count the propagating degrees of freedom.
+In addition, we corroborate that result with a method equivalent to the one of Dirac.
 And in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results.
-In order to make the paper self-contained, we have included three appendices: In Appendix~\ref{DA}, we describe a dimensional analysis strategy that allowed us to build up the most general action consistent with diffeomorphisms.
+In order to make the paper self-contained, we have included three appendices: In Appendix~\ref{DA}, we describe a dimensional analysis strategy that allowed us to build up the most general action consistent with diffeomorphisms invariance.
 In Appendix~\ref{Known}, we show a collection of known solutions to the effective field equations of the model.

### 2016-05-10 AffGR-PRD.tex

@@
 \end{widetext}
-In Eq.~\eqref{4dfull}, we have dropped all terms which can be related through partial integration, and those which are topological invariant.
-A straightforward dimensional counting shows the impossibility of other contributions into the action, see Appendix~\ref{DA}.
+In Eq.~\eqref{4dfull}, we have dropped all terms which can be related through partial integration, and those which are topological invariant (e.g.
+the Euler density).
+A straightforward dimensional analysis shows the impossibility of other contributions into the action, see Appendix~\ref{DA} (in particular Sec.~\ref{sec:ld}).
 Interestingly, the above action turns out to be power-counting renormalizable, which does not guarantee renormalizability but is a nice feature.
@@
 Next, by analysing the first order perturbations of the actions, we found a choice of the coupling constants which allow nontrivial solutions of these field equations, together with the non-relativistic limit of the geodesic equation.
-Then, we substitute the field components by their their scalar perturbation decomposition,
+Then, we substitute the field components by their scalar perturbation decomposition,
 \begin{equation}
-  a_\mu \to \delta_\mu^0 a+\delta_\mu^m \partial_{m}a_L,
+  a_\mu \to \delta_\mu^0 a+\delta_\mu^m \partial_{m}a_{\mathtt{L}},
 \end{equation}
@@
   \begin{split}
-    t^{\mu,\nu\rho} &\to \delta^{\mu}_m\delta^{\nu\rho}_{n0} \Big(t \delta^{m n} + \partial^m \partial^n t_L \Big)
-    +\delta^{\mu}_0 \delta^{\nu\rho}_{m0} \partial^m c_L
+    t^{\mu,\nu\rho} &\to \delta^{\mu}_m\delta^{\nu\rho}_{n0} \Big(t \delta^{m n} + \partial^m \partial^n t_{\mathtt{L}} \Big)
+    +\delta^{\mu}_0 \delta^{\nu\rho}_{m0} \partial^m c_{\mathtt{L}}
     \\
@@
     \delta^\lambda_0\delta^0_\mu\delta^0_\nu u 
-    + \delta^\lambda_m \delta^0_\mu\delta^0_\nu \partial^m v_L
-    + 2\delta^\lambda_0 \delta^0_{(\mu}\delta^m_{\nu)} \partial_m w_L
+    + \delta^\lambda_m \delta^0_\mu\delta^0_\nu \partial^m v_{\mathtt{L}}
+    + 2\delta^\lambda_0 \delta^0_{(\mu}\delta^m_{\nu)} \partial_m w_{\mathtt{L}}
     \\
-    & \quad + \delta^\lambda_0 \delta^m_\mu\delta^n_\nu \Big(x \delta_{mn} + \partial_m \partial_n x_L\Big)
+    & \quad + \delta^\lambda_0 \delta^m_\mu\delta^n_\nu \Big(x \delta_{mn} + \partial_m \partial_n x_{\mathtt{L}}\Big)
     \\
-    & \quad + 2\delta^\lambda_m \delta^0_{(\mu}\delta^n_{\nu)} \Big(y_1 \delta^m{}_n + \epsilon^{m p}{}_{n} \partial_p y_2 + \partial^m \partial_n y_L\Big)
+    & \quad + 2\delta^\lambda_m \delta^0_{(\mu}\delta^n_{\nu)} \Big(y_1 \delta^m{}_n + \epsilon^{m p}{}_{n} \partial_p y_2 + \partial^m \partial_n y_{\mathtt{L}}\Big)
     \\
@@
     \\
-    & \qquad +  (\epsilon^{m q}{}_n \partial_p+\epsilon^{m q}{}_p \partial_n) \partial_q z_3 + \partial^m \partial_n \partial_p z_L\Big),
+    & \qquad +  (\epsilon^{m q}{}_n \partial_p+\epsilon^{m q}{}_p \partial_n) \partial_q z_3 + \partial^m \partial_n \partial_p z_{\mathtt{L}}\Big),
   \end{split}
 \end{equation}
-where the ``L'' sub-index identifies the longitudinal degrees of freedom.
+where the ``\texttt{L}'' sub-index identifies the longitudinal degrees of freedom.
 
@@
 %% Additionally, we studied perturbative inhomogeneous sources to the connection field equations, by considering a generic matter action.
-Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general $\binom{2}{0}$-type symmetric tensor density, $\mathfrak{g}^{\mu \nu}$, constructed with at most quadratic terms in the available fields.
+Albeit the inclusion of matter in a non-metric spacetime is a nonstandard procedure, we assumed that the matter action would depend on the most general, symmetric $\binom{2}{0}$-tensor density, $\mathfrak{g}^{\mu \nu}$, built up with the available fields.
 The dimensional analysis in Sec.~\ref{sec:im} shows that this tensor density contains the same terms as what we call the ``Eddington's metric density''~\footnote{Despite the suggestive name, this is a $\binom{2}{0}$-tensor density which does not necessarily satisfy the metric conditions.
@@
 %% by assuming a matter action that depends on $\bar{g}^{\mu\nu}$.
-Therefore, in the following we will restrict ourselves to consider $\mathfrak{g}^{\mu \nu} = \bar{g}^{\mu\nu}$.
+%% Therefore, in the following we will restrict ourselves to consider $\mathfrak{g}^{\mu \nu} = \bar{g}^{\mu\nu}$.
 
@@
 \end{equation}
-is the usual Newtonian force induced by a massive source.
-%% Notice that we restricted ourselves to consider $\mathfrak{g}^{\mu \nu} = \bar{g}^{\mu\nu}$ to obtain the above result.
+is the usual Newtonian force induced by a massive source, where we restricted ourselves to consider $\mathfrak{g}^{\mu \nu} = \bar{g}^{\mu\nu}$.
 
@@
 
-Equation~\eqref{SimpleEOM} is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.}  All Einstein manifolds, whose Ricci tensor is proportional to the metric, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition due to the metricity condition, and therefore every vacuum solution to the Einstein's equations solves the (torsion-free) field equations of our model.
+Equation~\eqref{SimpleEOM} is a generalization of a condition known in Riemannian geometry as covariantly constant Ricci curvature---aka parallel Ricci curvature---, \mbox{$\nab{\rho} R_{\mu\nu} = 0$.}  All Einstein manifolds, whose Ricci tensor is proportional to the metric, \mbox{$R_{\mu\nu} \propto g_{\mu\nu}$,} satisfy the parallel Ricci condition due to the metricity condition, and therefore every vacuum solution to the Einstein's equations solves the (simplified) field equations of our model.
 Consequently, the fact that the non-relativistic limit of the gravitational potential in Eq.~\eqref{NewtonPot} yields a Newtonian potential seems clearer, and we can argue that even the post-Newtonian corrections coming from General Relativity are present in the chosen scenario of our model.

### 2016-05-10 AffGR-PRD.tex
Reviewed until propagators section

@@
 
-Until now, the most general diffeomorphism-invariant and power-counting renormalizable (gravitational) theory for an affine connection has been built, and we have showed that in a certain sector it is equivalent to General Relativity.
+Until now, the most general diffeomorphism-invariant and power-counting renormalizable (gravitational) theory for an affine connection has been built, and we have showed that in a certain sector it is a generalization of General Relativity.
 In what follows, we show an attempt of including scalar matter into the model.
-The theory does not require a spacetime metric, but instead we should consider the most general $\binom{2}{0}$-tensor density, $\mathfrak{g}^{\mu\nu}$,  built with the available fields, and use it to build Lagrangian densities for the matter content.
+The theory does not require a spacetime metric, but instead we should consider the most general, symmetric $\binom{2}{0}$-tensor density, $\mathfrak{g}^{\mu\nu}$,  built with the available fields (see Appendix~\ref{sec:im}), and use it to build Lagrangian densities for the matter content.
 Following our precept, the matter content---scalar matter---should couple to $\mathfrak{g}^{\mu\nu}$, given by
@@
 \end{dmath}
-which makes a nontrivial contribution to the field equations once we restrict to the sector of interest, where the torsion is set to zero and the connection is compatible with a metric.
+which makes a nontrivial contribution to the field equations once we restrict to the sector of interest.
+%%, where the torsion is set to zero and the connection is compatible with a metric.
 
@@
 %% Additionally, 
-Therefore, in notation of Eqs.~\eqref{GammaExp} we have that $A = T = 0$, and the contribution due to the torsion (and non-metricity) enters as a perturbative effect.
+Therefore, in notation of Eqs.~\eqref{GammaExp} we have that $A = T = 0$, and the contribution due to the torsion and non-metricity enters as a perturbative effect.
 Thus, most terms in the action~\eqref{4dfull} do not contribute to the propagator analysis.
@@
 \end{dmath}
-where all the indices are transverse except those of the derivative $\nabla_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\mathtt{L}}$ indicates that this is the longitudinal projection of the tensor, while the sub indices $\mathtt{s}$, $\mathtt{a}$ and $\mathtt{v}$ specify that the tensor is symmetric, antisymmetric or a vector representation.
+where all the indices are transverse except those of the derivative $\nabla_\mu$, the subindex $\perp$ indicates that it corresponds to the fully transverse projection of the tensor in all of its indices, the subindex ${\mathtt{L}}$ indicates that this is the longitudinal projection of the tensor, while the subindices $\mathtt{s}$, $\mathtt{a}$ and $\mathtt{v}$ specify whether the tensor is symmetric, antisymmetric or a vector representation.
 %%In particular, $t_\perp^{\lambda}{}_\kappa$ is traceless.

### 2016-05-11 AffGR-PRD.tex
Approved to be uploaded

@@
 %% \input{Def-article.tex}
-\usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
-\usepackage{graphicx}
-\usepackage{centernot}
+%% \usepackage{mathtools,amsmath,amssymb,amsfonts,dsfont,mathrsfs,amsthm}
+%% \usepackage{graphicx}
+%% \usepackage{centernot}
 %% \usepackage{hyperref}
 \usepackage{xcolor}
-\usepackage{comment}
+%% \usepackage{comment}
 %% \hypersetup{linktocpage,colorlinks=true,urlcolor=blue!80!red,linkcolor=blue,citecolor=red}
@@
 %-------------------------------Theorems
-\newtheorem{Def}{Definition}[section]
-\newtheorem{Thm}[Def]{Theorem}
-\newtheorem{Lem}[Def]{Lemma}
-\newtheorem{Pos}[Def]{Postulate}
-\newtheorem{Exa}[Def]{Example}
-\newtheorem{Cor}[Def]{Corrolary}
-\newtheorem{Pro}[Def]{Proposition}
+%% \newtheorem{Def}{Definition}[section]
+%% \newtheorem{Thm}[Def]{Theorem}
+%% \newtheorem{Lem}[Def]{Lemma}
+%% \newtheorem{Pos}[Def]{Postulate}
+%% \newtheorem{Exa}[Def]{Example}
+%% \newtheorem{Cor}[Def]{Corrolary}
+%% \newtheorem{Pro}[Def]{Proposition}
 
@@
 
-\renewcommand{\(}{\left(}
-\renewcommand{\)}{\right)}
-\renewcommand{\[}{\left[}
-\renewcommand{\]}{\right]}
+%% \renewcommand{\(}{\left(}
+%% \renewcommand{\)}{\right)}
+%% \renewcommand{\[}{\left[}
+%% \renewcommand{\]}{\right]}
 
@@
 Finally, we present a brief analysis of the propagators of the gravitational theory, and count the degrees of freedom.
-For completeness we include three appendices, including one in which we show that a Birkhoff-like theorem is valid for the analyzed sector.
+For completeness we prove that a Birkhoff-like theorem is valid for the analyzed sector.
 \end{abstract}
 
-\pacs{02.40.Ma,04.50.Kd,04.90.+e}
-\keywords{Affine Gravity, Torsion, Generalized Gravity.}
+\pacs{02.40.Hw,04.50.Kd,04.90.+e}
+\keywords{Polynomial Affine Gravity, Torsion, Generalized Gravity.}
 
@@
 A hundred years ago, A.~Einstein presented by the first time the correct field equations of its relativistic theory of gravitation, known as General Relativity~\cite{einstein1915feldgleichungen}.
-It was not only consistent with the available observations, but it also predicted several effects that have been consistently observed and measured---see Ref.~\cite{Will:2014kxa} for a recent review---, being the last one the confirmation of the existence of the existence of gravitational waves~\cite{Abbott:2016blz}.
+It was not only consistent with the available observations, but it also predicted several effects that have been consistently observed and measured---see Ref.~\cite{Will:2014kxa} for a recent review---, being the last one the confirmation of the existence of gravitational waves~\cite{Abbott:2016blz}.
 Thus, General Relativity has become the most successful theory of gravitational interactions nowadays.
 
-However, General Relativity seems to be an effective theory of a, yet to be discovered, more fundamental one.
+However, General Relativity seems to be an effective theory of a, yet to be discovered, more fundamental description of gravitational effects.
 A first hint was pointed out by E.~Cartan, after remarking that the curvature is not built up from a metric field but from a connection, and that a part of it was left behind if one chooses to work with the Levi-Civita connection~\cite{Cartan1922,Cartan1923,Cartan1924,Cartan1925}.
@@
 Second, the Wheeler--DeWitt equations are not well-defined in general due to their nonpolynomial dependence on the Arnowitt--Deser--Misner (or ADM) variables~\cite{Arnowitt:1959ah,Arnowitt:1960es,WheelerGeo,DeWitt:1967yk,DeWitt:1967ub,DeWitt:1967uc}.
-One of the most successful quantization methods of gravitational interactions---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, by Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that General Relativity is not as complete as expected, since the Lagrangian formulation includes (at least) an extra term known as Holst term~\cite{Holst:1995pc}.
+One of the most successful quantization methods of gravitational interactions---developed from ideas by Gambini and Trias~\cite{Gambini:1980yz,Gambini:1986ew}, by Ashtekar~\cite{Ashtekar:1986yd,Ashtekar:1987gu}---, hints that a first order formulation of General Relativity is not as complete as expected, since the Lagrangian formulation should include an extra term known as Holst term~\cite{Holst:1995pc}.
 Finally, it is well known that once matter couples to gravity (in particular fermionic matter), the assumption of vanishing torsion in standard General Relativity is no longer preserved as a field equation, and the best approach is to consider Cartan's generalization of General Relativity~\cite{Kibble:1961ba,Hehl:1976kj,Shapiro:2001rz,Hammond:2002rm}.
@@
 Albeit these gravitational theories with an arbitrary connection possess ghosts, there are examples of well-behaved (stable) systems which have ghosts, such are the cases of the Pais--Uhlenbeck oscillator~\cite{Mannheim:2004qz,Bender:2007wu,Smilga:2008pr,Ilhan:2013xe}, or the higher derivative supersymmetric quantum mechanical system presented in Ref.~\cite{Robert:2008}.
-The last sentence, allows to argue that a model cannot be discarded  for the presence of ghosts model, without a rigorous analysis of its stability.
+The last sentence, allows to argue that a model cannot be disregarded for the presence of ghosts model, without a rigorous analysis of its stability.
 
@@
 Interestingly, by construction, the polynomial affine gravity proposed in Ref.~\cite{Skirzewski:2014eta} has no explicit terms leading to three-point graviton vertices, since all graviton \emph{self-interaction} is mediated by non-Riemannian parts of the connection.
-This characteristic might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it was proved that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
+This feature might allow to bypass the general postulates supporting the no-go theorems stated in Refs.~\cite{McGady:2013sga,Camanho:2014apa}, where it was proven that generic three-point graviton interactions are highly constrained by causality and analyticity of the $S$-matrix, and the only \emph{acceptable} structure of the three-point graviton vertices is the one coming from General Relativity.
 %%Additionally, it is well known that the three-point graviton vertices lead to non-renormalizability of a theory ---in a model independent way---~\cite{McGady:2013sga,Camanho:2014apa}.
@@
 In Sec.~\ref{propag}, we present a brief analysis of the propagators of the model, which allows us to count the propagating degrees of freedom.
-In addition, we corroborate that result with a method equivalent to the one of Dirac.
-And in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results.
+In addition, we corroborate that result with a method equivalent to the one of Dirac~\cite{Diaz:2014yua}.
+Finally, in Sec.~\ref{conclusions} we summarize and discuss the possible implications of the results.
 In order to make the paper self-contained, we have included three appendices: In Appendix~\ref{DA}, we describe a dimensional analysis strategy that allowed us to build up the most general action consistent with diffeomorphisms invariance.
@@
 
-First of all, we highlight that the model constructed below has as only fundamental field an affine connection, and no metric field is needed either for contracting nor lowering or raising indices.
+First of all, we highlight that the model constructed below has as only fundamental field an affine connection, and no metric field is needed neither for contracting nor lowering or raising indices.
 Moreover, in order to guarantee the correct transformation of the Lagrangian density, the geometrical objects used to write down the action will be the curvature and torsion of an affine connection, $\hat{\Gamma}^\mu{}_{\rho\sigma}$, which accepts a decomposition on irreducible components as
 \begin{equation}
-  \hat{\Gamma}^\mu{}_{\rho\sigma} = {\Gamma}^\mu{}_{\rho\sigma} + T^\mu{}_{\rho\sigma} = {\Gamma}^\mu{}_{\rho\sigma} + \epsilon_{\rho\sigma\lambda\kappa}T^{\mu,\lambda\kappa}+A_{[\rho}\delta^\mu_{\nu]},
-\end{equation}
-where ${\Gamma}^\mu{}_{\rho\sigma}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying \mbox{$T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$} and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$.
+  \hat{\Gamma}^\mu{}_{\rho\sigma} = \hat{\Gamma}^\mu{}_{(\rho\sigma)} + \hat{\Gamma}^\mu{}_{[\rho\sigma]} = {\Gamma}^\mu{}_{\rho\sigma} + \epsilon_{\rho\sigma\lambda\kappa}T^{\mu,\lambda\kappa}+A_{[\rho}\delta^\mu_{\nu]},
+\end{equation}
+where ${\Gamma}^\mu{}_{\rho\sigma} = \hat{\Gamma}^\mu{}_{(\rho\sigma)}$ is symmetric in the lower indices, $A_\mu$ is a vector field corresponding to the trace of torsion, and  $T^{\mu,\lambda\kappa}$ is a Curtright field~\cite{Curtright:1980yk}, satisfying \mbox{$T^{\kappa,\mu\nu } = - T^{\kappa,\nu\mu }$} and $\epsilon_{\lambda\kappa\mu\nu}T^{\kappa,\mu\nu }=0$.
 Since no metric is present, the epsilon symbols are not related by raising (lowering) their indices, but instead we demand that \mbox{$\epsilon^{\delta\eta\lambda\kappa}\epsilon_{\mu\nu\rho\sigma}=4!\delta^{\delta}{}_{[\mu}\delta^\eta{}_{\nu}\delta^{\lambda}{}_{\rho} \delta^\kappa{}_{\sigma]}$.}
@@
 A straightforward dimensional analysis shows the impossibility of other contributions into the action, see Appendix~\ref{DA} (in particular Sec.~\ref{sec:ld}).
-Interestingly, the above action turns out to be power-counting renormalizable, which does not guarantee renormalizability but is a nice feature.
+Interestingly, the above action turns out to be power-counting renormalizable, which does not guarantee renormalizability, but is a nice feature.
 The structure of the model yields no three-point graviton vertices, which might allow to overcome  the \emph{no-go} theorems found in Refs.~\cite{McGady:2013sga,Camanho:2014apa}.
-It is worth mentioning that all coupling constants are dimensionless, which might be a hint of conformal invariance of the model~\cite{Buchholz:1976hz}.
+It is worth mentioning that all coupling constants are dimensionless, which might be a hint of conformal invariance of the model~\cite{Buchholz:1976hz}, and further analysis of this invariance will be presented in Ref.~\cite{OCF-future3}.
 
@@
 with $\delta^{\mu\nu}_{\lambda\kappa}=\delta^{\mu}_{\lambda}\delta^{\nu}_{\kappa}-\delta^{\mu}_{\kappa}\delta^{\nu}_{\lambda}$.
-Next, by analysing the first order perturbations of the actions, we found a choice of the coupling constants which allow nontrivial solutions of these field equations, together with the non-relativistic limit of the geodesic equation.
+Next, by analysing the first order perturbations of the actions, we found a choice of the coupling constants which allows nontrivial solutions of these field equations, together with the non-relativistic limit of the geodesic equation.
 Then, we substitute the field components by their scalar perturbation decomposition,
@@
 %%%%%%%%% COMPARISON GR %%%%%%%%%
-Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, a \emph{post}-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the deviation of light by a gravitational source.
+Despite we obtained the correct Newtonian gravitational potential in the non-relativistic limit, see Eq.~\eqref{NewtonPot}, a \emph{post}-Newtonian approximation is necessary to explain gravitational phenomena like Mercury's perihelion and the bending of light by a gravitational source.
 Therefore, we should go beyond the Newtonian limit in order to compare our model with General Relativity.
@@
 \begin{align}
-  \cdf \Ff*[2] &= 0, & \cdf \st \Ff*[2] &= 0,
+  \cdf \Ff* &= 0, & \cdf \st \Ff* &= 0,
 \end{align}
-where $\Ff*[2] = \cdf \Af*[1]$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle, see for example Ref.~\cite{bourguignon1982yang,Nakahara}), and the operator $\st$ denotes the Hodge star.
+where $\Ff* = \cdf \Af*$ is the field strength 2-form (the curvature 2-form of the connection in the principal bundle, see for example Ref.~\cite{bourguignon1982yang,Nakahara}), and the operator $\st$ denotes the Hodge star.
 Now, these Yang--Mills field equations are obtained from the variation of the action functional
 \begin{equation}
-  S_{\textsc{ym}} = \int \Tr \Big( \Ff*[2] \st \Ff*[2] \Big),
+  S_{\textsc{ym}} = \int \Tr \Big( \Ff* \st \Ff* \Big),
 \end{equation}
@@
 \end{equation*}
-that can be written in the more conventional form~\footnote{We have used a suggestive notation by denoting with $g_{\mu\nu}$ a covariantly constant, invertible, and symmetric two-tensor.
+where we have used a suggestive notation by denoting with $g_{\mu\nu}$ a covariantly constant, invertible, and symmetric two-tensor.
+Notice that $\alpha$ is the gravitational coupling constant, which in Einstein--Hilbert gravity is proportional to $G_N$.
+This equation can be written in the more conventional form
+%%~\footnote{We have used a suggestive notation by denoting with $g_{\mu\nu}$ a covariantly constant, invertible, and symmetric two-tensor.
 Notice that $\alpha$ is the gravitational coupling constant, which in Einstein--Hilbert gravity is proportional to $G_N$.}
@@
 A step toward the analysis of renormalizability of the model should be the computation of the free propagators of the model around a given background.
-The choice of background will necessarily in order to simplify the computations.
+The choice of background is necessary in order to simplify the computations.
 Our first task is to expand up to second order in the fields around a maximally symmetric Riemannian background.
@@
     \int\dn{4}{x} \bigg[
-      C_1 \big( - \Lambda {\nabla}_{\alpha}{{t}^{\beta \alpha \gamma}}\,  {g}_{\beta \gamma} - \Lambda {\gamma}^{\alpha}\,_{\beta \delta} {g}_{\alpha \gamma} {t}^{\beta \delta \gamma} + {\nabla}_{\alpha}{{\gamma}^{\alpha}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\beta \delta \gamma}}\,  - {\nabla}_{\alpha}{{\gamma}^{\beta}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\delta \alpha \gamma}}\, \big)
+      C_1 \big( - \Lambda {\gamma}^{\alpha}\,_{\beta \delta} {g}_{\alpha \gamma} {t}^{\beta \delta \gamma} + {\nabla}_{\alpha}{{\gamma}^{\alpha}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\beta \delta \gamma}}\,  - {\nabla}_{\alpha}{{\gamma}^{\beta}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\delta \alpha \gamma}}\, \big)
       + 2\, C_2 {\nabla}_{\alpha}{{\gamma}^{\beta}\,_{\beta \delta}}\,  {\nabla}_{\gamma}{{t}^{\gamma \alpha \delta}}\,
@@
 In this paper we have shown that the \emph{polynomial affine gravity} presented in Ref.~\cite{Skirzewski:2014eta} is the most general (polynomial) model for an affine theory of gravity, see the Appendix~\ref{sec:ld}, consistent with invariance under diffeomorphisms.
-The action in Eq.~\eqref{4dfull}, is parametrized by a nineteen-dimensional moduli space---after the boundary and topological terms have been dropped---, which in some sense made us wonder about a possible \emph{duality} between this model and the one proposed in Ref.~\cite{Pagani:2015ema}, even though the last one possesses a metric field.
+The action in Eq.~\eqref{4dfull}, is parametrized by a nineteen-dimensional moduli space---after the boundary and topological terms have been dropped---, which in some sense made us wonder about a possible \emph{duality} between this model and the one proposed in Ref.~\cite{Pagani:2015ema}.
 %% (boundary condition, topological terms, ...)
@@
 The field equations obtained from the action~\eqref{4dfull} are a set of very complex coupled partial differential equations.
-However, they are consistent with the limit of $T^{\lambda,\mu\nu}$ and $A_\mu$ going to zero.
+However, the system is consistent with the limit of $T^{\lambda,\mu\nu}$ and $A_\mu$ going to zero.
 This consistency is what is usually called a \emph{consistent truncation} of the theory.
-In this paper we have restrict ourselves to such a truncation of our model, which constrained us to the torsion-less sector of the moduli space.
+In this paper we have restricted ourselves to such a truncation of our model, which constrained us to the torsion-less sector of the moduli space.
 Additionally, this truncation leaves only one nontrivial field equation, Eq.~\eqref{almostSimpleEOM}.
@@
 Notice that such a tensor density \emph{does not} necessarily satisfy a non-degeneracy condition as required for a metric, but even though it is an interesting question to ask under what considerations does this construct satisfy the properties of a metric.
-Using this tensor density, we proposed a \emph{kinetic} term for a scalar field (under diffeomorphisms), and show that in generically the effective field equations for gravity are equivalent to those of General Relativity, when we restrict ourselves to the torsion-free sector.
+Using this tensor density, we proposed a \emph{kinetic} term for a scalar field (under diffeomorphisms), and show that the effective field equations are a generalization to those of General Relativity, when we restrict ourselves to the torsion-free sector.
 Despite the fact that in this sector the field equation for the scalar field collapses, and cannot be obtained from the variation of the action, using the algorithm proposed in Ref.~\cite{Bekenstein:2014uwa}, the usual scalar field equation is recovered in virtue of the second Bianchi identity.
@@
 Finally, we analyzed the second order perturbation of the action in Eq.~\eqref{4dfull}, around a maximally symmetric spacetime.
-From this analysis it is possible to conclude that, at perturbative level, the number of degrees of freedom are eighteen.
-These degrees of freedom come from a pair of transverse, symmetric, rank-two-tensors, and a pair of transverse vectors.
-Moreover, we applied the Lagrangian equivalent of Dirac's formalism for constrained systems (see Ref.~\cite{Diaz:2014yua}), and obtain the same number of physical states---which in principle do not need to coincide, because the perturbative analysis is not exact~\footnote{We want to thank to M.~Blagojevi\'c and B.~Cvetkovi\'c for clarifications in this respect.}.
+From this analysis it is possible to conclude that, at perturbative level, the number of degrees of freedom is eighteen, coming from a pair of transverse, symmetric, rank-two-tensors, and a pair of transverse vectors.
+Moreover, we applied the Lagrangian equivalent of Dirac's formalism for constrained systems (see Ref.~\cite{Diaz:2014yua}), and obtain the same number of physical states---it is a nice feature, because there are known physical systems for which the perturbative analysis of degrees of freedom do not coincide with the exact one~\footnote{We want to thank to M.~Blagojevi\'c, B.~Cvetkovi\'c and O.~Mi\v{s}kovi\'c for clarifications in this respect.}.
 
@@
 \begin{acknowledgments}
-  We thank to N.~Pantoja, A.~Melfo, M.~Blagojevi\'c, B.~Cvetkovi\'c, C.~Corral, V.~Sharma, O.~Orellana and R.~L.~Bryant for their helpful discussions and inspiring comments, to J.~Zanelli for his suggestions on the physical insight into the problem and careful but critical review of the manuscript.
-  This work was partially supported by CONICYT (Chile) under project No. 79140040.
+  We thank to N.~Pantoja, A.~Melfo, M.~Blagojevi\'c, B.~Cvetkovi\'c, O.~Mi\v{s}kovi\'c, C.~Corral, V.~Sharma, O.~Orellana and R.~L.~Bryant for their helpful discussions and inspiring comments, to J.~Zanelli for his suggestions on the physical insight into the problem and careful but critical review of the manuscript.
+  This work was partially supported by CONICYT (Chile) under project No. 79140040. The ``Centro Cient\'ifico y Tecnol\'ogico de Valpara\'iso'' \mbox{(CCTVal)} is funded by the
+Chilean Government through the Centers of Excellence Base Financing Program of CONICYT.
 \end{acknowledgments}
@@
 
-\input{DA.tex}
-\input{MS.tex}
+%% \input{DA.tex}
+%% \input{MS.tex}
+\section{\label{DA}Dimensional analysis method}
+
+We built the model using six ingredients, a Curtright ($T^{\mu,\nu\lambda}$), a vector ($A_\mu$), the covariant derivative defined with the Levi-Civita connection ($\nab{\mu}$), both Levi-Civita tensors ($\epsilon_{\mu\nu\lambda\rho}$ and $\epsilon^{\mu\nu\lambda\rho}$), and the Riemannian curvature ($R_{\mu\nu}{}^\lambda{}_\rho$).
+Since the Riemannian curvature is defined as the commutator of the covariant derivative, it is not an independent field, so it will be left out of the analysis, and only five ingredients remain.
+
+Our interest is in general to build tensor densities.
+Therefore, we need to account for the number of \emph{free} indices, and weight density of these quantities.
+Denote by $N(\Phi)$  the operator which count the number (and position) of indices of the field $\Phi$, being positive (negative) for upper (lower) indices.
+Thus, we have that
+\begin{equation*}
+  \begin{aligned}
+    N( T^{\mu,\nu\lambda} ) &= 3 & N( A_\mu ) &= -1 & N(  \nab{\mu} ) &= -1 \\
+    N( \epsilon_{\mu\nu\lambda\rho} ) &= -4 & & & N( \epsilon^{\mu\nu\lambda\rho} ) &= 4 
+  \end{aligned}
+\end{equation*}
+Then, for a general expression of the form
+\begin{equation*}
+  T^a A^b \nabla^c {\epsilon_{\dots}}^d {\epsilon^{\dots}}^e,
+\end{equation*}
+the indices counting yield
+\begin{equation}
+  N( T^a A^b \nabla^c {\epsilon_{\dots}}^d {\epsilon^{\dots}}^e ) = n,
+\end{equation}
+with
+\begin{equation}
+  n = 3a -b -c -4d + 4e = 3 a -b - c + 4 \ell,
+  \label{ni}
+\end{equation}
+where we defined $\ell = e - d$, for the sake of simplicity.
+
+In the same spirit, we define an operator which counts the weight density,
+\begin{equation*}
+  \begin{aligned}
+    W( T^{\mu,\nu\lambda} ) &= 1 & W( A_\mu ) &= 0 & W(  \nab{\mu} ) &= 0 \\
+    W( \epsilon_{\mu\nu\lambda\rho} ) &= -1 & & & W( \epsilon^{\mu\nu\lambda\rho} ) &= 1 .
+  \end{aligned}
+\end{equation*}
+Thus, the weight ($w$) of the general expression above is given by
+\begin{equation}
+  w = a + \ell.
+  \label{wd}
+\end{equation}
+
+\subsection{\label{sec:im}Inverse metric density}
+
+Now, we illustrate the usefulness of the \emph{dimensional analysis} by building the most general symmetric $\binom{2}{0}$-tensor density, which we call the \emph{inverse metric density}.
+This particular case fixes $n = 2$ and $w = 1$.
+
+Equation~\eqref{wd} can solved by choosing either $a=1$ or $\ell = 1$, which imply that Eq.~\eqref{ni} is restricted to
+\begin{equation*}
+  3 - b - c = 2,
+\end{equation*}
+or
+\begin{equation*}
+  4 - b - c = 2,
+\end{equation*}
+respectively. The former, yields the terms
+\begin{equation}
+  T^{\mu,\nu\lambda} A_\lambda \text{ and } \nabla_\lambda T^{\mu,\nu\lambda},
+\end{equation}
+no other contraction of indices is allowed due to the symmetry. The latter, yields another possibility,
+\begin{equation}
+  \epsilon_{\lambda\kappa\rho\sigma} T^{\mu, \lambda\kappa} T^{\nu, \rho\sigma}.
+\end{equation}
+
+Finally, one can check that any other choice to solve Eq.~\eqref{wd}---by allowing negative values of $\ell$---make impossible to solve Eq.~\eqref{ni}.
+Ergo, there is no other term in a symmetric $\binom{2}{0}$-tensor density built up with these fields.
+Explicitly, this general tensor density is written in Eq.~\eqref{geng}.
+The summary of this analysis is presented in Table~\ref{tab:imd}.
+\begin{table}
+  \caption{Possible terms contributing to the inverse density metric. }
+  \label{tab:imd}
+  \begin{tabular}{|C{.23\linewidth}C{.23\linewidth}C{.23\linewidth}C{.23\linewidth}|}
+    \hline
+    $a$ & $b$ & $c$ & $\ell$ \\
+    \hline
+    1 & 1 & 0 & 0 \\
+    1 & 0 & 1 & 0 \\
+    2 & 0 & 0 &-1 \\
+    0 & 2 & 0 & 1 \\
+    0 & 1 & 1 & 1 \\
+    0 & 0 & 2 & 1 \\
+    \hline
+  \end{tabular}
+\end{table}
+
+\subsection{\label{sec:ld}Lagrangian density}
+
+\begin{table}
+  \caption{Possible terms contributing to the Lagrangian density.}
+  \label{tab:ld}
+  \begin{tabular}{|C{.23\linewidth}C{.23\linewidth}C{.23\linewidth}C{.23\linewidth}|}
+    \hline
+    $a$ & $b$ & $c$ & $\ell$ \\
+    \hline
+    1 & 3 & 0 & 0\\
+    1 & 2 & 1 & 0\\
+    1 & 1 & 2 & 0\\
+    1 & 0 & 3 & 0\\
+    2 & 2 & 0 & -1\\
+    2 & 1 & 1 & -1\\
+    2 & 0 & 2 & -1\\
+    3 & 1 & 0 & -2\\
+    3 & 0 & 1 & -2\\
+    4 & 0 & 0 & -3\\
+    0 & 4 & 0 & 1\\
+    0 & 3 & 1 & 1\\
+    0 & 2 & 2 & 1\\
+    0 & 1 & 3 & 1\\
+    0 & 0 & 4 & 1\\
+    \hline
+  \end{tabular}
+\end{table}
+
+The work of building up the most general scalar density with our ingredients is as simple as before, but the analysis is much longer. Thus, we will show the procedure with lesser details than before.
+
+First, we are interested in a scalar density, which sets $n = 0$ and $w = 1$ in Eqs.~\eqref{ni} and~\eqref{wd}, i.e.,
+\begin{align}
+  3a -b -c  + 4\ell &= 0, \label{nib}\\
+  a + \ell &= 1. \label{wdb}
+\end{align}
+
+A possible solution of Eq~\eqref{wdb} is $a=1$ and $\ell = 0$.
+Such choice allows four possible solutions of Eq.~\eqref{nib}, but only three of them are nonvanishing.
+These generate the terms of Eq.~\eqref{4dfull} whose coefficients were called $B_3$, $B_4$, $B_5$, $C_1$, $C_2$, $D_6$, $D_7$ and $E_2$.
+
+If one choose $\ell = 1$ for solving Eq.~\eqref{wdb}, all possible solutions for Eq.~\eqref{nib} are either vanishing or yield topological terms.
+%%The action in Eq.~\eqref{4dfull} was written up to topological and boundary terms, thus
+
+The case with $a=2$ and $\ell = -1$ gives three possibilities to solve Eq.~\eqref{nib}.
+These choices give the terms the Lagrangian density whose coefficients are $B_1$, $B_2$, $D_4$, $D_5$, $E_1$, and $F_4$.
+
+For $a = 3$ and $\ell = -2$ there are only two possible solutions of Eq.~\eqref{nib}, and these yield the terms of the action with coefficients $D_1$, $D_2$, $D_3$ and $F_3$.
+And also, the choice $a = 4$ and $\ell = -3$ solves the equations, and yield the terms in the action with coefficients $F_1$ and $F_2$.
+
+Notice that for values $a \ge 5$, it is not possible to solve both Eqs.~\eqref{nib} and~\eqref{wdb} simultaneously.
+Therefore, we conclude that Eq.~\eqref{4dfull} is the most general action built up with these fields.
+A summary of the choices for building the Lagrangian density is presented in Table~\ref{tab:ld}.
+
+\section{\label{Known}Known metric solutions to the parallel Ricci equations}
+
+In this Appendix, we will present a brief compendium of known (Riemannian) metric solutions of Eq.~\eqref{SimpleEOM} in four dimensions.
+The results presented in this Appendix is not original, and can be found in Refs.~\cite{gray1978einstein,derdzinski1980classification,derdzinski1982compact,Derdzinski:1985,Besse}.
+
+\paragraph{Einstein spaces.---} The simplest example of a manifold with parallel Ricci is a Riemannian Einstein manifols. This example was explained on the main text.
+
+\paragraph{Riemannian products.---} The Riemamian product of manifolds with harmonic curvature.
+
+\paragraph{Conformally flat manifolds.---} These are solutions in four dimensions if their scalar curvature is constant.
+
+\paragraph{Warped products.---} Compact warped products of the form \mbox{$(S^1 \times \bar{M}, \de{t}^2 + f(t) \de{s}^2(\bar{g}) )$,} where $(\bar{M}, \bar{g})$ is an Einstein manifold with positive scalar curvature, $\bar{R} > 0$, and $f$ is a positive function on $S^1$ satisfying the differential equation
+\begin{equation}
+  \ddot{f} - \frac{1}{3} \bar{R} = c f,
+\end{equation}
+for a negative constant $c$.
+
+{Twisted} warped products of the form $(\R \times \bar{M} ) / \Z$ have parallel Ricci, if the $\Z$-action on the product metric involves an isometry of $\bar{g}$.
+
+Compact warped products of the form \mbox{$(M_1 \times M_2, f^{2} \cdot (g_1 \times g_2) )$,} where $M_i$ are two two-dimensional manifolds, $M_1$ has constant Gau\ss{}ian curvature, $K_1 < 0$, and $M_2$ is an Einstein manifold with scalar curvature $R_2 = - 2 K_1$.
+The function $f: M_1 \to \R^+$ is a $C^\infty$ solution of
+\begin{equation*}
+  \Lap f = c \, f^3 \text{ for } c > 0.
+\end{equation*}
+
+Many examples and explicit conditions of Riemannian metrics with harmonic curvature, and conditions for them to have parallel Ricci, can be found in Ref.~\cite{derdzinski1988riemannian}.
+
+Although the above are examples of manifolds with parallel Ricci within the context of ``Riemannian'' geometries, examples of connnections with parallel Ricci can be found in symplectic geometries, see Ref.~\cite{cahen2000symplectic}.
+
+\section{\label{Schw}Explicit example: Schwarzschild ansatz, and Birkhoff theorem}
+
+%% As a disclaimer\hl{What is this... Should this be dropped?}, we clarify that the example below is a pseudo-Riemannian manifold.
+
+%% \subsubsection{Schwarzschild metric}
+
+As pointed out, all vacuum solutions of Einstein's equations---with and without cosmological constant---satisfy the parallel Ricci condition trivially~\cite{bourguignon1981varietes}.
+Nonetheless, an important result in General Relativity is the stability of the Schwarzschild metric, known as the Birkhoff theorem~\cite{Jebsen1921,Birkhoff1923,Alexandrow1923,Eisland1925}, which implies that the gravitational collapse of a spherically symmetric astrophysical object cannot emit gravitational radiation.
+
+In this section we show that the simplest ansatz of a static and spherically symmetric metric, which solves the Eq.~\eqref{SimpleEOM} is necessarily the (Anti-)de-Sitter--Schwarzschild metric.
+This should be taken as a first step toward a Birkhoff theorem, despite the fact that a complete proof is far from been achieved.
+
+Consider first the simplest metric ansatz, whose line element is
+\begin{equation}
+  \de{s}^2 = - f(t,r) \de{t}^2 + \frac{ \de{r}^2 }{ f(t,r) } + r^2 \de{\Omega}^2.
+  \label{simpleSchw}
+\end{equation}
+\begin{widetext}
+  The nontrivial field equation for the ansatz~\eqref{simpleSchw} are
+  \begin{dmath}
+    \nabla_{[\mu} R_{\nu]\lambda} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) \,
+    \delta_{\mu\nu}^{10} \delta_\lambda^0
+    +
+    \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) \,
+    \delta_{\mu\nu}^{10} \delta_\lambda^1
+    +
+    r \frac{\partial^2}{\partial t^{}\partial r^{}}f \,
+    \Big( \delta_{\mu\nu}^{20} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{30} \delta_\lambda^3 \Big)
+    +
+    \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg) \,
+    \Big( \delta_{\mu\nu}^{21} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{31} \delta_\lambda^3 \Big)
+    = 0
+  \end{dmath}
+  %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+  %%   \begin{dmath}
+  %%   \nabla_{[1} R_{0]0} = \frac{1}{2 \, r^{2} f^{3}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial r^{3}}f + 2 \, r f^{4} \frac{\partial^2}{\partial r^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}f - 4 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{}\partial r^{}}f - 2 \, f^{4} \frac{\partial}{\partial r^{}}f + 2 \, {\left(3 \, r^{2} \frac{\partial}{\partial r^{}}f - 2 \, r f\right)} \frac{\partial}{\partial t^{}}f^{2} - 2 \, {\left(r^{2} f \frac{\partial}{\partial r^{}}f - r f^{2}\right)} \frac{\partial^2}{\partial t^{2}}f \Bigg) ,
+  %%   \label{e100}
+  %% \end{dmath}
+  %% \begin{dmath}
+  %%   \nabla_{[1} R_{0]1} = \frac{1}{2 \, r^{2} f^{5}} \Bigg( r^{2} f^{4} \frac{\partial^3}{\partial t^{}\partial r^{2}}f + 2 \, f^{4} \frac{\partial}{\partial t^{}}f + 6 \, r^{2} \frac{\partial}{\partial t^{}}f^{3} - 6 \, r^{2} f \frac{\partial}{\partial t^{}}f \frac{\partial^2}{\partial t^{2}}f + r^{2} f^{2} \frac{\partial^3}{\partial t^{3}}f \Bigg) .
+  %%   \label{e101}
+  %% \end{dmath}
+  %% \begin{dmath}
+  %%   \nabla_{[2} R_{0]2} = r \frac{\partial^2}{\partial t^{}\partial r^{}}f,
+  %%   \label{e202}
+  %% \end{dmath}
+  %% \begin{dmath}
+  %%   \nabla_{[2} R_{1]2} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3} \Bigg),
+  %%   \label{e212}
+  %% \end{dmath}
+  %% %% \begin{dmath}
+  %% %%   \nabla_{[3} R_{0]3} = r \sin\left({\theta}\right)^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}f,
+  %% %%   \label{e303}
+  %% %% \end{dmath}
+  %% %% and
+  %% %% \begin{dmath}
+  %% %%   \nabla_{[3} R_{1]3} = \frac{1}{2 \, r f^{3}} \Bigg(r^{2} f^{3} \frac{\partial^2}{\partial r^{2}}f - 2 \, f^{4} + 2 \, r^{2} \frac{\partial}{\partial t^{}}f^{2} - r^{2} f \frac{\partial^2}{\partial t^{2}}f + 2 \, f^{3}\Bigg) \sin\left({\theta}\right)^{2}.
+  %% %%   \label{e313}
+  %% %% \end{dmath}
+  %% \begin{align}
+  %%   \nabla_{[3} R_{0]3} &= \sin\left({\theta}\right)^{2} \nabla_{[2} R_{0]2}, &
+  %%   \nabla_{[3} R_{1]3} &= \sin\left({\theta}\right)^{2} \nabla_{[2} R_{1]2}.
+  %% \end{align}
+\end{widetext}
+Even though four out of the six nontrivial field equations are independent, the system can be solved uniquely.
+First, the component along the $(\mu\nu\lambda) = (2,0,2)$ yields $f = T(t) + R(r)$.
+Then, one notices that the equation along $(\mu\nu\lambda) = (1,0,1)$ contains a term depending solely on $t$, which implies that $\dot{T}$ vanishes, i.e., $T$ is a constant.
+From here, the equation for $(\mu\nu\lambda) = (2,1,2)$ gets simple enough to be solved and yields, \mbox{$R(r) = 1 - T + \frac{\alpha}{r} + \beta r^2$} or equivalently
+\begin{equation}
+  f(r) = 1 + \frac{\alpha}{r} + \beta r^2,
+  \label{simplef}
+\end{equation}
+with $\alpha$ and $\beta$ integration constants.
+Finally, it can be checked that albeit the equation along the components $(\mu,\nu,\lambda) = (1,0,0)$ was not used, it is satisfied by Eq.~\eqref{simplef}.
+
+The above shows that the simplest time-dependent generalization of Schwarzschild metric is not a solution for the field equations of the considered affine model.
+Unless, the spacetime metric is static and exactly that for a Schwarzschild's exterior solution, with or without cosmological constant.
+
+However, if one tries a metric ansatz with two different factors, say
+\begin{equation}
+  \de{s}^2 = - A(t,r) \de{t}^2 + \frac{ \de{r}^2 }{ B(t,r) } + r^2 \de{\Omega}^2,
+  \label{ABmetric}
+\end{equation}
+the field equations are so complicated, that although hints on the solubility were found---and yield to Eq.~\eqref{simplef} for both $A$ and $B$---, the uniqueness of the solution has not been proven.
+The field equations for the metric~\eqref{ABmetric} are %%shown in Appendix~\ref{app:eqAB}.
+\begin{widetext}
+  \begin{dmath}
+    \nabla_{[\mu} R_{\nu]\lambda} = \frac{1}{4 \, r^{2} B^{3} A^{2}} \Bigg( 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{3} + 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial r^{3}}A + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{2}\partial r^{}}B - 6 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}B - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{}\partial r^{}}A + 6 \, {\left(r^{2} A^{2} \frac{\partial}{\partial r^{}}B - r B A^{2}\right)} \frac{\partial}{\partial t^{}}B^{2} - 2 \, {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B + r B^{4} A\right)} \frac{\partial}{\partial r^{}}A^{2} - 2 \, {\left(r^{2} B A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A^{2}\right)} \frac{\partial^2}{\partial t^{2}}B - {\left(r^{2} B^{2} A \frac{\partial^2}{\partial t^{}\partial r^{}}B - 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - {\left(r^{2} B A \frac{\partial}{\partial r^{}}B - 2 \, r B^{2} A\right)} \frac{\partial}{\partial t^{}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial^2}{\partial r^{2}}B + 2 \, r B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, B^{4} A^{2} + 3 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial r^{}}A + {\left(3 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 4 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A + 4 \, r B^{4} A^{2}\right)} \frac{\partial^2}{\partial r^{2}}A \Bigg) \,
+    \delta_{\mu\nu}^{10} \delta_\lambda^0
+    +
+    \frac{1}{4 \, r^{2} B^{4} A^{3}} \Bigg( 2 \, r^{2} B^{4} A^{2} \frac{\partial^3}{\partial t^{}\partial r^{2}}A + r^{2} B^{3} A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{3} A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial r^{2}}A + 4 \, B^{3} A^{3} \frac{\partial}{\partial t^{}}B + 6 \, r^{2} A^{2} \frac{\partial}{\partial t^{}}B^{3} - 8 \, r^{2} B A^{2} \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}B + 2 \, r^{2} B^{2} A^{2} \frac{\partial^3}{\partial t^{3}}B + 2 \, r^{2} B^{2} \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A^{2} - r^{2} B^{2} A \frac{\partial}{\partial t^{}}B \frac{\partial^2}{\partial t^{2}}A - {\left(r^{2} B^{3} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - 2 \, r^{2} B^{4} \frac{\partial}{\partial r^{}}A^{2} + 2 \, r^{2} B^{4} A \frac{\partial^2}{\partial r^{2}}A - 4 \, r^{2} B A \frac{\partial}{\partial t^{}}B^{2} + 3 \, r^{2} B^{2} A \frac{\partial^2}{\partial t^{2}}B\right)} \frac{\partial}{\partial t^{}}A + {\left(r^{2} B^{3} A^{2} \frac{\partial}{\partial r^{}}B - 2 \, r^{2} B^{4} A \frac{\partial}{\partial r^{}}A\right)} \frac{\partial^2}{\partial t^{}\partial r^{}}A \Bigg) \,
+    \delta_{\mu\nu}^{10} \delta_\lambda^1
+    +
+    \frac{1}{2 \, A^{2}} \Bigg( r A^{2} \frac{\partial^2}{\partial t^{}\partial r^{}}B + r B A \frac{\partial^2}{\partial t^{}\partial r^{}}A + r A \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial r^{}}A - r B \frac{\partial}{\partial t^{}}A \frac{\partial}{\partial r^{}}A \Bigg) \,
+    \Big( \delta_{\mu\nu}^{20} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{30} \delta_\lambda^3 \Big)
+    +
+    \frac{1}{4 \, r B^{2} A^{2}} \Bigg( 2 \, r^{2} B^{2} A^{2} \frac{\partial^2}{\partial r^{2}}B + r^{2} B^{2} A \frac{\partial}{\partial r^{}}B \frac{\partial}{\partial r^{}}A - r^{2} B^{3} \frac{\partial}{\partial r^{}}A^{2} + 3 \, r^{2} A \frac{\partial}{\partial t^{}}B^{2} - 2 \, r^{2} B A \frac{\partial^2}{\partial t^{2}}B + r^{2} B \frac{\partial}{\partial t^{}}B \frac{\partial}{\partial t^{}}A - 4 \, {\left(B^{3} - B^{2}\right)} A^{2} \Bigg) \,
+    \Big( \delta_{\mu\nu}^{21} \delta_\lambda^2 + \sin^2(\theta) \delta_{\mu\nu}^{31} \delta_\lambda^3 \Big)
+    = 0,
+    \label{hugeeq}
+  \end{dmath}
+\end{widetext}
+which are very complex.
+Nonetheless, the symmetries in some of the components of these equations seem to favour the relation $A = B$ as solution.
+In addition, we found a very interesting reference in which a proof of the Birkhoff theorem is given for an Einstein--Cartan theory coupled with the gravitational Yang--Mills~\cite{Ramaswamy:1979zz}, which support the hand-waving symmetry argument above.
+
+Hence, further analysis requires a new strategy. Instead of considering a metric, a connection ansatz is proposed based in the structure of a spherically symmetric metric of the form,
+\begin{equation}
+  \de{s}^2 = g_{ab}(x) \, \de{x}^a\de{x}^b + e^{2\rho(x)} \, g_{AB}(\vph)  \de{\vph}^A\de{\vph}^B,
+  \label{sphere-gen}
+\end{equation}
+where $x^m$ represent the temporal an radial directions, while $\vph^M$ represent angular coordinates.
+Notice that the four-dimensional indices have been partitioned as \mbox{$\mu = (a,A)$,} then the general form of the connection is
+%~\footnote{For the metric of Eq.~\eqref{sphere-gen}, the factors are \mbox{$M^a(x) = - e^{2\rho(x)} g^{am}\partial_m \rho$} and \mbox{$N_c = \partial_c \rho$.}}
+\begin{dmath}
+  \Ga^\lambda{}_{\mu\nu} = \delta^\lambda_a \delta^b_\mu \delta^c_\nu \ga^a{}_{bc} + \delta^\lambda_A \delta^B_\mu \delta^C_\nu \ga^A{}_{BC} + \delta^\lambda_a \delta^B_\mu \delta^C_\nu g_{BC} M^a(x) +  \delta^\lambda_A \delta^A_{(\mu} \delta^c_{\nu)} N_{c}(x),
+  \label{connSchw}
+\end{dmath}
+where $\ga^a{}_{bc}$ and $\ga^A{}_{BC}$ are the Levi-Civita connection for the metrics $g_{ab}$ and $g_{AB}$ respectively, and the factors are \mbox{$M^a(x) = - \tfrac{1}{2}  g^{am}\partial_m e^{2\rho(x)}$} and \mbox{$N_c = 2 \partial_c \rho$}.
+
+From the connection ansatz~\eqref{connSchw} the Ricci tensor is
+\begin{dmath}
+  R_{\mu\nu}
+  = \delta_\mu^m \delta_\nu^n \big( R_{mn} - 2 \nab{m} N_n - 2 N_m N_n \big)
+  + \delta_\mu^M \delta_\nu^N \big( R_{MN} + g_{MN} \nab{a} M^a \big),
+  %% + ( \delta_\mu^M \delta_\nu^n + \delta_\mu^n \delta_\nu^M ) \gamma^A{}_{AM} N_n
+\end{dmath}
+and the equations of motion are
+\begin{widetext}
+  \begin{dmath}
+    \nabla_{[\lambda} R_{\mu]\nu}
+    = \delta_\lambda^l \delta_\mu^m \delta_\nu^n  \bigg( \frac{1}{2} g_{n[m} \partial_{l]} \mathcal{R} + 2 \mathcal{R}  g_{n[m} N_{l]}(x) - 2 \nabla_{[l} \Big( N_{m]} N_n \Big) \bigg)
+    + \delta_\lambda^{[l} \delta_\mu^{M]} \delta_\nu^N \, g_{MN} \bigg( \nab{l} \nab{a} M^a + \frac{\mathcal{R}}{2} g_{la} M^a - 2 N_l - 2 \nab{a} \Big( M^a N_l \Big) - 2 M^a N_a N_l \bigg).
+    \label{OurEq}
+  \end{dmath}
+\end{widetext}
+We have used that $g_{AB}(\varphi)$ is the metric of a two-sphere, and its curvature tensors are well known.
+In addition, since the metric $g_{ab}(x)$ is two-dimensional too, its curvature tensors are related with the metric by the relation
+\begin{dmath}
+  R_{ab}{}^c{}_d = \frac{\mathcal{R}}{2} \Big( \delta^c_a g_{bd} - \delta^c_b g_{ad} \Big).
+\end{dmath}
+
+As argue  in Refs.~\cite{bergmann1965spherically,hawking1973large},  the solution depends on the nature of the surfaces described by $\rho = \text{const.}$, which in our parametrization translate to the nature of $N_a$.
+We first consider the condition $g^{ab} N_a N_b > 0 $, which allows to set $\rho$ as a good radial coordinate.
+Therefore, the general metric ansatz $g_{ab}$ is diagonal, and the radial direction would be $\rho$, i.e.,
+\begin{equation}
+  g_{ab} = - \alpha^2(t,\rho) \de{t}_a \otimes \de{t}_b + \beta^2(t,\rho) \de{\rho}_a \otimes \de{\rho}_b.
+  \label{metr2d}
+\end{equation}
+With this ansatz, the nontrivial components of Eq.~\eqref{OurEq} are
+\begin{align}
+  \beta^2 \pa{t} \mathcal{R} + 8 \gamma^\rho{}_{t \rho} &= 0,
+  \label{eq1}
+  \\
+  \pa{\rho} \mathcal{R} - 4 \mathcal{R} + 16 \alpha^{-2} \gamma^\rho{}_{tt} &= 0,
+  \label{eq2}
+  \\
+  \pa{t} \big( \Delta_x e^{2\rho} \big) + 4 \beta^{-2} e^{2\rho} \gamma^\rho{}_{t \rho} &= 0,
+  \label{eq3}
+\end{align}
+and
+\begin{dmath}
+  \pa{\rho} \big( \Delta_x e^{2\rho} \big) + 8 - 4 \Delta_x e^{2\rho} - 16 \beta^{-2} e^{2\rho} - 4 \beta^{-2} e^{2\rho} \gamma^{\rho}{}_{\rho\rho}  + \mathcal{R} e^{2\rho} = 0.
+  \label{eq4}
+\end{dmath}
+From equation~\eqref{eq1} it follows that,
+%% can be rewritten as
+%% \begin{equation}
+%%   \pa{t} \big( \mathcal{R} - 8 \beta^{-2} \big) = 0,
+%%   \label{eq1a}
+%% \end{equation}
+%% or 
+\begin{equation}
+  \mathcal{R} - 8 \beta^{-2} = G_1(\rho).
+  \label{eq1b}
+\end{equation}
+In addition, since
+\begin{equation}
+  \Delta_x e^{2\rho}
+  = e^{2\rho} \bigg[ 4 \beta^{-2} + \frac{2}{\alpha \beta} \pa{\rho} \bigg( \frac{\alpha}{\beta} \bigg) \bigg]
+  \equiv  e^{2\rho} \Big[ 4 \beta^{-2} + \mathcal{F} \Big],
+\end{equation}
+it follows from Eqs.~\eqref{eq3} that,
+%% \begin{equation}
+%%   \pa{t} \big( F + 2 \beta^{-2} \big) = 0,
+%%   \label{eq3a}
+%% \end{equation}
+%% or 
+\begin{equation}
+  \mathcal{F} + 2 \beta^{-2} = G_2(\rho).
+  \label{eq3b}
+\end{equation}
+
+Equations~\eqref{eq1b} and~\eqref{eq3b} implies that all temporal dependence on time within $\mathcal{R}$, $\mathcal{F}$ and $\beta^{-2}$, enters through an additive common function, say $B(t,\rho)$.
+However, the consistency of these equations with the value of $\mathcal{R}$ calculated from the metric ansatz, in Eq.~\eqref{metr2d}, sets this additive function to zero, $B(t,\rho)$.
+Therefore, neither $\mathcal{R}$, $\mathcal{F}$ nor $\beta^{-2}$ depend on $t$.
+By extension---from the definition of $\mathcal{F}$---, $\alpha$ could depend on time through a multiplicative function.
+Nonetheless, this multiplicative function can be eliminated of the problem by a redefinition of the \emph{time} coordinate.
+
+At this stage, we have proved that \emph{any spherically symmetric (metric) solution of the Eqs.~\eqref{SimpleEOM} is necessarily static}, which is one of the main statements of Birkhoff's theorem.
+
+This result, simplifies the Eq.~\eqref{hugeeq} but the equations are still non-linear.
+However, one can get ride off the non-linearity by setting $A(r) = B(r)$.
+In this \emph{linearized} regime, according to Eq.~\eqref{simplef} the general (metric) solution is the (Anti-)de-Sitter--Schwarzschild metric.
+
+Although we restricted ourselves to the \emph{linearized} regime of the field equations, it is possible to go a bit further in the nonlinear regime.
+As a preliminary result~\cite{OCF-future2}, we have found that using the Frobenius methods with a Laurent series expansion, the leading order of the solutions is three-fold in the radial coordinate.
+These solutions correspond to the pairs given by $(\alpha,\beta)$---$\alpha$ (resp.
+$\beta)$ is the leading order of the series expansion for the function $A(r)$ (resp.
+$B(r)$)---equals to $(-1,-1)$, $(2,-2)$ and $(0,-1)$.
+%%Two of these branches coincide with the reciprocal and quadratic dependence on $r$ of $A$ and $B$, while the third one gives novel dependence,
+%% \begin{equation}
+%%   A(r) = 1 + \frac{\alpha}{r} + \beta r^2 + \frac{\gamma}{r^2},
+%% \end{equation}
+%% and
+%% \begin{equation}
+%%   B(r) = 1 + \frac{\alpha}{r} + (\beta + \gamma) r^2.
+%% \end{equation}
+
+%% \section{extra... DELETE IT}
+
+%% \begin{widetext}
+%%   \begin{dmath*}
+%%     todo2 :=
+%%     %% \Lambda {\epsilon}_{\alpha \beta \gamma \delta} (B_1 + \frac{1}{3}\, B_2) {t_{\perp}}_{\eta}\,^{\alpha \beta} {t_{\perp}}^{\eta \gamma \delta} + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}_{\eta}{{ta}^{\alpha \beta}}\,  (4\, B_1 + \frac{4}{3}\, B_2) {t_{\perp}}^{\eta \gamma \delta} + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{t_{\mathtt{v}}}^{\beta}}\,  (4\, B_1 + \frac{4}{3}\, B_2) {t_{\perp}}^{\eta \gamma \delta} + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\eta}{{ta}^{\gamma \delta}}\,  (4\, B_1 + \frac{4}{3}\, B_2) + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\gamma}{{ts}^{\delta \eta}}\,  (8\, B_1 + \frac{8}{3}\, B_2) + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\gamma \eta}{{t_{\mathtt{v}}}^{\delta}}\,  (8\, B_1 + \frac{8}{3}\, B_2) + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{t_{\mathtt{v}}}^{\beta}}\,  {\nabla}^{\gamma \eta}{{t_{\mathtt{v}}}^{\delta}}\,  (4\, B_1 + \frac{4}{3}\, B_2)
+%%     + \Lambda ( - B_3 + \frac{2}{3}\, B_4) {at}_{\alpha} {t_{\perp}}_{\beta}\,^{\alpha \beta} + \Lambda {\nabla}^{\alpha}\,_{\beta}{{t_{\mathtt{v}}}^{\beta}}\,  ( - B_3 + \frac{2}{3}\, B_4) {at}_{\alpha} + \Lambda {\nabla}^{\alpha}\,_{\alpha}{{t_{\mathtt{v}}}^{\beta}}\,  (B_3 - \frac{2}{3}\, B_4) {at}_{\beta} + \Lambda {\nabla}_{\alpha}{aL}\,  ( - B_3 + \frac{2}{3}\, B_4) {t_{\perp}}_{\beta}\,^{\alpha \beta} + \Lambda {\nabla}_{\alpha}{aL}\,  {\nabla}^{\alpha}\,_{\beta}{{t_{\mathtt{v}}}^{\beta}}\,  ( - B_3 + \frac{2}{3}\, B_4) + \Lambda {\nabla}_{\alpha}{aL}\,  {\nabla}^{\beta}\,_{\beta}{{t_{\mathtt{v}}}^{\alpha}}\,  (B_3 - \frac{2}{3}\, B_4) + C_1 \Lambda {gt}_{\alpha \beta \gamma} {t_{\perp}}^{\beta \alpha \gamma} + C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {t_{\perp}}^{\beta \alpha \gamma} + 3\, C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta}{{ta}^{\alpha \gamma}}\,  - C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta}{{ts}^{\alpha \gamma}}\,  - C_1 \Lambda {\nabla}^{\alpha}\,_{\alpha}{{ts}^{\beta \gamma}}\,  {gs}_{\beta \gamma} - C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta \gamma}{{t_{\mathtt{v}}}^{\alpha}}\, %
+%%     + C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\alpha \beta}{{t_{\mathtt{v}}}^{\gamma}}\,  + C_1 \Lambda {\nabla}_{\alpha \beta}{{gv}_{\gamma}}\,  {t_{\perp}}^{\alpha \beta \gamma} + 2\, C_1 \Lambda {\nabla}_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}^{\alpha}\,_{\beta}{{gv}_{\gamma}}\,  - C_1 \Lambda {\nabla}_{\alpha \beta}{{gv}_{\gamma}}\,  {\nabla}^{\alpha \gamma}{{t_{\mathtt{v}}}^{\beta}}\,  + C_1 \Lambda {\nabla}_{\alpha \beta}{{gv}_{\gamma}}\,  {\nabla}^{\alpha \beta}{{t_{\mathtt{v}}}^{\gamma}}\,  + 2\, C_1 \Lambda {\nabla}_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}_{\beta \gamma}{{gvp}^{\alpha}}\,  + 2\, C_1 \Lambda {\nabla}_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}^{\alpha}\,_{\beta \gamma}{gL}\,  + 2\, C_1 \Lambda {\nabla}^{\alpha}\,_{\beta}{{t_{\mathtt{v}}}^{\gamma}}\,  {\nabla}_{\alpha}\,^{\beta}\,_{\gamma}{gL}\,  + 3\, C_1 {\nabla}^{\alpha}\,_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta}\,_{\delta}{{ta}^{\gamma \delta}}\,  - C_1 {\nabla}^{\alpha}\,_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ts}^{\beta \gamma}}\,  - C_1 {\nabla}^{\alpha}\,_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  + 3\, C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\beta}\,_{\delta}{{ta}^{\gamma \delta}}\,  + 3\, C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\gamma}\,_{\delta}{{ta}^{\beta \delta}}\,  - 2\, C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ts}^{\beta \gamma}}\,  - C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\beta \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  - C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\gamma \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\beta}}\,  + {\nabla}^{\alpha}\,_{\beta}{{ta}^{\beta \gamma}}\,  {\nabla}_{\alpha}\,^{\delta}\,_{\delta}{{gv}_{\gamma}}\,  ( - 2\, C_1 + 2\, C_2) + {\nabla}^{\alpha}\,_{\beta}{{ta}^{\beta \gamma}}\,  {\nabla}_{\gamma}\,^{\delta}\,_{\delta}{{gv}_{\alpha}}\,  ( - C_1 - 2\, C_2) + {\nabla}^{\alpha}\,_{\alpha}{{ta}^{\beta \gamma}}\,  {\nabla}_{\beta}\,^{\delta}\,_{\delta}{{gv}_{\gamma}}\,  ( - C_1 + 4\, C_2) - C_1 {\nabla}^{\alpha}\,_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}_{\beta}\,^{\delta}\,_{\delta}{{gv}_{\gamma}}\, %
+%%     + {\nabla}^{\alpha}\,_{\alpha \beta}{{gv}_{\gamma}}\,  {\nabla}^{\beta \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  ( - C_1 + 2\, C_2) + {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\gamma}\,_{\delta}{{ta}^{\alpha \delta}}\,  ( - 2\, C_1 + 2\, C_2) + {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\alpha}\,_{\delta}{{ta}^{\gamma \delta}}\,  ( - C_1 - 2\, C_2) + {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ta}^{\alpha \gamma}}\,  ( - C_1 + 4\, C_2) + C_1 {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ts}^{\alpha \gamma}}\,  + {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\gamma \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\alpha}}\,  (C_1 - 2\, C_2) - 3\, C_1 {\nabla}_{\alpha \beta}{{gp}^{\gamma}\,_{\gamma}}\,  {\nabla}^{\alpha}\,_{\delta}{{ta}^{\beta \delta}}\,  + C_1 {\nabla}_{\alpha \beta}{{gp}^{\gamma}\,_{\gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ts}^{\alpha \beta}}\,  + C_1 {\nabla}_{\alpha \beta}{{gp}^{\gamma}\,_{\gamma}}\,  {\nabla}^{\alpha \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\beta}}\,  + 3\, C_1 {\nabla}^{\alpha}\,_{\beta}{{ta}^{\beta \gamma}}\,  {\nabla}_{\alpha \gamma}\,^{\delta}{{gv}_{\delta}}\,  + C_1 {\nabla}^{\alpha}\,_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}_{\beta \gamma}\,^{\delta}{{gv}_{\delta}}\,  + C_1 {\nabla}^{\alpha}\,_{\beta \gamma}{{gv}_{\alpha}}\,  {\nabla}^{\beta \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  + 2\, C_2 {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\alpha \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  - 2\, C_2 {\nabla}^{\alpha}\,_{\alpha \beta}{{gv}_{\gamma}}\,  {\nabla}^{\gamma \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\beta}}\,
+%%     %% + 4\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\eta}\,_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\lambda}\,_{\lambda}{{ta}^{\gamma \delta}}\,  - 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{ta}^{\beta \eta}}\,  {\nabla}^{\lambda}\,_{\lambda}{{ta}^{\gamma \delta}}\,  + 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\eta}\,_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\gamma \lambda}\,_{\lambda}{{t_{\mathtt{v}}}^{\delta}}\,  + 4\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{ta}^{\beta \eta}}\,  {\nabla}^{\gamma}\,_{\lambda}{{ta}^{\delta \lambda}}\,  - 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{ta}^{\beta \eta}}\,  {\nabla}^{\gamma \lambda}\,_{\lambda}{{t_{\mathtt{v}}}^{\delta}}\,  + 4\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha \eta}\,_{\eta}{{t_{\mathtt{v}}}^{\beta}}\,  {\nabla}^{\gamma \lambda}\,_{\lambda}{{t_{\mathtt{v}}}^{\delta}}\, %
+%%     + 3\, E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\gamma}\,_{\gamma}{{ta}^{\alpha \beta}}\,  - 3\, E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\alpha}\,_{\gamma}{{ta}^{\beta \gamma}}\,  + 2\, E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\alpha \gamma}\,_{\gamma}{{t_{\mathtt{v}}}^{\beta}}\,  - E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\beta \gamma}\,_{\gamma}{{t_{\mathtt{v}}}^{\alpha}}\,  - 3\, E_2 {\nabla}_{\alpha \beta}{aL}\,  {\nabla}^{\alpha}\,_{\gamma}{{ta}^{\beta \gamma}}\,  + E_2 {\nabla}_{\alpha \beta}{aL}\,  {\nabla}^{\alpha \gamma}\,_{\gamma}{{t_{\mathtt{v}}}^{\beta}}\,  + E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\gamma}\,_{\gamma}{{ts}^{\alpha \beta}}\,  + E_2 {\nabla}_{\alpha \beta}{aL}\,  {\nabla}^{\gamma}\,_{\gamma}{{ts}^{\alpha \beta}}\, ;
+%%   \end{dmath*}
+%% \end{widetext}
 
 %%%%%%%%% BIBLIOGRAPHY %%%%%%%%%
-%%\bibliographystyle{apsrev4-1}
+%% \bibliographystyle{utphys}
 \bibliography{References.bib}

### 2016-05-11 DA.tex
With Vijay comments, and others by me
Approved to be uploaded

@@
-\section{\label{DA}Dimensional analysis for building the polynomial affine gravity}
+\section{\label{DA}Dimensional analysis method}
 
@@
 
-\subsection{Inverse metric density}
+\subsection{\label{sec:im}Inverse metric density}
 
@@
 
-Finally, one can check that any other choice to solve Eq.~\eqref{wd} ---by allowing negative values of $\ell$--- make impossible to solve Eq.~\eqref{ni}.
+Finally, one can check that any other choice to solve Eq.~\eqref{wd}---by allowing negative values of $\ell$---make impossible to solve Eq.~\eqref{ni}.
 Ergo, there is no other term in a symmetric $\binom{2}{0}$-tensor density built up with these fields.
@@
 
-\subsection{Lagrangian density}
+\subsection{\label{sec:ld}Lagrangian density}
 

### 2016-05-11 MS.tex
Almost complete. Please finish conclusions
Approved to be uploaded

@@
 
-As pointed out, all vacuum solutions of Einstein's equations ---with and without cosmological constant--- satisfy the parallel Ricci condition trivially~\cite{bourguignon1981varietes}.
+As pointed out, all vacuum solutions of Einstein's equations---with and without cosmological constant---satisfy the parallel Ricci condition trivially~\cite{bourguignon1981varietes}.
 Nonetheless, an important result in General Relativity is the stability of the Schwarzschild metric, known as the Birkhoff theorem~\cite{Jebsen1921,Birkhoff1923,Alexandrow1923,Eisland1925}, which implies that the gravitational collapse of a spherically symmetric astrophysical object cannot emit gravitational radiation.
 
-In this section we show that the simplest ansatz of a static and spherically symmetric metric, which solves the Eq.~\eqref{SimpleEOM} is necessarily the $\Lambda$--Schwarzschild metric.
+In this section we show that the simplest ansatz of a static and spherically symmetric metric, which solves the Eq.~\eqref{SimpleEOM} is necessarily the (Anti-)de-Sitter--Schwarzschild metric.
 This should be taken as a first step toward a Birkhoff theorem, despite the fact that a complete proof is far from been achieved.
@@
 \end{widetext}
-Even though four out of the six nontrivial field equations are independent, the system can be solve uniquely.
+Even though four out of the six nontrivial field equations are independent, the system can be solved uniquely.
 First, the component along the $(\mu\nu\lambda) = (2,0,2)$ yields $f = T(t) + R(r)$.
@@
 The above shows that the simplest time-dependent generalization of Schwarzschild metric is not a solution for the field equations of the considered affine model.
-Unless, the spacetime metric is static and exactly that for a Schwarzschild exterior solution, with or without cosmological constant.
+Unless, the spacetime metric is static and exactly that for a Schwarzschild's exterior solution, with or without cosmological constant.
 
@@
 \end{equation}
-the field equations are so complicated, that although hints on the solubility were found ---and yield to Eq.~\eqref{simplef} for both $A$ and $B$---, the uniqueness of the solution is far for been proved.
+the field equations are so complicated, that although hints on the solubility were found---and yield to Eq.~\eqref{simplef} for both $A$ and $B$---, the uniqueness of the solution has not been proven.
 The field equations for the metric~\eqref{ABmetric} are %%shown in Appendix~\ref{app:eqAB}.
@@
 \end{widetext}
-which are very complex, and ---to our knowledge--- these are not possible to solve in general.
-Nonetheless, the symmetries in some of the components of these equations seems to favour the relation $A = B$ as solution.
+which are very complex.
+Nonetheless, the symmetries in some of the components of these equations seem to favour the relation $A = B$ as solution.
 In addition, we found a very interesting reference in which a proof of the Birkhoff theorem is given for an Einstein--Cartan theory coupled with the gravitational Yang--Mills~\cite{Ramaswamy:1979zz}, which support the hand-waving symmetry argument above.
@@
 $\beta)$ is the leading order of the series expansion for the function $A(r)$ (resp.
-$B(r)$)---equals to $(-1,-1)$, $(2,-2)$ and $(-2,2)$.
+$B(r)$)---equals to $(-1,-1)$, $(2,-2)$ and $(0,-1)$.
 %%Two of these branches coincide with the reciprocal and quadratic dependence on $r$ of $A$ and $B$, while the third one gives novel dependence,
@@
 %% \end{equation}
+
+%% \section{extra... DELETE IT}
+
+%% \begin{widetext}
+%%   \begin{dmath*}
+%%     todo2 :=
+%%     %% \Lambda {\epsilon}_{\alpha \beta \gamma \delta} (B_1 + \frac{1}{3}\, B_2) {t_{\perp}}_{\eta}\,^{\alpha \beta} {t_{\perp}}^{\eta \gamma \delta} + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}_{\eta}{{ta}^{\alpha \beta}}\,  (4\, B_1 + \frac{4}{3}\, B_2) {t_{\perp}}^{\eta \gamma \delta} + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{t_{\mathtt{v}}}^{\beta}}\,  (4\, B_1 + \frac{4}{3}\, B_2) {t_{\perp}}^{\eta \gamma \delta} + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\eta}{{ta}^{\gamma \delta}}\,  (4\, B_1 + \frac{4}{3}\, B_2) + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\gamma}{{ts}^{\delta \eta}}\,  (8\, B_1 + \frac{8}{3}\, B_2) + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\gamma \eta}{{t_{\mathtt{v}}}^{\delta}}\,  (8\, B_1 + \frac{8}{3}\, B_2) + \Lambda {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{t_{\mathtt{v}}}^{\beta}}\,  {\nabla}^{\gamma \eta}{{t_{\mathtt{v}}}^{\delta}}\,  (4\, B_1 + \frac{4}{3}\, B_2)
+%%     + \Lambda ( - B_3 + \frac{2}{3}\, B_4) {at}_{\alpha} {t_{\perp}}_{\beta}\,^{\alpha \beta} + \Lambda {\nabla}^{\alpha}\,_{\beta}{{t_{\mathtt{v}}}^{\beta}}\,  ( - B_3 + \frac{2}{3}\, B_4) {at}_{\alpha} + \Lambda {\nabla}^{\alpha}\,_{\alpha}{{t_{\mathtt{v}}}^{\beta}}\,  (B_3 - \frac{2}{3}\, B_4) {at}_{\beta} + \Lambda {\nabla}_{\alpha}{aL}\,  ( - B_3 + \frac{2}{3}\, B_4) {t_{\perp}}_{\beta}\,^{\alpha \beta} + \Lambda {\nabla}_{\alpha}{aL}\,  {\nabla}^{\alpha}\,_{\beta}{{t_{\mathtt{v}}}^{\beta}}\,  ( - B_3 + \frac{2}{3}\, B_4) + \Lambda {\nabla}_{\alpha}{aL}\,  {\nabla}^{\beta}\,_{\beta}{{t_{\mathtt{v}}}^{\alpha}}\,  (B_3 - \frac{2}{3}\, B_4) + C_1 \Lambda {gt}_{\alpha \beta \gamma} {t_{\perp}}^{\beta \alpha \gamma} + C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {t_{\perp}}^{\beta \alpha \gamma} + 3\, C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta}{{ta}^{\alpha \gamma}}\,  - C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta}{{ts}^{\alpha \gamma}}\,  - C_1 \Lambda {\nabla}^{\alpha}\,_{\alpha}{{ts}^{\beta \gamma}}\,  {gs}_{\beta \gamma} - C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta \gamma}{{t_{\mathtt{v}}}^{\alpha}}\, %
+%%     + C_1 \Lambda {\nabla}_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\alpha \beta}{{t_{\mathtt{v}}}^{\gamma}}\,  + C_1 \Lambda {\nabla}_{\alpha \beta}{{gv}_{\gamma}}\,  {t_{\perp}}^{\alpha \beta \gamma} + 2\, C_1 \Lambda {\nabla}_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}^{\alpha}\,_{\beta}{{gv}_{\gamma}}\,  - C_1 \Lambda {\nabla}_{\alpha \beta}{{gv}_{\gamma}}\,  {\nabla}^{\alpha \gamma}{{t_{\mathtt{v}}}^{\beta}}\,  + C_1 \Lambda {\nabla}_{\alpha \beta}{{gv}_{\gamma}}\,  {\nabla}^{\alpha \beta}{{t_{\mathtt{v}}}^{\gamma}}\,  + 2\, C_1 \Lambda {\nabla}_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}_{\beta \gamma}{{gvp}^{\alpha}}\,  + 2\, C_1 \Lambda {\nabla}_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}^{\alpha}\,_{\beta \gamma}{gL}\,  + 2\, C_1 \Lambda {\nabla}^{\alpha}\,_{\beta}{{t_{\mathtt{v}}}^{\gamma}}\,  {\nabla}_{\alpha}\,^{\beta}\,_{\gamma}{gL}\,  + 3\, C_1 {\nabla}^{\alpha}\,_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta}\,_{\delta}{{ta}^{\gamma \delta}}\,  - C_1 {\nabla}^{\alpha}\,_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ts}^{\beta \gamma}}\,  - C_1 {\nabla}^{\alpha}\,_{\alpha}{{gs}_{\beta \gamma}}\,  {\nabla}^{\beta \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  + 3\, C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\beta}\,_{\delta}{{ta}^{\gamma \delta}}\,  + 3\, C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\gamma}\,_{\delta}{{ta}^{\beta \delta}}\,  - 2\, C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ts}^{\beta \gamma}}\,  - C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\beta \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  - C_1 {\nabla}_{\alpha \beta}{{gp}^{\alpha}\,_{\gamma}}\,  {\nabla}^{\gamma \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\beta}}\,  + {\nabla}^{\alpha}\,_{\beta}{{ta}^{\beta \gamma}}\,  {\nabla}_{\alpha}\,^{\delta}\,_{\delta}{{gv}_{\gamma}}\,  ( - 2\, C_1 + 2\, C_2) + {\nabla}^{\alpha}\,_{\beta}{{ta}^{\beta \gamma}}\,  {\nabla}_{\gamma}\,^{\delta}\,_{\delta}{{gv}_{\alpha}}\,  ( - C_1 - 2\, C_2) + {\nabla}^{\alpha}\,_{\alpha}{{ta}^{\beta \gamma}}\,  {\nabla}_{\beta}\,^{\delta}\,_{\delta}{{gv}_{\gamma}}\,  ( - C_1 + 4\, C_2) - C_1 {\nabla}^{\alpha}\,_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}_{\beta}\,^{\delta}\,_{\delta}{{gv}_{\gamma}}\, %
+%%     + {\nabla}^{\alpha}\,_{\alpha \beta}{{gv}_{\gamma}}\,  {\nabla}^{\beta \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  ( - C_1 + 2\, C_2) + {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\gamma}\,_{\delta}{{ta}^{\alpha \delta}}\,  ( - 2\, C_1 + 2\, C_2) + {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\alpha}\,_{\delta}{{ta}^{\gamma \delta}}\,  ( - C_1 - 2\, C_2) + {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ta}^{\alpha \gamma}}\,  ( - C_1 + 4\, C_2) + C_1 {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ts}^{\alpha \gamma}}\,  + {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\gamma \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\alpha}}\,  (C_1 - 2\, C_2) - 3\, C_1 {\nabla}_{\alpha \beta}{{gp}^{\gamma}\,_{\gamma}}\,  {\nabla}^{\alpha}\,_{\delta}{{ta}^{\beta \delta}}\,  + C_1 {\nabla}_{\alpha \beta}{{gp}^{\gamma}\,_{\gamma}}\,  {\nabla}^{\delta}\,_{\delta}{{ts}^{\alpha \beta}}\,  + C_1 {\nabla}_{\alpha \beta}{{gp}^{\gamma}\,_{\gamma}}\,  {\nabla}^{\alpha \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\beta}}\,  + 3\, C_1 {\nabla}^{\alpha}\,_{\beta}{{ta}^{\beta \gamma}}\,  {\nabla}_{\alpha \gamma}\,^{\delta}{{gv}_{\delta}}\,  + C_1 {\nabla}^{\alpha}\,_{\alpha}{{ts}^{\beta \gamma}}\,  {\nabla}_{\beta \gamma}\,^{\delta}{{gv}_{\delta}}\,  + C_1 {\nabla}^{\alpha}\,_{\beta \gamma}{{gv}_{\alpha}}\,  {\nabla}^{\beta \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  + 2\, C_2 {\nabla}_{\alpha}{{gt}^{\beta}\,_{\beta \gamma}}\,  {\nabla}^{\alpha \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\gamma}}\,  - 2\, C_2 {\nabla}^{\alpha}\,_{\alpha \beta}{{gv}_{\gamma}}\,  {\nabla}^{\gamma \delta}\,_{\delta}{{t_{\mathtt{v}}}^{\beta}}\,
+%%     %% + 4\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\eta}\,_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\lambda}\,_{\lambda}{{ta}^{\gamma \delta}}\,  - 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{ta}^{\beta \eta}}\,  {\nabla}^{\lambda}\,_{\lambda}{{ta}^{\gamma \delta}}\,  + 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\eta}\,_{\eta}{{ta}^{\alpha \beta}}\,  {\nabla}^{\gamma \lambda}\,_{\lambda}{{t_{\mathtt{v}}}^{\delta}}\,  + 4\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{ta}^{\beta \eta}}\,  {\nabla}^{\gamma}\,_{\lambda}{{ta}^{\delta \lambda}}\,  - 8\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha}\,_{\eta}{{ta}^{\beta \eta}}\,  {\nabla}^{\gamma \lambda}\,_{\lambda}{{t_{\mathtt{v}}}^{\delta}}\,  + 4\, E_1 {\epsilon}_{\alpha \beta \gamma \delta} {\nabla}^{\alpha \eta}\,_{\eta}{{t_{\mathtt{v}}}^{\beta}}\,  {\nabla}^{\gamma \lambda}\,_{\lambda}{{t_{\mathtt{v}}}^{\delta}}\, %
+%%     + 3\, E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\gamma}\,_{\gamma}{{ta}^{\alpha \beta}}\,  - 3\, E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\alpha}\,_{\gamma}{{ta}^{\beta \gamma}}\,  + 2\, E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\alpha \gamma}\,_{\gamma}{{t_{\mathtt{v}}}^{\beta}}\,  - E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\beta \gamma}\,_{\gamma}{{t_{\mathtt{v}}}^{\alpha}}\,  - 3\, E_2 {\nabla}_{\alpha \beta}{aL}\,  {\nabla}^{\alpha}\,_{\gamma}{{ta}^{\beta \gamma}}\,  + E_2 {\nabla}_{\alpha \beta}{aL}\,  {\nabla}^{\alpha \gamma}\,_{\gamma}{{t_{\mathtt{v}}}^{\beta}}\,  + E_2 {\nabla}_{\alpha}{{at}_{\beta}}\,  {\nabla}^{\gamma}\,_{\gamma}{{ts}^{\alpha \beta}}\,  + E_2 {\nabla}_{\alpha \beta}{aL}\,  {\nabla}^{\gamma}\,_{\gamma}{{ts}^{\alpha \beta}}\, ;
+%%   \end{dmath*}
+%% \end{widetext}

### 2016-05-12 AffGR-PRD.tex
Sent to PRD

@@
-\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint%,longbibliography
+\documentclass[aps,prd,12pt,twocolumn,superscriptaddress,showpacs,showkeys,reprint,longbibliography
 ]{revtex4-1}
@@
 ]{hyperref}
-\usepackage{etoolbox}
+%\usepackage{etoolbox}
 \usepackage{breqn}
@@
 %\usepackage{feynmf}
-\usepackage{siunitx}
+%\usepackage{siunitx}
 \usepackage{array}
@@
 %\usepackage{tikz}
-\usepackage{braket}
+%\usepackage{braket}
 \usepackage{xparse}
@@
 %% \newcommand{\bra}[1]{\left.\left<#1\right.\right|}
-\renewcommand\bra[1]{\Bra{#1}}
-\renewcommand\ket[1]{\Ket{#1}}
+%% \renewcommand\bra[1]{\Bra{#1}}
+%% \renewcommand\ket[1]{\Ket{#1}}
 \newcommand{\bkt}[3]{\Braket{ {#1} | {#2} | {#3} } }
@@
 \newcommand{\vev}[1]{\ensuremath{\left<#1\right>}}
-\renewcommand{\set}[1]{\ensuremath{\Set{ #1 }}}
+%% \renewcommand{\set}[1]{\ensuremath{\Set{ #1 }}}
 
@@
 %%%%%%%%% BIBLIOGRAPHY %%%%%%%%%
-%% \bibliographystyle{utphys}
-\bibliography{References.bib}
+%% \bibliographystyle{unsrt}
+%% \bibliography{References.bib}
+%merlin.mbs apsrev4-1.bst 2010-07-25 4.21a (PWD, AO, DPC) hacked
+%Control: key (0)
+%Control: author (0) dotless jnrlst
+%Control: editor formatted (1) identically to author
+%Control: production of article title (0) allowed
+%Control: page (1) range
+%Control: year (0) verbatim
+%Control: production of eprint (0) enabled
+\begin{thebibliography}{86}%
+\makeatletter
+\providecommand \@ifxundefined [1]{%
+ \@ifx{#1\undefined}
+}%
+\providecommand \@ifnum [1]{%
+ \ifnum #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \@ifx [1]{%
+ \ifx #1\expandafter \@firstoftwo
+ \else \expandafter \@secondoftwo
+ \fi
+}%
+\providecommand \natexlab [1]{#1}%
+\providecommand \enquote  [1]{``#1''}%
+\providecommand \bibnamefont  [1]{#1}%
+\providecommand \bibfnamefont [1]{#1}%
+\providecommand \citenamefont [1]{#1}%
+\providecommand \href@noop [0]{\@secondoftwo}%
+\providecommand \href [0]{\begingroup \@sanitize@url \@href}%
+\providecommand \@href[1]{\@@startlink{#1}\@@href}%
+\providecommand \@@href[1]{\endgroup#1\@@endlink}%
+\providecommand \@sanitize@url [0]{\catcode `\\12\catcode `\$12\catcode
+  `\&12\catcode `\#12\catcode `\^12\catcode `\_12\catcode `\%12\relax}%
+\providecommand \@@startlink[1]{}%
+\providecommand \@@endlink[0]{}%
+\providecommand \url  [0]{\begingroup\@sanitize@url \@url }%
+\providecommand \@url [1]{\endgroup\@href {#1}{\urlprefix }}%
+\providecommand \urlprefix  [0]{URL }%
+\providecommand \Eprint [0]{\href }%
+\providecommand \doibase [0]{http://dx.doi.org/}%
+\providecommand \selectlanguage [0]{\@gobble}%
+\providecommand \bibinfo  [0]{\@secondoftwo}%
+\providecommand \bibfield  [0]{\@secondoftwo}%
+\providecommand \translation [1]{[#1]}%
+\providecommand \BibitemOpen [0]{}%
+\providecommand \bibitemStop [0]{}%
+\providecommand \bibitemNoStop [0]{.\EOS\space}%
+\providecommand \EOS [0]{\spacefactor3000\relax}%
+\providecommand \BibitemShut  [1]{\csname bibitem#1\endcsname}%
+\let\auto@bib@innerbib\@empty
+%</preamble>
+\bibitem [{\citenamefont {Einstein}(1915)}]{einstein1915feldgleichungen}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Albert}\ \bibnamefont
+  {Einstein}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Die
+  feldgleichungen der gravitation},}\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Sitzungsber. preuss. Akad. Wiss.}\ }\textbf {\bibinfo
+  {volume} {1}},\ \bibinfo {pages} {844--847} (\bibinfo {year}
+  {1915})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Will}(2014)}]{Will:2014kxa}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Clifford~M.}\
+  \bibnamefont {Will}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{The
+  confrontation between Gerenal Relativity and experiment}},}\ }\href {\doibase
+  10.12942/lrr-2014-4} {\bibfield  {journal} {\bibinfo  {journal} {Living Rev.
+  Rel.}\ }\textbf {\bibinfo {volume} {17}},\ \bibinfo {pages} {4} (\bibinfo
+  {year} {2014})},\ \Eprint {http://arxiv.org/abs/1403.7377} {arXiv:1403.7377
+  [gr-qc]} \BibitemShut {NoStop}%
+%%CITATION = ARXIV:1002.4928;%%
+\bibitem [{\citenamefont {Abbott}\ \emph {et~al.}(2016)\citenamefont {Abbott}
+  \emph {et~al.}}]{Abbott:2016blz}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {B.~P.}\ \bibnamefont
+  {Abbott}} \emph {et~al.} (\bibinfo {collaboration} {{Virgo and LIGO
+  scientific}}),\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Observation
+  of gravitational waves from a binary black hole merger}},}\ }\href {\doibase
+  10.1103/PhysRevLett.116.061102} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages}
+  {061102} (\bibinfo {year} {2016})},\ \Eprint
+  {http://arxiv.org/abs/1602.03837} {arXiv:1602.03837 [gr-qc]} \BibitemShut
+  {NoStop}%
+%%CITATION = ARXIV:1602.03837;%%
+\bibitem [{\citenamefont {Cartan}(1922)}]{Cartan1922}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elie}\ \bibnamefont
+  {Cartan}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sur une
+  g\'en\'eralisation de la notion de courbure de riemann et les espaces \`a
+  torsion},}\ }\href {http://gallica.bnf.fr/ark:/12148/bpt6k3127j.image.langFR}
+  {\bibfield  {journal} {\bibinfo  {journal} {C. R. Acad. Sci. Paris}\ }\textbf
+  {\bibinfo {volume} {174}},\ \bibinfo {pages} {593} (\bibinfo {year}
+  {1922})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cartan}(1923)}]{Cartan1923}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elie}\ \bibnamefont
+  {Cartan}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sur les
+  vari{\'e}t{\'e}s {\`a} connexion affine et la th{\'e}orie de la
+  relativit{\'e} g{\'e}n{\'e}ralis{\'e}e (premi{\`e}re partie)},}\ }\href
+  {http://archive.numdam.org/article/ASENS_1923_3_40__325_0.pdf} {\bibfield
+  {journal} {\bibinfo  {journal} {Ann. Ec. Norm. Super.}\ }\textbf {\bibinfo
+  {volume} {40}},\ \bibinfo {pages} {325} (\bibinfo {year} {1923})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Cartan}(1924)}]{Cartan1924}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elie}\ \bibnamefont
+  {Cartan}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sur les
+  vari\'et\'es \`a connexion affine, et la th\'eorie de la relativit\'e
+  g\'en\'eralis\'ee (premi\`ere partie) (suite)},}\ }\href
+  {http://www.numdam.org/numdam-bin/item?id=ASENS_1924_3_41__1_0} {\bibfield
+  {journal} {\bibinfo  {journal} {Ann. Ec. Norm. Super.}\ }\textbf {\bibinfo
+  {volume} {41}},\ \bibinfo {pages} {1} (\bibinfo {year} {1924})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Cartan}(1925)}]{Cartan1925}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Elie}\ \bibnamefont
+  {Cartan}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Sur les
+  vari\'et\'es \`a connexion affine et la th\'eorie de la relativit\'e
+  g\'en\'eralis\'ee, part ii,},}\ }\href
+  {http://www.numdam.org/numdam-bin/item?id=ASENS_1925_3_42__17_0} {\bibfield
+  {journal} {\bibinfo  {journal} {Ann. Ec. Norm. Super.}\ }\textbf {\bibinfo
+  {volume} {42}},\ \bibinfo {pages} {17} (\bibinfo {year} {1925})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {'t~Hooft}(1973)}]{'tHooft:1973us}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gerard}\ \bibnamefont
+  {'t~Hooft}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{An algorithm
+  for the poles at dimension four in the dimensional regularization
+  procedure}},}\ }\href {\doibase 10.1016/0550-3213(73)90263-0} {\bibfield
+  {journal} {\bibinfo  {journal} {Nucl. Phys. B}\ }\textbf {\bibinfo {volume}
+  {62}},\ \bibinfo {pages} {444} (\bibinfo {year} {1973})}\BibitemShut
+  {NoStop}%
+%%CITATION = NUPHA,B62,444;%%
+\bibitem [{\citenamefont {'t~Hooft}\ and\ \citenamefont
+  {Veltman}(1974)}]{'tHooft:1974bx}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Gerard}\ \bibnamefont
+  {'t~Hooft}}\ and\ \bibinfo {author} {\bibfnamefont {M.~J.~G.}\ \bibnamefont
+  {Veltman}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{One loop
+  divergencies in the theory of gravitation}},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Annales Poincare Phys. Theor. A}\ }\textbf
+  {\bibinfo {volume} {20}},\ \bibinfo {pages} {69} (\bibinfo {year}
+  {1974})}\BibitemShut {NoStop}%
+%%CITATION = AHPAA,A20,69;%%
+\bibitem [{\citenamefont {Deser}\ and\ \citenamefont {van
+  Nieuwenhuizen}(1974{\natexlab{a}})}]{Deser:1974cz}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Stanley}\ \bibnamefont
+  {Deser}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {van
+  Nieuwenhuizen}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{One Loop
+  Divergences of Quantized Einstein-Maxwell Fields}},}\ }\href {\doibase
+  10.1103/PhysRevD.10.401} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. D}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {401} (\bibinfo
+  {year} {1974}{\natexlab{a}})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,D10,401;%%
+\bibitem [{\citenamefont {Deser}\ and\ \citenamefont {van
+  Nieuwenhuizen}(1974{\natexlab{b}})}]{Deser:1974cy}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Stanley}\ \bibnamefont
+  {Deser}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {van
+  Nieuwenhuizen}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Nonrenormalizability of the Quantized Dirac-Einstein System}},}\ }\href
+  {\doibase 10.1103/PhysRevD.10.411} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. D}\ }\textbf {\bibinfo {volume} {10}},\ \bibinfo {pages} {411}
+  (\bibinfo {year} {1974}{\natexlab{b}})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,D10,411;%%
+\bibitem [{\citenamefont {Arnowitt}\ \emph {et~al.}(1959)\citenamefont
+  {Arnowitt}, \citenamefont {Deser},\ and\ \citenamefont
+  {Misner}}]{Arnowitt:1959ah}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Richard~L.}\
+  \bibnamefont {Arnowitt}}, \bibinfo {author} {\bibfnamefont {Stanley}\
+  \bibnamefont {Deser}}, \ and\ \bibinfo {author} {\bibfnamefont {Charles~W.}\
+  \bibnamefont {Misner}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Dynamical Structure and Definition of Energy in General Relativity}},}\
+  }\href {\doibase 10.1103/PhysRev.116.1322} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {116}},\ \bibinfo {pages}
+  {1322} (\bibinfo {year} {1959})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,116,1322;%%
+\bibitem [{\citenamefont {Arnowitt}\ \emph {et~al.}(1960)\citenamefont
+  {Arnowitt}, \citenamefont {Deser},\ and\ \citenamefont
+  {Misner}}]{Arnowitt:1960es}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Richard~L.}\
+  \bibnamefont {Arnowitt}}, \bibinfo {author} {\bibfnamefont {Stanley}\
+  \bibnamefont {Deser}}, \ and\ \bibinfo {author} {\bibfnamefont {Charles~W.}\
+  \bibnamefont {Misner}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Canonical variables for general relativity}},}\ }\href {\doibase
+  10.1103/PhysRev.117.1595} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev.}\ }\textbf {\bibinfo {volume} {117}},\ \bibinfo {pages} {1595} (\bibinfo
+  {year} {1960})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,117,1595;%%
+\bibitem [{\citenamefont {Wheeler}(1964)}]{WheelerGeo}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {John~A.}\ \bibnamefont
+  {Wheeler}},\ }\enquote {\bibinfo {title} {{R}elativity, groups and
+  topology},}\ \ (\bibinfo  {publisher} {Gordon and Breach},\ \bibinfo {year}
+  {1964})\ Chap.\ \bibinfo {chapter} {{G}eometrodynamics and the issue of the
+  final state}, p.\ \bibinfo {pages} {317}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {DeWitt}(1967{\natexlab{a}})}]{DeWitt:1967yk}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Bryce~S.}\
+  \bibnamefont {DeWitt}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Quantum Theory of Gravity. 1. The Canonical Theory}},}\ }\href {\doibase
+  10.1103/PhysRev.160.1113} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev.}\ }\textbf {\bibinfo {volume} {160}},\ \bibinfo {pages} {1113} (\bibinfo
+  {year} {1967}{\natexlab{a}})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,160,1113;%%
+\bibitem [{\citenamefont {DeWitt}(1967{\natexlab{b}})}]{DeWitt:1967ub}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Bryce~S.}\
+  \bibnamefont {DeWitt}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Quantum Theory of Gravity. 2. The Manifestly Covariant Theory}},}\ }\href
+  {\doibase 10.1103/PhysRev.162.1195} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {162}},\ \bibinfo {pages}
+  {1195} (\bibinfo {year} {1967}{\natexlab{b}})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,162,1195;%%
+\bibitem [{\citenamefont {DeWitt}(1967{\natexlab{c}})}]{DeWitt:1967uc}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Bryce~S.}\
+  \bibnamefont {DeWitt}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Quantum Theory of Gravity. 3. Applications of the Covariant Theory}},}\
+  }\href {\doibase 10.1103/PhysRev.162.1239} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev.}\ }\textbf {\bibinfo {volume} {162}},\ \bibinfo {pages}
+  {1239} (\bibinfo {year} {1967}{\natexlab{c}})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,162,1239;%%
+\bibitem [{\citenamefont {Gambini}\ and\ \citenamefont
+  {Trias}(1981)}]{Gambini:1980yz}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.}~\bibnamefont
+  {Gambini}}\ and\ \bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Trias}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{On the
+  Geometrical Origin of Gauge Theories}},}\ }\href {\doibase
+  10.1103/PhysRevD.23.553} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. D}\ }\textbf {\bibinfo {volume} {23}},\ \bibinfo {pages} {553} (\bibinfo
+  {year} {1981})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,D23,553;%%
+\bibitem [{\citenamefont {Gambini}\ and\ \citenamefont
+  {Trias}(1986)}]{Gambini:1986ew}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Rodolfo}\ \bibnamefont
+  {Gambini}}\ and\ \bibinfo {author} {\bibfnamefont {Antoni}\ \bibnamefont
+  {Trias}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Gauge Dynamics
+  in the C Representation}},}\ }\href {\doibase 10.1016/0550-3213(86)90221-X}
+  {\bibfield  {journal} {\bibinfo  {journal} {Nucl. Phys. B}\ }\textbf
+  {\bibinfo {volume} {278}},\ \bibinfo {pages} {436} (\bibinfo {year}
+  {1986})}\BibitemShut {NoStop}%
+%%CITATION = NUPHA,B278,436;%%
+\bibitem [{\citenamefont {Ashtekar}(1986)}]{Ashtekar:1986yd}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Ashtekar}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{New Variables
+  for Classical and Quantum Gravity}},}\ }\href {\doibase
+  10.1103/PhysRevLett.57.2244} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {57}},\ \bibinfo {pages}
+  {2244--2247} (\bibinfo {year} {1986})}\BibitemShut {NoStop}%
+%%CITATION = PRLTA,57,2244;%%
+\bibitem [{\citenamefont {Ashtekar}(1987)}]{Ashtekar:1987gu}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.}~\bibnamefont
+  {Ashtekar}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{New
+  Hamiltonian Formulation of General Relativity}},}\ }\href {\doibase
+  10.1103/PhysRevD.36.1587} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. D}\ }\textbf {\bibinfo {volume} {36}},\ \bibinfo {pages} {1587}
+  (\bibinfo {year} {1987})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,D36,1587;%%
+\bibitem [{\citenamefont {Holst}(1996)}]{Holst:1995pc}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Soren}\ \bibnamefont
+  {Holst}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Barbero's
+  Hamiltonian derived from a generalized Hilbert-Palatini action}},}\ }\href
+  {\doibase 10.1103/PhysRevD.53.5966} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. D}\ }\textbf {\bibinfo {volume} {53}},\ \bibinfo
+  {pages} {5966} (\bibinfo {year} {1996})},\ \Eprint
+  {http://arxiv.org/abs/gr-qc/9511026} {arXiv:gr-qc/9511026 [gr-qc]}
+  \BibitemShut {NoStop}%
+%%CITATION = GR-QC/9511026;%%
+\bibitem [{\citenamefont {Kibble}(1961)}]{Kibble:1961ba}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {T.~W.~B.}\
+  \bibnamefont {Kibble}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Lorentz invariance and the gravitational field}},}\ }\href {\doibase
+  10.1063/1.1703702} {\bibfield  {journal} {\bibinfo  {journal} {J. Math.
+  Phys.}\ }\textbf {\bibinfo {volume} {2}},\ \bibinfo {pages} {212--221}
+  (\bibinfo {year} {1961})}\BibitemShut {NoStop}%
+%%CITATION = JMAPA,2,212;%%
+\bibitem [{\citenamefont {Hehl}\ \emph {et~al.}(1976)\citenamefont {Hehl},
+  \citenamefont {von~der Heyde}, \citenamefont {Kerlick},\ and\ \citenamefont
+  {Nester}}]{Hehl:1976kj}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Friedrich~W.}\
+  \bibnamefont {Hehl}}, \bibinfo {author} {\bibfnamefont {Paul}\ \bibnamefont
+  {von~der Heyde}}, \bibinfo {author} {\bibfnamefont {G.~David}\ \bibnamefont
+  {Kerlick}}, \ and\ \bibinfo {author} {\bibfnamefont {James~M.}\ \bibnamefont
+  {Nester}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {General
+  relativity with spin and torsion: Foundations and prospects},}\ }\href
+  {\doibase 10.1103/RevModPhys.48.393} {\bibfield  {journal} {\bibinfo
+  {journal} {Rev. Mod. Phys.}\ }\textbf {\bibinfo {volume} {48}},\ \bibinfo
+  {pages} {393} (\bibinfo {year} {1976})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Shapiro}(2002)}]{Shapiro:2001rz}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {I.~L.}\ \bibnamefont
+  {Shapiro}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Physical
+  aspects of the space-time torsion}},}\ }\href {\doibase
+  10.1016/S0370-1573(01)00030-8} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rep.}\ }\textbf {\bibinfo {volume} {357}},\ \bibinfo {pages} {113}
+  (\bibinfo {year} {2002})},\ \Eprint {http://arxiv.org/abs/hep-th/0103093}
+  {arXiv:hep-th/0103093 [hep-th]} \BibitemShut {NoStop}%
+%%CITATION = HEP-TH/0103093;%%
+\bibitem [{\citenamefont {Hammond}(2002)}]{Hammond:2002rm}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {R.~T.}\ \bibnamefont
+  {Hammond}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Torsion
+  gravity}},}\ }\href {\doibase 10.1088/0034-4885/65/5/201} {\bibfield
+  {journal} {\bibinfo  {journal} {Rept. Prog. Phys.}\ }\textbf {\bibinfo
+  {volume} {65}},\ \bibinfo {pages} {599} (\bibinfo {year} {2002})}\BibitemShut
+  {NoStop}%
+%%CITATION = RPPHA,65,599;%%
+\bibitem [{\citenamefont {Hehl}\ \emph {et~al.}(1995)\citenamefont {Hehl},
+  \citenamefont {McCrea}, \citenamefont {Mielke},\ and\ \citenamefont
+  {Ne'eman}}]{Hehl:1994ue}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Friedrich~W.}\
+  \bibnamefont {Hehl}}, \bibinfo {author} {\bibfnamefont {J.~Dermott}\
+  \bibnamefont {McCrea}}, \bibinfo {author} {\bibfnamefont {Eckehard~W.}\
+  \bibnamefont {Mielke}}, \ and\ \bibinfo {author} {\bibfnamefont {Yuval}\
+  \bibnamefont {Ne'eman}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Metric affine gauge theory of gravity: Field equations, Noether identities,
+  world spinors, and breaking of dilation invariance}},}\ }\href {\doibase
+  10.1016/0370-1573(94)00111-F} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Rep.}\ }\textbf {\bibinfo {volume} {258}},\ \bibinfo {pages} {1--171}
+  (\bibinfo {year} {1995})},\ \Eprint {http://arxiv.org/abs/gr-qc/9402012}
+  {arXiv:gr-qc/9402012 [gr-qc]} \BibitemShut {NoStop}%
+%%CITATION = GR-QC/9402012;%%
+\bibitem [{\citenamefont {Pagani}\ and\ \citenamefont
+  {Percacci}(2015)}]{Pagani:2015ema}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Carlo}\ \bibnamefont
+  {Pagani}}\ and\ \bibinfo {author} {\bibfnamefont {Roberto}\ \bibnamefont
+  {Percacci}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Quantum
+  gravity with torsion and non-metricity}},}\ }\href {\doibase
+  10.1088/0264-9381/32/19/195019} {\bibfield  {journal} {\bibinfo  {journal}
+  {Class. Quant. Grav.}\ }\textbf {\bibinfo {volume} {32}},\ \bibinfo {pages}
+  {195019} (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1506.02882} {arXiv:1506.02882 [gr-qc]} \BibitemShut
+  {NoStop}%
+%%CITATION = ARXIV:1506.02882;%%
+\bibitem [{\citenamefont {Sezgin}\ and\ \citenamefont {van
+  Nieuwenhuizen}(1980)}]{Sezgin:1979zf}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {E.}~\bibnamefont
+  {Sezgin}}\ and\ \bibinfo {author} {\bibfnamefont {P.}~\bibnamefont {van
+  Nieuwenhuizen}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{New Ghost
+  Free Gravity Lagrangians with Propagating Torsion}},}\ }\href {\doibase
+  10.1103/PhysRevD.21.3269} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. D}\ }\textbf {\bibinfo {volume} {21}},\ \bibinfo {pages} {3269}
+  (\bibinfo {year} {1980})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,D21,3269;%%
+\bibitem [{\citenamefont {Mannheim}\ and\ \citenamefont
+  {Davidson}(2005)}]{Mannheim:2004qz}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Philip~D.}\
+  \bibnamefont {Mannheim}}\ and\ \bibinfo {author} {\bibfnamefont {Aharon}\
+  \bibnamefont {Davidson}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Dirac quantization of the Pais-Uhlenbeck fourth order oscillator}},}\
+  }\href {\doibase 10.1103/PhysRevA.71.042110} {\bibfield  {journal} {\bibinfo
+  {journal} {Phys. Rev. A}\ }\textbf {\bibinfo {volume} {71}},\ \bibinfo
+  {pages} {042110} (\bibinfo {year} {2005})},\ \Eprint
+  {http://arxiv.org/abs/hep-th/0408104} {arXiv:hep-th/0408104 [hep-th]}
+  \BibitemShut {NoStop}%
+%%CITATION = HEP-TH/0408104;%%
+\bibitem [{\citenamefont {Bender}\ and\ \citenamefont
+  {Mannheim}(2008{\natexlab{a}})}]{Bender:2007wu}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Carl~M.}\ \bibnamefont
+  {Bender}}\ and\ \bibinfo {author} {\bibfnamefont {Philip~D.}\ \bibnamefont
+  {Mannheim}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{No-ghost
+  theorem for the fourth-order derivative Pais-Uhlenbeck oscillator model}},}\
+  }\href {\doibase 10.1103/PhysRevLett.100.110402} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo {volume} {100}},\
+  \bibinfo {pages} {110402} (\bibinfo {year} {2008}{\natexlab{a}})},\ \Eprint
+  {http://arxiv.org/abs/0706.0207} {arXiv:0706.0207 [hep-th]} \BibitemShut
+  {NoStop}%
+%%CITATION = ARXIV:0706.0207;%%
+\bibitem [{\citenamefont {Smilga}(2009)}]{Smilga:2008pr}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
+  {Smilga}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Comments on the
+  dynamics of the Pais-Uhlenbeck oscillator}},}\ }\bibfield  {booktitle} {\emph
+  {\bibinfo {booktitle} {{Proceedings, 7th Workshop on Quantum Physics with
+  Non-Hermitian Operators (PHHQP VII)}}},\ }\href {\doibase
+  10.3842/Sigma.2009.017} {\bibfield  {journal} {\bibinfo  {journal} {SIGMA}\
+  }\textbf {\bibinfo {volume} {5}},\ \bibinfo {pages} {017} (\bibinfo {year}
+  {2009})},\ \Eprint {http://arxiv.org/abs/0808.0139} {arXiv:0808.0139
+  [quant-ph]} \BibitemShut {NoStop}%
+%%CITATION = ARXIV:0808.0139;%%
+\bibitem [{\citenamefont {Ilhan}\ and\ \citenamefont
+  {Kovner}(2013)}]{Ilhan:2013xe}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Ibrahim~Burak}\
+  \bibnamefont {Ilhan}}\ and\ \bibinfo {author} {\bibfnamefont {Alex}\
+  \bibnamefont {Kovner}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Some Comments on Ghosts and Unitarity: The Pais-Uhlenbeck Oscillator
+  Revisited}},}\ }\href {\doibase 10.1103/PhysRevD.88.044045} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. D}\ }\textbf {\bibinfo {volume}
+  {88}},\ \bibinfo {pages} {044045} (\bibinfo {year} {2013})},\ \Eprint
+  {http://arxiv.org/abs/1301.4879} {arXiv:1301.4879 [hep-th]} \BibitemShut
+  {NoStop}%
+%%CITATION = ARXIV:1301.4879;%%
+\bibitem [{\citenamefont {Robert}\ and\ \citenamefont
+  {Smilga}(2008)}]{Robert:2008}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Robert}}\ and\ \bibinfo {author} {\bibfnamefont {A.~V.}\ \bibnamefont
+  {Smilga}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Supersymmetry
+  versus ghosts}},}\ }\href {\doibase 10.1063/1.2904474} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Math. Phys.}\ }\textbf {\bibinfo {volume} {49}},\
+  \bibinfo {eid} {042104} (\bibinfo {year} {2008}),\
+  10.1063/1.2904474}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Castillo-Felisola}\ and\ \citenamefont
+  {Skirzewski}(2015)}]{Skirzewski:2014eta}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Oscar}\ \bibnamefont
+  {Castillo-Felisola}}\ and\ \bibinfo {author} {\bibfnamefont {Aureliano}\
+  \bibnamefont {Skirzewski}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{A polynomial model of purely affine Gravity}},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Rev. Mex. Fis.}\ }\textbf {\bibinfo {volume}
+  {61}},\ \bibinfo {pages} {421} (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1410.6183} {arXiv:1410.6183 [gr-qc]} \BibitemShut
+  {NoStop}%
+%%CITATION = ARXIV:1410.6183;%%
+\bibitem [{\citenamefont {Eddington}(1923)}]{Eddington1923math}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Arthur~S.}\
+  \bibnamefont {Eddington}},\ }\href@noop {} {\emph {\bibinfo {title} {The
+  mathematical theory of relativity}}}\ (\bibinfo  {publisher} {Cambridge
+  University Press},\ \bibinfo {year} {1923})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Schr{\"o}dinger}(1950)}]{schrodinger1950space}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Erwin}\ \bibnamefont
+  {Schr{\"o}dinger}},\ }\href@noop {} {\emph {\bibinfo {title} {Space-time
+  structure}}}\ (\bibinfo  {publisher} {Cambridge University Press},\ \bibinfo
+  {year} {1950})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Lewandowski}\ \emph {et~al.}(2006)\citenamefont
+  {Lewandowski}, \citenamefont {Okolow}, \citenamefont {Sahlmann},\ and\
+  \citenamefont {Thiemann}}]{Lewandowski:2005jk}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jerzy}\ \bibnamefont
+  {Lewandowski}}, \bibinfo {author} {\bibfnamefont {Andrzej}\ \bibnamefont
+  {Okolow}}, \bibinfo {author} {\bibfnamefont {Hanno}\ \bibnamefont
+  {Sahlmann}}, \ and\ \bibinfo {author} {\bibfnamefont {Thomas}\ \bibnamefont
+  {Thiemann}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Uniqueness of
+  diffeomorphism invariant states on holonomy-flux algebras}},}\ }\href
+  {\doibase 10.1007/s00220-006-0100-7} {\bibfield  {journal} {\bibinfo
+  {journal} {Commun. Math. Phys.}\ }\textbf {\bibinfo {volume} {267}},\
+  \bibinfo {pages} {703} (\bibinfo {year} {2006})},\ \Eprint
+  {http://arxiv.org/abs/gr-qc/0504147} {arXiv:gr-qc/0504147 [gr-qc]}
+  \BibitemShut {NoStop}%
+%%CITATION = GR-QC/0504147;%%
+\bibitem [{\citenamefont {McGady}\ and\ \citenamefont
+  {Rodina}(2014)}]{McGady:2013sga}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {David~A.}\
+  \bibnamefont {McGady}}\ and\ \bibinfo {author} {\bibfnamefont {Laurentiu}\
+  \bibnamefont {Rodina}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Higher-spin massless $S$-matrices in four-dimensions}},}\ }\href {\doibase
+  10.1103/PhysRevD.90.084048} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. D}\ }\textbf {\bibinfo {volume} {90}},\ \bibinfo {pages} {084048}
+  (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1311.2938}
+  {arXiv:1311.2938 [hep-th]} \BibitemShut {NoStop}%
+%%CITATION = ARXIV:1311.2938;%%
+\bibitem [{\citenamefont {Camanho}\ \emph {et~al.}(2014)\citenamefont
+  {Camanho}, \citenamefont {Edelstein}, \citenamefont {Maldacena},\ and\
+  \citenamefont {Zhiboedov}}]{Camanho:2014apa}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Xian~O.}\ \bibnamefont
+  {Camanho}}, \bibinfo {author} {\bibfnamefont {Jose~D.}\ \bibnamefont
+  {Edelstein}}, \bibinfo {author} {\bibfnamefont {Juan}\ \bibnamefont
+  {Maldacena}}, \ and\ \bibinfo {author} {\bibfnamefont {Alexander}\
+  \bibnamefont {Zhiboedov}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Causality Constraints on Corrections to the Graviton Three-Point
+  Coupling}},}\ }\href@noop {} {\  (\bibinfo {year} {2014})},\ \Eprint
+  {http://arxiv.org/abs/1407.5597} {arXiv:1407.5597 [hep-th]} \BibitemShut
+  {NoStop}%
+%%CITATION = ARXIV:1407.5597;%%
+\bibitem [{\citenamefont {Diaz}\ \emph {et~al.}(2014)\citenamefont {Diaz},
+  \citenamefont {Higuita},\ and\ \citenamefont {Montesinos}}]{Diaz:2014yua}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Bogar}\ \bibnamefont
+  {Diaz}}, \bibinfo {author} {\bibfnamefont {Daniel}\ \bibnamefont {Higuita}},
+  \ and\ \bibinfo {author} {\bibfnamefont {Merced}\ \bibnamefont
+  {Montesinos}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Lagrangian
+  approach to the physical degree of freedom count}},}\ }\href {\doibase
+  10.1063/1.4903183} {\bibfield  {journal} {\bibinfo  {journal} {J. Math.
+  Phys.}\ }\textbf {\bibinfo {volume} {55}},\ \bibinfo {pages} {122901}
+  (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1406.1156}
+  {arXiv:1406.1156 [hep-th]} \BibitemShut {NoStop}%
+%%CITATION = ARXIV:1406.1156;%%
+\bibitem [{\citenamefont {Curtright}(1985)}]{Curtright:1980yk}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Thomas}\ \bibnamefont
+  {Curtright}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Generalized
+  Gauge Fields}},}\ }\href {\doibase 10.1016/0370-2693(85)91235-3} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Lett. B}\ }\textbf {\bibinfo {volume}
+  {165}},\ \bibinfo {pages} {304} (\bibinfo {year} {1985})}\BibitemShut
+  {NoStop}%
+%%CITATION = PHLTA,B165,304;%%
+\bibitem [{\citenamefont {Buchholz}\ and\ \citenamefont
+  {Fredenhagen}(1977)}]{Buchholz:1976hz}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {D.}~\bibnamefont
+  {Buchholz}}\ and\ \bibinfo {author} {\bibfnamefont {K.}~\bibnamefont
+  {Fredenhagen}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Dilations
+  and Interaction}},}\ }\href {\doibase 10.1063/1.523370} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Math. Phys.}\ }\textbf {\bibinfo {volume} {18}},\
+  \bibinfo {pages} {1107} (\bibinfo {year} {1977})}\BibitemShut {NoStop}%
+%%CITATION = JMAPA,18,1107;%%
+\bibitem [{\citenamefont {Castillo-Felisola}\ and\ \citenamefont
+  {Skirzewski}()}]{OCF-future3}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Oscar}\ \bibnamefont
+  {Castillo-Felisola}}\ and\ \bibinfo {author} {\bibfnamefont {Aureliano}\
+  \bibnamefont {Skirzewski}},\ }\href@noop {} {\enquote {\bibinfo {title}
+  {{M}etric, torsion, non-metricity and background independence in polynomial
+  affine gravity},}\ }\bibinfo {note} {(in preparation)}\BibitemShut {NoStop}%
+\bibitem [{Note1()}]{Note1}%
+  \BibitemOpen
+  \bibinfo {note} {Despite the suggestive name, this is a $\protect \genfrac
+  {}(){0pt}{2}{0}$-tensor density which does not necessarily satisfy the metric
+  conditions. However, for the simple case of the Einstein--Hilbert action, it
+  is in fact the inverse metric density.}\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Pop{\l}awski}(2014)}]{Poplawski:2012bw}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Nikodem~J.}\
+  \bibnamefont {Pop{\l}awski}},\ }\bibfield  {title} {\enquote {\bibinfo
+  {title} {{Affine theory of gravitation}},}\ }\href {\doibase
+  10.1007/s10714-013-1625-7} {\bibfield  {journal} {\bibinfo  {journal} {Gen.
+  Rel. Grav.}\ }\textbf {\bibinfo {volume} {46}},\ \bibinfo {pages} {1625}
+  (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1203.0294}
+  {arXiv:1203.0294 [gr-qc]} \BibitemShut {NoStop}%
+%%CITATION = ARXIV:1203.0294;%%
+\bibitem [{Note2()}]{Note2}%
+  \BibitemOpen
+  \bibinfo {note} {We cross-check our result using the software Cadabra~\cite
+  {Peeters2007550,peeters2007symbolic,Peeters:2007wn}.}\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Nomizu}\ and\ \citenamefont
+  {Sasaki}(1994)}]{nomizu1994affine}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Katsumi}\ \bibnamefont
+  {Nomizu}}\ and\ \bibinfo {author} {\bibfnamefont {Takeshi}\ \bibnamefont
+  {Sasaki}},\ }\href@noop {} {\emph {\bibinfo {title} {Affine differential
+  geometry}}}\ (\bibinfo  {publisher} {Cambridge University Press},\ \bibinfo
+  {year} {1994})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bryant}()}]{MO-Bryant02}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Robert~L.}\
+  \bibnamefont {Bryant}},\ }\href@noop {} {\enquote {\bibinfo {title}
+  {{S}ymmetries of non-{R}iemannian curvature tensor (answer)},}\ }\bibinfo
+  {howpublished} {{MathOverflow}},\ \bibinfo {note}
+  {{URL}:~\url{http://mathoverflow.net/a/212794/25356} (visited on
+  2015-08-03)}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Besse}(2007)}]{Besse}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Arthur~L.}\
+  \bibnamefont {Besse}},\ }\href@noop {} {\emph {\bibinfo {title} {Einstein
+  manifolds}}}\ (\bibinfo  {publisher} {Springer},\ \bibinfo {year}
+  {2007})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bourguignon}(1981)}]{bourguignon1981varietes}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jean-Pierre}\
+  \bibnamefont {Bourguignon}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Les vari{\'e}t{\'e}s de dimension 4 {\`a} signature non nulle dont la
+  courbure est harmonique sont d'einstein},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Inventiones mathematicae}\ }\textbf {\bibinfo
+  {volume} {63}},\ \bibinfo {pages} {263} (\bibinfo {year} {1981})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Berger}\ and\ \citenamefont
+  {Ebin}(1969)}]{Berger:1969}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {M.}~\bibnamefont
+  {Berger}}\ and\ \bibinfo {author} {\bibfnamefont {D.}~\bibnamefont {Ebin}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {{S}ome decomposition of the
+  space of symmetric tensors on riemannian manifold},}\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {J. Diff. Geom.}\ }\textbf
+  {\bibinfo {volume} {3}} (\bibinfo {year} {1969})}\BibitemShut {NoStop}%
+\bibitem [{Note3()}]{Note3}%
+  \BibitemOpen
+  \bibinfo {note} {A Codazzi tensor is a symmetric $(0,2)$-type tensor, $T$,
+  satisfying the condition \unhbox \voidb@x \hbox {$D_X T(Y,Z) = D_Y
+  T(X,Z)$~\cite {Derdzinski01071983}.}}\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Derdzi\'nski}(1985)}]{Derdzinski:1985}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrzej}\ \bibnamefont
+  {Derdzi\'nski}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Riemannian
+  manifolds with harmonic curvature},}\ }in\ \href {\doibase
+  10.1007/BFb0075087} {\emph {\bibinfo {booktitle} {Global Differential
+  Geometry and Global Analysis 1984}}},\ \bibinfo {series} {Lecture Notes in
+  Mathematics}, Vol.\ \bibinfo {volume} {1156},\ \bibinfo {editor} {edited by\
+  \bibinfo {editor} {\bibfnamefont {Dirk}\ \bibnamefont {Ferus}}, \bibinfo
+  {editor} {\bibfnamefont {Robert~B.}\ \bibnamefont {Gardner}}, \bibinfo
+  {editor} {\bibfnamefont {Sigurdur}\ \bibnamefont {Helgason}}, \ and\ \bibinfo
+  {editor} {\bibfnamefont {Udo}\ \bibnamefont {Simon}}}\ (\bibinfo  {publisher}
+  {Springer Berlin Heidelberg},\ \bibinfo {year} {1985})\ p.~\bibinfo {pages}
+  {74}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Bourguignon}\ and\ \citenamefont
+  {Lawson~Jr}(1982)}]{bourguignon1982yang}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jean-Pierre}\
+  \bibnamefont {Bourguignon}}\ and\ \bibinfo {author} {\bibfnamefont
+  {H.~Blaine}\ \bibnamefont {Lawson~Jr}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {Yang-mills theory: its physical origins and differential
+  geometric aspects},}\ }in\ \href@noop {} {\emph {\bibinfo {booktitle}
+  {Seminar on differential Geometry}}},\ Vol.\ \bibinfo {volume} {102}\
+  (\bibinfo {organization} {Annals of Mathematics Studies},\ \bibinfo {year}
+  {1982})\ p.\ \bibinfo {pages} {395}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Nakahara}(2005)}]{Nakahara}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Mikio}\ \bibnamefont
+  {Nakahara}},\ }\href@noop {} {\emph {\bibinfo {title} {Geometry, Topology and
+  Physics}}}\ (\bibinfo  {publisher} {Institute Of Physics},\ \bibinfo {year}
+  {2005})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Stephenson}(1958)}]{stephenson1958quadratic}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {G.}~\bibnamefont
+  {Stephenson}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Quadratic
+  lagrangians and general relativity},}\ }\href {\doibase 10.1007/BF02724929}
+  {\bibfield  {journal} {\bibinfo  {journal} {Il Nuovo Cimento Series 10}\
+  }\textbf {\bibinfo {volume} {9}},\ \bibinfo {pages} {263--269} (\bibinfo
+  {year} {1958})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Kilmister}\ and\ \citenamefont
+  {Newman}(1961)}]{kilmister1961use}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~W.}\ \bibnamefont
+  {Kilmister}}\ and\ \bibinfo {author} {\bibfnamefont {D.~J.}\ \bibnamefont
+  {Newman}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {The use of
+  algebraic structures in physics},}\ }in\ \href {\doibase
+  10.1017/S0305004100036008} {\emph {\bibinfo {booktitle} {Mathematical
+  Proceedings of the Cambridge Philosophical Society}}},\ Vol.~\bibinfo
+  {volume} {57}\ (\bibinfo  {publisher} {Cambridge University Press},\ \bibinfo
+  {year} {1961})\ p.\ \bibinfo {pages} {851}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Yang}(1974)}]{Yang1974}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {C.~N.}\ \bibnamefont
+  {Yang}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Integral formalism
+  for gauge fields},}\ }\href {\doibase 10.1103/PhysRevLett.33.445} {\bibfield
+  {journal} {\bibinfo  {journal} {Phys. Rev. Lett.}\ }\textbf {\bibinfo
+  {volume} {33}},\ \bibinfo {pages} {445} (\bibinfo {year} {1974})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Zanelli}()}]{JZcomm}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jorge}\ \bibnamefont
+  {Zanelli}},\ }\href@noop {} {\enquote {\bibinfo {title} {Private
+  communication},}\ }\bibinfo {note} {We thank J.~Zanelli for sharing his
+  personal communications with C.~N.~Yang, and clarify this aspect of the
+  effective model.}\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Chen}(2010)}]{Chen:2010at}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Pisin}\ \bibnamefont
+  {Chen}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Gauge Theory of
+  Gravity with de Sitter Symmetry as a Solution to the Cosmological Constant
+  Problem and the Dark Energy Puzzle}},}\ }\href {\doibase
+  10.1142/9789814335614_0029, 10.1142/S0217732310034274} {\bibfield  {journal}
+  {\bibinfo  {journal} {Mod. Phys. Lett. A}\ }\textbf {\bibinfo {volume}
+  {25}},\ \bibinfo {pages} {2795} (\bibinfo {year} {2010})},\ \Eprint
+  {http://arxiv.org/abs/1002.4275} {arXiv:1002.4275 [gr-qc]} \BibitemShut
+  {NoStop}%
+%%CITATION = ARXIV:1002.4275;%%
+\bibitem [{\citenamefont {Kleinert}(1987)}]{Kleinert:1987eb}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {H.}~\bibnamefont
+  {Kleinert}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Spontaneous
+  quantum gravity: a soluble model}},}\ }\href {\doibase
+  10.1016/0370-2693(87)90747-7} {\bibfield  {journal} {\bibinfo  {journal}
+  {Phys. Lett. B}\ }\textbf {\bibinfo {volume} {196}},\ \bibinfo {pages} {355}
+  (\bibinfo {year} {1987})}\BibitemShut {NoStop}%
+%%CITATION = PHLTA,B196,355;%%
+\bibitem [{\citenamefont {Bender}\ and\ \citenamefont
+  {Mannheim}(2008{\natexlab{b}})}]{Bender:2008vh}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Carl~M.}\ \bibnamefont
+  {Bender}}\ and\ \bibinfo {author} {\bibfnamefont {Philip~D.}\ \bibnamefont
+  {Mannheim}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Giving up the
+  ghost}},}\ }\href {\doibase 10.1088/1751-8113/41/30/304018} {\bibfield
+  {journal} {\bibinfo  {journal} {J. Phys. A}\ }\textbf {\bibinfo {volume}
+  {41}},\ \bibinfo {pages} {304018} (\bibinfo {year} {2008}{\natexlab{b}})},\
+  \Eprint {http://arxiv.org/abs/0807.2607} {arXiv:0807.2607 [hep-th]}
+  \BibitemShut {NoStop}%
+%%CITATION = ARXIV:0807.2607;%%
+\bibitem [{\citenamefont {Mannheim}(2013)}]{Mannheim:2009zj}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Philip~D.}\
+  \bibnamefont {Mannheim}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{PT symmetry as a necessary and sufficient condition for unitary time
+  evolution}},}\ }\href {\doibase 10.1098/rsta.2012.0060} {\bibfield  {journal}
+  {\bibinfo  {journal} {Phil. Trans. Roy. Soc. Lond. A}\ }\textbf {\bibinfo
+  {volume} {371}},\ \bibinfo {pages} {20120060} (\bibinfo {year} {2013})},\
+  \Eprint {http://arxiv.org/abs/0912.2635} {arXiv:0912.2635 [hep-th]}
+  \BibitemShut {NoStop}%
+%%CITATION = ARXIV:0912.2635;%%
+\bibitem [{\citenamefont {Bekenstein}\ and\ \citenamefont
+  {Majhi}(2015)}]{Bekenstein:2014uwa}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Jacob~D.}\
+  \bibnamefont {Bekenstein}}\ and\ \bibinfo {author} {\bibfnamefont
+  {Bibhas~Ranjan}\ \bibnamefont {Majhi}},\ }\bibfield  {title} {\enquote
+  {\bibinfo {title} {{Is the principle of least action a must?}}}\ }\href
+  {\doibase 10.1016/j.nuclphysb.2015.01.015} {\bibfield  {journal} {\bibinfo
+  {journal} {Nucl. Phys. B}\ }\textbf {\bibinfo {volume} {892}},\ \bibinfo
+  {pages} {337} (\bibinfo {year} {2015})},\ \Eprint
+  {http://arxiv.org/abs/1411.2424} {arXiv:1411.2424 [hep-th]} \BibitemShut
+  {NoStop}%
+%%CITATION = ARXIV:1411.2424;%%
+\bibitem [{\citenamefont {Weinberg}(1972)}]{weinberg1972gravitation}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Steven}\ \bibnamefont
+  {Weinberg}},\ }\href@noop {} {\emph {\bibinfo {title} {Gravitation and
+  cosmology: principles and applications of the general theory of
+  relativity}}}\ (\bibinfo  {publisher} {Wiley},\ \bibinfo {year}
+  {1972})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Castillo-Felisola}\ \emph {et~al.}()\citenamefont
+  {Castillo-Felisola}, \citenamefont {Orellana},\ and\ \citenamefont
+  {Skirzewski}}]{OCF-future2}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Oscar}\ \bibnamefont
+  {Castillo-Felisola}}, \bibinfo {author} {\bibfnamefont {Oscar}\ \bibnamefont
+  {Orellana}}, \ and\ \bibinfo {author} {\bibfnamefont {Aureliano}\
+  \bibnamefont {Skirzewski}},\ }\href@noop {} {\enquote {\bibinfo {title}
+  {Spherically symmetric solutions to the polynomial affine gravity},}\
+  }\bibinfo {note} {(in preparation)}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Chen}(2014)}]{Chen:2013kia}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Pisin}\ \bibnamefont
+  {Chen}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Recent Progress
+  in Cosmology and Particle Astrophysics}},}\ }\href {\doibase
+  10.7566/JPSCP.1.011002} {\bibfield  {journal} {\bibinfo  {journal} {JPS Conf.
+  Proc.}\ }\textbf {\bibinfo {volume} {1}},\ \bibinfo {pages} {011002}
+  (\bibinfo {year} {2014})},\ \Eprint {http://arxiv.org/abs/1310.1107}
+  {arXiv:1310.1107 [hep-ph]} \BibitemShut {NoStop}%
+%%CITATION = ARXIV:1310.1107;%%
+\bibitem [{\citenamefont {Chen}\ \emph {et~al.}(2013)\citenamefont {Chen},
+  \citenamefont {Izumi},\ and\ \citenamefont {Tung}}]{Chen:2013ota}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Pisin}\ \bibnamefont
+  {Chen}}, \bibinfo {author} {\bibfnamefont {Keisuke}\ \bibnamefont {Izumi}}, \
+  and\ \bibinfo {author} {\bibfnamefont {Nien-En}\ \bibnamefont {Tung}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {{Natural emergence of
+  cosmological constant and dark radiation from the
+  Stephenson-Kilmister-Yang-Camenzind theory of gravity}},}\ }\href {\doibase
+  10.1103/PhysRevD.88.123006} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. D}\ }\textbf {\bibinfo {volume} {88}},\ \bibinfo {pages} {123006}
+  (\bibinfo {year} {2013})},\ \Eprint {http://arxiv.org/abs/1304.6334}
+  {arXiv:1304.6334 [gr-qc]} \BibitemShut {NoStop}%
+%%CITATION = ARXIV:1304.6334;%%
+\bibitem [{Note4()}]{Note4}%
+  \BibitemOpen
+  \bibinfo {note} {We want to thank to M.~Blagojevi\'c, B.~Cvetkovi\'c and
+  O.~Mi\v {s}kovi\'c for clarifications in this respect.}\BibitemShut {Stop}%
+\bibitem [{\citenamefont {Gray}(1978)}]{gray1978einstein}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Alfred}\ \bibnamefont
+  {Gray}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Einstein-like
+  manifolds which are not einstein},}\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {Geometriae dedicata}\ }\textbf {\bibinfo {volume}
+  {7}},\ \bibinfo {pages} {259} (\bibinfo {year} {1978})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont
+  {Derdzi{\'n}ski}(1980)}]{derdzinski1980classification}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrzej}\ \bibnamefont
+  {Derdzi{\'n}ski}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {{Classification of certain compact Riemannian manifolds with harmonic
+  curvature and non-parallel Ricci tensor}},}\ }\href@noop {} {\bibfield
+  {journal} {\bibinfo  {journal} {Mathematische Zeitschrift}\ }\textbf
+  {\bibinfo {volume} {172}},\ \bibinfo {pages} {273} (\bibinfo {year}
+  {1980})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Derdzi{\'n}ski}(1982)}]{derdzinski1982compact}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrzej}\ \bibnamefont
+  {Derdzi{\'n}ski}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {On
+  compact riemannian manifolds with harmonic curvature},}\ }\href@noop {}
+  {\bibfield  {journal} {\bibinfo  {journal} {Mathematische Annalen}\ }\textbf
+  {\bibinfo {volume} {259}},\ \bibinfo {pages} {145} (\bibinfo {year}
+  {1982})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Derdzi{\'n}ski}(1988)}]{derdzinski1988riemannian}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrzej}\ \bibnamefont
+  {Derdzi{\'n}ski}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Riemannian metrics with harmonic curvature on 2-sphere bundles over compact
+  surfaces},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Bulletin de la Soci{\'e}t{\'e} Math{\'e}matique de France}\ }\textbf
+  {\bibinfo {volume} {116}},\ \bibinfo {pages} {133--156} (\bibinfo {year}
+  {1988})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Cahen}\ \emph {et~al.}(2000)\citenamefont {Cahen},
+  \citenamefont {Gutt},\ and\ \citenamefont {Rawnsley}}]{cahen2000symplectic}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Michel}\ \bibnamefont
+  {Cahen}}, \bibinfo {author} {\bibfnamefont {Simone}\ \bibnamefont {Gutt}}, \
+  and\ \bibinfo {author} {\bibfnamefont {John}\ \bibnamefont {Rawnsley}},\
+  }\bibfield  {title} {\enquote {\bibinfo {title} {Symplectic connections with
+  parallel ricci tensor},}\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Banach Center Publications}\ }\textbf {\bibinfo {volume} {51}},\
+  \bibinfo {pages} {31} (\bibinfo {year} {2000})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Jebsen}(1921)}]{Jebsen1921}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J{\o}rg~Tofte}\
+  \bibnamefont {Jebsen}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo
+  {journal} {Ark. Mat. Ast. Fys.}\ }\textbf {\bibinfo {volume} {15}} (\bibinfo
+  {year} {1921})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Birkhoff}(1923)}]{Birkhoff1923}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Garrett~D.}\
+  \bibnamefont {Birkhoff}},\ }\href@noop {} {\emph {\bibinfo {title}
+  {Relativity and Modern Physics}}}\ (\bibinfo  {publisher} {Harvard University
+  Press},\ \bibinfo {year} {1923})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Alexandrow}(1923)}]{Alexandrow1923}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {W.}~\bibnamefont
+  {Alexandrow}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Ann. der Phys.}\ }\textbf {\bibinfo {volume} {72}},\ \bibinfo {pages} {141}
+  (\bibinfo {year} {1923})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Eisland}(1925)}]{Eisland1925}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {J.}~\bibnamefont
+  {Eisland}},\ }\href@noop {} {\bibfield  {journal} {\bibinfo  {journal}
+  {Trans. Amer. Math. Soc.}\ }\textbf {\bibinfo {volume} {23}},\ \bibinfo
+  {pages} {213} (\bibinfo {year} {1925})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Ramaswamy}\ and\ \citenamefont
+  {Yasskin}(1979)}]{Ramaswamy:1979zz}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Sriram}\ \bibnamefont
+  {Ramaswamy}}\ and\ \bibinfo {author} {\bibfnamefont {Philip~B.}\ \bibnamefont
+  {Yasskin}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Birkhoff
+  theorem for an $R+R^2$ theory of gravity with torsion}},}\ }\href {\doibase
+  10.1103/PhysRevD.19.2264} {\bibfield  {journal} {\bibinfo  {journal} {Phys.
+  Rev. D}\ }\textbf {\bibinfo {volume} {19}},\ \bibinfo {pages} {2264}
+  (\bibinfo {year} {1979})}\BibitemShut {NoStop}%
+%%CITATION = PHRVA,D19,2264;%%
+\bibitem [{\citenamefont {Bergmann}\ \emph {et~al.}(1965)\citenamefont
+  {Bergmann}, \citenamefont {Cahen},\ and\ \citenamefont
+  {Komar}}]{bergmann1965spherically}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {P.~G.}\ \bibnamefont
+  {Bergmann}}, \bibinfo {author} {\bibfnamefont {Michel}\ \bibnamefont
+  {Cahen}}, \ and\ \bibinfo {author} {\bibfnamefont {A.~B.}\ \bibnamefont
+  {Komar}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{S}pherically
+  symmetric gravitational fields},}\ }\href@noop {} {\bibfield  {journal}
+  {\bibinfo  {journal} {J. Math. Phys.}\ }\textbf {\bibinfo {volume} {6}},\
+  \bibinfo {pages} {1--5} (\bibinfo {year} {1965})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Hawking}\ and\ \citenamefont
+  {Ellis}(1973)}]{hawking1973large}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Stephen~W.}\
+  \bibnamefont {Hawking}}\ and\ \bibinfo {author} {\bibfnamefont {George
+  Francis~Rayner}\ \bibnamefont {Ellis}},\ }\href@noop {} {\emph {\bibinfo
+  {title} {The large scale structure of space-time}}}\ (\bibinfo  {publisher}
+  {Cambridge University Press},\ \bibinfo {year} {1973})\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Peeters}(2007{\natexlab{a}})}]{Peeters2007550}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Kasper}\ \bibnamefont
+  {Peeters}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Cadabra: a
+  field-theory motivated symbolic computer algebra system},}\ }\href {\doibase
+  http://dx.doi.org/10.1016/j.cpc.2007.01.003} {\bibfield  {journal} {\bibinfo
+  {journal} {Comput. Phys. Commun.}\ }\textbf {\bibinfo {volume} {176}},\
+  \bibinfo {pages} {550} (\bibinfo {year} {2007}{\natexlab{a}})}\BibitemShut
+  {NoStop}%
+\bibitem [{\citenamefont {Peeters}(2007{\natexlab{b}})}]{peeters2007symbolic}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Kasper}\ \bibnamefont
+  {Peeters}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {Symbolic field
+  theory with cadabra},}\ }\href
+  {http://www.fachgruppe-computeralgebra.de/CA-Rundbrief/car41.pdf} {\bibfield
+  {journal} {\bibinfo  {journal} {Computeralgebra Rundbrief}\ }\textbf
+  {\bibinfo {volume} {41}},\ \bibinfo {pages} {16} (\bibinfo {year}
+  {2007}{\natexlab{b}})}\BibitemShut {NoStop}%
+\bibitem [{\citenamefont {Peeters}(2007{\natexlab{c}})}]{Peeters:2007wn}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Kasper}\ \bibnamefont
+  {Peeters}},\ }\bibfield  {title} {\enquote {\bibinfo {title} {{Introducing
+  Cadabra: A Symbolic computer algebra system for field theory problems}},}\
+  }\href@noop {} {\  (\bibinfo {year} {2007}{\natexlab{c}})},\ \Eprint
+  {http://arxiv.org/abs/hep-th/0701238} {arXiv:hep-th/0701238 [hep-th]}
+  \BibitemShut {NoStop}%
+%%CITATION = HEP-TH/0701238;%%
+\bibitem [{\citenamefont {Derdzi{\'n}ski}\ and\ \citenamefont
+  {Shen}(1983)}]{Derdzinski01071983}%
+  \BibitemOpen
+  \bibfield  {author} {\bibinfo {author} {\bibfnamefont {Andrzej}\ \bibnamefont
+  {Derdzi{\'n}ski}}\ and\ \bibinfo {author} {\bibfnamefont {Chun-Li}\
+  \bibnamefont {Shen}},\ }\bibfield  {title} {\enquote {\bibinfo {title}
+  {Codazzi tensor fields, curvature and pontryagin forms},}\ }\href {\doibase
+  10.1112/plms/s3-47.1.15} {\bibfield  {journal} {\bibinfo  {journal}
+  {Proceedings of the London Mathematical Society}\ }\textbf {\bibinfo {volume}
+  {s3-47}},\ \bibinfo {pages} {15} (\bibinfo {year} {1983})}\BibitemShut
+  {NoStop}%
+\end{thebibliography}%
 
